### 2025-03-31 Paper7.tex
Update local file

\documentclass[preprint,12pt]{elsarticle}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{array}
\usepackage{graphicx}
\usepackage{placeins}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{subcaption}
\usepackage{mwe}
\usepackage{caption}
\usepackage{booktabs}
\usepackage{adjustbox}
\usepackage{multirow}
\usepackage{hyperref}
\usepackage[noabbrev,nameinlink]{cleveref}
\usepackage[title]{appendix}
\usepackage[utf8]{inputenc}
\usepackage{stanli}
\usepackage{tikz}
\usepackage{siunitx}
\usepackage{xspace}
\usepackage{lmodern}
\usepackage{nomencl}
\makenomenclature
\usepackage{longtable}
\usepackage{lineno}
\usetikzlibrary{arrows.meta} % Load the arrows.meta library
\usetikzlibrary{shapes,positioning}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

\AtBeginEnvironment{appendices}{\crefalias{section}{appendix}}

% Derivatives should be upright d (JSV requires it)
% I don't have the docs for the derivate package with me, so I'll just do this bad hack for now.
% Could update all the ODEs to use the derivative package
% Update: hack didn't work due to \d already defined somewhere - leaving this for now
%\DeclareMathOperator{\d}{\textnormal{d}}

\newcommand{\kph}{~\unit{\kilo\metre\per\hour}\xspace}
\newcommand{\um}{~\unit{\metre}\xspace}
\newcommand{\ukg}{~\unit{\kilogram}\xspace}
\newcommand{\urho}{~\unit{\kilogram\per\meter}\xspace}
\newcommand{\uI}{~\unit{\kilogram\square\metre}\xspace}
\newcommand{\urd}{~\unit{\newton\square\metre}\xspace}
\newcommand{\ustif}{~\unit{\newton\per\metre}\xspace}
\newcommand{\udamp}{~\unit{\newton\second\per\metre}\xspace}
\newcommand{\DAF}{\textnormal{DAF}}
% Hacky - is there a better upright i?
%\newcommand{\ii}{\textnormal{i}}
\newcommand{\id}{\mathrm{d}\mkern1mu}
\newcommand{\ii}{\mathrm{i}\mkern1mu}
\newcommand{\nukg}{\unit{\kilogram}\xspace}
\newcommand{\nustif}{\unit{\newton\per\metre}\xspace}
\newcommand{\nudamp}{\unit{\newton\second\per\metre}\xspace}
\newcommand{\nugpa}{\si{\giga\pascal}\xspace}
\begin{document}

% I made some comments about x/L being xi - it's not used much so you can ignore these.
% There are some cases where I added text in [square brackets] and not necessarily in a latex comment
% Check the bib file - two references had no journal - I added these as XXXX
% Section 4 does too much - could you consider splitting this section up a bit? 
% I did add some more subsubsections to try structure section 4 a bit better, but I'm not sure it's optimal yet.
\begin{frontmatter}
\title{The dynamic stiffness matrix based on the extended separation-of-variables type solutions for the free vibration of orthotropic rectangular thin plates}
\author[1]{Shiyi Mei}\ead{shiyi.mei1@monash.edu}
\author[1]{Colin Caprani\corref{cor1}}\ead{colin.caprani@monash.edu}
\author[2]{Daniel Cantero}\ead{daniel.cantero@ntnu.no}
\cortext[cor1]{Corresponding author}
\affiliation[1]{organization={Department of Civil Engineering, Monash University},city={Melbourne},state={Victoria},country={Australia}}
\affiliation[2]{organization={Department of Structural Engineering, Norwegian University of Science \& Technology NTNU},city={Trondheim}, country={Norway}}
\begin{abstract}
The dynamic stiffness matrix based on the extended separation-of-variables mode functions is developed for the free vibration analysis of an orthotropic rectangular thin plate with general homogeneous boundary conditions.  
The governing differential equation and boundary conditions are derived from Rayleigh’s principle.  
Based on the boundary conditions, the dynamic stiffness matrix is formulated and solved using an improved Wittrick-Williams algorithm.  
In this improved algorithm, simply supported frequencies are required instead of fully clamped frequencies, and the closed-form expression for the simply supported frequencies is provided, enhancing the efficiency and systematicity of solving the eigenvalue problem.  
The proposed method is validated by the numerical experiments.
\end{abstract}
\end{frontmatter}
\linenumbers
\section{Introduction}
Rectangular plates play an important role in various engineering fields, including civil, mechanical, and aerospace engineering \citep{biancolini2005approximate}. 
The free vibration of plates has been a fundamental research problem for over two centuries. 
The earliest exact solutions for this problem are the Navier \citep{navier1823extrait} and Levy \citep{levy1899equilibre} solutions, which require at least one pair of opposite edges to be simply supported or guided.
To solve problems with other boundary conditions, approximate solutions such as the Rayleigh–Ritz method \cite{leissa1973free} and the Galerkin method \cite{laura1967study} have been widely applied. 
For these approximation methods, beam functions, polynomials, trigonometric functions, and their combinations \cite{li2004vibration} are commonly used as the assumed approximate functions.
The accuracy of these solutions depends on how well the assumed approximate functions represent the displacement of the plate.

Besides the approximation methods, several analytical methods have been developed over the past decades, including the Kantorovich-Krylov method \cite{kantorovich1958approximate,kerr1968extension}, the symplectic eigenfunction expansion method \cite{zhong1995new,xing2009new2}, the separation-of-variable (SOV) method \cite{xing2009new}, the dynamic stiffness matrix (DSM) method \cite{banerjee1997dynamic}, and series expansion-based methods \cite{xing2022review}.
The series expansion-based methods include the superposition method \cite{timoshenko1940theory,gorman2005free}, Fourier series method \cite{khov2009accurate,li2009exact}, the finite integral transform method \cite{li2009finite,zhong2013free}, and other series methods. 
These methods represent the plate displacement in terms of an infinite series and mostly are capable of handling any general boundary conditions. 
However, sufficient truncation of the series is required to ensure the accuracy and convergence of the results, and the eigenvalue equation is generally difficult to express explicitly.
Therefore, solving the corresponding eigenvalue problem can be computationally expensive.

Despite being a powerful method for the dynamic analysis of plate assemblies, the finite element method (FEM) requires a sufficient number of elements and is computationally expensive to accurately capture higher-order modes.
Thus, the DSM method is developed as an accurate and efficient analytical approach to alternatively solve complex plate structures \cite{boscolo2011dynamic,fazzolari2013exact}. 
The DSM can be considered as an analytical FEM since the mode functions of the plate are expressed by analytical solutions, where Levy-type solution \cite{ghorbel2015dynamic} or components of infinite Fourier series \cite{banerjee2015dynamic,liu2016free} are applied.
To avoid solving the cumbersome transcendental frequency equation directly, the Wittrick-Williams (W-W) algorithm \cite{wittrick1971general} is applied to the eigenvalue problem.
The W-W algorithm determines the lower and upper bounds of natural frequencies rather than solving the frequency equation directly. 
Thus, the DSM has the potential to be effectively and systematically solved using the W-W algorithm.
However, a critical part in applying the W-W algorithm is to priorly determine all natural frequencies of the fully clamped structure within the interested frequency range.
Strategies such as using a sufficiently fine mesh or including a sufficient number of terms in series expansions \cite{banerjee2015dynamic} can ensure that all fully clamped frequencies are accounted for, thereby maintaining the accuracy of the algorithm. However, these approaches are computationally expensive and complex, posing a significant obstacle to the wider adoption and application of the DSM method based on the W-W algorithm \cite{han2018improved}.
To resolve the fully clamped plate problem, \citet{liu2015exact} suggested that the fully clamped frequencies can be indirectly obtained from the simply supported plate problem, where the Navier solution serves as the analytical solution. This provides a significant enhancement to the W-W algorithm, increasing the efficiency of applying DSM methods. 
However, since infinite-term series expansion-based solutions are used for plate analysis instead of explicit and closed-form solutions, a sufficient number of truncation terms is required to ensure accuracy and capture the necessary modal degrees.

Inspired by the Navier and Levy solutions, \citet{xing2009new} proposed the separation-of-variables (SOV) method, which provides concise and explicit eigensolutions.
The mode shape function has a separable form, $\phi(x) \psi(y)$, requiring only one $\phi(x)$ and one $\psi(y)$ for each mode order, allowing each eigenvalue equation to be explicitly expressed.
However, this SOV method is not suitable to deal with plate with free boundary conditions.
Therefore, an extended SOV method \cite{xing2018overall, xing2020extended} based on the Rayleigh quotient is proposed to accommodate plates with all classical boundary conditions, i.e., simply supported, clamped, guided, and free.
Based on the Rayleigh quotient model, alternative iterative and improved SOV methods have been subsequently proposed \cite{xing2020improved}.
Although SOV methods provide concise closed-form analytical solutions, solving the highly nonlinear eigenvalue equations is required.

In this study, the free vibration of orthotropic plates with general boundary conditions is analyzed by extending the SOV method based on the Rayleigh quotient to obtain the solution for elastically restrained plates.
Subsequently, dynamic stiffness matrices in both the \(x\) and \(y\) directions, derived from the SOV-form solutions, are developed to solve the eigenvalue problem.
By applying the 'hypothetical structure method', a modified W-W algorithm is developed, requiring only the natural frequencies of the simply supported structure instead of the necessity of fully clamped frequencies.
The concise closed-form expression for the simply supported frequencies is directly obtained from the eigenvalue equation based on the SOV method, eliminating the extensive computational effort typically required in DSM methods to determine all fully clamped frequencies within the frequency range.  
Therefore, this approach can improve the systematic and effective application of the DSM method depending on the W-W algorithm.
Alternatively, it can also be considered as an efficient technique for solving transcendental eigenvalue equations in the SOV method.

\FloatBarrier
\section{Mathematical model}\label{sec:Mathematical model}
\begin{figure}[!htbp]
	\centering
	\resizebox{0.8\textwidth}{!}
	{
		\input{figs/general_plate_tikz.tex}
	}
	\caption{\small The orthotropic rectangular plate with all edges elastically restrained.} 
	\label{fig:platemode}
\end{figure}
Consider a thin orthotropic rectangular plate of length \(2a\) and width \(2b\), with all four edges restrained by vertical translational springs \(k^v\) and rotational springs \(k^r\), as shown in \Cref{fig:platemode}. 
The coordinate origin is located at the center of the plate.

The governing differential equation for the free vibration of a thin orthotropic plate is given by \citep{xing2020improved}:  
%
\begin{equation}\label{eq:governing_EOM}
	D_{11}\frac{\partial^4w}{\partial \xi^4} + 2D_3\alpha^2\frac{\partial^4w}{\partial \xi^2 \partial \eta^2} + D_{22}\alpha^4\frac{\partial^4w}{\partial \eta^4} = \rho h\alpha^4\omega^2w,
\end{equation}
%
where the bending stiffness parameters are defined as:
%
\begin{equation}\label{eq:bd_stiff}
	\begin{split}
		&D_{11} = \frac{E_1h^3}{12(1-v_{12}v_{21})}, \quad D_{22} = \frac{E_2h^3}{12(1-v_{12}v_{21})}, \\  
		&D_{66} = \frac{G_{12}h^3}{12}, \quad D_{12} = v_{12}D_{22} = v_{21}D_{11}, \quad D_3 = D_{12} + 2D_{66},
	\end{split}
\end{equation}
%
where \(\rho\) and \(h\) denote the mass density and thickness of the plate, respectively; \(E_1\) and \(E_2\) are the Young’s moduli in the \(x\)- and \(y\)-directions, respectively; \(G_{12}\) is the shear modulus, and \(v_{12}\) and \(v_{21}\) are the Poisson’s ratios.

Instead of solving the free vibration of the thin orthotropic plate using \Cref{eq:governing_EOM}, it is suggested that the vibration of the thin plate can also be solved using the Rayleigh quotient variational principle \cite{xing2018overall}:
%
\begin{equation}\label{eq:Rayleigh}
	\begin{split}
		\delta U_{mag} &= \omega^2\,\delta T_0,
	\end{split}
\end{equation}
%
where \(\delta\) denotes variation, \(U_{mag}\) is the magnitude of the potential energy of the plate, and \(\omega^2 T_0\) represents the magnitude of the kinetic energy of the plate.
The potential energy of the plate can be expressed as \cite{xing2020extended}:
%
\begin{equation}\label{eq:poten_energy}
	\begin{split}
		U^{I} &= \frac{1}{2}\iint \Big[D_{11}\left(\frac{\partial^2 W}{\partial x^2}\right)^2 + 2D_{12}\frac{\partial^2 W}{\partial x^2}\frac{\partial^2 W}{\partial y^2} + D_{22}\left(\frac{\partial^2 W}{\partial y^2}\right)^2 \\
		&\qquad + 4D_{66}\left(\frac{\partial^2 W}{\partial x \partial y}\right)^2\Big] \, \mathrm{d}x \, \mathrm{d}y.
	\end{split}
\end{equation}
%
And the kinetic energy is:
%
\begin{equation}\label{eq:kine_energy}
	\begin{split}
		T &= \frac{1}{2}\iint \rho h \left(\frac{\partial W}{\partial t}\right)^2 \, \mathrm{d}x \, \mathrm{d}y.
	\end{split}
\end{equation}

Assuming the solution of the deflection \( W(x, y; t) = w(x, y) e^{i \omega t} \) for harmonic plate motion, 
where \( \ii = \sqrt{-1} \), \( w(x, y) \) is the mode shape, and \( \omega \) is the radial frequency.  
By substituting \( W(x, y; t) = w(x, y) e^{i \omega t} \) into \Cref{eq:poten_energy,eq:kine_energy} and expressing the system in dimensionless coordinates, we have:
%
\begin{equation}\label{eq:poten_energy_mag}
	\begin{split}
		U_{\text{mag}}^{I} &= \frac{ab}{2} \iint \left[ \frac{D_{11}}{a^4} \left( \frac{\partial^2 w}{\partial \xi^2} \right)^2 + \frac{2 D_{12}}{a^2 b^2} \frac{\partial^2 w}{\partial \xi^2} \frac{\partial^2 w}{\partial \eta^2} + \frac{D_{22}}{b^4} \left( \frac{\partial^2 w}{\partial \eta^2} \right)^2 \right. \\
		&\quad \left. + \frac{4 D_{66}}{a^2 b^2} \left( \frac{\partial^2 w}{\partial \xi \partial \eta} \right)^2 \right] \, \mathrm{d} \xi \, \mathrm{d} \eta,
	\end{split}
\end{equation}
%
and
%
\begin{equation}\label{eq:kine_energy_mag}
	\begin{split}
		T &= \omega^2 \frac{ab}{2} \rho h \iint w^2 \, \mathrm{d} \xi \, \mathrm{d} \eta = \omega^2 T_0
	\end{split},
\end{equation}
%
where \( \alpha = a / b \) is the aspect ratio; \( \xi = x / a \) and \( \eta = y / b \) are the normalized coordinates.
The separable form of the mode shape function \( w(\xi, \eta) \) is given by:
%
\begin{equation}\label{eq:displace_func}
	w(\xi, \eta) = \phi(\xi) \psi(\eta),
\end{equation}
%
where \( \phi(\xi) \) and \( \psi(\eta) \) can be expressed as:
\begin{subequations}\label{eq:phi_psi_solution}
	\begin{align}
		\phi(\xi) &= A_1 \sin{(\alpha_1 \xi)} + A_2 \cos{(\alpha_1 \xi)} + A_3 \sinh{(\beta_1 \xi)} + A_4 \cosh{(\beta_1 \xi)},\label{eq:phi_solution1}\\
		\psi(\eta) &= B_1 \sin{(\alpha_2 \eta)} + B_2 \cos{(\alpha_2 \eta)} + B_3 \sinh{(\beta_2 \eta)} + B_4 \cosh{(\beta_2 \eta)}. \label{eq:phi_solution2}
	\end{align}
\end{subequations}

It should be noted that \Cref{eq:governing_EOM} represents the strong-form governing equation of the orthotropic plate, while \Cref{eq:Rayleigh} is the weak-form governing equation, with the latter being equivalent to the former.
Based on \Cref{eq:Rayleigh}, the frequencies $\omega_x$ and $\omega_y$, corresponding to the mode shapes $\phi(\xi)$ and $\psi(\eta)$, respectively, are assumed to be independent of each other.

\subsection{Dynamic stiffness matrix corresponding to $\omega_x$}\label{sec:DSMx}
For given general homogeneous boundary conditions, we can first assume that the mode shape $\psi(\eta)$ corresponding to the $y$ direction is known. 
Supposing the edges of the plate in both the \(x\)- and \(y\)-directions are elastically restrained by homogeneous vertical translational and rotational springs.
The vertical translational and rotational springs at the \(\xi = -1\) end are defined as \(k^v_{\xi = -1}\) and \(k^r_{\xi = -1}\), respectively, and at the \(\xi = 1\) end as \(k^v_{\xi = 1}\) and \(k^r_{\xi = 1}\), respectively. 
Thus, the potential energy along the supported edge in the \(x\)-direction can be expressed by:
%
\begin{equation}\label{eq:poten_energy_edgex}
	\begin{split}
		U^{II} &=  \int\left[k^r_{\xi=-1} \left( \frac{\partial W}{\partial x} \right)^2 + k^v_{\xi=-1} \left( W \right)^2\right]_{x=-a} \id y\\
		&\quad +  \int\left[k^r_{\xi=1} \left( \frac{\partial W}{\partial x} \right)^2 + k^v_{\xi=1} \left( W \right)^2\right]_{x=a} \id y.
	\end{split}
\end{equation}
%
From \Cref{eq:poten_energy_edgex}, the magnitude of total potential energy along the edges in the \(x\)-direction is obtained as:
%
\begin{equation}\label{eq:poten_energy_edgex2}
	\begin{split}
		U^{II}_{mag} &= ab \int\left[\frac{k^r_{\xi=-1}}{a^3} \left( \frac{\partial w}{\partial \xi} \right)^2 + \frac{k^v_{\xi=-1}}{a} \left( w \right)^2\right]_{\xi=-1} \, \id \eta \\
		&\quad + ab \int\left[\frac{k^r_{\xi=1}}{a^3} \left( \frac{\partial w}{\partial \xi} \right)^2 + \frac{k^v_{\xi=1}}{a} \left( w \right)^2\right]_{\xi=1} \, \id \eta.
	\end{split}
\end{equation}
%
The magnitude of potential energy of the plate in the \(x\)-direction can be obtained from \Cref{eq:poten_energy_mag,eq:poten_energy_edgex2} as:
%
\begin{equation}\label{eq:poten_energy_tolx}
	\begin{split}
		U_{mag} &= U^{I}_{mag} + U^{II}_{mag} \\
		&= \frac{ab}{2} \iint \left[ \frac{D_{11}}{a^4} \left( \frac{\partial^2 w}{\partial \xi^2} \right)^2 + \frac{2 D_{12}}{a^2 b^2} \frac{\partial^2 w}{\partial \xi^2} \frac{\partial^2 w}{\partial \eta^2} + \frac{D_{22}}{b^4} \left( \frac{\partial^2 w}{\partial \eta^2} \right)^2 \right. \\
		&\quad \left.  + \frac{4 D_{66}}{a^2 b^2} \left( \frac{\partial^2 w}{\partial \xi \partial \eta} \right)^2 \right] \, \id\xi \, \id\eta + ab \int \left[\frac{k^r_{\xi=1}}{a^3} \left( \frac{\partial w}{\partial \xi} \right)^2 + \frac{k^v_{\xi=1}}{a} \left( w \right)^2 \right]_{\xi=1} \, \id \eta \\
		&\quad  + ab \int \left[\frac{k^r_{\xi=-1}}{a^3} \left( \frac{\partial w}{\partial \xi} \right)^2 + \frac{k^v_{\xi=-1}}{a} \left( w \right)^2 \right]_{\xi=-1} \, \id \eta
	\end{split}
\end{equation}
%
By substituting \Cref{eq:displace_func} into \Cref{eq:poten_energy_tolx}, we have:
%
\begin{equation}\label{eq:poten_energy_tolx2}
	\begin{split}
		U_{mag}&=U^{I}_{mag}+U^{II}_{mag}\\
		&=\frac{ab}{2} \int_{-1}^{1} \left[ \frac{D_{11}}{a^4}S_1 \left( \frac{\id^2\phi }{\id \xi^2} \right)^2 + \frac{2 D_{12}}{a^2 b^2}S_2 \frac{\id^2\phi }{\id \xi^2}\phi  + \frac{D_{22}}{b^4}S_4  \phi^2 \right. \\
		&\quad \left. + \frac{4 D_{66}}{a^2 b^2}S_3 \left( \frac{\id \phi }{\id \xi}\right)^2 \right] \, \id\xi +abS_1 \left[\frac{k^r_{\xi=-1}}{a^3} \left( \frac{\id \phi}{\id \xi} \right)^2+ \frac{k^v_{\xi=-1}}{a} \left( \phi \right)^2\right]_{\xi=-1}\\
		&\quad+abS_1 \left[\frac{k^r_{\xi=1}}{a^3} \left( \frac{\id \phi}{\id \xi} \right)^2+ \frac{k^v_{\xi=1}}{a} \left( \phi \right)^2\right]_{\xi=1},
	\end{split}
\end{equation}
%
where the integral parameters are defined as:
%
\begin{equation}\label{eq:inte_phi_text}  
	\begin{split}  
		&S_1 = \int_{-1}^{1} \psi^2 \, \id\eta, \\  
		&S_2 = \int_{-1}^{1} \left( \frac{\id^2 \psi}{\id \eta^2} \psi \right) \, \id\eta, \\  
		&S_3 = \int_{-1}^{1} \left( \frac{\id \psi}{\id \eta} \right)^2 \, \id\eta, \\  
		&S_4 = \int_{-1}^{1} \left( \frac{\id^2 \psi}{\id \eta^2} \right)^2 \, \id\eta.  
	\end{split}  
\end{equation}   
%
By taking \Cref{eq:displace_func} into account, the coefficient \(T_0\) of the kinetic energy in \Cref{eq:kine_energy_mag} for the plate can be expressed as:
%
\begin{equation}\label{eq:kine_energyx}
	\begin{split}
		T_0 = \frac{ab}{2}\rho h\iint w^2 \, \id \xi \, \id \eta = \frac{ab}{2}\rho h S_1\int_{-1}^{1} \phi^2 \, \id \xi.
	\end{split}
\end{equation}

Take the Rayleigh principle in the form:
%
\begin{equation}\label{eq:Rayleighx}
	\begin{split}
		\delta U_{mag} &= \omega_x^2 \, \delta T_0.
	\end{split}
\end{equation}
%
By substituting \Cref{eq:poten_energy_tolx2,eq:kine_energyx} into \Cref{eq:Rayleighx}, relieve \(\delta \phi\) and \(\delta\frac{\id  \phi}{\id \xi}\) in \Cref{eq:Rayleighx} by variation calculus, yielding:
%
\begin{equation}\label{eq:Rayleighx2}
	\begin{split}
		0 &= \int_{-1}^{1} \bigg[ \frac{D_{11}}{a^4} S_1 \frac{\id^4 \phi}{\id \xi^4} 
		+ \bigg( \frac{2D_{12}}{a^2b^2} S_2 - \frac{4D_{66}}{a^2b^2} S_3 \bigg) \frac{\id^2 \phi}{\id \xi^2} \\
		&\quad + \bigg( \frac{D_{22}}{b^4} S_4 - \omega_x^2 \rho h S_1 \bigg) \phi \bigg] \delta \phi \, \id \xi \\
		&\quad + \frac{2k^v_{\xi=-1}}{a} S_1 \big(\phi \delta \phi\big)_{\xi=-1} 
		+ \frac{2k^v_{\xi=1}}{a} S_1 \big(\phi \delta \phi\big)_{\xi=1} \\
		&\quad + \bigg[ \bigg( \frac{4D_{66}}{a^2b^2} S_3 - \frac{D_{12}}{a^2b^2} S_2 \bigg) \frac{\id \phi}{\id \xi} 
		- \frac{D_{11}}{a^4} S_1 \frac{\id^3 \phi}{\id \xi^3} \bigg] \delta \phi \Big|^{\xi=1}_{\xi=-1} \\
		&\quad + \bigg( \frac{D_{12}}{a^2b^2} S_2 \phi + \frac{D_{11}}{a^4} S_1 \frac{\id^2 \phi}{\id \xi^2} \bigg) 
		\delta\frac{\id  \phi}{\id \xi} \Big|^{\xi=1}_{\xi=-1} \\
		&\quad + \frac{2k^r_{\xi=-1}}{a^3} S_1 \bigg(\frac{\id \phi}{\id \xi}\delta \frac{\id \phi}{\id \xi}\bigg)_{\xi=-1} 
		+ \frac{2k^r_{\xi=1}}{a^3} S_1 \bigg(\frac{\id \phi}{\id \xi} \delta\frac{\id \phi}{\id \xi}\bigg)_{\xi=1}.
	\end{split}
\end{equation}
%
Thus, the governing differential equation in the \( x \)-direction can be obtained from the integration part in \Cref{eq:Rayleighx2}:
%
\begin{equation}\label{eq:ODEx}
		\frac{\id^4 \phi}{\id \xi^4}+ 2\alpha^2\left(\frac{D_{12}S_2}{D_{11}S_1}-2\frac{D_{66}S_3}{D_{11}S_1}\right)\frac{\id^2 \phi}{\id \xi^2}+\left(\alpha^4\frac{D_{22}S_4}{D_{11}S_1}-a^4\Omega_x^4\right)\phi=0,
\end{equation}
%
where \(\Omega_x = \sqrt[4]{\omega_x^2 \rho h / D_{11}}\).
By substituting \(\phi(\xi) = A e^{\mu \xi}\) into \Cref{eq:ODEx}, yields:
%
\begin{equation}\label{eq:ODEx2}
	\begin{split}
		\mu^4 + 2\alpha^2\left(\frac{D_{12}S_2}{D_{11}S_1}-2\frac{D_{66}S_3}{D_{11}S_1}\right)\mu^2 + \left(\alpha^4\frac{D_{22}S_4}{D_{11}S_1}-a^4\Omega_x^4\right) = 0.
	\end{split}
\end{equation}
%
The solution for \(\mu\) can be expressed as:
%
\begin{equation}\label{eq:mu}
	\begin{split}
		\mu_{1,2} = \pm\textit{i} \alpha_1, \qquad \mu_{3,4} = \pm \beta_1,
	\end{split}
\end{equation}
%
where,
%
\begin{subequations}\label{eq:alphax}
	\begin{align}
		\alpha_1 &= \alpha \sqrt{\sqrt{\left(\frac{D_{12}S_2}{D_{11}S_1}-2\frac{D_{66}S_3}{D_{11}S_1}\right)^2 - \frac{D_{22}S_4}{D_{11}S_1} + b^4\Omega_x^4} + \frac{D_{12}S_2}{D_{11}S_1} - 2\frac{D_{66}S_3}{D_{11}S_1}},\label{eq:alphax1}\\
		\beta_1 &= \alpha \sqrt{\sqrt{\left(\frac{D_{12}S_2}{D_{11}S_1}-2\frac{D_{66}S_3}{D_{11}S_1}\right)^2 - \frac{D_{22}S_4}{D_{11}S_1} + b^4\Omega_x^4} - \frac{D_{12}S_2}{D_{11}S_1} + 2\frac{D_{66}S_3}{D_{11}S_1}}.\label{eq:alphax2}
	\end{align}
\end{subequations}
%
The boundary conditions along the edges in the \(x\)-direction can be obtained from the remaining \(\delta \phi\) and \(\delta \frac{\id \phi}{\id \xi}\) parts in \Cref{eq:Rayleighx2}. 
The shear force equilibrium can be obtained from the \(\delta \phi\) part:
%
\begin{equation}\label{eq:inertial_forcex}
	\begin{split}
		&\left[ \left( \frac{4D_{66}}{a^2b^2} S_3 - \frac{D_{12}}{a^2b^2} S_2 \right) \frac{\id \phi}{\id \xi} 
		- \frac{D_{11}}{a^4} S_1 \frac{\id^3 \phi}{\id \xi^3} \right] \Big|^{\xi=1}_{\xi=-1}\\
		&\quad+ \frac{2k^v_{\xi=-1}}{a} S_1 \left(\phi\right)_{\xi=-1}
		 + \frac{2k^v_{\xi=1}}{a} S_1 \left(\phi\right)_{\xi=1} = 0,
	\end{split}
\end{equation}
%
and from the \(\delta \frac{\id \phi}{\id \xi}\) part, the bending moment equilibrium:
%
\begin{equation}\label{eq:inertial_forcex2}
	\begin{split}	
		\left( \frac{D_{12}}{a^2b^2} S_2 \phi + \frac{D_{11}}{a^4} S_1 \frac{\partial^2 \phi}{\partial \xi^2} \right) 
		\Big|^{\xi=1}_{\xi=-1} 
		&+ \frac{2k^r_{\xi=-1}}{a^3} S_1 \left(\frac{\partial \phi}{\partial \xi}\right)_{\xi=-1} \\
		&+ \frac{2k^r_{\xi=1}}{a^3} S_1 \left(\frac{\partial \phi}{\partial \xi}\right)_{\xi=1} = 0.
	\end{split}
\end{equation}
%
Thus, we can obtain the shear force and bending moment equilibrium along the edges \(\xi = -1\) and \(\xi = 1\) from \Cref{eq:inertial_forcex,eq:inertial_forcex2}, respectively, as:
%
\begin{subequations}\label{eq:boundaryx}
	\begin{align}
		&  \frac{\id^3 \phi}{\id \xi^3} - \alpha^2\left( \frac{4D_{66}S_3}{D_{11}S_1}  - \frac{D_{12}S_2}{D_{11}S_1}  \right) \frac{\id \phi}{\id \xi} 
		+\frac{2a^3k^v_{\xi=-1}}{D_{11}}\phi = 0, \quad &\xi = -1, \\
		& \frac{\id^2 \phi}{\id \xi^2} + \frac{\alpha^2 D_{12} S_2}{D_{11} S_1} \phi - \frac{2a k^r_{\xi=-1}}{D_{11}} \frac{\id \phi}{\id \xi} = 0, \quad &\xi = -1, \\
		& \frac{\id^3 \phi}{\id \xi^3} - \alpha^2\left( \frac{4D_{66}S_3}{D_{11}S_1}  - \frac{D_{12}S_2}{D_{11}S_1}  \right) \frac{\id \phi}{\id \xi} 
		-\frac{2a^3 k^v_{\xi=1}}{D_{11}} \phi = 0, \quad &\xi = 1, \\
		& \frac{\id^2 \phi}{\id \xi^2} + \frac{\alpha^2 D_{12} S_2}{D_{11} S_1} \phi + \frac{2a k^r_{\xi=1}}{D_{11}} \frac{\id \phi}{\id \xi} = 0, \quad &\xi = 1.
	\end{align}
\end{subequations}
%
Substituting \Cref{eq:phi_solution1} into \Cref{eq:boundaryx}, and denoting \( k^{v*}_{\xi} = \frac{2a^3 k^v_{\xi}}{D_{11}} \), \( k^{r*}_{\xi} = \frac{2a k^r_{\xi}}{D_{11}} \), \( \sin\alpha_1 = S_{\alpha_1} \), \( \cos\alpha_1 = C_{\alpha_1} \), \( \sinh\alpha_1 = Sh_{\alpha_1} \), \( \cosh\alpha_1 = Ch_{\alpha_1} \), \( \sin\beta_1 = S_{\beta_1} \), \( \cos\beta_1 = C_{\beta_1} \), \( \sinh\beta_1 = Sh_{\beta_1} \), and \( \cosh\beta_1 = Ch_{\beta_1} \), we have:
%
\begin{equation}\label{eq:ABx}
	\begin{split}
		&\left[ \begin{array}{c}
			\gamma_1 C_{\alpha_1} - k^{v*}_{\xi=-1} S_{\alpha_1} \\ 
			\gamma_3 S_{\alpha_1} + k^{r*}_{\xi=-1} \alpha_1 C_{\alpha_1} \\ 
			-\gamma_1 C_{\alpha_1} + k^{v*}_{\xi=1} S_{\alpha_1} \\ 
			\gamma_3 S_{\alpha_1} + k^{r*}_{\xi=1} \alpha_1 C_{\alpha_1}
		\end{array} 
		\begin{array}{c}
			\gamma_1 S_{\alpha_1} + k^{v*}_{\xi=-1} C_{\alpha_1} \\ 
			-\gamma_3 C_{\alpha_1} + k^{r*}_{\xi=-1} \alpha_1 S_{\alpha_1} \\ 
			\gamma_1 S_{\alpha_1} + k^{v*}_{\xi=1} C_{\alpha_1} \\ 
			\gamma_3 C_{\alpha_1} - k^{r*}_{\xi=1} \alpha_1 S_{\alpha_1}
		\end{array} 
		\begin{array}{c}
			\gamma_2 Ch_{\beta_1} - k^{v*}_{\xi=-1} Sh_{\beta_1} \\ 
			\gamma_4 Sh_{\beta_1} + k^{r*}_{\xi=-1} \beta_1 Ch_{\beta_1} \\ 
			-\gamma_2 Ch_{\beta_1} + k^{v*}_{\xi=1} Sh_{\beta_1} \\ 
			\gamma_4 Sh_{\beta_1} + k^{r*}_{\xi=1} \beta_1 Ch_{\beta_1}
		\end{array} \right. \\ 
		&\quad
		\left. \begin{array}{c}
			-\gamma_2 Sh_{\beta_1} + k^{v*}_{\xi=-1} Ch_{\beta_1} \\ 
			-\gamma_4 Ch_{\beta_1} - k^{r*}_{\xi=-1} \beta_1 Sh_{\beta_1} \\ 
			-\gamma_2 Sh_{\beta_1} + k^{v*}_{\xi=1} Ch_{\beta_1} \\ 
			\gamma_4 Ch_{\beta_1} + k^{r*}_{\xi=1} \beta_1 Sh_{\beta_1}
		\end{array} \right] \begin{Bmatrix}
			A_1 \\ A_2 \\ A_3 \\ A_4
		\end{Bmatrix} =  \begin{Bmatrix}
			0 \\ 0 \\ 0 \\ 0
		\end{Bmatrix},
	\end{split}
\end{equation}
%
or,
%
\begin{equation}\label{eq:ABx1}
		\mathbf{R}_x \mathbf{A} = \mathbf{0},
\end{equation}
%
where,
%
\begin{equation}\label{eq:gamma}
	\begin{split}
		&\gamma_1 = -\alpha_1^3 - \alpha^2 \left( \frac{4D_{66}S_3}{D_{11}S_1} - \frac{D_{12}S_2}{D_{11}S_1} \right) \alpha_1, \\
		&\gamma_2 = \beta_1^3 - \alpha^2 \left( \frac{4D_{66}S_3}{D_{11}S_1} - \frac{D_{12}S_2}{D_{11}S_1} \right) \beta_1, \\
		&\gamma_3 = -\alpha_1^2 + \frac{\alpha^2 D_{12} S_2}{D_{11} S_1}, \\
		&\gamma_4 = \beta_1^2 + \frac{\alpha^2 D_{12} S_2}{D_{11} S_1}.
	\end{split}
\end{equation}
%
Note that the classic boundary conditions can be obtained by selecting extremely large or small srping stiffness constants.
For non-trivial solutions, the characteristic equation or eigenvalue equation is obtained from the determinant of the matrix $\mathbf{R}_x$ in \Cref{eq:ABx1}, which must be zero.
However, solving these trancedental equations are cunmbersome and tedious, thus the DSM is introducted to avoid the ineffective computation.

To develop its dynamic stiffness matrix, with the help of \Cref{eq:phi_solution1}, the vertical displacement and rotation corresponding to the mode shape $\phi(\xi)$ along the $x$-direction at edges $\xi = -1$ and $\xi = 1$ can be expressed as:
%
\begin{equation}\label{eq:UBx}
	\begin{split}
		\begin{Bmatrix}
			\phi(\xi=-1)\\\frac{\id \phi(\xi=-1)}{\id \xi}\\\phi(\xi=1)\\\frac{\id \phi(\xi=1)}{\id \xi}
		\end{Bmatrix}
		= \begin{bmatrix}
			-S_{\alpha_1}&C_{\alpha_1}&-Sh_{\beta_1}&Ch_{\beta_1}\\
			\alpha_1 C_{\alpha_1}/a&\alpha_1S_{\alpha_1}/a&\beta_1Ch_{\beta_1}/a&-\beta_1Sh_{\beta_1}/a\\
			S_{\alpha_1}&C_{\alpha_1}&Sh_{\beta_1}&Ch_{\beta_1}\\
			\alpha_1 C_{\alpha_1}/a&-\alpha_1S_{\alpha_1}/a&\beta_1Ch_{\beta_1}/a&\beta_1Sh_{\beta_1}/a
		\end{bmatrix}
		\begin{Bmatrix}
			A_1\\A_2\\A_3\\A_4
		\end{Bmatrix} ,
	\end{split}
\end{equation}
%
or,
%
\begin{equation}\label{eq:UBx1}
	\mathbf{\delta}_x= \mathbf{Q}_x\mathbf{A}.
\end{equation}
%
Note that the eigenvector $\mathbf{A}$ can be expressed by multiplying the inverse matrix $\mathbf{Q}_x^{-1}$ on the left side of \Cref{eq:UBx1}, and then substituting $\mathbf{A}$ into \Cref{eq:ABx1}, we obtain:
%
\begin{equation}\label{eq:DSM_eqx}
	\mathbf{R}_x \mathbf{A}=\mathbf{R}_x\mathbf{Q}_x^{-1}\mathbf{\delta}_x = \mathbf{0}.
\end{equation}
%
where the dynamic stiffness matrix, denoted as $\mathbf{K}_x = \mathbf{R}_x\mathbf{Q}_x^{-1}$, can be obtained from \Cref{eq:DSM_eqx}. 
This matrix can be used to compute the natural frequencies of the system instead of solving the eigenvalue equation, 
and the method for the computation will be given in \Cref{sec:WWA}.

\subsection{Dynamic stiffness matrix corresponding to \(\omega_y\)}\label{sec:DSMy}
In this section, the mode shape \(\phi(\xi)\) derived in \(\Cref{sec:DSMx}\) is utilized to obtain the dynamic stiffness matrix in the \(y\)-direction.  
The vertical translational and rotational springs at \(\eta = -1\) are denoted as \(k^v_{\eta = -1}\) and \(k^r_{\eta = -1}\), respectively, while those at \(\eta = 1\) are represented by \(k^v_{\eta = 1}\) and \(k^r_{\eta = 1}\).

Similarly, the potential energy along the edges in the \( y \)-direction is given by:  
%
\begin{equation}\label{eq:poten_energy_edgey2}  
	\begin{split}  
		U^{III}_{mag} &= ab \int \left[ \frac{k^r_{\eta=-1}}{a^3} \left( \frac{\partial w}{\partial \eta} \right)^2 + \frac{k^v_{\eta=-1}}{a} w^2 \right]_{\eta=-1} \id \xi \\  
		&\quad + ab \int \left[ \frac{k^r_{\eta=1}}{a^3} \left( \frac{\partial w}{\partial \eta} \right)^2 + \frac{k^v_{\eta=1}}{a} w^2 \right]_{\eta=1} \id \xi.  
	\end{split}  
\end{equation} 
% 
The total potential energy of the plate in the \( y \)-direction can be determined from \Cref{eq:poten_energy_mag,eq:poten_energy_edgey2} as:
%
\begin{equation}\label{eq:poten_energy_toly}
	\begin{split}
		U_{mag}&=U^{I}_{mag}+U^{III}_{mag}\\
		&=\frac{ab}{2} \iint \left[ \frac{D_{11}}{a^4} \left( \frac{\partial^2 w}{\partial \xi^2} \right)^2 + \frac{2 D_{12}}{a^2 b^2} \frac{\partial^2 w}{\partial \xi^2} \frac{\partial^2 w}{\partial \eta^2} + \frac{D_{22}}{b^4} \left( \frac{\partial^2 w}{\partial \eta^2} \right)^2 \right. \\
		&\quad \left.  + \frac{4 D_{66}}{a^2 b^2}\left( \frac{\partial^2 w}{\partial \xi \partial \eta} \right)^2 \right] \, \id\xi \, \id\eta+ab \int \left[ \frac{k^r_{\eta=1}}{b^3} \left( \frac{\partial w}{\partial \eta} \right)^2 + \frac{k^v_{\eta=1}}{b} \left( w \right)^2 \right]_{\eta=1} \id\xi\\
		&\quad+ab \int \left[ \frac{k^r_{\eta=-1}}{b^3} \left( \frac{\partial w}{\partial \eta} \right)^2 + \frac{k^v_{\eta=-1}}{b} \left( w \right)^2 \right]_{\eta=-1} \id\xi.
	\end{split}
\end{equation}

By substituting \Cref{eq:displace_func} into \Cref{eq:poten_energy_toly}, we obtain:  
%
\begin{equation}\label{eq:poten_energy_toly2}
	\begin{split}
		U_{mag} &= U^{I}_{mag} + U^{III}_{mag} \\
		&= \frac{ab}{2} \int_{-1}^{1} \left[ \frac{D_{11}}{a^4} T_4 \psi^2 
		+ \frac{2D_{12}}{a^2b^2} T_2 \frac{\id^2\psi }{\id \eta^2} \psi 
		+ \frac{D_{22}}{b^4} T_1 \left(\frac{\id^2\psi }{\id \eta^2} \right)^2 \right. \\
		&\quad \left. + \frac{4D_{66}}{a^2b^2} T_3 \left(\frac{\id \psi }{\id \eta} \right)^2 \right] \, \id\eta  + ab \left[ \frac{k^r_{\eta=1}}{b^3} T \left( \frac{\id \psi}{\id \eta} \right)^2
		+ \frac{k^v_{\eta=1}}{b} T_1 \left(\psi\right)^2 \right]_{\eta=1} \\
		&\quad + ab \left[ \frac{k^r_{\eta=-1}}{b^3} T \left( \frac{\id \psi}{\id \eta} \right)^2
		+ \frac{k^v_{\eta=-1}}{b} T_1 \left(\psi\right)^2 \right]_{\eta=-1},
	\end{split}
\end{equation}
%
where the integral parameters are defined as:  
%
\begin{equation}\label{eq:inte_psi}  
	\begin{split}  
		&T_1 = \int_{-1}^{1} \phi^2 \, \id\xi, \\  
		&T_2 = \int_{-1}^{1} \left( \frac{\id^2\phi}{\id\xi^2} \phi \right) \, \id\xi, \\  
		&T_3 = \int_{-1}^{1} \left( \frac{\id\phi}{\id\xi} \right)^2 \, \id\xi, \\  
		&T_4 = \int_{-1}^{1} \left( \frac{\id^2\phi}{\id\xi^2} \right)^2 \, \id\xi.  
	\end{split}  
\end{equation}  
%
The coefficient \( T_0 \) of the kinetic energy in \Cref{eq:kine_energy_mag} for the plate can be expressed as:
%
\begin{equation}\label{eq:kine_energyy}
	\begin{split}
		T_0 &= \frac{ab}{2} \rho h T_1 \int_{-1}^{1} \psi^2 \, \id\eta.
	\end{split}
\end{equation}

Taking the Rayleigh principle in the form:
%
\begin{equation}\label{eq:Rayleighy}
	\begin{split}
		\delta U_{mag} &= \omega_y^2 \, \delta T_0.
	\end{split}
\end{equation}
%
By substituting \Cref{eq:poten_energy_toly2,eq:kine_energyy} into \Cref{eq:Rayleighy}, and applying the variational calculus to eliminate \( \delta \psi \) and \( \delta\frac{\id \psi}{\id \eta} \) in \Cref{eq:Rayleighy}, we obtain:
%
\begin{equation}\label{eq:Rayleighy2}
	\begin{split}
		0 &= \int_{-1}^{1} \left[ \frac{D_{22}}{b^4} T_1 \frac{d^4 \psi}{\id \eta^4} 
		+ \left( \frac{2D_{12}}{a^2b^2} T_2 - \frac{4D_{66}}{a^2b^2} T_3 \right) \frac{\id^2 \psi}{\id \eta^2} \right. \\
		&\quad \left. + \left( \frac{D_{11}}{a^4} T_4 - \omega_y^2 \rho h T_1 \right) \psi \right] \delta \psi \, \id\eta \\
		&\quad + \frac{2k^v_{\eta=-1}}{b} T_1 (\psi \delta \psi)_{\eta=-1} 
		+ \frac{2k^v_{\eta=1}}{b} T_1 (\psi \delta \psi)_{\eta=1} \\
		&\quad + \left[ \left( \frac{4D_{66}}{a^2b^2} T_3 - \frac{D_{12}}{a^2b^2} T_2 \right) \frac{\id \psi}{\id \eta} 
		- \frac{D_{22}}{b^4} T_1 \frac{\id^3 \psi}{\id \eta^3} \right] \delta \psi \Big|^{\eta=1}_{\eta=-1} \\
		&\quad + \left( \frac{D_{12}}{a^2b^2} T_2 \psi + \frac{D_{22}}{b^4} T_1 \frac{\id^2 \psi}{\id \eta^2} \right) 
		\delta\frac{\id  \psi}{\id \eta} \Big|^{\eta=1}_{\eta=-1} \\
		&\quad + \frac{2k^r_{\eta=-1}}{b^3} T_1 \left( \frac{\id \psi}{\id \eta} \delta\frac{\id \psi}{\id \eta} \right)_{\eta=-1} 
		+ \frac{2k^r_{\eta=1}}{b^3} T_1 \left( \frac{\id \psi}{\id \eta} \delta\frac{\id \psi}{\id \eta} \right)_{\eta=1}.
	\end{split}
\end{equation}
%
Thus, the governing differential equation in the \( y \)-direction can be obtained from the integration part in \Cref{eq:Rayleighy2}:
%
\begin{equation}\label{eq:ODEy}
		\frac{\id^4 \psi}{\id \eta^4} + \frac{2}{\alpha^2}\left(\frac{D_{12}T_2}{D_{22}T_1} - 2\frac{D_{66}T_3}{D_{22}T_1}\right)\frac{\id^2 \psi}{\id \eta^2} + \left( \frac{D_{11}T_4}{\alpha^4D_{22}T_1} - \frac{b^4D_{11}}{D_{22}} \Omega_y^4 \right) \psi = 0,
\end{equation}
%
where \( \Omega_y = \sqrt[4]{\frac{\omega_y^2 \rho h}{D_{11}}} \).
Substituting \( \psi(\eta) = B e^{\lambda \eta} \) into \Cref{eq:ODEy}, yields:
%
\begin{equation}\label{eq:ODEy2}
	\begin{split}
		\lambda^4 + \frac{2}{\alpha^2} \left( \frac{D_{12}T_2}{D_{22}T_1} - 2\frac{D_{66}T_3}{D_{22}T_1} \right) \lambda^2 + \left( \frac{D_{11}T_4}{\alpha^4D_{22}T_1} - \frac{b^4D_{11}}{D_{22}} \Omega_y^4 \right) = 0.
	\end{split}
\end{equation}
%
The solution for \( \lambda \) can be expressed as:
%
\begin{equation}\label{eq:lambda}
	\begin{split}
		\lambda_{1,2} &= \pm \textit{i} \alpha_2, \qquad \lambda_{3,4} = \pm \beta_2,
	\end{split}
\end{equation}
%
where,
%
\begin{subequations}\label{eq:beta}
	\begin{align}
		\alpha_2 &= \frac{1}{\alpha} \sqrt{ \sqrt{ \left( \frac{D_{12}T_2}{D_{22}T_1} - 2\frac{D_{66}T_3}{D_{22}T_1} \right)^2 - \frac{D_{11}T_4}{D_{22}T_1} + \frac{a^4 D_{11}}{D_{22}} \Omega_y^4 } + \frac{D_{12}T_2}{D_{22}T_1} - 2 \frac{D_{66}T_3}{D_{22}T_1}}, \\
		\beta_2 &= \frac{1}{\alpha} \sqrt{ \sqrt{ \left( \frac{D_{12}T_2}{D_{22}T_1} - 2 \frac{D_{66}T_3}{D_{22}T_1} \right)^2 - \frac{D_{11}T_4}{D_{22}T_1} + \frac{a^4 D_{11}}{D_{22}} \Omega_y^4 } - \frac{D_{12}T_2}{D_{22}T_1} + 2 \frac{D_{66}T_3}{D_{22}T_1}}.
	\end{align}
\end{subequations}
%
The boundary conditions along the edges in the \( y \)-direction can be obtained from the remaining \( \delta \psi \) and \( \delta \frac{\id \psi}{\id \eta} \) parts in \Cref{eq:Rayleighy2}. 
The shear force equilibrium can be obtained from the \( \delta \psi \) part:
%
\begin{equation}\label{eq:inertial_forcey}
	\begin{split}
		& \left[ \left( \frac{4D_{66}}{a^2b^2} T_3 - \frac{D_{12}}{a^2b^2} T_2 \right) \frac{\id \psi}{\id \eta} 
		- \frac{D_{22}}{b^4} T_1 \frac{\id^3 \psi}{\id \eta^3} \right] \Big|^{\eta=1}_{\eta=-1} \\
		&\quad + \frac{2k^v_{\eta=-1}}{b} T_1 (\psi )_{\eta=-1} + \frac{2k^v_{\eta=1}}{b} T_1 (\psi )_{\eta=1} = 0,
	\end{split}
\end{equation}
%
and from the \( \delta \frac{\id \psi}{\id \eta} \) part, the bending moment equilibrium:
%
\begin{equation}\label{eq:inertial_forcey2}	
 \begin{split}
 	\left( \frac{D_{12}}{a^2b^2} T_2 \psi + \frac{D_{22}}{b^4} T_1 \frac{\id^2 \psi}{\id \eta^2} \right) 
 	\Big|^{\eta=1}_{\eta=-1} 
 	&+ \frac{2k^r_{\eta=-1}}{b^3} T_1 \left( \frac{\id \psi}{\id \eta} \right)_{\eta=-1} \\
 	&+ \frac{2k^r_{\eta=1}}{b^3} T_1 \left( \frac{\id \psi}{\id \eta} \right)_{\eta=1}=0.
 \end{split}
\end{equation}
%
Thus, we can obtain the shear force and bending moment equilibrium along the edges \( \eta = -1 \) and \( \eta = 1 \) from \Cref{eq:inertial_forcey,eq:inertial_forcey2}, respectively, as:
%
\begin{subequations}\label{eq:boundaryy}
	\begin{align}
		&  \frac{\id^3 \psi}{\id \eta^3}-\left( \frac{4D_{66}T_3}{\alpha^2D_{22}T_1}  - \frac{D_{12}T_2}{\alpha^2D_{22}T_1}  \right) \frac{\id \psi}{\id \eta} 
		+\frac{2b^3k^v_{\eta=-1}}{D_{22}}\psi=0,\quad &\eta=-1,\\
		& \frac{\id^2 \psi}{\id \eta^2}+\frac{D_{12}T_2}{\alpha^2D_{22}T_1} \psi -\frac{2bk^r_{\eta=-1}}{D_{22}}\frac{\id\psi }{\id \eta}=0,\quad &\eta=-1,\\
		&  \frac{\id^3 \psi}{\id \eta^3}-\left( \frac{4D_{66}T_3}{\alpha^2D_{22}T_1}  - \frac{D_{12}T_2}{\alpha^2D_{22}T_1}  \right) \frac{\id \psi}{\id \eta} 
		-\frac{2b^3k^v_{\eta=1}}{D_{22}}\psi=0,\quad &\eta=1,\\
		&\frac{\id^2 \psi}{\id \eta^2}+\frac{D_{12}T_2}{\alpha^2D_{22}T_1} \psi +\frac{2bk^r_{\eta=1}}{D_{22}}\frac{\id\psi }{\id \eta}=0,\quad &\eta=1.
	\end{align}
\end{subequations}
%
Substituting \Cref{eq:phi_solution2} into \Cref{eq:boundaryy} and introducing the notations 
\( k^{v*}_{\eta} = \frac{2b^3 k^v_{\eta}}{D_{22}} \), 
\( k^{r*}_{\eta} = \frac{2b k^r_{\eta}}{D_{22}} \), 
\( \sin\alpha_2 = S_{\alpha_2} \), 
\( \cos\alpha_2 = C_{\alpha_2} \), 
\( \sinh\alpha_2 = Sh_{\alpha_2} \), 
\( \cosh\alpha_2 = Ch_{\alpha_2} \), 
\( \sin\beta_2 = S_{\beta_2} \), 
\( \cos\beta_2 = C_{\beta_2} \), 
\( \sinh\beta_2 = Sh_{\beta_2} \), and 
\( \cosh\beta_2 = Ch_{\beta_2} \), 
We obtain:
%
\begin{equation}\label{eq:ABy}
	\begin{split}
		&\left[ \begin{array}{c}
			\hat{\gamma}_1C_{\alpha_2}-k^{v*}_{\eta=-1}S_{\alpha_2} \\ \hat{\gamma}_3S_{\alpha_2}+k^{r*}_{\eta=-1}\alpha_2C_{\alpha_2} \\ -\hat{\gamma}_1C_{\alpha_2}+k^{v*}_{\eta=1}S_{\alpha_2} \\ \hat{\gamma}_3S_{\alpha_2}+k^{r*}_{\eta=1}\alpha_2C_{\alpha_2}
		\end{array} \begin{array}{c}
			\hat{\gamma}_1S_{\alpha_2}+k^{v*}_{\eta=-1}C_{\alpha_2} \\ -\hat{\gamma}_3C_{\alpha_2}+k^{r*}_{\eta=-1}\alpha_2S_{\alpha_2} \\ \hat{\gamma}_1S_{\alpha_2}+k^{v*}_{\eta=1}C_{\alpha_2} \\ \hat{\gamma}_3C_{\alpha_2}-k^{r*}_{\eta=1}\alpha_2S_{\alpha_2}
		\end{array} \begin{array}{c}
			\hat{\gamma}_2Ch_{\beta_2}-k^{v*}_{\eta=-1}Sh_{\beta_2} \\ \hat{\gamma}_4Sh_{\beta_2}+k^{r*}_{\eta=-1}\beta_2Ch_{\beta_2} \\ -\hat{\gamma}_2Ch_{\beta_2}+k^{v*}_{\eta=1}Sh_{\beta_2} \\ \hat{\gamma}_4Sh_{\beta_2}+k^{r*}_{\eta=1}\beta_2Ch_{\beta_2}
		\end{array} \right. \\
		&\quad
		\left. \begin{array}{c}
			-\hat{\gamma}_2Sh_{\beta_2}+k^{v*}_{\eta=-1}Ch_{\beta_2} \\ -\hat{\gamma}_4Ch_{\beta_2}-k^{r*}_{\eta=-1}\beta_2Sh_{\beta_2} \\ -\hat{\gamma}_2Sh_{\beta_2}+k^{v*}_{\eta=1}Ch_{\beta_2} \\ \hat{\gamma}_4Ch_{\beta_2}+k^{r*}_{\eta=1}\beta_2Sh_{\beta_2}
		\end{array} \right]\begin{Bmatrix}
			B_1\\B_2\\B_3\\B_4
		\end{Bmatrix}=\begin{Bmatrix}
			0\\0\\0\\0
		\end{Bmatrix},
	\end{split}
\end{equation}
%
or,
%
\begin{equation}\label{eq:ABy1}
	\mathbf{R}_y \mathbf{B} = \mathbf{0},
\end{equation}
%
where,
%
\begin{equation}\label{eq:gammay}
	\begin{split}
		&\hat{\gamma}_1=-\alpha_2^3-\left( \frac{4D_{66}T_3}{\alpha^2D_{22}T_1}  - \frac{D_{12}T_2}{\alpha^2D_{22}T_1}  \right)\alpha_2,\\
		&\hat{\gamma}_2=\beta_2^3-\left( \frac{4D_{66}T_3}{\alpha^2D_{22}T_1}  - \frac{D_{12}T_2}{\alpha^2D_{22}T_1}  \right)\beta_2,\\
		&\hat{\gamma}_3=-\alpha_2^2+\frac{D_{12}T_2}{\alpha^2D_{22}T_1},\\
		&\hat{\gamma}_4=\beta_2^2+\frac{D_{12}T_2}{\alpha^2D_{22}T_1}.
	\end{split}
\end{equation}
%
With the help of \Cref{eq:phi_solution2}, the vertical displacement and rotation corresponding to the mode shape $\psi$ along the $y$-direction at the edges $\eta = -1$ and $\eta = 1$ can be expressed as:
%
\begin{equation}\label{eq:UBy}
	\begin{split}
		\begin{Bmatrix}
			\psi_{\eta=-1}\\\frac{\id \psi}{\id \eta}_{\eta=-1}\\\psi_{\eta=1}\\\frac{\id \psi}{\id \eta}_{\eta=1}
		\end{Bmatrix}
		= \begin{bmatrix}
			-S_{\alpha_2} & C_{\alpha_2} & -Sh_{\beta_2} & Ch_{\beta_2} \\
			\frac{\alpha_2 C_{\alpha_2}}{b} & \frac{\alpha_2 S_{\alpha_2}}{b} & \frac{\beta_2 Ch_{\beta_2}}{b} & -\frac{\beta_2 Sh_{\beta_2}}{b} \\
			S_{\alpha_2} & C_{\alpha_2} & Sh_{\beta_2} & Ch_{\beta_2} \\
			\frac{\alpha_2 C_{\alpha_2}}{b} & -\frac{\alpha_2 S_{\alpha_2}}{b} & \frac{\beta_2 Ch_{\beta_2}}{b} & \frac{\beta_2 Sh_{\beta_2}}{b}
		\end{bmatrix}
		\begin{Bmatrix}
			B_1\\B_2\\B_3\\B_4
		\end{Bmatrix},		
	\end{split}
\end{equation}
%
or,
%
\begin{equation}\label{eq:UBy1}
	\mathbf{\delta}_y= \mathbf{Q}_y\mathbf{B}.
\end{equation}
%
Note that the eigenvector \(\mathbf{B}\) can be expressed by multiplying the inverse matrix \(\mathbf{Q}_y^{-1}\) on the left-hand side of \Cref{eq:UBy1}, and then substituting \(\mathbf{B}\) into \Cref{eq:ABy1}, we obtain:
%
\begin{equation}\label{eq:DSM_eqy}
	\mathbf{R}_y\mathbf{B}=\mathbf{R}_y \mathbf{Q}_x^{-1} 
	\mathbf{\delta}_y = \mathbf{0},
\end{equation}
%
where the dynamic stiffness matrix, denoted as \(\mathbf{K}_y = \mathbf{R}_y \mathbf{Q}_y^{-1}\), can be obtained from \Cref{eq:DSM_eqy}.

\section{Frequency and mode shape computation}\label{sec:WWA}
\subsection{Wittrick–Williams algorithm}\label{sec:WWA2}
The Wittrick–Williams (W-W) algorithm \cite{wittrick1971general} is an effective method for determining the natural frequencies from the dynamic stiffness matrix with high reliability. 
Instead of directly solving the equations, the algorithm computes the total number \(J\) of natural frequencies below a given frequency \(\omega^*\), which is represented as:
\begin{equation}\label{eq:WWalgorithm}
	J(\omega^*) = J_0(\omega^*) + s\{\mathbf{K}^{\Delta}(\omega^*)\} = J_0(\omega^*) + J_k(\omega^*),
\end{equation}
where \(J_0\) represents the number of natural frequencies for the system with both ends fully clamped, \(\mathbf{K}^{\Delta}\) is the upper triangular matrix obtained from the dynamic stiffness matrix \(\mathbf{K}\) after applying Gaussian elimination, and \(J_k(\omega^*)\) denotes the number of negative elements in the leading diagonal of \(\mathbf{K}^{\Delta}\).

It should be noted that the \( J_0 \) count is a crucial aspect when applying the W-W algorithm. Many previous studies use a sufficiently fine mesh or enough terms in series expansions to capture all fully clamped natural frequencies, ensuring computational accuracy \cite{banerjee2015dynamic}. However, this approach can make the application process cumbersome. 
To address this issue, the fully clamped problem can be replaced with a simply supported problem, where the Navier solution for the simply supported plate is used to count \( J_0 \) \citep{liu2015exact}. 
Nevertheless, since analytical solutions in DSM methods involve an infinite series of Fourier terms, a sufficient number of truncation terms is required to ensure accuracy and convergence.

However, the idea of solving the simply supported problem proposes an effective and systematic approach to indirectly determine the \( J_0 \) count for a fully clamped structure using the 'hypothetical structure method', where the boundary conditions are modeled as pinned supports rather than clamped ones \cite{han2018improved}:
%
\begin{equation}\label{eq:J_o_pin}
	J_0(p_1,\omega^*) = J(\bar{p}_1,\omega^*) - J_k(\bar{p}_1,\omega^*),
\end{equation}
%
where \( p_1 \) and \( \bar{p}_1 \) represent clamped and pinned supports, respectively.
By substituting \Cref{eq:J_o_pin} into \Cref{eq:WWalgorithm} we get the algorithm as:  
%
\begin{equation}\label{eq:new_WWalgorithm}
	J(p,\omega^*) = J(\bar{p}_1,\omega^*) - J_k(\bar{p}_1,\omega^*) + J_k(p,\omega^*)
\end{equation} 
%
where \( p \) represents the original boundary conditions of the structure.
Therefore, the challenge of determining \( J_0(p_1, \omega^*) \) can be transformed into the problem of solving \( J(\bar{p}_1, \omega^*) \) instead. The eigenvalue equation corresponding to the natural frequency parameter \( \Omega_x \) can be obtained from the determinant of the coefficient matrix \( \mathbf{R}_x \) in \Cref{eq:ABx}, which is given by:
%
\begin{equation}\label{eq:SSx} 
	\sin 2\alpha_1 = 0.
\end{equation}
%
With the help of \Cref{eq:alphax1,eq:SSx}, the closed-form solution of the \(n_x\)th simply supported frequency \(\Omega_{x,n_x}\) for the given \(n_y\)-order \(\psi_{n_y}(\eta)\) can be expressed as:
%
\begin{equation}\label{eq:J_simpx}
	\Omega_{x,n_x} =
	\frac{1}{b} \sqrt[4]{%
		%\large % slightly smaller than \Large
		\begin{aligned}
			&\left[\left(\frac{n_x\pi}{2\alpha}\right)^2 - \frac{D_{12}S_2}{D_{11}S_1} + 2 \frac{D_{66}S_3}{D_{11}S_1}\right]^2 - \left(\frac{D_{12}S_2}{D_{11}S_1} - 2 \frac{D_{66}S_3}{D_{11}S_1}\right)^2 \\
			&+ \frac{D_{22}S_4}{D_{11}S_1}.
		\end{aligned}
	}
\end{equation}
%
For \(\Omega_{x,n_x} \leq \Omega_x^* < \Omega_{x,n_{x+1}}\), \(J(\bar{p}_1, \Omega_x^*) = n_x\).
Similarly, the closed-form solution of the \(n_y\)th simply supported frequency \(\Omega_{y,n_y}\) for the given \(n_x\)-order \(\phi_{n_x}(\xi)\) can be expressed as:
%
\begin{equation}\label{eq:J_simpy}
	\Omega_{y,n_y}= 
	\frac{1}{a} \sqrt[4]{%
		\begin{aligned}
			&\frac{D_{22}}{D_{11}}\left\{\left[\left(\frac{n_y\pi\alpha}{2}\right)^2 - \frac{D_{12}T_2}{D_{22}T_1} + 2 \frac{D_{66}T_3}{D_{22}T_1}\right]^2 - \left(\frac{D_{12}T_2}{D_{22}T_1} - 2 \frac{D_{66}T_3}{D_{22}T_1}\right)^2\right. \\
			&\left.  + \frac{D_{11}T_4}{D_{22}T_1}\right\}.
		\end{aligned}
	}
\end{equation}
%
For \(\Omega_{y,n_y} \leq \Omega_y^* < \Omega_{y,n_{y+1}}\), \(J(\bar{p}_1, \Omega_y^*) = n_y\).
According to the relationships 
$\Omega_x = \sqrt[4]{\frac{\omega_x^2 \rho h}{D_{11}}}$ and\ $\Omega_y = \sqrt[4]{\frac{\omega_y^2 \rho h}{D_{11}}}$, 
the values of \(J(\bar{p}_1, \omega_x^*)\) and \(J(\bar{p}_1, \omega_y^*)\) can be derived from \(J(\bar{p}_1, \Omega_x^*)\) and \(J(\bar{p}_1, \Omega_y^*)\), respectively. Therefore, this refined W-W algorithm can be applied to estimate the lower and upper bounds of the frequency range, denoted as \(\omega_l\) and \(\omega_u\), yielding an approximation for the frequency \(\omega_a \in (\omega_l, \omega_u)\).

The mode shape coefficients \( A_1 \) to \( A_4 \) and \( B_1 \) to \( B_4 \) in the eigenvectors \( \mathbf{A} \) and \( \mathbf{B} \) for all classic boundary conditions are provided in \cite{xing2020extended}. 
Alternatively, these coefficients can also be obtained through a simple numerical method, which this work presents as an approach.
Here, we illustrate solving the eigenvector \( \mathbf{A} \) as an example.
By assuming the exact natural frequency as \( \omega_k \), we can expand the coefficient matrix \( \mathbf{R}_{x} \) in \Cref{eq:ABx} using a first-order Taylor series about \( \omega_a \):
%
\begin{equation}\label{eq:Taylor}
	\mathbf{R}_{x,k}(\omega_k)\mathbf{A}_k = \mathbf{R}_{x,a}\mathbf{A}_k + (\omega_k - \omega_a)\mathbf{R}'_{x,a}\mathbf{A}_k + O\left((\omega_k - \omega_a)^2\right) = 0.
\end{equation}
%
Ignoring higher-order terms, an eigenvalue problem can be derived from \Cref{eq:Taylor}:
%
\begin{equation}\label{eq:Newgeigen}
	(\mathbf{R}^{'}_{x,a})^{-1} \mathbf{R}_{x,a} \mathbf{A} = (\omega_a - \omega_k)\mathbf{A} = \tau \mathbf{A}.
\end{equation}
%
This eigenvalue problem can be solved using the inverse iteration procedure \cite{yuan2004second}:
%
\begin{equation}\label{eq:Inversepower}
	\bar{\mathbf{A}}^{(i+1)} = \mathbf{R}_{x,a}^{-1} \mathbf{R}^{'}_{x,a} \mathbf{A}^{(i)},	
\end{equation}
%
where the initial guess for \( \mathbf{A}^{(0)} \) is a column vector consisting of four randomly generated elements, each of which falls within the range (0,1). The updated eigenvalue for the next step can be obtained as:
%
\begin{equation}\label{eq:Newgeigenvalue}
	\tau^{(i+1)} = \frac{1}{\bar{A}_j^{(i+1)}},
\end{equation}
%
where,
%
\begin{equation}\label{eq:updatetau}
	\mid \bar{A}_j^{(i+1)} \mid = \max(\mid \bar{A}_1^{(i+1)} \mid, \mid \bar{A}_2^{(i+1)} \mid, \mid\bar{A}_3^{(i+1)}\mid , \mid \bar{A}_4^{(i+1)} \mid).
\end{equation}
%
The updated eigenvector can be obtained as:
%
\begin{equation}\label{eq:updateeigenvalue}
	\mathbf{A}^{(i+1)} = \tau^{(i+1)} \bar{\mathbf{A}}^{(i+1)}.
\end{equation}
%
The procedure can be controlled by the error tolerance \( \epsilon \) or maximum allowed steps \( i_{\text{max}} \):
%
\begin{subequations}
	\begin{align}
		\max \mid A_n^{(i+1)} - A_n^{(i)} \mid < \epsilon, \\ 
		i = i_{\text{max}}.
	\end{align}
\end{subequations}
%
Note that the mode shape coefficients \( A_1 \) to \( A_4 \) obtained from \(\mathbf{A}^{(i+1)}\) are applied for the elastically restrained boundary conditions.

\subsection{Application procedure}
The procedure of the proposed method is as follows:   
\subsubsection{Iterative procedure}\label{sec:Iterative_procedure}
\begin{itemize}[]
	\item \textbf{Step 1} Assume initial integral parameters \(S^{(0)}_1, S^{(0)}_2, S^{(0)}_3\), and \(S^{(0)}_4\) in the \(y\)-direction. Using the given boundary conditions (BCs) at \(\xi = -1\) and \(\xi = 1\), determine \(\mathbf{K}^{(0)}_x\) from \Cref{eq:DSM_eqx}. Then, apply the computational algorithms in \Cref{sec:WWA2} to compute the \(n_x\)-th frequency \(\omega^{(0)}_{x,n_x}\) and its corresponding mode shape \(\phi^{(0)}_{n_x}\), where \(n_x = 1, 2, 3, \ldots\).

	\item \textbf{Step 2} Use \(\phi^{(0)}_{n_x}\) as the prescribed mode to determine \(\mathbf{K}^{(1)}_y\) in \Cref{eq:DSM_eqy}, considering the BCs at \(\eta = -1\) and \(\eta = 1\). Apply the computational algorithms to obtain the \(n_y\)-th frequency \(\omega^{(1)}_{y,n_y}\) and its corresponding mode shape \(\psi^{(1)}_{n_y}\), where \(n_y = 1, 2, 3, \ldots\). This completes the first iteration cycle.

	\item \textbf{Step 3} Use \(\psi^{(1)}_{n_y}\) as the prescribed \(n_y\)-th mode shape in the \(y\)-direction to compute \(\mathbf{K}^{(1)}_x\) from \Cref{eq:DSM_eqx}, then determine the \(n_x\)-th frequency \(\omega^{(1)}_{x,n_x}\) and its corresponding mode shape \(\phi^{(1)}_{n_x}\).

	\item \textbf{Step 4} Use \(\phi^{(1)}_{n_x}\) as the prescribed mode in the \(x\)-direction to compute the \(n_y\)-th frequency \(\omega^{(2)}_{y,n_y}\) and its corresponding mode shape \(\psi^{(2)}_{n_y}\), completing the second iteration cycle.

	\item \textbf{Step 5} Stop the iteration if \(\mid\omega^{(i)}_{x,n_x} - \omega^{(i+1)}_{x,n_x}\mid \leq \Delta\omega\) or \(\mid\omega^{(i)}_{y,n_y} - \omega^{(i+1)}_{y,n_y}\mid \leq \Delta\omega\), where \(\Delta\omega\) is the frequency interval defined in \Cref{sec:WWA}, where, \(\Delta\omega = \omega_u - \omega_l\).

	\item \textbf{Step 6} Finally, construct the \((n_x, n_y)\)-th mode shape as \(w(\xi, \eta) = \phi_{n_x}(\xi) \psi_{n_y}(\eta)\) using \Cref{eq:displace_func}.  
\end{itemize}
\subsubsection{Non-iterative Procedure}\label{sec:Noniterative_procedure}  
Although the iterative procedure in \Cref{sec:Iterative_procedure} can be used to obtain any desired mode, a non-iterative approach can enhance the efficiency of numerical calculations when an exact mode is known.

Once a nonzero mode shape \(\phi_{n_x}(\xi) \psi_{n_y}(\eta)\) is determined by following the iterative procedure in \Cref{sec:Iterative_procedure}, \(\psi_{n_y}(\eta)\) can be chosen as the exact known mode in the \(y\)-direction.  
This allows the computation of infinitely many modes \(\phi(\xi)\) in the \(x\)-direction by following only \textbf{Step 1}, without requiring further iterations.  
Similarly, if \(\phi_{n_x}(\xi)\) is selected as the exact known mode in the \(x\)-direction, infinitely many modes \(\psi(\eta)\) in the \(y\)-direction can be computed by following only \textbf{Step 2}, without iterations.

For example, if the \((n_x, n_y)\)-th mode is nonzero and obtained through the iteration procedure, then based on \(\psi_{n_y}(\eta)\), the modes \((1,n_y)\), \((2,n_y)\), ..., \((\infty,n_y)\) of the plate can be computed without further iteration.  
Similarly, based on \(\phi_{n_x}(\xi)\), the modes \((n_x,1)\), \((n_x,2)\), ..., \((n_x,\infty)\) of the plate can be determined.  
That is, only one iteration procedure is required to calculate all frequencies of the plate, which helps reduce the computational cost.

\FloatBarrier
\section{Numerical Results}  
This section presents the numerical validation of the proposed method for classic boundary conditions and elastically restrained boundary conditions.  
For all numerical calculations, the initial integral parameters are assumed as \(S^{(0)}_1=1\), \(S^{(0)}_2=1\), \(S^{(0)}_3=1\), and \(S^{(0)}_4=10\) in the \(y\)-direction, serving as the starting point of \textbf{Step 1} for any mode in all BCs.  
In this section, the interval between the upper and lower bounds of the non-dimensional frequency parameter, \(2a\Delta\Omega\), is set to 0.005, defining the error range.  
According to our numerical calculations, two iteration cycles are sufficient to meet the convergence requirement for most cases, with at most three cycles needed when applying the iterative procedure in \Cref{sec:Iterative_procedure}.

\subsection{Classical boundary conditions}
In this subsection, the proposed method is validated by comparison with the extended SOV method \cite{xing2020extended}.  
The properties of the orthotropic plate, consistent with those in \cite{xing2020extended}, are as follows:  
\(E_1 = 185 \nugpa\), \(E_2 = 10.5 \nugpa\), \(G_{12} = 7.3 \nugpa\), \(\rho = 1600 \urho\), and \(\nu_{12} = 0.28\).

The initial guess for \(S^{(0)}_1, S^{(0)}_2, S^{(0)}_3\), and \(S^{(0)}_4\) is assumed to be \(1, 1, 1, 10\) for all boundary conditions and mode orders. This differs from the iterative SOV method \citealp{xing2018overall}, which requires a different initial guess for each mode order.  
The translational springs (\(k^v_\xi\)) and rotational springs (\(k^r_\xi\)) along all edges can be set to zero or infinity (represented as \(1 \times 10^{15} \ustif\) in the numerical calculations of this study) to obtain different classic boundary conditions.

The results for SSSS, SCSF, GCGC, CCCC, SSCC, SCCC, GGCC, CCFF, CFCF, CFFF, and FFFF boundary conditions are presented in \Cref{tab:sov1,tab:sov2,tab:sov3}. These results demonstrate high accuracy compared to the extended SOV method, with errors remaining smaller than the interval between the upper and lower bounds (0.005). The frequency parameters in both directions are equal (\(2a\Omega_x - 2a\Omega_y = 0\)) in almost all cases, with a few exceptions where \(2a\Omega_x - 2a\Omega_y = 0.005\).  
\Cref{fig:FFFF} shows the first six nonzero mode shapes of a square orthotropic plate with FFFF boundary conditions.

\begin{figure}
	\centering
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{figs/FFFF1.png}
		\caption[]%
		{{\small }}    
		\label{fig:FFF1}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.49\textwidth}  
		\centering 
		\includegraphics[width=\textwidth]{figs/FFFF2.png}
		\caption[]%
		{{\small }}    
		\label{fig:FFF2}
	\end{subfigure}
	\vfill
	\begin{subfigure}[b]{0.49\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{figs/FFFF3.png}
		\caption[]%
		{{\small }}    
		\label{fig:FFF3}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.49\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{figs/FFFF4.png}
		\caption[]%
		{{\small }}    
		\label{fig:FFF4}
	\end{subfigure}
	\vskip\baselineskip
	\begin{subfigure}[b]{0.49\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{figs/FFFF5.png}
		\caption[]%
		{{\small}}    
		\label{fig:FFF5}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.49\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{figs/FFFF6.png}
		\caption[]%
		{{\small }}    
		\label{fig:FFF6}
	\end{subfigure}
	\caption[]  
	{\small The first six nonzero mode shapes of a square orthotropic plate with FFFF boundary conditions: (a) the first mode; (b) the second mode; (c) the third mode; (d) the fourth mode; (e) the fifth mode; (f) the sixth mode.}  
	\label{fig:FFFF}
\end{figure}

\begin{table}[!htbp] 
	\centering
	\caption{The first seven frequency parameter $2a\Omega$ of of orthotropic rectangular plates with SSSS, SCSF and GCGC boundary conditions.}
	\begin{tabular}{c c l c c c c c c c}
		\toprule
		\multicolumn{3}{c}{} & \multicolumn{7}{c}{$2a\Omega_x=2a\Omega_y=2a\sqrt[4]{\rho h \omega^2/D_{11}}$} \\ 
		\cmidrule(lr){4-10}
		BCs & $\alpha$ & Mode & 1 & 2 & 3 & 4 & 5 & 6 & 7 \\
		\midrule
		SSSS & 0.5 & Mode number  & (1,1) & (1,2) & (1,3) & (1,4) & (1,5) & (1,6) & (1,7) \\
		&     & extended SOV \Citealp{xing2020extended}   & 3.1807 & 3.3190 & 3.5938 & 4.0135 & 4.5495 & 5.1635 & 5.8265 \\
		&     & Present       & 3.1825 & 3.3225 & 3.5975 & 4.0175 & 4.5525 & 5.1625 & 5.8275 \\
		& 1   & Mode number  & (1,1) & (1,2) & (1,3) & (2,1) & (1,4) & (2,2) & (2,3) \\
		&     & extended SOV \Citealp{xing2020extended}   & 3.3190 & 4.0135 & 5.1635 & 6.3615 & 6.5200 & 6.6379 & 7.1876 \\
		&     & Present       & 3.3175 & 4.0175 & 5.1625 & 6.3625 & 6.5175 & 6.6375 & 7.1875 \\
		& 1.5 & Mode number  & (1,1) & (1,2) & (2,1) & (2,2) & (1,3) & (2,3) & (1,4) \\
		&     & extended SOV \Citealp{xing2020extended}   & 3.5938 & 5.1635 & 6.4698 & 7.1876 & 7.2331 & 8.5389 & 9.4352 \\
		&     & Present       & 3.5975 & 5.1675 & 6.4725 & 7.1875 & 7.2325 & 8.5375 & 9.4375 \\
		SCSF & 0.5 & Mode number  & (1,1) & (1,2) & (1,3) & (1,4) & (1,5) & (1,6) & (1,7) \\
		&     & extended SOV \Citealp{xing2020extended}   & 3.1516 & 3.2451 & 3.4588 & 3.8131 & 4.2950 & 4.8711 & 5.5087 \\
		&     & Present      & 3.1525 & 3.2475 & 3.4575 & 3.8175 & 4.2925 & 4.8725 & 5.5075 \\
		& 1   & Mode number  & (1,1) & (1,2) & (1,3) & (1,4) & (2,1) & (2,2) & (2,3) \\
		&     & extended SOV \Citealp{xing2020extended}  & 3.1908 & 3.6428 & 4.5972 & 5.8599 & 6.3033 & 6.4901 & 6.9177 \\
		&     & Present        & 3.1925 & 3.6425 & 4.5975 & 5.8575 & 6.3025 & 6.4925 & 6.9175 \\
		& 1.5 & Mode number & (1,1) & (1,2) & (1,3) & (2,1) & (2,2) & (2,3) & (1,4) \\
		&     & extended SOV \Citealp{xing2020extended}   & 3.2710 & 4.3430 & 6.2157 & 6.3337 & 6.8043 & 7.8718 & 8.3518 \\
		&     & Present      & 3.2725 & 4.3425 & 6.2175 & 6.3325 & 6.8025 & 7.8725 & 8.3525 \\
		GCGC & 0.5 & Mode number & (1,1) & (1,2) & (1,3) & (2,1) & (2,2) & (1,4) & (2,3) \\
		&     & extended SOV \Citealp{xing2020extended}   & 1.1544 & 1.9166 & 2.6835 & 3.1983 & 3.3890 & 3.4501 & 3.7372 \\
		&     & Present      & 1.1525 & 1.9175 & 2.6825 & 3.1975 & 3.3875 & 3.4525 & 3.7375 \\
		& 1   & Mode number  & (1,1) & (2,1) & (1,2) & (2,2) & (1,3) & (2,3) & (3,1) \\
		&     & extended SOV \Citealp{xing2020extended}   & 2.3087 & 3.4900 & 3.8331 & 4.4682 & 5.3669 & 5.7736 & 6.3967 \\
		&     & Present       & 2.3075 & 3.4875 & 3.8325 & 4.4675 & 5.3675 & 5.7725 & 6.3975 \\
		& 1.5 & Mode number  & (1,1) & (2,1) & (1,2) & (2,2) & (3,1) & (3,2) & (1,3) \\
		&     & extended SOV \Citealp{xing2020extended}   & 3.4631 & 4.1353 & 5.7497 & 6.0981 & 6.6049 & 7.6449 & 8.0504 \\
		&     & Present       & 3.4625 & 4.1325 & 5.7475 & 6.0975 & 6.6075 & 7.6425 & 8.0525 \\
		\bottomrule
	\end{tabular}
	\label{tab:sov1}
\end{table}
\begin{table}[!htbp] 
	\centering
	\caption{The first seven frequency parameter $2a\Omega$ of of orthotropic rectangular plates with CCCC, SSCC, SCCC and GGCC boundary conditions.}
	\begin{tabular}{c c l c c c c c c c}
		\toprule
		\multicolumn{3}{c}{} & \multicolumn{7}{c}{$2a\Omega_x=2a\Omega_y=2a\sqrt[4]{\rho h \omega^2/D_{11}}$} \\ 
		\cmidrule(lr){4-10}
		BCs & $\alpha$ & Mode & 1 & 2 & 3 & 4 & 5 & 6 & 7 \\
		\midrule
		CCCC & 0.5 & Mode number  & (1,1) & (1,2) & (1,3) & (1,4) & (1,5) & (1,6) & (1,7) \\
		&     & extended SOV \Citealp{xing2020extended}   & 4.7500 & 4.8208 & 4.9682 & 5.2177 & 5.5791 & 6.0430 & 6.5892 \\
		&     & Present       & 4.7475 & 4.8225 & 4.9725 & 5.2175 & 5.5825 & 6.0425 & 6.5875 \\
		& 1   & Mode number   & (1,1) & (1,2) & (1,3) & (1,4) & (2,1) & (2,2) & (2,3) \\
		&     & extended SOV \Citealp{xing2020extended}   & 4.8579 & 5.3546 & 6.2819 & 7.4972 & 7.9193 & 8.1490 & 8.6054 \\
		&     & Present       & 4.8575 & 5.3575 & 6.2875 & 7.4975 & 7.9175 & 8.1475 & 8.6075 \\
		& 1.5 & Mode number   & (1,1) & (1,2) & (2,1) & (1,3) & (2,2) & (2,3) & (1,4) \\
		&     & extended SOV \Citealp{xing2020extended}   & 5.1581 & 6.5412 & 8.0409 & 8.4945 & 8.7204 & 9.9793 & 10.6460 \\
		&     & Present       & 5.1575 & 6.5375 & 8.0425 & 8.4975 & 8.7175 & 9.9775 & 10.6425 \\
		SSCC & 0.5 & Mode number   & (1,1) & (1,2) & (1,3) & (1,4) & (1,5) & (1,6) & (1,7) \\
		&     & extended SOV \Citealp{xing2020extended}   & 3.9542 & 4.0520 & 4.2525 & 4.5785 & 5.0254 & 5.5682 & 6.1789 \\
		&     & Present       & 3.9575 & 4.0525 & 4.2475 & 4.5775 & 5.0225 & 5.5725 & 6.1825 \\
		& 1   & Mode number  & (1,1) & (1,2) & (1,3) & (1,4) & (2,1) & (2,2) & (2,3) \\
		&     & extended SOV \Citealp{xing2020extended}   & 4.0745 & 4.6606 & 5.7009 & 6.9940 & 7.1396 & 7.3894 & 7.8881 \\
		&     & Present       & 4.0775 & 4.6625 & 5.7025 & 6.9925 & 7.1375 & 7.3875 & 7.8875 \\
		& 1.5 & Mode number   & (1,1) & (1,2) & (2,1) & (1,3) & (2,2) & (2,3) & (1,4) \\
		&     & extended SOV \Citealp{xing2020extended}   & 4.3602 & 5.8384 & 7.2531 & 7.8560 & 7.9481 & 9.2515 & 10.0366 \\
		&     & Present       & 4.3625 & -5.8325 & 7.2525 & 7.8575 & 7.9525 & 9.2525 & 10.0325 \\
		SCCC & 0.5 & Mode number & (1,1) & (1,2) & (1,3) & (1,4) & (1,5) & (1,6) & (1,7) \\
		&     & extended SOV \Citealp{xing2020extended}   & 3.9596 & 4.0745 & 4.3027 & 4.6606 & 5.1361 & 5.7009 & 6.3271 \\
		&     & Present       & 3.9575 & 4.0725 & 4.3025 & 4.6625 & 5.1325 & 5.7025 & 6.3325 \\
		& 1   & Mode number  & (1,1) & (1,2) & (1,3) & (2,1) & (1,4) & (2,2) & (2,3) \\
		&     & extended SOV \Citealp{xing2020extended}   & 4.1349 & 4.8478 & 5.9805 & 7.1541 & 7.3192 & 7.4478 & 8.0121 \\
		&     & Present       & 4.1325 & 4.8475 & 5.9825 & 7.1525 & 7.3175 & 7.4475 & 8.0125 \\
		& 1.5 & Mode number  & (1,1) & (1,2) & (2,1) & (2,2) & (1,3) & (2,3) & (3,1) \\
		&     &extended SOV \Citealp{xing2020extended}  & 4.5824 & 6.2766 & 7.3116 & 8.1528 & 8.3705 & 9.5986 & 10.3507 \\
		&     & Present       & 4.5825 & 6.2775 & 7.3125 & 8.1525 & 8.3725 & 9.5975 & 10.3525 \\
		GGCC & 0.5 & Mode number  & (1,1) & (1,2) & (1,3) & (1,4) & (1,5) & (1,6) & (1,7) \\
		&     & extended SOV \Citealp{xing2020extended}   & 2.3750 & 2.4841 & 2.7895 & 3.2946 & 3.9226 & 4.6123 & 5.3326 \\
		&     & Present       & 2.3725 & 2.4875 & 2.7925 & 3.2975 & 3.9225 & 4.6075 & 5.3325 \\
		& 1   & Mode number  & (1,1) & (1,2) & (1,3) & (2,1) & (2,2) & (1,4) & (2,3) \\
		&     & extended SOV \Citealp{xing2020extended}   & 2.4290 & 3.1410 & 4.4293 & 5.5202 & 5.7315 & 5.8801 & 6.2606 \\
		&     & Present       & 2.4325 & 3.1425 & 4.4325 & 5.5225 & 5.7325 & 5.8775 & 6.2625 \\
		& 1.5 & Mode number  & (1,1) & (1,2) & (2,1) & (2,2) & (1,3) & (2,3) & (3,1) \\
		&     & extended SOV \Citealp{xing2020extended}   & 2.5790 & 4.2472 & 5.5565 & 6.1533 & 6.4347 & 7.5231 & 8.6732 \\
		&     & Present       & 2.5825 & 4.2475 & 5.5575 & 6.1525 & 6.4325 & 7.5225 & 8.6725 \\
		\bottomrule
	\end{tabular}
	\label{tab:sov2}
\end{table}

\begin{table}[!htbp] 
	\centering
	\caption{The first seven nonzero frequency parameter $2a\Omega$ of of orthotropic rectangular plates with CCFF, CFCF, CFFF and FFFF boundary conditions.}
	\begin{tabular}{c c l c c c c c c c}
		\toprule
		\multicolumn{3}{c}{} & \multicolumn{7}{c}{$2a\Omega_x=2a\Omega_y=2a\sqrt[4]{\rho h \omega^2/D_{11}}$} \\ 
		\cmidrule(lr){4-10}
		BCs & $\alpha$ & Mode & 1 & 2 & 3 & 4 & 5 & 6 & 7 \\
		\midrule
		CCFF & 0.5 & Mode number   & (1,1) & (1,2) & (1,3) & (1,4) & (1,5) & (1,6) & (2,1) \\
		&     & extended SOV \Citealp{xing2020extended}   & 1.8978 & 2.0905 & 2.4925 & 3.0563 & 3.7110 & 4.4117 & 4.7029 \\
		&     & Present       & 1.8975 & 2.0925 & 2.4925 & 3.0575 & 3.7125 & 4.4125 & 4.7025 \\
		& 1   & Mode number  & (1,1) & (1,2) & (1,3) & (2,1) & (2,2) & (1,4) & (2,3) \\
		&     & extended SOV \Citealp{xing2020extended}   & 1.9930 & 2.7895 & 4.0733 & 4.7338 & 5.0652 & 5.5128 & 5.7419 \\
		&     & Present       & 1.9925 & 2.7875 & 4.0725 & 4.7325 & 5.0675 & 5.5125 & 5.7425 \\
		& 1.5 & Mode number  & (1,1) & (1,2) & (2,1) & (2,2) & (1,3) & (2,3) & (3,1) \\
		&     & extended SOV \Citealp{xing2020extended}   & 2.1780 & 3.7411 & 4.7931 & 5.5758 & 5.8895 & 7.0263 & 7.9006 \\
		&     & Present       & 2.1775 & 3.7425 & 4.7925 & 5.5725 & 5.8875 & 7.0275 & 7.9025 \\
		CFCF & 0.5 & Mode number   & (1,1) & (1,2) & (1,3) & (1,4) & (1,5) & (1,6) & (1,7) \\
		&     & extended SOV \Citealp{xing2020extended}   & 4.7297 & 4.7427 & 4.7881 & 4.8819 & 5.0478 & 5.3072 & 5.6694 \\
		&     & Present       & 4.7275 & 4.7425 & 4.7875 & 4.8825 & 5.0475 & 5.3075 & 5.6675 \\
		& 1   & Mode number  & (1,1) & (1,2) & (1,3) & (1,4) & (1,5) & (1,6) & (2,1) \\
		&     & extended SOV \Citealp{xing2020extended}   & 4.7295 & 4.7817 & 5.0012 & 5.5348 & 6.4407 & 7.6182 & 7.8523 \\
		&     & Present       & 4.7275 & 4.7825 & 5.0025 & 5.5325 & 6.4425 & 7.6175 & 7.8525 \\
		& 1.5 & Mode number  &(1,1) & (1,2) & (1,3) & (1,4) & (2,1) & (2,2) & (2,3) \\
		&     & extended SOV \Citealp{xing2020extended}   & 4.7292 & 4.8458 & 5.4221 & 6.7635 & 7.8518 & 7.9470 & 8.3021 \\
		&     & Present       & 4.7275 & 4.8475 & 5.4225 & 6.7625 & 7.8525 & 7.9475 & 8.3025 \\
		CFFF & 0.5 & Mode number   & (1,1) & (1,2) & (1,3) & (1,4) & (1,5) & (1,6) & (1,7) \\
		&     & extended SOV \Citealp{xing2020extended}   & 1.8751 & 1.9439 & 2.1679 & 2.5657 & 3.1106 & 3.7486 & 4.4382 \\
		&     & Present       & 1.8775 & 1.9425 & 2.1675 & 2.5675 & 3.1125 & 3.7475 & 4.4375 \\
		& 1   & Mode number  &(1,1) & (1,2) & (1,3) & (1,4) & (2,1) & (2,2) & (2,3) \\
		&     & extended SOV \Citealp{xing2020extended}   & 1.8750 & 2.1242 & 2.9077 & 4.1319 & 4.6937 & 4.8226 & 5.2263 \\
		&     & Present       & 1.8775 & 2.1225 & 2.9075 & 4.1325 & 4.6925 & 4.8225 & 5.2275 \\
		& 1.5 & Mode number  &(1,1) & (1,2) & (1,3) & (2,1) & (2,2) & (2,3) & (1,4) \\
		&     & extended SOV \Citealp{xing2020extended}   & 1.8750 & 2.3402 & 3.8522 & 4.6935 & 4.9753 & 5.8314 & 5.9292 \\
		&     & Present       & 1.8775 & 2.3425 & 3.8525 & 4.6925 & 4.9775 & 5.8325 & 5.9275 \\
		FFFF & 0.5 & Mode number  &(1,3) & (2,2) & (1,4) & (2,3) & (1,5) & (2,4) & (2,5) \\
		&     & extended SOV \Citealp{xing2020extended}   & 1.1540 & 1.4858 & 1.9157 & 2.1704 & 2.6821 & 2.7881 & 3.4093 \\
		&     & Present       & 1.1525 & 1.4875 & 1.9175 & 2.1725 & 2.6825 & 2.7875 & 3.4075 \\
		& 1   & Mode number  &(2,2) & (1,3) & (2,3) & (1,4) & (2,4) & (3,1) & (3,2) \\
		&     & extended SOV \Citealp{xing2020extended}   & 2.1311 & 2.3082 & 3.2734 & 3.8320 & 4.4962 & 4.7298 & 4.9138 \\
		&     & Present       & 2.1325 & 2.3075 & 3.2725 & 3.8325 & 4.4975 & 4.7275 & 4.9125 \\
		& 1.5 & Mode number  &(2,2) & (1,3) & (2,3) & (3,1) & (3,2) & (1,4) & (3,3) \\
		&     & extended SOV \Citealp{xing2020extended}   & 2.6277 & 3.4625 & 4.2915 & 4.7296 & 5.1259 & 5.7485 & 6.1588 \\
		&     & Present       & 2.6275 & 3.4625 & 4.2925 & 4.7275 & 5.1275 & 5.7475 & 6.1575 \\
		\bottomrule
	\end{tabular}
	\label{tab:sov3}
\end{table}
\subsection{Rotationally restrained boundary conditions}
In this subsection, rectangular orthotropic plates with rotationally restrained edges (\(k^v_\xi = k^v_\eta = \infty\)) are validated.  
The rotational stiffness coefficients are defined as: 
% 
\begin{subequations}\label{eq:rotation_coex}
	\begin{align}
		r_{\xi} &= \frac{2a k^r_{\xi}}{D_{11}}, \\
		r_{\eta} &= \frac{2b k^r_{\eta}}{D_{22}}.
	\end{align}
\end{subequations}

The first example considers a square isotropic plate with all four edges rotationally restrained. The vertical translational springs along the four edges are numerically set as \( k^v_{\xi=-1} = k^v_{\xi=1} = k^v_{\eta=-1} = k^v_{\eta=1} = 1 \times 10^{12} \ustif \). The material properties are given as \( D_{11} = D_{22} = D_3 \) and \( v_{12} = v_{21} = 0.3 \).

\Cref{tab:rot1} presents the frequency parameter \( 2a\Omega \) for different rotational stiffness coefficients \( r_{\xi} = r_{\eta} \) with values \( 0.1, 1, 10, 100, \) and \( 1000 \).  
Notably, when \( r_{\xi} = r_{\eta} = 0 \) and \( r_{\xi} = r_{\eta} = \infty \), the boundary conditions correspond to SSSS and CCCC, respectively.

Interestingly, the results indicate that the frequencies \(\Omega_x\) and \(\Omega_y\) are not strictly equal for some mode shapes under rotationally restrained boundary conditions.  
The actual frequency \(\Omega\) lies between \(\Omega_x\) and \(\Omega_y\), which may be attributed to the fact that \(\Omega_x\) and \(\Omega_y\) satisfy Rayleigh’s principle in \Cref{eq:Rayleigh}, representing the weak-form governing equations, but do not necessarily satisfy the strong-form governing equations in \Cref{eq:governing_EOM}.
For a physical problem with exact solutions, both \Cref{eq:Rayleigh,eq:governing_EOM} must be satisfied.  
If this condition is not met, applying \Cref{eq:Rayleigh} still provides a viable approach for approximating the exact solution of the plate.  
Thus, the exact frequency can be estimated as \(\Omega = (\Omega_x + \Omega_y)/2\).  
As shown in \Cref{tab:rot1}, the maximum difference between \(\Omega\) and the solutions reported in \Citealp{zhang2019new} is less than \(1.3\%\).
\Cref{fig:iso} illustrates the variation in mode shapes corresponding to the fundamental natural frequency as the rotational stiffness \(r_{\xi} = r_{\eta}\) increases from zero to \(\infty\), transitioning the boundary conditions from SSSS to CCCC.

\begin{figure}
	\centering
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{figs/iso0.png}
		\caption[]%
		{{\small }}    
		\label{fig:iso0}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.49\textwidth}  
		\centering 
		\includegraphics[width=\textwidth]{figs/iso1.png}
		\caption[]%
		{{\small }}    
		\label{fig:iso1}
	\end{subfigure}
	\vfill
	\begin{subfigure}[b]{0.49\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{figs/iso10.png}
		\caption[]%
		{{\small }}    
		\label{fig:iso10}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.49\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{figs/iso20.png}
		\caption[]%
		{{\small }}    
		\label{fig:iso20}
	\end{subfigure}
	\vskip\baselineskip
	\begin{subfigure}[b]{0.49\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{figs/iso100.png}
		\caption[]%
		{{\small}}    
		\label{fig:iso100}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.49\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{figs/isoinf.png}
		\caption[]%
		{{\small }}    
		\label{fig:isoinf}
	\end{subfigure}
	\caption[]  
	{\small The first mode shape of a square isotropic plate with all four edges rotationally restrained: (a) \(r_{\xi} = r_{\eta} = 0\); (b) \(r_{\xi} = r_{\eta} = 1\); (c) \(r_{\xi} = r_{\eta} = 10\); (d) \(r_{\xi} = r_{\eta} = 20\); (e) \(r_{\xi} = r_{\eta} = 100\); (f) \(r_{\xi} = r_{\eta} = \infty\).}  
	\label{fig:iso}  
\end{figure}

\begin{table}[!htbp]
	\centering
	\caption{The first six frequency parameters, \(2a\Omega = 2a\sqrt[4]{\rho h \omega^2/D_{11}}\), of a square isotropic plate with all four edges rotationally restrained, where \(k^r_{\xi=-1} = k^r_{\xi=1} = k^r_{\eta=-1} = k^r_{\eta=1}\).}  
	\begin{tabular}{c l c c c c c c}
		\toprule
		\multicolumn{1}{c}{} & \multicolumn{6}{c}{$2a\Omega$} \\ 
		\cmidrule(lr){3-8}
		$r_{\xi}=r_{\eta}$ & Mode & 1 & 2 & 3 & 4 & 5 & 6 \\ 
		\midrule
		0.1 & Mode number   & (1,1) & (1,2) & (2,1) & (2,2) & (1,3) & (3,1) \\
		& Ref.\Citealp{mukhopadhyay1979free} & 4.454 & 6.992 & 7.045 & 8.890  & 9.782  & 9.960 \\
		& Ref.\Citealp{zhang2019new} & 4.465 & 7.039 & 7.039 &8.897  &9.945& 9.945 \\
		& Present ($\Omega$)   & 4.463    & 7.035     & 7.035      &8.893     & 9.945     & 9.945   \\
		& Present ($\Omega_x$)   & 4.463     & 7.028     & 7.043     & 8.893     & 9.938       & 9.953  \\
		& Present ($\Omega_y$)   & 4.463    &7.043     &  7.028       & 8.893   &  9.953    & 9.938 \\ 
		&Difference (\%)& 0.044     & 0.056      & 0.056      & 0.044     &  0.000     & 0.000
		\\
		\\
		1 & Mode number   &  (1,1) & (1,2) & (2,1) & (2,2) & (3,1) & (1,3) \\
		& Ref.\Citealp{mukhopadhyay1979free} & 4.529& 7.008 &7.136 &8.936& 9.787& 10.036 \\
		& Ref.\Citealp{zhang2019new} & 4.637 &7.155 & 7.155 & 8.991 & 10.029 & 10.030 \\
		& Present ($\Omega$)   & 4.648      & 7.160   & 7.160     & 8.993    &   10.030   & 10.033   \\
		& Present ($\Omega_x$)   & 4.648     & 7.098      &7.223     & 8.993     &   10.093    & 9.968  \\
		& Present ($\Omega_y$)   & 4.648     & 7.223     & 7.098       & 8.993     &   9.968     & 10.098
		\\ 
		&Difference (\%)& 0.237    & 0.069      & 0.069      & 0.022     &  0.009     &0.029
		\\
		\\
		10 & Mode number   &  (1,1) & (1,2) & (2,1) & (2,2) & (1,3) & (3,1) \\
		& Ref.\Citealp{zhang2019new}  & 5.346 & 7.768 & 7.768 & 9.537 & 10.552 & 10.563 \\
		& Present ($\Omega$)   &5.413      & 7.835     & 7.835     & 9.598   &  10.615    & 10.618  \\
		& Present ($\Omega_x$)   & 5.413      & 7.718      & 7.953     & 9.598     & 10.448      & 10.782 \\
		& Present ($\Omega_y$)   & 5.413     & 7.953     & 7.718      & 9.598    & 10.782      & 10.453
		\\ 
		&Difference (\%)& 1.253     & 0.862      & 0.862      & 0.639     &  0.597     & 0.520  \\
		\\
		100 & Mode number   &  (1,1) & (1,2) & (2,1) & (2,2) & (1,3) & (3,1) \\
		& Ref.\Citealp{mukhopadhyay1979free} & 5.895& 8.326 &8.422 &10.167 &10.957 &11.297 \\
		& Ref.\Citealp{zhang2019new} & 5.901 & 8.442 & 8.442 & 10.253 & 11.307 & 11.333 \\
		& Present ($\Omega$)   & 5.913     & 8.450     & 8.450     & 10.258     &  11.333    & 11.333  \\
		& Present ($\Omega_x$)   & 5.913     & 8.428      & 8.473    & 10.258     & 11.293      & 11.373 \\
		& Present ($\Omega_y$)   & 5.913    & 8.473     & 8.478    & 10.258     & 11.373     & 11.293
		\\ 
		&Difference (\%)& 0.203     & 0.094      & 0.094      & 0.048     & 0.229     & 0.000 \\
		\\
		1000 & Mode number   & (1,1) & (1,2) & (2,1) & (2,2) & (1,3) & (3,1) \\
		& Ref.\Citealp{zhang2019new} & 6.011 & 8.585 & 8.585 & 10.424 & 11.495 & 11.522 \\
		& Present ($\Omega$)   & 5.988      & 8.553    & 8.553     & 10.388    &  11.470     & 11.470  \\
		& Present ($\Omega_x$)   & 5.988     & 8.553      & 8.553      & 10.388      & 11.463      & 11.478 \\
		& Present ($\Omega_y$)   & 5.988     & 8.553     & 8.553    & 10.388      & 11.478       & 11.463
		\\ 
		&Difference (\%)& 0.382    & 0.372      & 0.372      & 0.345     &  0.217     & 0.451
		 \\
		\\
		\bottomrule
	\end{tabular}
	\label{tab:rot1}
\end{table}

The next example considers a rectangular orthotropic plate with three simply supported edges (\(k^r_{\xi=-1} = k^r_{\xi=1} = k^r_{\eta=1} = 0\)), while the edge at \(\eta = -1\) is rotationally restrained. 
The material properties are consistent with those in \citealp{zhang2019new}, where \(2D_{11} = 2D_{22} = D_3\) and \(\nu_{12} = \nu_{21} = 0.3\).  
\Cref{tab:oth2} shows the fundamental frequency results for different length ratios (\(b/a\)), comparing them with those reported in \citealp{zhang2019new}. 
The maximum observed difference is $0.8\%$ when \(r_{\eta=-1} = 10\). 
Furthermore, \Cref{fig:oth} shows how the fundamental mode shape of the square orthotropic plate evolves as the rotational spring stiffness \(k^r_{\eta=-1}\) increases.

In certain numerical calculations involving rotationally restrained boundary conditions, the variables $\alpha_1$ and $\alpha_2$ may take complex values rather than being purely real.  
Consequently, the mode shape coefficients $A_1$, $A_2$, $B_1$, and $B_2$ become complex-valued, leading to $\mathbf{R}$ and $\mathbf{Q}^{-1}$ being complex matrices.  
However, the mode shapes $\phi(\xi)$ and $\psi(\eta)$ remain real-valued, and the dynamic stiffness matrix $\mathbf{K} = \mathbf{R}\mathbf{Q}^{-1}$ is a real symmetric matrix.
Thus, the frequency $\Omega$ can be obtained by solving $\mathbf{K}$ using the refined W-W algorithm provided in this study, which avoids solving the eigenvalue equations in both the real and complex domains.

\begin{table}[!htbp]  
	\centering
	\caption{Fundamental frequency parameter \(2a\Omega = 2a\sqrt[4]{\rho h \omega^2/D_{11}}\) of rectangular orthotropic plates with three edges simply supported (\(k^r_{\xi=-1} = k^r_{\xi=1} = k^r_{\eta=1} = 0\)) and the edge at \(\eta = -1\) rotationally restrained.}
	\begin{tabular}{c c c c c c c }
		\toprule
		\multicolumn{2}{c}{} & \multicolumn{4}{c}{$2a\Omega$} & \\ 
		\cmidrule(lr){3-7}
		$b/a$ & $r_{\eta=-1}$ & Ref.\Citealp{zhang2019new} & Present ($\Omega$) & Present ($\Omega_x$) & Present ($\Omega_y$) & Difference (\%) \\ 
		\midrule
		0.5 & 0         & 7.530 & 7.523 & 7.523 & 7.523 & 0.092 \\ 
		& 1         & 7.690 & 7.700 & 7.588 & 7.813 & 0.130 \\ 
		& 10        & 8.250 & 8.308 & 8.198 & 8.418 & 0.703 \\ 
		& $\infty$  & 8.705 & 8.695 & 8.695 & 8.695 & 0.114 \\ 
		\\
		1.0 & 0         & 4.917 & 4.918 & 4.918 & 4.918 & 0.020 \\ 
		& 1         & 4.954 & 4.960 & 4.933 & 4.988 & 0.121 \\ 
		& 10        & 5.114 & 5.128 & 5.088 & 5.168 & 0.273 \\ 
		& $\infty$  & 5.289 & 5.278 & 5.278 & 5.278 & 0.207 \\ 
		\\
		1.5 & 0         & 4.126 & 4.128 & 4.128 & 4.128 & 0.048 \\ 
		& 1         & 4.139 & 4.138 & 4.128 & 4.148 & 0.024 \\ 
		& 10        & 4.202 & 4.208 & 4.188 & 4.228 & 0.142 \\ 
		& $\infty$  & 4.292 & 4.288 & 4.288 & 4.288 & 0.093 \\ 
		\bottomrule
	\end{tabular}
	\label{tab:oth2}
\end{table}
\begin{figure}
	\centering
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{figs/otho0.png}
		\caption[]%
		{{\small }}    
		\label{fig:otho0}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.49\textwidth}  
		\centering 
		\includegraphics[width=\textwidth]{figs/otho1.png}
		\caption[]%
		{{\small }}    
		\label{fig:otho1}
	\end{subfigure}
	\vfill
	\begin{subfigure}[b]{0.49\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{figs/otho10.png}
		\caption[]%
		{{\small }}    
		\label{fig:otho10}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.49\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{figs/otho20.png}
		\caption[]%
		{{\small }}    
		\label{fig:otho20}
	\end{subfigure}
	\vskip\baselineskip
	\begin{subfigure}[b]{0.49\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{figs/otho100.png}
		\caption[]%
		{{\small}}    
		\label{fig:otho100}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.49\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{figs/othoinf.png}
		\caption[]%
		{{\small }}    
		\label{fig:othoinf}
	\end{subfigure}
	\caption[]  
	{\small The first mode shape of a square orthotropic plate with the edge at \(\eta=-1\) rotationally restrained: (a) \(r_{\eta=-1} = 0\); (b) \(r_{\eta=-1} = 1\); (c) \(r_{\eta=-1} = 10\); (d) \(r_{\eta=-1} = 20\); (e) \(r_{\eta=-1} = 100\); (f) \(r_{\eta=-1} = \infty\).}  
	\label{fig:oth}  
\end{figure}
\FloatBarrier
\section{Conclusion}
In this study, the dynamic stiffness matrix (DSM) based on the extended separation-of-variable (SOV) mode functions has been developed for the vibration analysis of an orthotropic rectangular plate with general homogeneous boundary conditions.

Based on the Rayleigh quotient, the governing equation of the plate, along with the shear force and bending moment equilibrium related to the boundary conditions, are derived.  
The extend-SOV type solutions obtained from the governing equation are then used to develop the dynamic stiffness matrices by applying the boundary conditions.
Instead of solving eigenvalue equations involving highly nonlinear and transcendental functions derived from the determinant of the dynamic stiffness matrix, a refined W-W algorithm based on the 'hypothetical structure method' is developed to address this eigenvalue problem.
The challenge of determining the fully clamped frequencies using the W-W algorithm is resolved by finding the simply supported frequencies, whose closed-form expression can be easily derived based on the SOV method.  
Due to the improved W-W algorithm and the concise SOV-form solutions, the process of solving the dynamic stiffness matrix becomes more systematic and efficient.

Classical boundary conditions, such as guided, simply supported, clamped, and free edges, can be realized by setting the translational springs (\(k^v_\xi\)) and rotational springs (\(k^r_\xi\)) along the plate edges to either zero or infinity.  
Numerical results confirm that accurate solutions are obtained for these boundary conditions.  
Despite some approximations in certain elastically restrained boundary conditions, the maximum percentage error across all numerical experiments remains within $1.25\%$.  
This may occur because the SOV-form solutions used are derived from the weak-form governing equation, which is based on Rayleigh's principle.

Since the SOV-form solution \(\phi(\xi) \psi(\eta)\) consists of only a single term, unlike the infinite series expansions used in the traditional DSM, each eigenvalue solution can be explicitly expressed.  
This suggests the potential for obtaining concise and closed-form solutions for assembled plate structures compared to traditional DSM methods.

\FloatBarrier
\begin{appendices}
\numberwithin{equation}{section}
\renewcommand{\theequation}{\thesection.\arabic{equation}}
\section{Integral parameters}\label{appendA}
The integral parameters \( S_1, S_2, S_3, \) and \( S_4 \) are defined as follows:
%
\begin{equation}\label{eq:inte_phi}
	\begin{aligned}
		S_1 &= \int_{0}^{1} \psi^2 \, d\eta \\
		&= (B_1^2 + B_2^2 - B_3^2 + B_4^2) 
		+ \frac{-B_1^2 + B_2^2}{2\alpha_2} \sin(2\alpha_2) 
		+ \frac{B_3^2 + B_4^2}{2\beta_2} \sinh(2\beta_2) \\
		&\quad + \frac{4(\alpha_2 B_2B_4 + \beta_2 B_1B_3)}{\alpha_2^2 + \beta_2^2} \sin(\alpha_2) \cosh(\beta_2) \\
		&\quad + \frac{4(-\alpha_2 B_1B_3 + \beta_2 B_2B_4)}{\alpha_2^2 + \beta_2^2} \cos(\alpha_2) \sinh(\beta_2).
	\end{aligned}
\end{equation}
%
\begin{equation}\label{eq:inte_dphi2}
\begin{split}
	S_2 &= \int_{0}^{1} \left( \psi \frac{d^2 \psi}{d \eta^2} \right) d \eta \\
	&= \left( -\alpha_2^2 B_1^2 - \alpha_2^2 B_2^2 - \beta_2^2 B_3^2 + \beta_2^2 B_4^2 \right) \\
	&\quad + \frac{\alpha_2 (B_1^2 - B_2^2)}{2} \sin(2 \alpha_2) 
	 + \frac{\beta_2 (B_3^2 + B_4^2)}{2} \sinh(2 \beta_2) \\
	&\quad + \frac{2(-\alpha_2^2 + \beta_2^2) (\alpha_2 B_2 B_4 + \beta_2 B_1 B_3)}{\alpha_2^2 + \beta_2^2} \sin(\alpha_2) \cosh(\beta_2) \\
	&\quad + \frac{2(-\alpha_2^2 + \beta_2^2) (-\alpha_2 B_1 B_3 + \beta_2 B_2 B_4)}{\alpha_2^2 + \beta_2^2} \cos(\alpha_2) \sinh(\beta_2).
\end{split}
\end{equation}
%
\begin{equation}\label{eq:inte_dphi3}
	\begin{aligned}
		S_3 &= \int_{0}^{1} \left(\frac{d\psi}{d\eta}\right)^2 \, d\eta \\
		&= \alpha_2^2 B_1^2 + \alpha_2^2 B_2^2 + \beta_2^2 B_3^2 - \beta_2^2 B_4^2 \\
		&\quad + \frac{\alpha_2 (B_1^2 - B_2^2)}{2} \sin(2\alpha_2) 
		 + \frac{\beta_2 (B_3^2 + B_4^2)}{2} \sinh(2\beta_2) \\
		&\quad + \frac{4 \alpha_2 \beta_2 (\alpha_2 B_1 B_3 - \beta_2 B_2 B_4)}{\alpha_2^2 + \beta_2^2} \sin(\alpha_2) \cosh(\beta_2) \\
		&\quad + \frac{4 \alpha_2 \beta_2 (\alpha_2 B_2 B_4 + \beta_2 B_1 B_3)}{\alpha_2^2 + \beta_2^2} \cos(\alpha_2) \sinh(\beta_2).
	\end{aligned}
\end{equation}
%
\begin{equation}\label{eq:inte_dphi4}
	\begin{split}
		S_4 &= \int_{0}^{1} \left( \frac{d^2 \psi}{d \eta^2} \right)^2 d \eta \\
		&= \left( \alpha_2^4 B_1^2 + \alpha_2^4 B_2^2 - \beta_2^4 B_3^2 + \beta_2^4 B_4^2 \right) \\
		&\quad + \frac{\alpha_2^3 (-B_1^2 + B_2^2)}{2} \sin(2 \alpha_2)
		+ \frac{\beta_2^3 (B_3^2 + B_4^2)}{2} \sinh(2 \beta_2) \\
		&\quad + \frac{4 \alpha_2^2 \beta_2^2 (-\alpha_2 B_2 B_4 - \beta_2 B_1 B_3)}{\alpha_2^2 + \beta_2^2} \sin(\alpha_2) \cosh(\beta_2) \\
		&\quad + \frac{4 \alpha_2^2 \beta_2^2 (\alpha_2 B_1 B_3 - \beta_2 B_2 B_4)}{\alpha_2^2 + \beta_2^2} \cos(\alpha_2) \sinh(\beta_2)
	\end{split}
\end{equation}
%
The integral parameters \( T_1 \), \( T_2 \), \( T_3 \), and \( T_4 \) can be obtained by replacing \( B_1 \) to \( B_4 \) by \( A_1 \) to \( A_4 \), respectively, and \( \alpha_2 \) and \( \beta_2 \) by \( \alpha_1 \) and \( \beta_1 \), respectively.

\end{appendices}
\FloatBarrier
\bibliographystyle{elsarticle-harv}
\bibliography{bibliography}

\end{document}

### 2025-03-31 figs/general_plate_tikz.tex
Update local file

\begin{tikzpicture}[yscale=1]
	\tikzset{
	pics/boundary-box/.style={
		code={
			\begin{scope}[shift={(0mm,0mm)}]
				\definecolor{fc}{RGB}{204,204,204}
				\draw [fill=none, draw=black, line width=0.6mm] (000.0mm,0.0mm)
				-- ++(0.0mm,60.0mm)
				-- ++(-60.0mm,0.0mm)
				-- ++(0.0mm,-60.0mm)  % Adjusted the vertical length to 20mm
				-- ++(60.0mm,0.0mm)  % Adjusted the vertical length to 20mm
				-- cycle;
				\node [black, anchor=west, font=\fontsize{100}{0}\selectfont\bfseries] at (-40mm, 30mm) { $\textbf{?}$ };
			\end{scope}
		}
	}
}
\tikzset{
	pics/Mass-circle/.style={
		code={
			\draw[fill=gray!30, draw=black, line width=0.6mm] (0mm, 0mm) circle [radius=38mm];
		}
	}
}
\tikzset{
	pics/Beam/.style={
		code={\draw [fill=none,draw=black,line width=10.0mm] (000.0mm,0.mm)
			-- ++(600.0mm,0.0mm)
			;
			%% curvature
			\draw[fill=none, draw=gray, line width=4.0mm, dash pattern=on 20pt off 20pt] (000.0mm,0.mm) .. controls (200mm,-100mm) and (300mm,-50mm) .. (600.0mm,0mm);

		}
	}
}
\tikzset{
	pics/Spring-damp/.style={
		code={\begin{scope}[cm={0.4,0,0,0.4,(40.0mm,0mm)}]
				\draw [fill=none,draw=black,line width=2.0mm] (145.0mm,707.4mm)
				-- ++(0.0mm,33.0mm)
				;
				\draw [fill=none,draw=black,line width=2.0mm] (120.0mm,867.4mm)
				-- ++(50.0mm,-15.0mm)
				;
				\draw [fill=none,draw=black,line width=2.0mm] (170.0mm,852.4mm)
				-- ++(-50.0mm,-15.0mm)
				;
				\draw [fill=none,draw=black,line width=2.0mm] (120.0mm,837.4mm)
				-- ++(50.0mm,-15.0mm)
				;
				\draw [fill=none,draw=black,line width=2.0mm] (170.0mm,822.4mm)
				-- ++(-50.0mm,-15.0mm)
				;

				\draw [fill=none,draw=black,line width=2.0mm] (120.0mm,807.4mm)
				-- ++(50.0mm,-15.0mm)
				;

				\draw [fill=none,draw=black,line width=2.0mm] (170.0mm,792.4mm)
				-- (120.0mm,777.4mm)
				;

				\draw [fill=none,draw=black,line width=2.0mm] (120.0mm,777.4mm)
				-- ++(50.0mm,-15.0mm)
				;

				\draw [fill=none,draw=black,line width=2.0mm] (170.0mm,762.4mm)
				-- ++(-50.0mm,-15.0mm)
				;

				\draw [fill=none,draw=black,line width=2.0mm] (145.0mm,875.4mm)
				-- ++(-25.0mm,-8.0mm)
				;

				\draw [fill=none,draw=black,line width=2.0mm] (120.0mm,747.4mm)
				-- ++(25.0mm,-7.0mm)
				;

				\draw [fill=none,draw=black,line width=2.0mm] (145.0mm,875.4mm)
				-- (145.0mm,907.4mm)
				;
			\end{scope}
			% horizontal line above mass left
			\draw [fill=none,draw=black,line width=2.0mm] (58.0mm,363mm)
			-- ++(40.0mm,0.0mm)
			;

			%% damping left
			\begin{scope}[cm={0.4,0,0,-0.4,(0.0mm,645.9mm)}]
				\draw [fill=none,draw=black,line width=2.0mm] (115.0mm,827.7mm)
				-- ++(0.0mm,-35.3mm)
				-- (175.0mm,792.4mm)
				-- ++(0.0mm,35.0mm)
				;

				\draw [fill=none,draw=black,line width=2.0mm] (145.0mm,707.4mm)
				-- ++(0.0mm,85.0mm)
				;

				\draw [fill=none,draw=black,line width=2.0mm] (123.0mm,807.4mm)
				-- ++(44.0mm,0.0mm)
				;

				\draw [fill=none,draw=black,line width=2.0mm] (145.0mm,807.4mm)
				-- ++(0.0mm,100.0mm)
				;
			\end{scope}

			%% suspension arrow left
			\draw [fill=none,draw=black,line width=2.0mm] (58.0mm,283.4mm)
			-- ++(40.0mm,0.0mm)
			;
			\draw [fill=none,draw=black,line width=2.0mm] (78.0mm,363.4mm)
			-- ++(0mm,27.0mm)
			;
			%% vertical line upp
			\draw [fill=none,draw=black,line width=2.0mm] (78.0mm,283.4mm)
			-- ++(0.0mm,-30.0mm)
			;
		}
	}
}
\tikzset{
	pics/beam-Spring/.style={
		code={\begin{scope}[cm={0.4,0,0,0.4,(-38.0mm,-256.4mm)}]
				\draw [fill=none,draw=black,line width=2.0mm] (145.0mm,782.4mm)
				-- ++(0.0mm,-60.0mm)
				;
				\draw [fill=none,draw=black,line width=2.0mm] (120.0mm,867.4mm)
				-- ++(50.0mm,-15.0mm)
				;
				\draw [fill=none,draw=black,line width=2.0mm] (170.0mm,852.4mm)
				-- ++(-50.0mm,-15.0mm)
				;
				\draw [fill=none,draw=black,line width=2.0mm] (120.0mm,837.4mm)
				-- ++(50.0mm,-15.0mm)
				;
				\draw [fill=none,draw=black,line width=2.0mm] (170.0mm,822.4mm)
				-- ++(-50.0mm,-15.0mm)
				;
				\draw [fill=none,draw=black,line width=2.0mm] (120.0mm,807.4mm)
				-- ++(50.0mm,-15.0mm)
				;
				\draw [fill=none,draw=black,line width=2.0mm] (170.0mm,792.4mm)
				-- (145.0mm,782.4mm)
				;

				\draw [fill=none,draw=black,line width=2.0mm] (145.0mm,875.4mm)
				-- ++(-25.0mm,-8.0mm)
				;

				\draw [fill=none,draw=black,line width=2.0mm] (145.0mm,875.4mm)
				-- (145.0mm,950.4mm)
				;
			\end{scope}

		}
	}
}
\tikzset{
	pics/beam-arrow/.style={
		code={% bridge curve property 
			\draw [fill=none,draw=black,line width=2.0mm] (380.0mm,32.0mm)
			.. controls ++(85.0mm,-8.0mm) and ++(-60.0mm,-6.0mm) .. ++(135.0mm,-32.0mm)
			;
			%% arraw of bridge curve property 
			\draw [->, black, line width=6mm, >=stealth, shorten >=1pt] (515.0mm,0mm) -- ++(0.5,0); % Draws the arrowhead separately

		}
	}
}
\tikzset{
	pics/beam-prop-arrow/.style={
		code={% bridge curve deflection yx
			\draw [fill=none,draw=black,line width=2.0mm] (440.0mm,0.0mm)
			.. controls ++(85.0mm,5.0mm) and ++(-60.0mm,4.0mm) .. ++(135.0mm,36.0mm)
			;
			%% arraw of bridge curve deflection yx
			\draw [black, line width=2mm] (570.0mm,36.0mm) -- (580.0mm,36.0mm);
			\draw [->, black, line width=6mm, >=stealth, shorten >=1pt] (580.0mm,36.0mm) -- ++(0.5,0); % Draws the arrowhead separately

		}
	}
}
\tikzset{
	pics/mass-defle/.style={
		code={%% arraw of vehicle deflection yv 
			\draw [->,fill=none,draw=black,line width=2.50mm] (0.0mm,25.0mm)
			-- (30.0mm,25.0mm)
			-- (30.0mm,65.3mm)
			;			
		}
	}
}
\tikzset{
	pics/floor/.style={
		code={
			%  left
			\begin{scope}[cm={0.4,0,0,-0.4,(-42.0mm,377.0mm)}]
				\draw [fill=none,draw=black,line width=2.0mm] (30.0mm,939mm)
				-- (190.0mm,939mm)
				;
				\draw [fill=none,draw=black,line width=2.0mm] (50.0mm,939mm)
				-- (30.0mm,965mm)
				;
				\draw [fill=none,draw=black,line width=2.0mm] (80.0mm,939mm)
				-- (60.0mm,965mm)
				;
				\draw [fill=none,draw=black,line width=2.0mm] (110.0mm,939mm)
				-- (90.0mm,965mm)
				;
				\draw [fill=none,draw=black,line width=2.0mm] (140.0mm,939mm)
				-- (120.0mm,965mm)
				;
				\draw [fill=none,draw=black,line width=2.0mm] (170.0mm,939mm)
				-- (150.0mm,965mm)
				;
			\end{scope}

		}
	}
}
\tikzset{
	pics/beam-rotation/.style={
		code={
			%%% arc representing rotation or deflection
			\draw [-,fill=none,draw=black,line width=2.00mm] 
			(0.0mm,25.0mm) arc [start angle=270, end angle=90, radius=30mm];
			\draw [fill=none,draw=black,line width=2.5mm] (0.0mm,60mm)
			-- (0.0mm,100mm)
			;

			\draw [fill=none,draw=black,line width=2.5mm] (0.0mm,70mm)
			-- (15.0mm,75mm)
			;
			\draw [fill=none,draw=black,line width=2.5mm] (0.0mm,80mm)
			-- (15.0mm,85mm)
			;
			\draw [fill=none,draw=black,line width=2.5mm] (0.0mm,90mm)
			-- (15.0mm,95mm)
			;

		}
	}
}
\tikzset{
	pics/beam-rotation-bot/.style={
		code={
			%%% arc representing rotation or deflection
			\draw [-,fill=none,draw=black,line width=2.00mm] 
			(0.0mm,25.0mm) arc [start angle=270, end angle=50, radius=30mm];
			\draw [fill=none,draw=black,line width=2.5mm] (0.0mm,60mm)
			-- (40.0mm,100mm)
			;

			\draw [fill=none,draw=black,line width=2.5mm] (10mm,70mm)
			-- (20.0mm,60mm)
			;
			\draw [fill=none,draw=black,line width=2.5mm] (20mm,80mm)
			-- (30.0mm,70mm)
			;
			\draw [fill=none,draw=black,line width=2.5mm] (30mm,90mm)
			-- (40.0mm,80mm)
			;

		}
	}
}
\tikzset{
	pics/Rectangular-Plate/.style={
		code={
			% Define the vertices of the rectangular plate
			\coordinate (A) at (0, 1, 0);
			\coordinate (B) at (90, 1, 0);
			\coordinate (C) at (90, 2, 0);
			\coordinate (D) at (0, 2, 0);
			\coordinate (A') at (0, 1, 80);
			\coordinate (B') at (90, 1, 80);
			\coordinate (C') at (90, 2, 80);
			\coordinate (D') at (0, 2, 80);
			\coordinate (E) at (0, 0, 0);
			\coordinate (F) at (90, 0, 0);
			\coordinate (E') at (0, 0, 80);
			\coordinate (F') at (90, 0, 80);

			% Fill the surface AA'B'B with gray and transparent
			\fill[gray!50, fill opacity=0.2] (A) -- (A') -- (B') -- (B) -- cycle;

			% Draw the edges of the bottom face
			\draw[black, line width=2mm, dashed, dash pattern=on 10mm off 5mm] (A) -- (B); % AB dashed
			\draw[black, line width=2mm] (B) -- (C) -- (D); % Remaining edges solid
			\draw[black, line width=2mm, dashed, dash pattern=on 10mm off 5mm] (D) -- (A); % AD dashed
			\draw[black, line width=2mm, dashed, dash pattern=on 10mm off 5mm] (A) -- (E); % AB dashed
			\draw[black, line width=2mm, dashed, dash pattern=on 10mm off 5mm] (F) -- (E); % AB dashed
			\draw[black, line width=2mm, dashed, dash pattern=on 10mm off 5mm] (F) -- (B); % AB dashed
			\draw[black, line width=2mm, dashed, dash pattern=on 10mm off 5mm] (E') -- (E); % AB dashed

			% Draw the edges of the top face
			\draw[black, line width=2mm] (A') -- (B') -- (C') -- (D') -- cycle;

			% Draw the vertical edges connecting the bottom and top faces
			\draw[black, line width=2mm, dashed, dash pattern=on 10mm off 5mm] (A) -- (A'); % AA' dashed
			\draw[black, line width=2mm] (B) -- (B');
			\draw[black, line width=2mm] (C) -- (C');
			\draw[black, line width=2mm] (D) -- (D');
			\draw[black, line width=2mm] (F) -- (F');
			\draw[black, line width=2mm] (A') -- (E');
			\draw[black, line width=2mm] (B') -- (F');
			\draw[black, line width=2mm] (F') -- (E');
		}
	}
}

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% drawing
	%\pic at (700mm,0mm) {boundary-box};
	%\pic at (40mm,0mm) {boundary-box};
	\pic at (20mm,-25mm) {beam-rotation};
	\pic at (0mm,-120mm) {beam-Spring};
	\pic at (20mm,-90mm) {floor};
	\pic at (-60mm,-105mm) {beam-rotation};
	\pic at (-80mm,-200mm) {beam-Spring};
	\pic at (-60mm,-170mm) {floor};
	\pic at (-140mm,-185mm) {beam-rotation};
	\pic at (-160mm,-280mm) {beam-Spring};
	\pic at (-140mm,-250mm) {floor};

	%%%%%%%%%%%%
	\pic[xscale=-1] at (900mm,-35mm) {beam-rotation};
	\pic at (880mm,-130mm) {beam-Spring};
	\pic at (900mm,-100mm) {floor};
	\pic[xscale=-1] at (820mm,-115mm) {beam-rotation};
	\pic at (810mm,-210mm) {beam-Spring};
	\pic at (820mm,-180mm) {floor};
	\pic[xscale=-1] at (730mm,-205mm) {beam-rotation};
	\pic at (720mm,-300mm) {beam-Spring};
	\pic at (730mm,-270mm) {floor};
%%%%%%%%%%%%%%%%%%%%%%%%
	\pic[xscale=-1] at (160mm,35mm) {beam-rotation-bot};
	\pic at (140mm,-65mm) {beam-Spring};
	\pic at (160mm,-35mm) {floor};
	\pic[xscale=-1] at (360mm,35mm) {beam-rotation-bot};
	\pic at (340mm,-65mm) {beam-Spring};
	\pic at (360mm,-35mm) {floor};
	\pic[xscale=-1] at (560mm,35mm) {beam-rotation-bot};
	\pic at (540mm,-65mm) {beam-Spring};
	\pic at (560mm,-35mm) {floor};
	\pic[xscale=-1] at (760mm,35mm) {beam-rotation-bot};
	\pic at (740mm,-65mm) {beam-Spring};
	\pic at (760mm,-35mm) {floor};
	%%%%%%%%%
	\pic[xscale=1] at (510mm,-275mm) {beam-rotation-bot};
	\pic at (490mm,-375mm) {beam-Spring};
	\pic at (510mm,-345mm) {floor};
	\pic[xscale=1] at (310mm,-275mm) {beam-rotation-bot};
	\pic at (290mm,-375mm) {beam-Spring};
	\pic at (310mm,-345mm) {floor};
	\pic[xscale=1] at (110mm,-275mm) {beam-rotation-bot};
	\pic at (90mm,-375mm) {beam-Spring};
	\pic at (110mm,-345mm) {floor};
	\pic[xscale=1] at (-90mm,-275mm) {beam-rotation-bot};
	\pic at (-110mm,-375mm) {beam-Spring};
	\pic at (-90mm,-345mm) {floor};

	%%%%%%%%
    \pic at (3mm, 6, 3) {Rectangular-Plate};

    %%%%%%%%%%%%%%%%%%%%%
    %%% 2b
    \begin{scope}[shift={(-35mm,-180.0mm)}]
    	\draw[{Latex[length=18mm, width=12mm]}-{Latex[length=18mm, width=12mm]}, fill=none, draw=black, line width=2.5mm] 
    	(700mm,-270.0mm) -- (1010mm,60.0mm);
    	\draw [-,fill=none,draw=black,line width=2.mm] (700mm,-150.0mm)
    	-- (700mm,-300.0mm)
    	;
    	\draw [-,fill=none,draw=black,line width=2.mm] (1010mm,90.0mm)
    	-- (1010mm,000.0mm)
    	;
    \end{scope}
    %%% 2a
    \begin{scope}[shift={(-35mm,150.0mm)}]
    	\draw[{Latex[length=18mm, width=12mm]}-{Latex[length=18mm, width=12mm]}, fill=none, draw=black, line width=2.5mm] 
    	 (110mm,50.0mm)
    	-- (1010mm,50.0mm);
    	\draw [-,fill=none,draw=black,line width=2.mm] (110mm,70.0mm)
    	-- (110mm,-30.0mm)
    	;
    	\draw [-,fill=none,draw=black,line width=2.mm] (1010mm,70.0mm)
    	-- (1010mm,-30.0mm)
    	;
    \end{scope}
        %%% h
    \begin{scope}[shift={(-35mm,150.0mm)}]
    	\draw[{Latex[length=12mm, width=8mm]}-{Latex[length=12mm, width=8mm]}, fill=none, draw=black, line width=2.5mm] 
    	(-250mm,-385.0mm)
    	-- (-250mm,-415.0mm);
    	\draw [-,fill=none,draw=black,line width=2.mm] (-260mm,-388.0mm)
    	-- (-200mm,-388.0mm)
    	;
    	\draw [-,fill=none,draw=black,line width=2.mm] (-260mm,-410.0mm)
    	-- (-200mm,-410.0mm)
    	;
    \end{scope}
     %%% xyz
    \begin{scope}[shift={(30mm,-150.0mm)}]
    	\draw[-{Latex[length=18mm, width=12mm]}, fill=none, draw=black, line width=2.5mm, dashed, dash pattern=on 10mm off 5mm] 
    	(360mm,50.0mm) -- (460mm,50.0mm);
    	\draw[-{Latex[length=18mm, width=12mm]}, fill=none, draw=black, line width=2.5mm] 
    	(360mm, 50.0mm) -- (360mm, 150.0mm); 		
    	\draw[-{Latex[length=18mm, width=12mm]}, fill=none, draw=black, line width=2.5mm, dashed, dash pattern=on 10mm off 5mm] 
    	(360mm, 50.0mm) -- (420mm, 110.0mm);

    \end{scope}
	%%%%%%%%%%%%%%%% text

	\begin{scope}[shift={(16.9mm,-8.4mm)}]
		\node [black,anchor=west,font=\fontsize{140}{0}\selectfont] at (340mm,-110mm) { $o$ };
		\node [black,anchor=west,font=\fontsize{140}{0}\selectfont] at (460mm,-120mm) { $x$ };
		\node [black,anchor=west,font=\fontsize{140}{0}\selectfont] at (430mm,-20mm) { $y$ };
		\node [black,anchor=west,font=\fontsize{140}{0}\selectfont] at (380mm,30mm) { $z$ };
		\node [black,anchor=west,font=\fontsize{140}{0}\selectfont] at (460mm,240mm) { $2a$ };
		\node [black,anchor=west,font=\fontsize{140}{0}\selectfont] at (860mm,-250mm) { $2b$ };
		\node [black,anchor=west,font=\fontsize{140}{0}\selectfont] at (-350mm,-240mm) { $h$ };
		\node [black,anchor=west,font=\fontsize{140}{0}\selectfont] at (-50mm,-140mm) { $k^v_{\xi=-1}$ };
		\node [black,anchor=west,font=\fontsize{140}{0}\selectfont] at (-200mm,20mm) { $k^r_{\xi=-1}$ };
		\node [black,anchor=west,font=\fontsize{140}{0}\selectfont] at (750mm,-220mm) { $k^v_{\xi=1}$ };
	    \node [black,anchor=west,font=\fontsize{140}{0}\selectfont] at (640mm,-50mm) { $k^r_{\xi=1}$ };
	    \node [black,anchor=west,font=\fontsize{140}{0}\selectfont] at (320mm,-300mm) { $k^v_{\eta=-1}$ };
		\node [black,anchor=west,font=\fontsize{140}{0}\selectfont] at (200mm,-150mm) { $k^r_{\eta=-1}$ };
		\node [black,anchor=west,font=\fontsize{140}{0}\selectfont] at (170mm,0mm) { $k^v_{\eta=1}$ };
		\node [black,anchor=west,font=\fontsize{140}{0}\selectfont] at (160mm,150mm) { $k^r_{\eta=1}$ };
	\end{scope}
\end{tikzpicture}

### 2025-05-13 Paper7.tex
SM revise

@@
 \begin{frontmatter}
-\title{The dynamic stiffness matrix based on the extended separation-of-variables type solutions for the free vibration of orthotropic rectangular thin plates}
+\title{The dynamic stiffness matrix based on the extended separation-of-variables type solution for the free vibration of orthotropic rectangular thin plates}
 \author[1]{Shiyi Mei}\ead{shiyi.mei1@monash.edu}
@@
 \begin{abstract}
-The dynamic stiffness matrix based on the extended separation-of-variables mode functions is developed for the free vibration analysis of an orthotropic rectangular thin plate with general homogeneous boundary conditions.
-The governing differential equation and boundary conditions are derived from Rayleigh’s principle.  
-Based on the boundary conditions, the dynamic stiffness matrix is formulated and solved using an improved Wittrick-Williams algorithm.  
-In this improved algorithm, simply supported frequencies are required instead of fully clamped frequencies, and the closed-form expression for the simply supported frequencies is provided, enhancing the efficiency and systematicity of solving the eigenvalue problem.
-The proposed method is validated by the numerical experiments.
+The dynamic stiffness matrix (DSM) based on the extended separation-of-variables (SOV) type mode solution is developed for the free vibration analysis of an orthotropic rectangular thin plate with general homogeneous boundary conditions.
+The method combines the advantages of the DSM method and the SOV method.
+The SOV type solution satisfies the governing differential equation derived from Rayleigh’s principle and is used to formulate the dynamic stiffness matrices.
+Owing to the characteristics of the SOV type solution, the fully clamped boundary condition problem associated with the Wittrick–Williams algorithm is resolved. 
+The enhanced algorithm is further proposed to solve dynamic stiffness matrices, rather than solving eigenvalue equations.
+A numerical technique for mode shape computation is also introduced.
+The accuracy of the proposed method is validated through numerical experiments.
+
 \end{abstract}
@@
 Despite being a powerful method for the dynamic analysis of plate assemblies, the finite element method (FEM) requires a sufficient number of elements and is computationally expensive to accurately capture higher-order modes.
-Thus, the DSM method is developed as an accurate and efficient analytical approach to alternatively solve complex plate structures \cite{boscolo2011dynamic,fazzolari2013exact}. 
+Thus, the DSM method was developed as an accurate and efficient analytical approach to alternatively solve complex plate structures \cite{boscolo2011dynamic,fazzolari2013exact}. 
 The DSM can be considered as an analytical FEM since the mode functions of the plate are expressed by analytical solutions, where Levy-type solution \cite{ghorbel2015dynamic} or components of infinite Fourier series \cite{banerjee2015dynamic,liu2016free} are applied.
@@
 However, these approaches are computationally expensive and complex, posing a significant obstacle to the wider adoption and application of the DSM method based on the W-W algorithm \cite{han2018improved}.
-To resolve the fully clamped plate problem, \citet{liu2015exact} suggested that the fully clamped frequencies can be indirectly obtained from the simply supported plate problem, where the Navier solution serves as the analytical solution.
+To resolve the fully clamped plate problem, \citet{liu2015exact} suggested that the frequencies can be indirectly obtained from the simply supported plate problem, where the Navier solution serves as the analytical solution.
 This provides a significant enhancement to the W-W algorithm, increasing the efficiency of applying DSM methods.
-However, since infinite-term series expansion-based solutions are used for plate analysis instead of explicit and closed-form solutions, a sufficient number of truncation terms is required to ensure accuracy and capture the necessary modal degrees.
+However, the solutions are not explicit and closed-form, but are expressed in an infinite series form, where a sufficient number of truncation terms is required to ensure accuracy.
 
@@
 The mode shape function has a separable form, $\phi(x) \psi(y)$, requiring only one $\phi(x)$ and one $\psi(y)$ for each mode order, allowing each eigenvalue equation to be explicitly expressed.
-However, this SOV method is not suitable to deal with plate with free boundary conditions.
-Therefore, an extended SOV method \cite{xing2018overall, xing2020extended} based on the Rayleigh quotient is proposed to accommodate plates with all classical boundary conditions, i.e., simply supported, clamped, guided, and free.
+However, this SOV method is not suitable to deal with plates with free boundary conditions.
+Therefore, an extended SOV method \cite{xing2018overall, xing2020extended} based on the Rayleigh quotient was proposed to accommodate plates with all four classical boundary conditions, i.e., simply supported, clamped, guided, and free.
 Based on the Rayleigh quotient model, alternative iterative and improved SOV methods have been subsequently proposed \cite{xing2020improved}.
-Although SOV methods provide concise closed-form analytical solutions, solving the highly nonlinear eigenvalue equations is required.
-
-In this study, the free vibration of orthotropic plates with general boundary conditions is analyzed by extending the SOV method based on the Rayleigh quotient to obtain the solution for elastically restrained plates.
-Subsequently, dynamic stiffness matrices in both the \(x\) and \(y\) directions, derived from the SOV-form solutions, are developed to solve the eigenvalue problem.
-By applying the 'hypothetical structure method', a modified W-W algorithm is developed, requiring only the natural frequencies of the simply supported structure instead of the necessity of fully clamped frequencies.
-The concise closed-form expression for the simply supported frequencies is directly obtained from the eigenvalue equation based on the SOV method, eliminating the extensive computational effort typically required in DSM methods to determine all fully clamped frequencies within the frequency range.
-Therefore, this approach can improve the systematic and effective application of the DSM method depending on the W-W algorithm.
-Alternatively, it can also be considered as an efficient technique for solving transcendental eigenvalue equations in the SOV method.
+Although SOV methods provide concise closed-form analytical solutions, they require solving a specific set of highly nonlinear eigenvalue equations for each type of boundary condition.
+However, even when considering only the four classic homogeneous cases, it becomes evident that 55 different boundary condition combinations exist for a rectangular plate, making the process tedious.
+
+In this study, the SOV method is extended to analyze the vibrations of plates with elastically restrained edges.
+The extended SOV type solution is then employed to construct the dynamic stiffness matrices, which accommodate all general homogeneous boundary conditions.
+By taking advantage of both the SOV and DSM methods, an enhanced W-W algorithm is developed to solve the eigenvalue problem without directly solving the eigenvalue equations.
+This enhanced approach resolves the challenge of determining fully clamped frequencies, a well-known limitation in the application of the  W-W algorithm.
+In addition, a novel numerical technique has been proposed to compute the mode shape coefficients.
 
@@
 %
-where the bending stiffness parameters are defined as:
+where \( \alpha = a / b \) is the aspect ratio; \( \xi = x / a \) and \( \eta = y / b \) are the normalized coordinates,
+and the bending stiffness parameters are defined as:
 %
@@
 %
-where \( \alpha = a / b \) is the aspect ratio; \( \xi = x / a \) and \( \eta = y / b \) are the normalized coordinates.
 The separable form of the mode shape function \( w(\xi, \eta) \) is given by:
@@
 
-It should be noted that \Cref{eq:governing_EOM} represents the strong-form governing equation of the orthotropic plate, while \Cref{eq:Rayleigh} is the weak-form governing equation, with the latter being equivalent to the former.
 Based on \Cref{eq:Rayleigh}, the frequencies $\omega_x$ and $\omega_y$, corresponding to the mode shapes $\phi(\xi)$ and $\psi(\eta)$, respectively, are assumed to be independent of each other.
@@
 \subsection{Dynamic stiffness matrix corresponding to $\omega_x$}\label{sec:DSMx}
-For given general homogeneous boundary conditions, we can first assume that the mode shape $\psi(\eta)$ corresponding to the $y$ direction is known. 
+For given general homogeneous boundary conditions, we can first assume that the mode shape $\psi(\eta)$ corresponding to the $y$-direction is known. 
 Supposing the edges of the plate in both the \(x\)- and \(y\)-directions are elastically restrained by homogeneous vertical translational and rotational springs.
@@
 		U_{mag}&=U^{I}_{mag}+U^{II}_{mag}\\
-		&=\frac{ab}{2} \int_{-1}^{1} \left[ \frac{D_{11}}{a^4}S_1 \left( \frac{\id^2\phi }{\id \xi^2} \right)^2 + \frac{2 D_{12}}{a^2 b^2}S_2 \frac{\id^2\phi }{\id \xi^2}\phi  + \frac{D_{22}}{b^4}S_4  \phi^2 \right.
+		&=\frac{ab}{2} \int_{-1}^{1} \left[ \frac{D_{11}}{a^4}I_1 \left( \frac{\id^2\phi }{\id \xi^2} \right)^2 + \frac{2 D_{12}}{a^2 b^2}I_2 \frac{\id^2\phi }{\id \xi^2}\phi  + \frac{D_{22}}{b^4}I_4  \phi^2 \right.
 \\
 		&\quad \left.
-+ \frac{4 D_{66}}{a^2 b^2}S_3 \left( \frac{\id \phi }{\id \xi}\right)^2 \right] \, \id\xi +abS_1 \left[\frac{k^r_{\xi=-1}}{a^3} \left( \frac{\id \phi}{\id \xi} \right)^2+ \frac{k^v_{\xi=-1}}{a} \left( \phi \right)^2\right]_{\xi=-1}\\
-		&\quad+abS_1 \left[\frac{k^r_{\xi=1}}{a^3} \left( \frac{\id \phi}{\id \xi} \right)^2+ \frac{k^v_{\xi=1}}{a} \left( \phi \right)^2\right]_{\xi=1},
++ \frac{4 D_{66}}{a^2 b^2}I_3 \left( \frac{\id \phi }{\id \xi}\right)^2 \right] \, \id\xi +abI_1 \left[\frac{k^r_{\xi=-1}}{a^3} \left( \frac{\id \phi}{\id \xi} \right)^2+ \frac{k^v_{\xi=-1}}{a} \left( \phi \right)^2\right]_{\xi=-1}\\
+		&\quad+abI_1 \left[\frac{k^r_{\xi=1}}{a^3} \left( \frac{\id \phi}{\id \xi} \right)^2+ \frac{k^v_{\xi=1}}{a} \left( \phi \right)^2\right]_{\xi=1},
 	\end{split}
@@
 	\begin{split}  
-		&S_1 = \int_{-1}^{1} \psi^2 \, \id\eta, \\  
-		&S_2 = \int_{-1}^{1} \left( \frac{\id^2 \psi}{\id \eta^2} \psi \right) \, \id\eta, \\  
-		&S_3 = \int_{-1}^{1} \left( \frac{\id \psi}{\id \eta} \right)^2 \, \id\eta, \\  
-		&S_4 = \int_{-1}^{1} \left( \frac{\id^2 \psi}{\id \eta^2} \right)^2 \, \id\eta.  
-	\end{split}  
-\end{equation}   
-%
-By taking \Cref{eq:displace_func} into account, the coefficient \(T_0\) of the kinetic energy in \Cref{eq:kine_energy_mag} for the plate can be expressed as:
+		&I_1 = \int_{-1}^{1} \psi^2 \, \id\eta, \\  
+		&I_2 = \int_{-1}^{1} \left( \frac{\id^2 \psi}{\id \eta^2} \psi \right) \, \id\eta, \\  
+		&I_3 = \int_{-1}^{1} \left( \frac{\id \psi}{\id \eta} \right)^2 \, \id\eta, \\  
+		&I_4 = \int_{-1}^{1} \left( \frac{\id^2 \psi}{\id \eta^2} \right)^2 \, \id\eta.  
+	\end{split}  
+\end{equation}   
+%
+By taking \Cref{eq:displace_func} into account, the coefficient \(T_0\) of the kinetic energy from \Cref{eq:kine_energy_mag} for the plate can be expressed as:
 %
@@
 	\begin{split}
-		T_0 = \frac{ab}{2}\rho h\iint w^2 \, \id \xi \, \id \eta = \frac{ab}{2}\rho h S_1\int_{-1}^{1} \phi^2 \, \id \xi.
-	\end{split}
-\end{equation}
-
+		T_0 = \frac{ab}{2}\rho h\iint w^2 \, \id \xi \, \id \eta = \frac{ab}{2}\rho h I_1\int_{-1}^{1} \phi^2 \, \id \xi.
+	\end{split}
+\end{equation}
+%
 Take the Rayleigh principle in the form:
@@
 %
-By substituting \Cref{eq:poten_energy_tolx2,eq:kine_energyx} into \Cref{eq:Rayleighx}, relieve \(\delta \phi\) and \(\delta\frac{\id  \phi}{\id \xi}\) in \Cref{eq:Rayleighx} by variation calculus, yielding:
+By substituting \Cref{eq:poten_energy_tolx2,eq:kine_energyx} into \Cref{eq:Rayleighx}, and relieving \(\delta \phi\) and \(\delta\frac{\id  \phi}{\id \xi}\) in \Cref{eq:Rayleighx} by variation calculus, yields:
 %
@@
 	\begin{split}
-		0 &= \int_{-1}^{1} \bigg[ \frac{D_{11}}{a^4} S_1 \frac{\id^4 \phi}{\id \xi^4} 
-		+ \bigg( \frac{2D_{12}}{a^2b^2} S_2 - \frac{4D_{66}}{a^2b^2} S_3 \bigg) \frac{\id^2 \phi}{\id \xi^2} \\
-		&\quad + \bigg( \frac{D_{22}}{b^4} S_4 - \omega_x^2 \rho h S_1 \bigg) \phi \bigg] \delta \phi \, \id \xi \\
-		&\quad + \frac{2k^v_{\xi=-1}}{a} S_1 \big(\phi \delta \phi\big)_{\xi=-1} 
-		+ \frac{2k^v_{\xi=1}}{a} S_1 \big(\phi \delta \phi\big)_{\xi=1} \\
-		&\quad + \bigg[ \bigg( \frac{4D_{66}}{a^2b^2} S_3 - \frac{D_{12}}{a^2b^2} S_2 \bigg) \frac{\id \phi}{\id \xi} 
-		- \frac{D_{11}}{a^4} S_1 \frac{\id^3 \phi}{\id \xi^3} \bigg] \delta \phi \Big|^{\xi=1}_{\xi=-1} \\
-		&\quad + \bigg( \frac{D_{12}}{a^2b^2} S_2 \phi + \frac{D_{11}}{a^4} S_1 \frac{\id^2 \phi}{\id \xi^2} \bigg) 
+		0 &= \int_{-1}^{1} \bigg[ \frac{D_{11}}{a^4} I_1 \frac{\id^4 \phi}{\id \xi^4} 
+		+ \bigg( \frac{2D_{12}}{a^2b^2} I_2 - \frac{4D_{66}}{a^2b^2} I_3 \bigg) \frac{\id^2 \phi}{\id \xi^2} \\
+		&\quad + \bigg( \frac{D_{22}}{b^4} I_4 - \omega_x^2 \rho h I_1 \bigg) \phi \bigg] \delta \phi \, \id \xi \\
+		&\quad + \frac{2k^v_{\xi=-1}}{a} I_1 \big(\phi \delta \phi\big)_{\xi=-1} 
+		+ \frac{2k^v_{\xi=1}}{a} I_1 \big(\phi \delta \phi\big)_{\xi=1} \\
+		&\quad + \bigg[ \bigg( \frac{4D_{66}}{a^2b^2} I_3 - \frac{D_{12}}{a^2b^2} I_2 \bigg) \frac{\id \phi}{\id \xi} 
+		- \frac{D_{11}}{a^4} I_1 \frac{\id^3 \phi}{\id \xi^3} \bigg] \delta \phi \Big|^{\xi=1}_{\xi=-1} \\
+		&\quad + \bigg( \frac{D_{12}}{a^2b^2} I_2 \phi + \frac{D_{11}}{a^4} I_1 \frac{\id^2 \phi}{\id \xi^2} \bigg) 
 		\delta\frac{\id  \phi}{\id \xi} \Big|^{\xi=1}_{\xi=-1} \\
-		&\quad + \frac{2k^r_{\xi=-1}}{a^3} S_1 \bigg(\frac{\id \phi}{\id \xi}\delta \frac{\id \phi}{\id \xi}\bigg)_{\xi=-1} 
-		+ \frac{2k^r_{\xi=1}}{a^3} S_1 \bigg(\frac{\id \phi}{\id \xi} \delta\frac{\id \phi}{\id \xi}\bigg)_{\xi=1}.
+		&\quad + \frac{2k^r_{\xi=-1}}{a^3} I_1 \bigg(\frac{\id \phi}{\id \xi}\delta \frac{\id \phi}{\id \xi}\bigg)_{\xi=-1} 
+		+ \frac{2k^r_{\xi=1}}{a^3} I_1 \bigg(\frac{\id \phi}{\id \xi} \delta\frac{\id \phi}{\id \xi}\bigg)_{\xi=1}.
 	\end{split}
@@
 \begin{equation}\label{eq:ODEx}
-		\frac{\id^4 \phi}{\id \xi^4}+ 2\alpha^2\left(\frac{D_{12}S_2}{D_{11}S_1}-2\frac{D_{66}S_3}{D_{11}S_1}\right)\frac{\id^2 \phi}{\id \xi^2}+\left(\alpha^4\frac{D_{22}S_4}{D_{11}S_1}-a^4\Omega_x^4\right)\phi=0,
+		\frac{\id^4 \phi}{\id \xi^4}+ 2\alpha^2\left(\frac{D_{12}I_2}{D_{11}I_1}-2\frac{D_{66}I_3}{D_{11}I_1}\right)\frac{\id^2 \phi}{\id \xi^2}+\left(\alpha^4\frac{D_{22}I_4}{D_{11}I_1}-a^4\Omega_x^4\right)\phi=0,
 \end{equation}
@@
 	\begin{split}
-		\mu^4 + 2\alpha^2\left(\frac{D_{12}S_2}{D_{11}S_1}-2\frac{D_{66}S_3}{D_{11}S_1}\right)\mu^2 + \left(\alpha^4\frac{D_{22}S_4}{D_{11}S_1}-a^4\Omega_x^4\right) = 0.
+		\mu^4 + 2\alpha^2\left(\frac{D_{12}I_2}{D_{11}I_1}-2\frac{D_{66}I_3}{D_{11}I_1}\right)\mu^2 + \left(\alpha^4\frac{D_{22}I_4}{D_{11}I_1}-a^4\Omega_x^4\right) = 0.
 	\end{split}
@@
 	\begin{align}
-		\alpha_1 &= \alpha \sqrt{\sqrt{\left(\frac{D_{12}S_2}{D_{11}S_1}-2\frac{D_{66}S_3}{D_{11}S_1}\right)^2 - \frac{D_{22}S_4}{D_{11}S_1} + b^4\Omega_x^4} + \frac{D_{12}S_2}{D_{11}S_1} - 2\frac{D_{66}S_3}{D_{11}S_1}},\label{eq:alphax1}\\
-		\beta_1 &= \alpha \sqrt{\sqrt{\left(\frac{D_{12}S_2}{D_{11}S_1}-2\frac{D_{66}S_3}{D_{11}S_1}\right)^2 - \frac{D_{22}S_4}{D_{11}S_1} + b^4\Omega_x^4} - \frac{D_{12}S_2}{D_{11}S_1} + 2\frac{D_{66}S_3}{D_{11}S_1}}.\label{eq:alphax2}
+		\alpha_1 &= \alpha \sqrt{\sqrt{\left(\frac{D_{12}I_2}{D_{11}I_1}-2\frac{D_{66}I_3}{D_{11}I_1}\right)^2 - \frac{D_{22}I_4}{D_{11}I_1} + b^4\Omega_x^4} + \frac{D_{12}I_2}{D_{11}I_1} - 2\frac{D_{66}I_3}{D_{11}I_1}},\label{eq:alphax1}\\
+		\beta_1 &= \alpha \sqrt{\sqrt{\left(\frac{D_{12}I_2}{D_{11}I_1}-2\frac{D_{66}I_3}{D_{11}I_1}\right)^2 - \frac{D_{22}I_4}{D_{11}I_1} + b^4\Omega_x^4} - \frac{D_{12}I_2}{D_{11}I_1} + 2\frac{D_{66}I_3}{D_{11}I_1}}.\label{eq:alphax2}
 	\end{align}
@@
 	\begin{split}
-		&\left[ \left( \frac{4D_{66}}{a^2b^2} S_3 - \frac{D_{12}}{a^2b^2} S_2 \right) \frac{\id \phi}{\id \xi} 
-		- \frac{D_{11}}{a^4} S_1 \frac{\id^3 \phi}{\id \xi^3} \right] \Big|^{\xi=1}_{\xi=-1}\\
-		&\quad+ \frac{2k^v_{\xi=-1}}{a} S_1 \left(\phi\right)_{\xi=-1}
-		 + \frac{2k^v_{\xi=1}}{a} S_1 \left(\phi\right)_{\xi=1} = 0,
+		&\left[ \left( \frac{4D_{66}}{a^2b^2} I_3 - \frac{D_{12}}{a^2b^2} I_2 \right) \frac{\id \phi}{\id \xi} 
+		- \frac{D_{11}}{a^4} I_1 \frac{\id^3 \phi}{\id \xi^3} \right] \Big|^{\xi=1}_{\xi=-1}\\
+		&\quad+ \frac{2k^v_{\xi=-1}}{a} I_1 \left(\phi\right)_{\xi=-1}
+		 + \frac{2k^v_{\xi=1}}{a} I_1 \left(\phi\right)_{\xi=1} = 0,
 	\end{split}
@@
 	\begin{split}	
-		\left( \frac{D_{12}}{a^2b^2} S_2 \phi + \frac{D_{11}}{a^4} S_1 \frac{\partial^2 \phi}{\partial \xi^2} \right) 
+		\left( \frac{D_{12}}{a^2b^2} I_2 \phi + \frac{D_{11}}{a^4} I_1 \frac{\partial^2 \phi}{\partial \xi^2} \right) 
 		\Big|^{\xi=1}_{\xi=-1} 
-		&+ \frac{2k^r_{\xi=-1}}{a^3} S_1 \left(\frac{\partial \phi}{\partial \xi}\right)_{\xi=-1} \\
-		&+ \frac{2k^r_{\xi=1}}{a^3} S_1 \left(\frac{\partial \phi}{\partial \xi}\right)_{\xi=1} = 0.
+		&+ \frac{2k^r_{\xi=-1}}{a^3} I_1 \left(\frac{\partial \phi}{\partial \xi}\right)_{\xi=-1} \\
+		&+ \frac{2k^r_{\xi=1}}{a^3} I_1 \left(\frac{\partial \phi}{\partial \xi}\right)_{\xi=1} = 0.
 	\end{split}
@@
 	\begin{align}
-		&  \frac{\id^3 \phi}{\id \xi^3} - \alpha^2\left( \frac{4D_{66}S_3}{D_{11}S_1}  - \frac{D_{12}S_2}{D_{11}S_1}  \right) \frac{\id \phi}{\id \xi} 
+		&  \frac{\id^3 \phi}{\id \xi^3} - \alpha^2\left( \frac{4D_{66}I_3}{D_{11}I_1}  - \frac{D_{12}I_2}{D_{11}I_1}  \right) \frac{\id \phi}{\id \xi} 
 		+\frac{2a^3k^v_{\xi=-1}}{D_{11}}\phi = 0, \quad &\xi = -1, \\
-		& \frac{\id^2 \phi}{\id \xi^2} + \frac{\alpha^2 D_{12} S_2}{D_{11} S_1} \phi - \frac{2a k^r_{\xi=-1}}{D_{11}} \frac{\id \phi}{\id \xi} = 0, \quad &\xi = -1, \\
-		& \frac{\id^3 \phi}{\id \xi^3} - \alpha^2\left( \frac{4D_{66}S_3}{D_{11}S_1}  - \frac{D_{12}S_2}{D_{11}S_1}  \right) \frac{\id \phi}{\id \xi} 
+		& \frac{\id^2 \phi}{\id \xi^2} + \frac{\alpha^2 D_{12} I_2}{D_{11} I_1} \phi - \frac{2a k^r_{\xi=-1}}{D_{11}} \frac{\id \phi}{\id \xi} = 0, \quad &\xi = -1, \\
+		& \frac{\id^3 \phi}{\id \xi^3} - \alpha^2\left( \frac{4D_{66}I_3}{D_{11}I_1}  - \frac{D_{12}I_2}{D_{11}I_1}  \right) \frac{\id \phi}{\id \xi} 
 		-\frac{2a^3 k^v_{\xi=1}}{D_{11}} \phi = 0, \quad &\xi = 1, \\
-		& \frac{\id^2 \phi}{\id \xi^2} + \frac{\alpha^2 D_{12} S_2}{D_{11} S_1} \phi + \frac{2a k^r_{\xi=1}}{D_{11}} \frac{\id \phi}{\id \xi} = 0, \quad &\xi = 1.
+		& \frac{\id^2 \phi}{\id \xi^2} + \frac{\alpha^2 D_{12} I_2}{D_{11} I_1} \phi + \frac{2a k^r_{\xi=1}}{D_{11}} \frac{\id \phi}{\id \xi} = 0, \quad &\xi = 1.
 	\end{align}
@@
 %
-Substituting \Cref{eq:phi_solution1} into \Cref{eq:boundaryx}, and denoting \( k^{v*}_{\xi} = \frac{2a^3 k^v_{\xi}}{D_{11}} \), \( k^{r*}_{\xi} = \frac{2a k^r_{\xi}}{D_{11}} \), \( \sin\alpha_1 = S_{\alpha_1} \), \( \cos\alpha_1 = C_{\alpha_1} \), \( \sinh\alpha_1 = Sh_{\alpha_1} \), \( \cosh\alpha_1 = Ch_{\alpha_1} \), \( \sin\beta_1 = S_{\beta_1} \), \( \cos\beta_1 = C_{\beta_1} \), \( \sinh\beta_1 = Sh_{\beta_1} \), and \( \cosh\beta_1 = Ch_{\beta_1} \), we have:
+Substituting \Cref{eq:phi_solution1} into \Cref{eq:boundaryx}, and denoting \( k^{v*}_{\xi} = \frac{2a^3 k^v_{\xi}}{D_{11}} \), \( k^{r*}_{\xi} = \frac{2a k^r_{\xi}}{D_{11}} \), \( S_{\alpha_1}=\sin\alpha_1  \), \( C_{\alpha_1}=\cos\alpha_1 \), \( Sh_{\alpha_1}=\sinh\alpha_1 \), \( Ch_{\alpha_1}=\cosh\alpha_1  \), \(S_{\beta_1}= \sin\beta_1 \), \( C_{\beta_1}=\cos\beta_1 \), \( Sh_{\beta_1}=\sinh\beta_1  \), and \(  Ch_{\beta_1}=\cosh\beta_1 \), we have:
 %
@@
 	\begin{split}
-		&\gamma_1 = -\alpha_1^3 - \alpha^2 \left( \frac{4D_{66}S_3}{D_{11}S_1} - \frac{D_{12}S_2}{D_{11}S_1} \right) \alpha_1, \\
-		&\gamma_2 = \beta_1^3 - \alpha^2 \left( \frac{4D_{66}S_3}{D_{11}S_1} - \frac{D_{12}S_2}{D_{11}S_1} \right) \beta_1, \\
-		&\gamma_3 = -\alpha_1^2 + \frac{\alpha^2 D_{12} S_2}{D_{11} S_1}, \\
-		&\gamma_4 = \beta_1^2 + \frac{\alpha^2 D_{12} S_2}{D_{11} S_1}.
-	\end{split}
-\end{equation}
-%
-Note that the classic boundary conditions can be obtained by selecting extremely large or small srping stiffness constants.
+		&\gamma_1 = -\alpha_1^3 - \alpha^2 \left( \frac{4D_{66}S_3}{D_{11}I_1} - \frac{D_{12}I_2}{D_{11}I_1} \right) \alpha_1, \\
+		&\gamma_2 = \beta_1^3 - \alpha^2 \left( \frac{4D_{66}S_3}{D_{11}I_1} - \frac{D_{12}I_2}{D_{11}I_1} \right) \beta_1, \\
+		&\gamma_3 = -\alpha_1^2 + \frac{\alpha^2 D_{12} I_2}{D_{11} I_1}, \\
+		&\gamma_4 = \beta_1^2 + \frac{\alpha^2 D_{12} I_2}{D_{11} I_1}.
+	\end{split}
+\end{equation}
+%
+Note that the classic boundary conditions can be obtained by selecting extremely large or small spring stiffness constants.
 For non-trivial solutions, the characteristic equation or eigenvalue equation is obtained from the determinant of the matrix $\mathbf{R}_x$ in \Cref{eq:ABx1}, which must be zero.
-However, solving these trancedental equations are cunmbersome and tedious, thus the DSM is introducted to avoid the ineffective computation.
+However, solving these transcendental equations are cunmbersome and tedious, thus the DSM is introducted to avoid the ineffective computation.
 
@@
 		\begin{Bmatrix}
-			\phi(\xi=-1)\\\frac{\id \phi(\xi=-1)}{\id \xi}\\\phi(\xi=1)\\\frac{\id \phi(\xi=1)}{\id \xi}
+			\phi_{\xi=-1}\\\frac{\id \phi}{\id \xi}_{\xi=-1}\\\phi_{\xi=1}\\\frac{\id \phi}{\id \xi}_{\xi=1}
 		\end{Bmatrix}
@@
 
-Similarly, the potential energy along the edges in the \( y \)-direction is given by:  
+The magnitude of total potential energy along the edges in the \( y \)-direction is given by:  
 %
@@
 % 
-The total potential energy of the plate in the \( y \)-direction can be determined from \Cref{eq:poten_energy_mag,eq:poten_energy_edgey2} as:
+The magnitude of potential energy of the plate in the \(y\)-direction can be obtained from
+\Cref{eq:poten_energy_mag,eq:poten_energy_edgey2} as:
 %
@@
 \end{equation}
-
+%
 By substituting \Cref{eq:displace_func} into \Cref{eq:poten_energy_toly}, we obtain:  
@@
 		U_{mag} &= U^{I}_{mag} + U^{III}_{mag} \\
-		&= \frac{ab}{2} \int_{-1}^{1} \left[ \frac{D_{11}}{a^4} T_4 \psi^2 
-		+ \frac{2D_{12}}{a^2b^2} T_2 \frac{\id^2\psi }{\id \eta^2} \psi 
-		+ \frac{D_{22}}{b^4} T_1 \left(\frac{\id^2\psi }{\id \eta^2} \right)^2 \right. \\
-		&\quad \left. + \frac{4D_{66}}{a^2b^2} T_3 \left(\frac{\id \psi }{\id \eta} \right)^2 \right] \, \id\eta  + ab \left[ \frac{k^r_{\eta=1}}{b^3} T \left( \frac{\id \psi}{\id \eta} \right)^2
-		+ \frac{k^v_{\eta=1}}{b} T_1 \left(\psi\right)^2 \right]_{\eta=1} \\
-		&\quad + ab \left[ \frac{k^r_{\eta=-1}}{b^3} T \left( \frac{\id \psi}{\id \eta} \right)^2
-		+ \frac{k^v_{\eta=-1}}{b} T_1 \left(\psi\right)^2 \right]_{\eta=-1},
+		&= \frac{ab}{2} \int_{-1}^{1} \left[ \frac{D_{11}}{a^4} J_4 \psi^2 
+		+ \frac{2D_{12}}{a^2b^2} J_2 \frac{\id^2\psi }{\id \eta^2} \psi 
+		+ \frac{D_{22}}{b^4} J_1 \left(\frac{\id^2\psi }{\id \eta^2} \right)^2 \right. \\
+		&\quad \left. + \frac{4D_{66}}{a^2b^2} J_3 \left(\frac{\id \psi }{\id \eta} \right)^2 \right] \, \id\eta  + abJ_1 \left[ \frac{k^r_{\eta=1}}{b^3} \left( \frac{\id \psi}{\id \eta} \right)^2
+		+ \frac{k^v_{\eta=1}}{b}  \left(\psi\right)^2 \right]_{\eta=1} \\
+		&\quad + abJ_1 \left[ \frac{k^r_{\eta=-1}}{b^3} \left( \frac{\id \psi}{\id \eta} \right)^2
+		+ \frac{k^v_{\eta=-1}}{b} \left(\psi\right)^2 \right]_{\eta=-1},
 	\end{split}
@@
 	\begin{split}  
-		&T_1 = \int_{-1}^{1} \phi^2 \, \id\xi, \\  
-		&T_2 = \int_{-1}^{1} \left( \frac{\id^2\phi}{\id\xi^2} \phi \right) \, \id\xi, \\  
-		&T_3 = \int_{-1}^{1} \left( \frac{\id\phi}{\id\xi} \right)^2 \, \id\xi, \\  
-		&T_4 = \int_{-1}^{1} \left( \frac{\id^2\phi}{\id\xi^2} \right)^2 \, \id\xi.  
-	\end{split}  
-\end{equation}  
-%
-The coefficient \( T_0 \) of the kinetic energy in \Cref{eq:kine_energy_mag} for the plate can be expressed as:
+		&J_1 = \int_{-1}^{1} \phi^2 \, \id\xi, \\  
+		&J_2 = \int_{-1}^{1} \left( \frac{\id^2\phi}{\id\xi^2} \phi \right) \, \id\xi, \\  
+		&J_3 = \int_{-1}^{1} \left( \frac{\id\phi}{\id\xi} \right)^2 \, \id\xi, \\  
+		&J_4 = \int_{-1}^{1} \left( \frac{\id^2\phi}{\id\xi^2} \right)^2 \, \id\xi.  
+	\end{split}  
+\end{equation}  
+%
+The coefficient \( T_0 \) of the kinetic energy from \Cref{eq:kine_energy_mag} for the plate can be expressed as:
 %
@@
 	\begin{split}
-		T_0 &= \frac{ab}{2} \rho h T_1 \int_{-1}^{1} \psi^2 \, \id\eta.
-	\end{split}
-\end{equation}
-
-Taking the Rayleigh principle in the form:
+		T_0 &= \frac{ab}{2} \rho h J_1 \int_{-1}^{1} \psi^2 \, \id\eta.
+	\end{split}
+\end{equation}
+%
+Take the Rayleigh principle in the form:
 %
@@
 %
-By substituting \Cref{eq:poten_energy_toly2,eq:kine_energyy} into \Cref{eq:Rayleighy}, and applying the variational calculus to eliminate \( \delta \psi \) and \( \delta\frac{\id \psi}{\id \eta} \) in \Cref{eq:Rayleighy}, we obtain:
+By substituting \Cref{eq:poten_energy_toly2,eq:kine_energyy} into \Cref{eq:Rayleighy}, and relieving \( \delta \psi \) and \( \delta\frac{\id \psi}{\id \eta} \) in \Cref{eq:Rayleighy} by variation calculus, yields:
 %
@@
 	\begin{split}
-		0 &= \int_{-1}^{1} \left[ \frac{D_{22}}{b^4} T_1 \frac{d^4 \psi}{\id \eta^4} 
-		+ \left( \frac{2D_{12}}{a^2b^2} T_2 - \frac{4D_{66}}{a^2b^2} T_3 \right) \frac{\id^2 \psi}{\id \eta^2} \right. \\
-		&\quad \left. + \left( \frac{D_{11}}{a^4} T_4 - \omega_y^2 \rho h T_1 \right) \psi \right] \delta \psi \, \id\eta \\
-		&\quad + \frac{2k^v_{\eta=-1}}{b} T_1 (\psi \delta \psi)_{\eta=-1} 
-		+ \frac{2k^v_{\eta=1}}{b} T_1 (\psi \delta \psi)_{\eta=1} \\
-		&\quad + \left[ \left( \frac{4D_{66}}{a^2b^2} T_3 - \frac{D_{12}}{a^2b^2} T_2 \right) \frac{\id \psi}{\id \eta} 
-		- \frac{D_{22}}{b^4} T_1 \frac{\id^3 \psi}{\id \eta^3} \right] \delta \psi \Big|^{\eta=1}_{\eta=-1} \\
-		&\quad + \left( \frac{D_{12}}{a^2b^2} T_2 \psi + \frac{D_{22}}{b^4} T_1 \frac{\id^2 \psi}{\id \eta^2} \right) 
+		0 &= \int_{-1}^{1} \left[ \frac{D_{22}}{b^4} J_1 \frac{d^4 \psi}{\id \eta^4} 
+		+ \left( \frac{2D_{12}}{a^2b^2} J_2 - \frac{4D_{66}}{a^2b^2} J_3 \right) \frac{\id^2 \psi}{\id \eta^2} \right. \\
+		&\quad \left. + \left( \frac{D_{11}}{a^4} J_4 - \omega_y^2 \rho h J_1 \right) \psi \right] \delta \psi \, \id\eta \\
+		&\quad + \frac{2k^v_{\eta=-1}}{b} J_1 (\psi \delta \psi)_{\eta=-1} 
+		+ \frac{2k^v_{\eta=1}}{b} J_1 (\psi \delta \psi)_{\eta=1} \\
+		&\quad + \left[ \left( \frac{4D_{66}}{a^2b^2} J_3 - \frac{D_{12}}{a^2b^2} J_2 \right) \frac{\id \psi}{\id \eta} 
+		- \frac{D_{22}}{b^4} J_1 \frac{\id^3 \psi}{\id \eta^3} \right] \delta \psi \Big|^{\eta=1}_{\eta=-1} \\
+		&\quad + \left( \frac{D_{12}}{a^2b^2} J_2 \psi + \frac{D_{22}}{b^4} J_1 \frac{\id^2 \psi}{\id \eta^2} \right) 
 		\delta\frac{\id  \psi}{\id \eta} \Big|^{\eta=1}_{\eta=-1} \\
-		&\quad + \frac{2k^r_{\eta=-1}}{b^3} T_1 \left( \frac{\id \psi}{\id \eta} \delta\frac{\id \psi}{\id \eta} \right)_{\eta=-1} 
-		+ \frac{2k^r_{\eta=1}}{b^3} T_1 \left( \frac{\id \psi}{\id \eta} \delta\frac{\id \psi}{\id \eta} \right)_{\eta=1}.
+		&\quad + \frac{2k^r_{\eta=-1}}{b^3} J_1 \left( \frac{\id \psi}{\id \eta} \delta\frac{\id \psi}{\id \eta} \right)_{\eta=-1} 
+		+ \frac{2k^r_{\eta=1}}{b^3} J_1 \left( \frac{\id \psi}{\id \eta} \delta\frac{\id \psi}{\id \eta} \right)_{\eta=1}.
 	\end{split}
@@
 \begin{equation}\label{eq:ODEy}
-		\frac{\id^4 \psi}{\id \eta^4} + \frac{2}{\alpha^2}\left(\frac{D_{12}T_2}{D_{22}T_1} - 2\frac{D_{66}T_3}{D_{22}T_1}\right)\frac{\id^2 \psi}{\id \eta^2} + \left( \frac{D_{11}T_4}{\alpha^4D_{22}T_1} - \frac{b^4D_{11}}{D_{22}} \Omega_y^4 \right) \psi = 0,
-\end{equation}
-%
-where \( \Omega_y = \sqrt[4]{\frac{\omega_y^2 \rho h}{D_{11}}} \).
-Substituting \( \psi(\eta) = B e^{\lambda \eta} \) into \Cref{eq:ODEy}, yields:
+		\frac{\id^4 \psi}{\id \eta^4} + \frac{2}{\alpha^2}\left(\frac{D_{12}J_2}{D_{22}J_1} - 2\frac{D_{66}J_3}{D_{22}J_1}\right)\frac{\id^2 \psi}{\id \eta^2} + \left( \frac{D_{11}J_4}{\alpha^4D_{22}J_1} - \frac{b^4D_{11}}{D_{22}} \Omega_y^4 \right) \psi = 0,
+\end{equation}
+%
+where \( \Omega_y = \sqrt[4]{{\omega_y^2 \rho h}/D_{11}} \).
+By substituting \( \psi(\eta) = B e^{\lambda \eta} \) into \Cref{eq:ODEy}, yields:
 %
@@
 	\begin{split}
-		\lambda^4 + \frac{2}{\alpha^2} \left( \frac{D_{12}T_2}{D_{22}T_1} - 2\frac{D_{66}T_3}{D_{22}T_1} \right) \lambda^2 + \left( \frac{D_{11}T_4}{\alpha^4D_{22}T_1} - \frac{b^4D_{11}}{D_{22}} \Omega_y^4 \right) = 0.
+		\lambda^4 + \frac{2}{\alpha^2} \left( \frac{D_{12}J_2}{D_{22}J_1} - 2\frac{D_{66}J_3}{D_{22}J_1} \right) \lambda^2 + \left( \frac{D_{11}J_4}{\alpha^4D_{22}J_1} - \frac{b^4D_{11}}{D_{22}} \Omega_y^4 \right) = 0.
 	\end{split}
@@
 	\begin{align}
-		\alpha_2 &= \frac{1}{\alpha} \sqrt{ \sqrt{ \left( \frac{D_{12}T_2}{D_{22}T_1} - 2\frac{D_{66}T_3}{D_{22}T_1} \right)^2 - \frac{D_{11}T_4}{D_{22}T_1} + \frac{a^4 D_{11}}{D_{22}} \Omega_y^4 } + \frac{D_{12}T_2}{D_{22}T_1} - 2 \frac{D_{66}T_3}{D_{22}T_1}}, \\
-		\beta_2 &= \frac{1}{\alpha} \sqrt{ \sqrt{ \left( \frac{D_{12}T_2}{D_{22}T_1} - 2 \frac{D_{66}T_3}{D_{22}T_1} \right)^2 - \frac{D_{11}T_4}{D_{22}T_1} + \frac{a^4 D_{11}}{D_{22}} \Omega_y^4 } - \frac{D_{12}T_2}{D_{22}T_1} + 2 \frac{D_{66}T_3}{D_{22}T_1}}.
+		\alpha_2 &= \frac{1}{\alpha} \sqrt{ \sqrt{ \left( \frac{D_{12}J_2}{D_{22}J_1} - 2\frac{D_{66}J_3}{D_{22}J_1} \right)^2 - \frac{D_{11}J_4}{D_{22}J_1} + \frac{a^4 D_{11}}{D_{22}} \Omega_y^4 } + \frac{D_{12}J_2}{D_{22}J_1} - 2 \frac{D_{66}J_3}{D_{22}J_1}}, \\
+		\beta_2 &= \frac{1}{\alpha} \sqrt{ \sqrt{ \left( \frac{D_{12}J_2}{D_{22}J_1} - 2 \frac{D_{66}J_3}{D_{22}J_1} \right)^2 - \frac{D_{11}J_4}{D_{22}J_1} + \frac{a^4 D_{11}}{D_{22}} \Omega_y^4 } - \frac{D_{12}J_2}{D_{22}J_1} + 2 \frac{D_{66}J_3}{D_{22}J_1}}.
 	\end{align}
@@
 	\begin{split}
-		& \left[ \left( \frac{4D_{66}}{a^2b^2} T_3 - \frac{D_{12}}{a^2b^2} T_2 \right) \frac{\id \psi}{\id \eta} 
-		- \frac{D_{22}}{b^4} T_1 \frac{\id^3 \psi}{\id \eta^3} \right] \Big|^{\eta=1}_{\eta=-1} \\
-		&\quad + \frac{2k^v_{\eta=-1}}{b} T_1 (\psi )_{\eta=-1} + \frac{2k^v_{\eta=1}}{b} T_1 (\psi )_{\eta=1} = 0,
+		& \left[ \left( \frac{4D_{66}}{a^2b^2} J_3 - \frac{D_{12}}{a^2b^2} J_2 \right) \frac{\id \psi}{\id \eta} 
+		- \frac{D_{22}}{b^4} J_1 \frac{\id^3 \psi}{\id \eta^3} \right] \Big|^{\eta=1}_{\eta=-1} \\
+		&\quad + \frac{2k^v_{\eta=-1}}{b} J_1 (\psi )_{\eta=-1} + \frac{2k^v_{\eta=1}}{b} J_1 (\psi )_{\eta=1} = 0,
 	\end{split}
@@
  \begin{split}
- 	\left( \frac{D_{12}}{a^2b^2} T_2 \psi + \frac{D_{22}}{b^4} T_1 \frac{\id^2 \psi}{\id \eta^2} \right) 
+ 	\left( \frac{D_{12}}{a^2b^2} J_2 \psi + \frac{D_{22}}{b^4} J_1 \frac{\id^2 \psi}{\id \eta^2} \right) 
  	\Big|^{\eta=1}_{\eta=-1} 
- 	&+ \frac{2k^r_{\eta=-1}}{b^3} T_1 \left( \frac{\id \psi}{\id \eta} \right)_{\eta=-1} \\
- 	&+ \frac{2k^r_{\eta=1}}{b^3} T_1 \left( \frac{\id \psi}{\id \eta} \right)_{\eta=1}=0.
+ 	&+ \frac{2k^r_{\eta=-1}}{b^3} J_1 \left( \frac{\id \psi}{\id \eta} \right)_{\eta=-1} \\
+ 	&+ \frac{2k^r_{\eta=1}}{b^3} J_1 \left( \frac{\id \psi}{\id \eta} \right)_{\eta=1}=0.
  \end{split}
@@
 	\begin{align}
-		&  \frac{\id^3 \psi}{\id \eta^3}-\left( \frac{4D_{66}T_3}{\alpha^2D_{22}T_1}  - \frac{D_{12}T_2}{\alpha^2D_{22}T_1}  \right) \frac{\id \psi}{\id \eta} 
+		&  \frac{\id^3 \psi}{\id \eta^3}-\left( \frac{4D_{66}J_3}{\alpha^2D_{22}J_1}  - \frac{D_{12}J_2}{\alpha^2D_{22}J_1}  \right) \frac{\id \psi}{\id \eta} 
 		+\frac{2b^3k^v_{\eta=-1}}{D_{22}}\psi=0,\quad &\eta=-1,\\
-		& \frac{\id^2 \psi}{\id \eta^2}+\frac{D_{12}T_2}{\alpha^2D_{22}T_1} \psi -\frac{2bk^r_{\eta=-1}}{D_{22}}\frac{\id\psi }{\id \eta}=0,\quad &\eta=-1,\\
-		&  \frac{\id^3 \psi}{\id \eta^3}-\left( \frac{4D_{66}T_3}{\alpha^2D_{22}T_1}  - \frac{D_{12}T_2}{\alpha^2D_{22}T_1}  \right) \frac{\id \psi}{\id \eta} 
+		& \frac{\id^2 \psi}{\id \eta^2}+\frac{D_{12}J_2}{\alpha^2D_{22}J_1} \psi -\frac{2bk^r_{\eta=-1}}{D_{22}}\frac{\id\psi }{\id \eta}=0,\quad &\eta=-1,\\
+		&  \frac{\id^3 \psi}{\id \eta^3}-\left( \frac{4D_{66}J_3}{\alpha^2D_{22}J_1}  - \frac{D_{12}J_2}{\alpha^2D_{22}J_1}  \right) \frac{\id \psi}{\id \eta} 
 		-\frac{2b^3k^v_{\eta=1}}{D_{22}}\psi=0,\quad &\eta=1,\\
-		&\frac{\id^2 \psi}{\id \eta^2}+\frac{D_{12}T_2}{\alpha^2D_{22}T_1} \psi +\frac{2bk^r_{\eta=1}}{D_{22}}\frac{\id\psi }{\id \eta}=0,\quad &\eta=1.
+		&\frac{\id^2 \psi}{\id \eta^2}+\frac{D_{12}J_2}{\alpha^2D_{22}J_1} \psi +\frac{2bk^r_{\eta=1}}{D_{22}}\frac{\id\psi }{\id \eta}=0,\quad &\eta=1.
 	\end{align}
@@
 %
-Substituting \Cref{eq:phi_solution2} into \Cref{eq:boundaryy} and introducing the notations 
+Substituting \Cref{eq:phi_solution2} into \Cref{eq:boundaryy} and denoting
 \( k^{v*}_{\eta} = \frac{2b^3 k^v_{\eta}}{D_{22}} \), 
 \( k^{r*}_{\eta} = \frac{2b k^r_{\eta}}{D_{22}} \), 
-\( \sin\alpha_2 = S_{\alpha_2} \), 
-\( \cos\alpha_2 = C_{\alpha_2} \), 
-\( \sinh\alpha_2 = Sh_{\alpha_2} \), 
-\( \cosh\alpha_2 = Ch_{\alpha_2} \), 
-\( \sin\beta_2 = S_{\beta_2} \), 
-\( \cos\beta_2 = C_{\beta_2} \), 
-\( \sinh\beta_2 = Sh_{\beta_2} \), and 
-\( \cosh\beta_2 = Ch_{\beta_2} \), 
+\( S_{\alpha_2}=\sin\alpha_2  \), 
+\( C_{\alpha_2}=\cos\alpha_2  \), 
+\( Sh_{\alpha_2}=\sinh\alpha_2  \), 
+\( Ch_{\alpha_2}=\cosh\alpha_2 \), 
+\( S_{\beta_2}=\sin\beta_2  \), 
+\( C_{\beta_2}=\cos\beta_2  \), 
+\( Sh_{\beta_2}=\sinh\beta_2 \), and 
+\(Ch_{\beta_2}= \cosh\beta_2 \), 
 We obtain:
@@
 		&\left[ \begin{array}{c}
-			\hat{\gamma}_1C_{\alpha_2}-k^{v*}_{\eta=-1}S_{\alpha_2} \\ \hat{\gamma}_3S_{\alpha_2}+k^{r*}_{\eta=-1}\alpha_2C_{\alpha_2} \\ -\hat{\gamma}_1C_{\alpha_2}+k^{v*}_{\eta=1}S_{\alpha_2} \\ \hat{\gamma}_3S_{\alpha_2}+k^{r*}_{\eta=1}\alpha_2C_{\alpha_2}
+			\zeta_1C_{\alpha_2}-k^{v*}_{\eta=-1}S_{\alpha_2} \\ \zeta_3S_{\alpha_2}+k^{r*}_{\eta=-1}\alpha_2C_{\alpha_2} \\ -\zeta_1C_{\alpha_2}+k^{v*}_{\eta=1}S_{\alpha_2} \\ \zeta_3S_{\alpha_2}+k^{r*}_{\eta=1}\alpha_2C_{\alpha_2}
 		\end{array} \begin{array}{c}
-			\hat{\gamma}_1S_{\alpha_2}+k^{v*}_{\eta=-1}C_{\alpha_2} \\ -\hat{\gamma}_3C_{\alpha_2}+k^{r*}_{\eta=-1}\alpha_2S_{\alpha_2} \\ \hat{\gamma}_1S_{\alpha_2}+k^{v*}_{\eta=1}C_{\alpha_2} \\ \hat{\gamma}_3C_{\alpha_2}-k^{r*}_{\eta=1}\alpha_2S_{\alpha_2}
+			\zeta_1S_{\alpha_2}+k^{v*}_{\eta=-1}C_{\alpha_2} \\ -\zeta_3C_{\alpha_2}+k^{r*}_{\eta=-1}\alpha_2S_{\alpha_2} \\ \zeta_1S_{\alpha_2}+k^{v*}_{\eta=1}C_{\alpha_2} \\ \zeta_3C_{\alpha_2}-k^{r*}_{\eta=1}\alpha_2S_{\alpha_2}
 		\end{array} \begin{array}{c}
-			\hat{\gamma}_2Ch_{\beta_2}-k^{v*}_{\eta=-1}Sh_{\beta_2} \\ \hat{\gamma}_4Sh_{\beta_2}+k^{r*}_{\eta=-1}\beta_2Ch_{\beta_2} \\ -\hat{\gamma}_2Ch_{\beta_2}+k^{v*}_{\eta=1}Sh_{\beta_2} \\ \hat{\gamma}_4Sh_{\beta_2}+k^{r*}_{\eta=1}\beta_2Ch_{\beta_2}
+			\zeta_2Ch_{\beta_2}-k^{v*}_{\eta=-1}Sh_{\beta_2} \\ \zeta_4Sh_{\beta_2}+k^{r*}_{\eta=-1}\beta_2Ch_{\beta_2} \\ -\zeta_2Ch_{\beta_2}+k^{v*}_{\eta=1}Sh_{\beta_2} \\ \zeta_4Sh_{\beta_2}+k^{r*}_{\eta=1}\beta_2Ch_{\beta_2}
 		\end{array} \right. \\
@@
 		\left. \begin{array}{c}
-			-\hat{\gamma}_2Sh_{\beta_2}+k^{v*}_{\eta=-1}Ch_{\beta_2} \\ -\hat{\gamma}_4Ch_{\beta_2}-k^{r*}_{\eta=-1}\beta_2Sh_{\beta_2} \\ -\hat{\gamma}_2Sh_{\beta_2}+k^{v*}_{\eta=1}Ch_{\beta_2} \\ \hat{\gamma}_4Ch_{\beta_2}+k^{r*}_{\eta=1}\beta_2Sh_{\beta_2}
+			-\zeta_2Sh_{\beta_2}+k^{v*}_{\eta=-1}Ch_{\beta_2} \\ -\zeta_4Ch_{\beta_2}-k^{r*}_{\eta=-1}\beta_2Sh_{\beta_2} \\ -\zeta_2Sh_{\beta_2}+k^{v*}_{\eta=1}Ch_{\beta_2} \\ \zeta_4Ch_{\beta_2}+k^{r*}_{\eta=1}\beta_2Sh_{\beta_2}
 		\end{array} \right]\begin{Bmatrix}
@@
 	\begin{split}
-		&\hat{\gamma}_1=-\alpha_2^3-\left( \frac{4D_{66}T_3}{\alpha^2D_{22}T_1}  - \frac{D_{12}T_2}{\alpha^2D_{22}T_1}  \right)\alpha_2,\\
-		&\hat{\gamma}_2=\beta_2^3-\left( \frac{4D_{66}T_3}{\alpha^2D_{22}T_1}  - \frac{D_{12}T_2}{\alpha^2D_{22}T_1}  \right)\beta_2,\\
-		&\hat{\gamma}_3=-\alpha_2^2+\frac{D_{12}T_2}{\alpha^2D_{22}T_1},\\
-		&\hat{\gamma}_4=\beta_2^2+\frac{D_{12}T_2}{\alpha^2D_{22}T_1}.
+		&\zeta_1=-\alpha_2^3-\left( \frac{4D_{66}J_3}{\alpha^2D_{22}J_1}  - \frac{D_{12}J_2}{\alpha^2D_{22}J_1}  \right)\alpha_2,\\
+		&\zeta_2=\beta_2^3-\left( \frac{4D_{66}T_3}{\alpha^2D_{22}J_1}  - \frac{D_{12}J_2}{\alpha^2D_{22}J_1}  \right)\beta_2,\\
+		&\zeta_3=-\alpha_2^2+\frac{D_{12}J_2}{\alpha^2D_{22}J_1},\\
+		&\zeta_4=\beta_2^2+\frac{D_{12}J_2}{\alpha^2D_{22}J_1}.
 	\end{split}
@@
 \section{Frequency and mode shape computation}\label{sec:WWA}
-\subsection{Wittrick–Williams algorithm}\label{sec:WWA2}
+\subsection{Wittrick–Williams algorithm and enhancement}\label{sec:WWA2}
 The Wittrick–Williams (W-W) algorithm \cite{wittrick1971general} is an effective method for determining the natural frequencies from the dynamic stiffness matrix with high reliability. 
@@
 
-However, the idea of solving the simply supported problem proposes an effective and systematic approach to indirectly determine the \( J_0 \) count for a fully clamped structure using the 'hypothetical structure method', where the boundary conditions are modeled as pinned supports rather than clamped ones \cite{han2018improved}:
+However, the idea of solving the simply supported problem proposes an effective and systematic approach to indirectly determine the \( J_0 \) count for a fully clamped structure, where the boundary conditions are modeled as pinned supports rather than clamped ones \cite{han2018improved}:
 %
@@
 Therefore, the challenge of determining \( J_0(p_1, \omega^*) \) can be transformed into the problem of solving \( J(\bar{p}_1, \omega^*) \) instead.
-The eigenvalue equation corresponding to the natural frequency parameter \( \Omega_x \) can be obtained from the determinant of the coefficient matrix \( \mathbf{R}_x \) in \Cref{eq:ABx}, which is given by:
+The eigenvalue equation corresponding to the natural frequency parameter \( \Omega_x \) can be obtained from the determinant of the coefficient matrix \( \mathbf{R}_x \) in \Cref{eq:ABx}, which is given by \citep{xing2020extended}:
 %
@@
 For \(\Omega_{x,n_x} \leq \Omega_x^* < \Omega_{x,n_{x+1}}\), \(J(\bar{p}_1, \Omega_x^*) = n_x\).
-Similarly, the closed-form solution of the \(n_y\)th simply supported frequency \(\Omega_{y,n_y}\) for the given \(n_x\)-order \(\phi_{n_x}(\xi)\) can be expressed as:
+Similarly, the closed-form solution of the \(n_y\)-th simply supported frequency \(\Omega_{y,n_y}\) for the given \(n_x\)-order \(\phi_{n_x}(\xi)\) can be expressed as:
 %
@@
 According to the relationships 
-$\Omega_x = \sqrt[4]{\frac{\omega_x^2 \rho h}{D_{11}}}$ and\ $\Omega_y = \sqrt[4]{\frac{\omega_y^2 \rho h}{D_{11}}}$, 
+$\Omega_x = \sqrt[4]{{\omega_x^2 \rho h}/{D_{11}}}$ and\ $\Omega_y = \sqrt[4]{{\omega_y^2 \rho h}/{D_{11}}}$, 
 the values of \(J(\bar{p}_1, \omega_x^*)\) and \(J(\bar{p}_1, \omega_y^*)\) can be derived from \(J(\bar{p}_1, \Omega_x^*)\) and \(J(\bar{p}_1, \Omega_y^*)\), respectively.
 Therefore, this refined W-W algorithm can be applied to estimate the lower and upper bounds of the frequency range, denoted as \(\omega_l\) and \(\omega_u\), yielding an approximation for the frequency \(\omega_a \in (\omega_l, \omega_u)\).
-
+\subsection{Mode shape computation}
 The mode shape coefficients \( A_1 \) to \( A_4 \) and \( B_1 \) to \( B_4 \) in the eigenvectors \( \mathbf{A} \) and \( \mathbf{B} \) for all classic boundary conditions are provided in \cite{xing2020extended}.
@@
 
-\subsection{Application procedure}
+\subsection{Application procedure}\label{sec:Application procedure}
 The procedure of the proposed method is as follows:   
-\subsubsection{Iterative procedure}\label{sec:Iterative_procedure}
 \begin{itemize}[]
-	\item \textbf{Step 1} Assume initial integral parameters \(S^{(0)}_1, S^{(0)}_2, S^{(0)}_3\), and \(S^{(0)}_4\) in the \(y\)-direction.
-Using the given boundary conditions (BCs) at \(\xi = -1\) and \(\xi = 1\), determine \(\mathbf{K}^{(0)}_x\) from \Cref{eq:DSM_eqx}.
-Then, apply the computational algorithms in \Cref{sec:WWA2} to compute the \(n_x\)-th frequency \(\omega^{(0)}_{x,n_x}\) and its corresponding mode shape \(\phi^{(0)}_{n_x}\), where \(n_x = 1, 2, 3, \ldots\).
-
-	\item \textbf{Step 2} Use \(\phi^{(0)}_{n_x}\) as the prescribed mode to determine \(\mathbf{K}^{(1)}_y\) in \Cref{eq:DSM_eqy}, considering the BCs at \(\eta = -1\) and \(\eta = 1\).
-Apply the computational algorithms to obtain the \(n_y\)-th frequency \(\omega^{(1)}_{y,n_y}\) and its corresponding mode shape \(\psi^{(1)}_{n_y}\), where \(n_y = 1, 2, 3, \ldots\).
+	\item \textbf{Step 1} Assume initial integral parameters \(I^{(0)}_1, I^{(0)}_2, I^{(0)}_3\), and \(I^{(0)}_4\) in the \(y\)-direction.
+Using the given boundary conditions at \(\xi = -1\) and \(\xi = 1\), determine \(\mathbf{K}^{(0)}_x\) from \Cref{eq:DSM_eqx}.
+	Then, apply the computational algorithms in \Cref{sec:WWA2} to compute the lower and upper bounds of the \(n_x\)-th non-dimensional frequency parameter, \(2a\Omega^{(0)}_{l,x,n_x}\) and \(2a\Omega^{(0)}_{u,x,n_x}\), and take the average \(2a\Omega^{(0)}_{x,n_x} = (2a\Omega^{(0)}_{l,x,n_x} + 2a\Omega^{(0)}_{u,x,n_x})/2\) along with its corresponding mode shape \(\phi^{(0)}_{n_x}\), where \(n_x = 1, 2, 3, \ldots\).
+
+	\item \textbf{Step 2} Use \(\phi^{(0)}_{n_x}\) as the prescribed mode to determine \(\mathbf{K}^{(1)}_y\) in \Cref{eq:DSM_eqy}, considering the boundary conditions at \(\eta = -1\) and \(\eta = 1\). 
+	Apply the computational algorithms to obtain the \(n_y\)-th frequency parameter \(2a\Omega^{(1)}_{y,n_y}\) and its corresponding mode shape \(\psi^{(1)}_{n_y}\), where \(n_y = 1, 2, 3, \ldots\).
 This completes the first iteration cycle.
 
-	\item \textbf{Step 3} Use \(\psi^{(1)}_{n_y}\) as the prescribed \(n_y\)-th mode shape in the \(y\)-direction to compute \(\mathbf{K}^{(1)}_x\) from \Cref{eq:DSM_eqx}, then determine the \(n_x\)-th frequency \(\omega^{(1)}_{x,n_x}\) and its corresponding mode shape \(\phi^{(1)}_{n_x}\).
-
-	\item \textbf{Step 4} Use \(\phi^{(1)}_{n_x}\) as the prescribed mode in the \(x\)-direction to compute the \(n_y\)-th frequency \(\omega^{(2)}_{y,n_y}\) and its corresponding mode shape \(\psi^{(2)}_{n_y}\), completing the second iteration cycle.
-
-	\item \textbf{Step 5} Stop the iteration if \(\mid\omega^{(i)}_{x,n_x} - \omega^{(i+1)}_{x,n_x}\mid \leq \Delta\omega\) or \(\mid\omega^{(i)}_{y,n_y} - \omega^{(i+1)}_{y,n_y}\mid \leq \Delta\omega\), where \(\Delta\omega\) is the frequency interval defined in \Cref{sec:WWA}, where, \(\Delta\omega = \omega_u - \omega_l\).
+	\item \textbf{Step 3} Use \(\psi^{(1)}_{n_y}\) as the prescribed \(n_y\)-th mode shape in the \(y\)-direction to compute \(\mathbf{K}^{(1)}_x\) from \Cref{eq:DSM_eqx}, then determine the \(n_x\)-th frequency parameter \(2a\Omega^{(1)}_{x,n_x}\) and its corresponding mode shape \(\phi^{(1)}_{n_x}\).
+
+	\item \textbf{Step 4} Use \(\phi^{(1)}_{n_x}\) as the prescribed mode in the \(x\)-direction to compute the \(n_y\)-th frequency parameter \(2a\Omega^{(2)}_{y,n_y}\) and its corresponding mode shape \(\psi^{(2)}_{n_y}\), completing the second iteration cycle.
+
+	\item \textbf{Step 5} Stop the iteration if \(\lvert 2a\Omega^{(i)}_{x,n_x} - 2a\Omega^{(i+1)}_{x,n_x} \rvert \leq \Delta 2a\Omega\) or \(\lvert 2a\Omega^{(i)}_{y,n_y} - 2a\Omega^{(i+1)}_{y,n_y} \rvert \leq \Delta 2a\Omega\), where \(\Delta 2a\Omega = 2a\Omega_u - 2a\Omega_l\).
+Here, \(2a\Omega_l\) and \(2a\Omega_u\) are the lower and upper bounds of the frequency parameter range, within which the actual frequency parameter \(2a\Omega\) lies, i.e., \(2a\Omega \in (2a\Omega_l, 2a\Omega_u)\).
+The quantity \(\Delta 2a\Omega\) represents the frequency parameter interval used in the W-W algorithm.
 
@@
 \end{itemize}
-\subsubsection{Non-iterative Procedure}\label{sec:Noniterative_procedure}  
-Although the iterative procedure in \Cref{sec:Iterative_procedure} can be used to obtain any desired mode, a non-iterative approach can enhance the efficiency of numerical calculations when an exact mode is known.
-
-Once a nonzero mode shape \(\phi_{n_x}(\xi) \psi_{n_y}(\eta)\) is determined by following the iterative procedure in \Cref{sec:Iterative_procedure}, \(\psi_{n_y}(\eta)\) can be chosen as the exact known mode in the \(y\)-direction.
-This allows the computation of infinitely many modes \(\phi(\xi)\) in the \(x\)-direction by following only \textbf{Step 1}, without requiring further iterations.  
-Similarly, if \(\phi_{n_x}(\xi)\) is selected as the exact known mode in the \(x\)-direction, infinitely many modes \(\psi(\eta)\) in the \(y\)-direction can be computed by following only \textbf{Step 2}, without iterations.
-
-For example, if the \((n_x, n_y)\)-th mode is nonzero and obtained through the iteration procedure, then based on \(\psi_{n_y}(\eta)\), the modes \((1,n_y)\), \((2,n_y)\), ..., \((\infty,n_y)\) of the plate can be computed without further iteration.
-Similarly, based on \(\phi_{n_x}(\xi)\), the modes \((n_x,1)\), \((n_x,2)\), ..., \((n_x,\infty)\) of the plate can be determined.  
-That is, only one iteration procedure is required to calculate all frequencies of the plate, which helps reduce the computational cost.
 
@@
 \section{Numerical Results}  
-This section presents the numerical validation of the proposed method for classic boundary conditions and elastically restrained boundary conditions.  
-For all numerical calculations, the initial integral parameters are assumed as \(S^{(0)}_1=1\), \(S^{(0)}_2=1\), \(S^{(0)}_3=1\), and \(S^{(0)}_4=10\) in the \(y\)-direction, serving as the starting point of \textbf{Step 1} for any mode in all BCs.
-In this section, the interval between the upper and lower bounds of the non-dimensional frequency parameter, \(2a\Delta\Omega\), is set to 0.005, defining the error range.  
-According to our numerical calculations, two iteration cycles are sufficient to meet the convergence requirement for most cases, with at most three cycles needed when applying the iterative procedure in \Cref{sec:Iterative_procedure}.
+This section presents the numerical validation of the proposed method for classic boundary conditions and rotationally restrained boundary conditions.  
+For all numerical calculations, the initial integral parameters are assumed as \(I^{(0)}_1=1\), \(I^{(0)}_2=1\), \(I^{(0)}_3=1\), and \(I^{(0)}_4=10\) in the \(y\)-direction, serving as the starting point of \textbf{Step 1} for any mode in all boundary conditions.
+In this section, the interval between the upper and lower bounds of the non-dimensional frequency parameter, \(2a\Delta\Omega\), is set to 0.005, limiting the error range.  
+According to our numerical calculations, two iteration cycles are generally sufficient to meet the convergence requirement (i.e., \(\lvert 2a\Omega^{(i)}_{x} - 2a\Omega^{(i+1)}_{x} \rvert \leq \Delta 2a\Omega\) or \(\lvert 2a\Omega^{(i)}_{y} - 2a\Omega^{(i+1)}_{y} \rvert \leq \Delta 2a\Omega\)) for most cases, with at most three cycles required when applying the iterative procedure in \Cref{sec:Application procedure}.
 
@@
 
-The initial guess for \(S^{(0)}_1, S^{(0)}_2, S^{(0)}_3\), and \(S^{(0)}_4\) is assumed to be \(1, 1, 1, 10\) for all boundary conditions and mode orders.
-This differs from the iterative SOV method \citealp{xing2018overall}, which requires a different initial guess for each mode order.
 The translational springs (\(k^v_\xi\)) and rotational springs (\(k^r_\xi\)) along all edges can be set to zero or infinity (represented as \(1 \times 10^{15} \ustif\) in the numerical calculations of this study) to obtain different classic boundary conditions.
@@
 The results for SSSS, SCSF, GCGC, CCCC, SSCC, SCCC, GGCC, CCFF, CFCF, CFFF, and FFFF boundary conditions are presented in \Cref{tab:sov1,tab:sov2,tab:sov3}. 
-These results demonstrate high accuracy compared to the extended SOV method, with errors remaining smaller than the interval between the upper and lower bounds (0.005).
+These results demonstrate high accuracy compared to the extended SOV method, with difference remaining smaller than the frequency parameter interval $2a\Delta\Omega=0.005$. 
 The frequency parameters in both directions are equal (\(2a\Omega_x - 2a\Omega_y = 0\)) in almost all cases, with a few exceptions where \(2a\Omega_x - 2a\Omega_y = 0.005\). 
-\Cref{fig:FFFF} shows the first six nonzero mode shapes of a square orthotropic plate with FFFF boundary conditions.
+In fact, higher accuracy compared to the extended SOV method can be achieved if the frequency parameter interval \(2a\Delta\Omega\) is set smaller than 0.005.
+It should be noted that the accuracy improves only by reducing \(2a\Delta\Omega\), and no additional iterations are required according to our calculations.
+\Cref{fig:FFFF} shows the first six nonzero mode shapes of a square orthotropic plate with FFFF boundary conditions, where the mode shape coefficients are calculated using the numerical method developed in this study.
+Instead of selecting fixed expressions for the mode shape coefficients based on specific boundary conditions, our method is applicable to all boundary conditions.
 
@@
 		&     & extended SOV \Citealp{xing2020extended}   & 4.3602 & 5.8384 & 7.2531 & 7.8560 & 7.9481 & 9.2515 & 10.0366 \\
-		&     & Present       & 4.3625 & -5.8325 & 7.2525 & 7.8575 & 7.9525 & 9.2525 & 10.0325 \\
+		&     & Present       & 4.3625 & 5.8325 & 7.2525 & 7.8575 & 7.9525 & 9.2525 & 10.0325 \\
 		SCCC & 0.5 & Mode number & (1,1) & (1,2) & (1,3) & (1,4) & (1,5) & (1,6) & (1,7) \\
@@
 		\cmidrule(lr){3-8}
-		$r_{\xi}=r_{\eta}$ & Mode & 1 & 2 & 3 & 4 & 5 & 6 \\ 
+		$r$ & Mode & 1 & 2 & 3 & 4 & 5 & 6 \\ 
 		\midrule
@@
 		& Ref.\Citealp{zhang2019new} & 4.465 & 7.039 & 7.039 &8.897  &9.945& 9.945 \\
-		& Present ($\Omega$)   & 4.463    & 7.035     & 7.035      &8.893     & 9.945     & 9.945   \\
 		& Present ($\Omega_x$)   & 4.463     & 7.028     & 7.043     & 8.893     & 9.938       & 9.953  \\
 		& Present ($\Omega_y$)   & 4.463    &7.043     &  7.028       & 8.893   &  9.953    & 9.938 \\ 
+		& Present ($\Omega$)   & 4.463    & 7.035     & 7.035      &8.893     & 9.945     & 9.945   \\
 		&Difference (\%)& 0.044     & 0.056      & 0.056      & 0.044     &  0.000     & 0.000
@@
 		& Ref.\Citealp{zhang2019new} & 4.637 &7.155 & 7.155 & 8.991 & 10.029 & 10.030 \\
-		& Present ($\Omega$)   & 4.648      & 7.160   & 7.160     & 8.993    &   10.030   & 10.033   \\
 		& Present ($\Omega_x$)   & 4.648     & 7.098      &7.223     & 8.993     &   10.093    & 9.968  \\
@@
 		\\ 
+		& Present ($\Omega$)   & 4.648      & 7.160   & 7.160     & 8.993    &   10.030   & 10.033   \\
 		&Difference (\%)& 0.237    & 0.069      & 0.069      & 0.022     &  0.009     &0.029
@@
 		& Ref.\Citealp{zhang2019new}  & 5.346 & 7.768 & 7.768 & 9.537 & 10.552 & 10.563 \\
-		& Present ($\Omega$)   &5.413      & 7.835     & 7.835     & 9.598   &  10.615    & 10.618  \\
 		& Present ($\Omega_x$)   & 5.413      & 7.718      & 7.953     & 9.598     & 10.448      & 10.782 \\
@@
 		\\ 
+		& Present ($\Omega$)   &5.413      & 7.835     & 7.835     & 9.598   &  10.615    & 10.618  \\
 		&Difference (\%)& 1.253     & 0.862      & 0.862      & 0.639     &  0.597     & 0.520  \\
@@
 		& Ref.\Citealp{zhang2019new} & 5.901 & 8.442 & 8.442 & 10.253 & 11.307 & 11.333 \\
-		& Present ($\Omega$)   & 5.913     & 8.450     & 8.450     & 10.258     &  11.333    & 11.333  \\
 		& Present ($\Omega_x$)   & 5.913     & 8.428      & 8.473    & 10.258     & 11.293      & 11.373 \\
@@
 		\\ 
+		& Present ($\Omega$)   & 5.913     & 8.450     & 8.450     & 10.258     &  11.333    & 11.333  \\
 		&Difference (\%)& 0.203     & 0.094      & 0.094      & 0.048     & 0.229     & 0.000 \\
@@
 		& Ref.\Citealp{zhang2019new} & 6.011 & 8.585 & 8.585 & 10.424 & 11.495 & 11.522 \\
-		& Present ($\Omega$)   & 5.988      & 8.553    & 8.553     & 10.388    &  11.470     & 11.470  \\
 		& Present ($\Omega_x$)   & 5.988     & 8.553      & 8.553      & 10.388      & 11.463      & 11.478 \\
@@
 		\\ 
+		& Present ($\Omega$)   & 5.988      & 8.553    & 8.553     & 10.388    &  11.470     & 11.470  \\
 		&Difference (\%)& 0.382    & 0.372      & 0.372      & 0.345     &  0.217     & 0.451
@@
 The maximum observed difference is $0.8\%$ when \(r_{\eta=-1} = 10\).
-Furthermore, \Cref{fig:oth} shows how the fundamental mode shape of the square orthotropic plate evolves as the rotational spring stiffness \(k^r_{\eta=-1}\) increases.
 
@@
 \end{table}
-\begin{figure}
-	\centering
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{figs/otho0.png}
-		\caption[]%
-		{{\small }}    
-		\label{fig:otho0}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.49\textwidth}  
-		\centering 
-		\includegraphics[width=\textwidth]{figs/otho1.png}
-		\caption[]%
-		{{\small }}    
-		\label{fig:otho1}
-	\end{subfigure}
-	\vfill
-	\begin{subfigure}[b]{0.49\textwidth}   
-		\centering 
-		\includegraphics[width=\textwidth]{figs/otho10.png}
-		\caption[]%
-		{{\small }}    
-		\label{fig:otho10}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.49\textwidth}   
-		\centering 
-		\includegraphics[width=\textwidth]{figs/otho20.png}
-		\caption[]%
-		{{\small }}    
-		\label{fig:otho20}
-	\end{subfigure}
-	\vskip\baselineskip
-	\begin{subfigure}[b]{0.49\textwidth}   
-		\centering 
-		\includegraphics[width=\textwidth]{figs/otho100.png}
-		\caption[]%
-		{{\small}}    
-		\label{fig:otho100}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.49\textwidth}   
-		\centering 
-		\includegraphics[width=\textwidth]{figs/othoinf.png}
-		\caption[]%
-		{{\small }}    
-		\label{fig:othoinf}
-	\end{subfigure}
-	\caption[]  
-	{\small The first mode shape of a square orthotropic plate with the edge at \(\eta=-1\) rotationally restrained: (a) \(r_{\eta=-1} = 0\); (b) \(r_{\eta=-1} = 1\); (c) \(r_{\eta=-1} = 10\); (d) \(r_{\eta=-1} = 20\); (e) \(r_{\eta=-1} = 100\); (f) \(r_{\eta=-1} = \infty\).}
-	\label{fig:oth}  
-\end{figure}
+
 \FloatBarrier
 \section{Conclusion}
-In this study, the dynamic stiffness matrix (DSM) based on the extended separation-of-variable (SOV) mode functions has been developed for the vibration analysis of an orthotropic rectangular plate with general homogeneous boundary conditions.
-
-Based on the Rayleigh quotient, the governing equation of the plate, along with the shear force and bending moment equilibrium related to the boundary conditions, are derived.  
-The extend-SOV type solutions obtained from the governing equation are then used to develop the dynamic stiffness matrices by applying the boundary conditions.
-Instead of solving eigenvalue equations involving highly nonlinear and transcendental functions derived from the determinant of the dynamic stiffness matrix, a refined W-W algorithm based on the 'hypothetical structure method' is developed to address this eigenvalue problem.
-The challenge of determining the fully clamped frequencies using the W-W algorithm is resolved by finding the simply supported frequencies, whose closed-form expression can be easily derived based on the SOV method.
-Due to the improved W-W algorithm and the concise SOV-form solutions, the process of solving the dynamic stiffness matrix becomes more systematic and efficient.
+In this study, the dynamic stiffness matrix (DSM) based on the extended separation-of-variable (SOV) type solution has been developed for the vibration analysis of an orthotropic rectangular plate with general homogeneous boundary conditions.
+
+Instead of solving highly nonlinear eigenvalue equations involved in the SOV methods, the extended SOV type solution is adopted to construct the dynamic stiffness matrices.
+Several novel techniques have proposed to solve the eigenvalue problem and mode shape computation.
+The challenge of determining the fully clamped frequencies using the Wittrick-Williams (W-W) algorithm is resolved by finding the simply supported frequencies, whose closed-form expression can be easily derived based on the SOV method.
 
 Classical boundary conditions, such as guided, simply supported, clamped, and free edges, can be realized by setting the translational springs (\(k^v_\xi\)) and rotational springs (\(k^r_\xi\)) along the plate edges to either zero or infinity.
-Numerical results confirm that accurate solutions are obtained for these boundary conditions.  
-Despite some approximations in certain elastically restrained boundary conditions, the maximum percentage error across all numerical experiments remains within $1.25\%$.  
-This may occur because the SOV-form solutions used are derived from the weak-form governing equation, which is based on Rayleigh's principle.
-
-Since the SOV-form solution \(\phi(\xi) \psi(\eta)\) consists of only a single term, unlike the infinite series expansions used in the traditional DSM, each eigenvalue solution can be explicitly expressed.
-This suggests the potential for obtaining concise and closed-form solutions for assembled plate structures compared to traditional DSM methods.
+Numerical experiments have validated accuracy of this approach for these boundary conditions.  
+The results shows that the SOV type solution can also be extended to handle elastically restrained boundary conditions.
+Despite certain approximations inherent in some elastically restrained cases, the maximum percentage error across all numerical experiments remains within $1.25\%$.  
+This may occur because the SOV type solution used is derived from the weak-form governing equation, which is based on Rayleigh's principle.
+
+Since the SOV type solution \(\phi(\xi) \psi(\eta)\) consists of only a single term for each mode order, unlike the infinite series expansions used in the traditional DSM, each eigenvalue solution can be explicitly expressed.
+This suggests the potential for obtaining more concise solutions for assembled plate structures compared to traditional DSM methods.
 
@@
 \section{Integral parameters}\label{appendA}
-The integral parameters \( S_1, S_2, S_3, \) and \( S_4 \) are defined as follows:
+The integral parameters \( I_1, I_2, I_3, \) and \( I_4 \) are defined as follows:
 %
@@
 	\begin{aligned}
-		S_1 &= \int_{0}^{1} \psi^2 \, d\eta \\
+		I_1 &= \int_{0}^{1} \psi^2 \, d\eta \\
 		&= (B_1^2 + B_2^2 - B_3^2 + B_4^2) 
@@
 \begin{split}
-	S_2 &= \int_{0}^{1} \left( \psi \frac{d^2 \psi}{d \eta^2} \right) d \eta \\
+	I_2 &= \int_{0}^{1} \left( \psi \frac{d^2 \psi}{d \eta^2} \right) d \eta \\
 	&= \left( -\alpha_2^2 B_1^2 - \alpha_2^2 B_2^2 - \beta_2^2 B_3^2 + \beta_2^2 B_4^2 \right) \\
@@
 	\begin{aligned}
-		S_3 &= \int_{0}^{1} \left(\frac{d\psi}{d\eta}\right)^2 \, d\eta \\
+		I_3 &= \int_{0}^{1} \left(\frac{d\psi}{d\eta}\right)^2 \, d\eta \\
 		&= \alpha_2^2 B_1^2 + \alpha_2^2 B_2^2 + \beta_2^2 B_3^2 - \beta_2^2 B_4^2 \\
@@
 	\begin{split}
-		S_4 &= \int_{0}^{1} \left( \frac{d^2 \psi}{d \eta^2} \right)^2 d \eta \\
+		I_4 &= \int_{0}^{1} \left( \frac{d^2 \psi}{d \eta^2} \right)^2 d \eta \\
 		&= \left( \alpha_2^4 B_1^2 + \alpha_2^4 B_2^2 - \beta_2^4 B_3^2 + \beta_2^4 B_4^2 \right) \\
@@
 %
-The integral parameters \( T_1 \), \( T_2 \), \( T_3 \), and \( T_4 \) can be obtained by replacing \( B_1 \) to \( B_4 \) by \( A_1 \) to \( A_4 \), respectively, and \( \alpha_2 \) and \( \beta_2 \) by \( \alpha_1 \) and \( \beta_1 \), respectively.
+The integral parameters \( J_1 \), \( J_2 \), \( J_3 \), and \( J_4 \) can be obtained by replacing \( B_1 \) to \( B_4 \) by \( A_1 \) to \( A_4 \), respectively, and \( \alpha_2 \) and \( \beta_2 \) by \( \alpha_1 \) and \( \beta_1 \), respectively.
 

### 2025-05-16 Paper7.tex
some twist

@@
 
-Inspired by the Navier and Levy solutions, \citet{xing2009new} proposed the separation-of-variables (SOV) method, which provides concise and explicit eigensolutions.
+Inspired by the Navier and Levy solutions, \citet{xing2009new} proposed the SOV method, which provides concise and explicit eigensolutions.
 The mode shape function has a separable form, $\phi(x) \psi(y)$, requiring only one $\phi(x)$ and one $\psi(y)$ for each mode order, allowing each eigenvalue equation to be explicitly expressed.
@@
 \end{figure}
-Consider a thin orthotropic rectangular plate of length \(2a\) and width \(2b\), with all four edges restrained by vertical translational springs \(k^v\) and rotational springs \(k^r\), as shown in \Cref{fig:platemode}.
+Consider a thin orthotropic rectangular plate of length $2a$ and width $2b$, with all four edges restrained by vertical translational springs $k^v$ and rotational springs $k^r$, as shown in \Cref{fig:platemode}.
 The coordinate origin is located at the center of the plate.
@@
 %
-where \( \alpha = a / b \) is the aspect ratio; \( \xi = x / a \) and \( \eta = y / b \) are the normalized coordinates,
+where $ \alpha = a / b $ is the aspect ratio; $ \xi = x / a $ and $ \eta = y / b $ are the normalized coordinates,
 and the bending stiffness parameters are defined as:
@@
 	\begin{split}
-		&D_{11} = \frac{E_1h^3}{12(1-v_{12}v_{21})}, \quad D_{22} = \frac{E_2h^3}{12(1-v_{12}v_{21})}, \\  
+		&D_{11} = \frac{E_1h^3}{12(1-v_{12}v_{21})}, \qquad D_{22} = \frac{E_2h^3}{12(1-v_{12}v_{21})}, \\  
 		&D_{66} = \frac{G_{12}h^3}{12}, \quad D_{12} = v_{12}D_{22} = v_{21}D_{11}, \quad D_3 = D_{12} + 2D_{66},
@@
 %
-where \(\rho\) and \(h\) denote the mass density and thickness of the plate, respectively; \(E_1\) and \(E_2\) are the Young’s moduli in the \(x\)- and \(y\)-directions, respectively; \(G_{12}\) is the shear modulus, and \(v_{12}\) and \(v_{21}\) are the Poisson’s ratios.
+where $\rho$ and $h$ denote the mass density and thickness of the plate, respectively; $E_1$ and $E_2$ are the Young’s moduli in the $x$- and $y$-directions, respectively; $G_{12}$ is the shear modulus, and $v_{12}$ and $v_{21}$ are the Poisson’s ratios.
 
@@
 %
-where \(\delta\) denotes variation, \(U_{mag}\) is the magnitude of the potential energy of the plate, and \(\omega^2 T_0\) represents the magnitude of the kinetic energy of the plate.
+where $\delta$ denotes variation, $U_{mag}$ is the magnitude of the potential energy of the plate, and $\omega^2 T_0$ represents the magnitude of the kinetic energy of the plate.
 The potential energy of the plate can be expressed as \cite{xing2020extended}:
@@
 
-Assuming the solution of the deflection \( W(x, y; t) = w(x, y) e^{i \omega t} \) for harmonic plate motion, 
-where \( \ii = \sqrt{-1} \), \( w(x, y) \) is the mode shape, and \( \omega \) is the radial frequency.  
-By substituting \( W(x, y; t) = w(x, y) e^{i \omega t} \) into \Cref{eq:poten_energy,eq:kine_energy} and expressing the system in dimensionless coordinates, we have:
+Assuming the solution of the deflection $ W(x, y; t) = w(x, y) e^{i \omega t} $ for harmonic plate motion, 
+where $ \ii = \sqrt{-1} $, $ w(x, y) $ is the mode shape, and $ \omega $ is the radial frequency.  
+By substituting $ W(x, y; t) = w(x, y) e^{i \omega t} $ into \Cref{eq:poten_energy,eq:kine_energy} and expressing the system in dimensionless coordinates, we have:
 %
@@
 %
-The separable form of the mode shape function \( w(\xi, \eta) \) is given by:
+The separable form of the mode shape function $ w(\xi, \eta)$ is given by:
 %
@@
 %
-where \( \phi(\xi) \) and \( \psi(\eta) \) can be expressed as:
+where $ \phi(\xi) $ and $\psi(\eta) $ can be expressed as:
 \begin{subequations}\label{eq:phi_psi_solution}
@@
 For given general homogeneous boundary conditions, we can first assume that the mode shape $\psi(\eta)$ corresponding to the $y$-direction is known. 
-Supposing the edges of the plate in both the \(x\)- and \(y\)-directions are elastically restrained by homogeneous vertical translational and rotational springs.
-The vertical translational and rotational springs at the \(\xi = -1\) end are defined as \(k^v_{\xi = -1}\) and \(k^r_{\xi = -1}\), respectively, and at the \(\xi = 1\) end as \(k^v_{\xi = 1}\) and \(k^r_{\xi = 1}\), respectively.
-Thus, the potential energy along the supported edge in the \(x\)-direction can be expressed by:
+Supposing the edges of the plate in both the $x$- and $y$-directions are elastically restrained by homogeneous vertical translational and rotational springs.
+The vertical translational and rotational springs at the $\xi = -1$ end are defined as $k^v_{\xi = -1}$ and $k^r_{\xi = -1}$, respectively, and at the $\xi = 1$ end as $k^v_{\xi = 1}$ and $k^r_{\xi = 1}$, respectively.
+Thus, the potential energy along the supported edge in the $x$-direction can be expressed by:
 %
@@
 		U^{II} &=  \int\left[k^r_{\xi=-1} \left( \frac{\partial W}{\partial x} \right)^2 + k^v_{\xi=-1} \left( W \right)^2\right]_{x=-a} \id y\\
-		&\quad +  \int\left[k^r_{\xi=1} \left( \frac{\partial W}{\partial x} \right)^2 + k^v_{\xi=1} \left( W \right)^2\right]_{x=a} \id y.
-	\end{split}
-\end{equation}
-%
-From \Cref{eq:poten_energy_edgex}, the magnitude of total potential energy along the edges in the \(x\)-direction is obtained as:
+		&\qquad +  \int\left[k^r_{\xi=1} \left( \frac{\partial W}{\partial x} \right)^2 + k^v_{\xi=1} \left( W \right)^2\right]_{x=a} \id y.
+	\end{split}
+\end{equation}
+%
+From \Cref{eq:poten_energy_edgex}, the magnitude of total potential energy along the edges in the $x$-direction is obtained as:
 %
@@
 		U^{II}_{mag} &= ab \int\left[\frac{k^r_{\xi=-1}}{a^3} \left( \frac{\partial w}{\partial \xi} \right)^2 + \frac{k^v_{\xi=-1}}{a} \left( w \right)^2\right]_{\xi=-1} \, \id \eta \\
-		&\quad + ab \int\left[\frac{k^r_{\xi=1}}{a^3} \left( \frac{\partial w}{\partial \xi} \right)^2 + \frac{k^v_{\xi=1}}{a} \left( w \right)^2\right]_{\xi=1} \, \id \eta.
-	\end{split}
-\end{equation}
-%
-The magnitude of potential energy of the plate in the \(x\)-direction can be obtained from \Cref{eq:poten_energy_mag,eq:poten_energy_edgex2} as:
+		&\qquad + ab \int\left[\frac{k^r_{\xi=1}}{a^3} \left( \frac{\partial w}{\partial \xi} \right)^2 + \frac{k^v_{\xi=1}}{a} \left( w \right)^2\right]_{\xi=1} \, \id \eta.
+	\end{split}
+\end{equation}
+%
+The magnitude of potential energy of the plate in the $x$-direction can be obtained from \Cref{eq:poten_energy_mag,eq:poten_energy_edgex2} as:
 %
@@
 \\
-		&\quad \left.
+		&\qquad \left.
 + \frac{4 D_{66}}{a^2 b^2} \left( \frac{\partial^2 w}{\partial \xi \partial \eta} \right)^2 \right] \, \id\xi \, \id\eta + ab \int \left[\frac{k^r_{\xi=1}}{a^3} \left( \frac{\partial w}{\partial \xi} \right)^2 + \frac{k^v_{\xi=1}}{a} \left( w \right)^2 \right]_{\xi=1} \, \id \eta \\
-		&\quad  + ab \int \left[\frac{k^r_{\xi=-1}}{a^3} \left( \frac{\partial w}{\partial \xi} \right)^2 + \frac{k^v_{\xi=-1}}{a} \left( w \right)^2 \right]_{\xi=-1} \, \id \eta
+		&\qquad  + ab \int \left[\frac{k^r_{\xi=-1}}{a^3} \left( \frac{\partial w}{\partial \xi} \right)^2 + \frac{k^v_{\xi=-1}}{a} \left( w \right)^2 \right]_{\xi=-1} \, \id \eta
 	\end{split}
@@
 \\
-		&\quad \left.
+		&\qquad \left.
 + \frac{4 D_{66}}{a^2 b^2}I_3 \left( \frac{\id \phi }{\id \xi}\right)^2 \right] \, \id\xi +abI_1 \left[\frac{k^r_{\xi=-1}}{a^3} \left( \frac{\id \phi}{\id \xi} \right)^2+ \frac{k^v_{\xi=-1}}{a} \left( \phi \right)^2\right]_{\xi=-1}\\
-		&\quad+abI_1 \left[\frac{k^r_{\xi=1}}{a^3} \left( \frac{\id \phi}{\id \xi} \right)^2+ \frac{k^v_{\xi=1}}{a} \left( \phi \right)^2\right]_{\xi=1},
+		&\qquad+abI_1 \left[\frac{k^r_{\xi=1}}{a^3} \left( \frac{\id \phi}{\id \xi} \right)^2+ \frac{k^v_{\xi=1}}{a} \left( \phi \right)^2\right]_{\xi=1},
 	\end{split}
@@
 %
-By taking \Cref{eq:displace_func} into account, the coefficient \(T_0\) of the kinetic energy from \Cref{eq:kine_energy_mag} for the plate can be expressed as:
+By taking \Cref{eq:displace_func} into account, the coefficient $T_0$ of the kinetic energy from \Cref{eq:kine_energy_mag} for the plate can be expressed as:
 %
@@
 %
-By substituting \Cref{eq:poten_energy_tolx2,eq:kine_energyx} into \Cref{eq:Rayleighx}, and relieving \(\delta \phi\) and \(\delta\frac{\id  \phi}{\id \xi}\) in \Cref{eq:Rayleighx} by variation calculus, yields:
+By substituting \Cref{eq:poten_energy_tolx2,eq:kine_energyx} into \Cref{eq:Rayleighx}, and relieving $\delta \phi$ and $\delta\frac{\id  \phi}{\id \xi}$ in \Cref{eq:Rayleighx} by variation calculus, yields:
 %
@@
 		+ \bigg( \frac{2D_{12}}{a^2b^2} I_2 - \frac{4D_{66}}{a^2b^2} I_3 \bigg) \frac{\id^2 \phi}{\id \xi^2} \\
-		&\quad + \bigg( \frac{D_{22}}{b^4} I_4 - \omega_x^2 \rho h I_1 \bigg) \phi \bigg] \delta \phi \, \id \xi \\
-		&\quad + \frac{2k^v_{\xi=-1}}{a} I_1 \big(\phi \delta \phi\big)_{\xi=-1} 
+		&\qquad + \bigg( \frac{D_{22}}{b^4} I_4 - \omega_x^2 \rho h I_1 \bigg) \phi \bigg] \delta \phi \, \id \xi \\
+		&\qquad + \frac{2k^v_{\xi=-1}}{a} I_1 \big(\phi \delta \phi\big)_{\xi=-1} 
 		+ \frac{2k^v_{\xi=1}}{a} I_1 \big(\phi \delta \phi\big)_{\xi=1} \\
-		&\quad + \bigg[ \bigg( \frac{4D_{66}}{a^2b^2} I_3 - \frac{D_{12}}{a^2b^2} I_2 \bigg) \frac{\id \phi}{\id \xi} 
+		&\qquad + \bigg[ \bigg( \frac{4D_{66}}{a^2b^2} I_3 - \frac{D_{12}}{a^2b^2} I_2 \bigg) \frac{\id \phi}{\id \xi} 
 		- \frac{D_{11}}{a^4} I_1 \frac{\id^3 \phi}{\id \xi^3} \bigg] \delta \phi \Big|^{\xi=1}_{\xi=-1} \\
-		&\quad + \bigg( \frac{D_{12}}{a^2b^2} I_2 \phi + \frac{D_{11}}{a^4} I_1 \frac{\id^2 \phi}{\id \xi^2} \bigg) 
+		&\qquad + \bigg( \frac{D_{12}}{a^2b^2} I_2 \phi + \frac{D_{11}}{a^4} I_1 \frac{\id^2 \phi}{\id \xi^2} \bigg) 
 		\delta\frac{\id  \phi}{\id \xi} \Big|^{\xi=1}_{\xi=-1} \\
-		&\quad + \frac{2k^r_{\xi=-1}}{a^3} I_1 \bigg(\frac{\id \phi}{\id \xi}\delta \frac{\id \phi}{\id \xi}\bigg)_{\xi=-1} 
+		&\qquad + \frac{2k^r_{\xi=-1}}{a^3} I_1 \bigg(\frac{\id \phi}{\id \xi}\delta \frac{\id \phi}{\id \xi}\bigg)_{\xi=-1} 
 		+ \frac{2k^r_{\xi=1}}{a^3} I_1 \bigg(\frac{\id \phi}{\id \xi} \delta\frac{\id \phi}{\id \xi}\bigg)_{\xi=1}.
@@
 %
-Thus, the governing differential equation in the \( x \)-direction can be obtained from the integration part in \Cref{eq:Rayleighx2}:
+Thus, the governing differential equation in the $ x $-direction can be obtained from the integration part in \Cref{eq:Rayleighx2}:
 %
@@
 %
-where \(\Omega_x = \sqrt[4]{\omega_x^2 \rho h / D_{11}}\).
-By substituting \(\phi(\xi) = A e^{\mu \xi}\) into \Cref{eq:ODEx}, yields:
+where $\Omega_x = \sqrt[4]{\omega_x^2 \rho h / D_{11}}$.
+By substituting $\phi(\xi) = A e^{\mu \xi}$ into \Cref{eq:ODEx}, yields:
 %
@@
 %
-The solution for \(\mu\) can be expressed as:
+The solution for $\mu$ can be expressed as:
 %
@@
 %
-The boundary conditions along the edges in the \(x\)-direction can be obtained from the remaining \(\delta \phi\) and \(\delta \frac{\id \phi}{\id \xi}\) parts in \Cref{eq:Rayleighx2}. 
-The shear force equilibrium can be obtained from the \(\delta \phi\) part:
+The boundary conditions along the edges in the $x$-direction can be obtained from the remaining $\delta \phi$ and $\delta \frac{\id \phi}{\id \xi}$ parts in \Cref{eq:Rayleighx2}. 
+The shear force equilibrium can be obtained from the $\delta \phi$ part:
 %
@@
 		- \frac{D_{11}}{a^4} I_1 \frac{\id^3 \phi}{\id \xi^3} \right] \Big|^{\xi=1}_{\xi=-1}\\
-		&\quad+ \frac{2k^v_{\xi=-1}}{a} I_1 \left(\phi\right)_{\xi=-1}
+		&\qquad+ \frac{2k^v_{\xi=-1}}{a} I_1 \left(\phi\right)_{\xi=-1}
 		 + \frac{2k^v_{\xi=1}}{a} I_1 \left(\phi\right)_{\xi=1} = 0,
@@
 %
-and from the \(\delta \frac{\id \phi}{\id \xi}\) part, the bending moment equilibrium:
+and from the $\delta \frac{\id \phi}{\id \xi}$ part, the bending moment equilibrium:
 %
@@
 		&+ \frac{2k^r_{\xi=-1}}{a^3} I_1 \left(\frac{\partial \phi}{\partial \xi}\right)_{\xi=-1} \\
-		&+ \frac{2k^r_{\xi=1}}{a^3} I_1 \left(\frac{\partial \phi}{\partial \xi}\right)_{\xi=1} = 0.
-	\end{split}
-\end{equation}
-%
-Thus, we can obtain the shear force and bending moment equilibrium along the edges \(\xi = -1\) and \(\xi = 1\) from \Cref{eq:inertial_forcex,eq:inertial_forcex2}, respectively, as:
+		& \qquad\frac{2k^r_{\xi=1}}{a^3} I_1 \left(\frac{\partial \phi}{\partial \xi}\right)_{\xi=1} = 0.
+	\end{split}
+\end{equation}
+%
+Thus, we can obtain the shear force and bending moment equilibrium along the edges $\xi = -1$ and $\xi = 1$ from \Cref{eq:inertial_forcex,eq:inertial_forcex2}, respectively, as:
 %
@@
 %
-Substituting \Cref{eq:phi_solution1} into \Cref{eq:boundaryx}, and denoting \( k^{v*}_{\xi} = \frac{2a^3 k^v_{\xi}}{D_{11}} \), \( k^{r*}_{\xi} = \frac{2a k^r_{\xi}}{D_{11}} \), \( S_{\alpha_1}=\sin\alpha_1  \), \( C_{\alpha_1}=\cos\alpha_1 \), \( Sh_{\alpha_1}=\sinh\alpha_1 \), \( Ch_{\alpha_1}=\cosh\alpha_1  \), \(S_{\beta_1}= \sin\beta_1 \), \( C_{\beta_1}=\cos\beta_1 \), \( Sh_{\beta_1}=\sinh\beta_1  \), and \(  Ch_{\beta_1}=\cosh\beta_1 \), we have:
+Substituting \Cref{eq:phi_solution1} into \Cref{eq:boundaryx}, and denoting $ k^{v*}_{\xi} = \frac{2a^3 k^v_{\xi}}{D_{11}} $, $ k^{r*}_{\xi} = \frac{2a k^r_{\xi}}{D_{11}} $, $ S_{\alpha_1}=\sin\alpha_1 $, $ C_{\alpha_1}=\cos\alpha_1 $, $ Sh_{\alpha_1}=\sinh\alpha_1 $, $ Ch_{\alpha_1}=\cosh\alpha_1 $, $S_{\beta_1}= \sin\beta_1 $, $C_{\beta_1}=\cos\beta_1$, $Sh_{\beta_1}=\sinh\beta_1 $, and $  Ch_{\beta_1}=\cosh\beta_1 $, we have:
 %
@@
 
-\subsection{Dynamic stiffness matrix corresponding to \(\omega_y\)}\label{sec:DSMy}
-In this section, the mode shape \(\phi(\xi)\) derived in \(\Cref{sec:DSMx}\) is utilized to obtain the dynamic stiffness matrix in the \(y\)-direction.  
-The vertical translational and rotational springs at \(\eta = -1\) are denoted as \(k^v_{\eta = -1}\) and \(k^r_{\eta = -1}\), respectively, while those at \(\eta = 1\) are represented by \(k^v_{\eta = 1}\) and \(k^r_{\eta = 1}\).
-
-The magnitude of total potential energy along the edges in the \( y \)-direction is given by:  
+\subsection{Dynamic stiffness matrix corresponding to $\omega_y$}\label{sec:DSMy}
+In this section, the mode shape $\phi(\xi)$ derived in $\Cref{sec:DSMx}$ is utilized to obtain the dynamic stiffness matrix in the $y$-direction.  
+The vertical translational and rotational springs at $\eta = -1$ are denoted as $k^v_{\eta = -1}$ and $k^r_{\eta = -1}$, respectively, while those at $\eta = 1$ are represented by $k^v_{\eta = 1}$ and $k^r_{\eta = 1}$.
+
+The magnitude of total potential energy along the edges in the $y$-direction is given by:  
 %
@@
 		U^{III}_{mag} &= ab \int \left[ \frac{k^r_{\eta=-1}}{a^3} \left( \frac{\partial w}{\partial \eta} \right)^2 + \frac{k^v_{\eta=-1}}{a} w^2 \right]_{\eta=-1} \id \xi \\  
-		&\quad + ab \int \left[ \frac{k^r_{\eta=1}}{a^3} \left( \frac{\partial w}{\partial \eta} \right)^2 + \frac{k^v_{\eta=1}}{a} w^2 \right]_{\eta=1} \id \xi.  
-	\end{split}  
-\end{equation} 
-% 
-The magnitude of potential energy of the plate in the \(y\)-direction can be obtained from
+		&\qquad + ab \int \left[ \frac{k^r_{\eta=1}}{a^3} \left( \frac{\partial w}{\partial \eta} \right)^2 + \frac{k^v_{\eta=1}}{a} w^2 \right]_{\eta=1} \id \xi.  
+	\end{split}  
+\end{equation} 
+% 
+The magnitude of potential energy of the plate in the $y$-direction can be obtained from
 \Cref{eq:poten_energy_mag,eq:poten_energy_edgey2} as:
@@
 \\
-		&\quad \left.
+		&\qquad \left.
 + \frac{4 D_{66}}{a^2 b^2}\left( \frac{\partial^2 w}{\partial \xi \partial \eta} \right)^2 \right] \, \id\xi \, \id\eta+ab \int \left[ \frac{k^r_{\eta=1}}{b^3} \left( \frac{\partial w}{\partial \eta} \right)^2 + \frac{k^v_{\eta=1}}{b} \left( w \right)^2 \right]_{\eta=1} \id\xi\\
-		&\quad+ab \int \left[ \frac{k^r_{\eta=-1}}{b^3} \left( \frac{\partial w}{\partial \eta} \right)^2 + \frac{k^v_{\eta=-1}}{b} \left( w \right)^2 \right]_{\eta=-1} \id\xi.
+		&\qquad+ab \int \left[ \frac{k^r_{\eta=-1}}{b^3} \left( \frac{\partial w}{\partial \eta} \right)^2 + \frac{k^v_{\eta=-1}}{b} \left( w \right)^2 \right]_{\eta=-1} \id\xi.
 	\end{split}
@@
 		+ \frac{D_{22}}{b^4} J_1 \left(\frac{\id^2\psi }{\id \eta^2} \right)^2 \right. \\
-		&\quad \left. + \frac{4D_{66}}{a^2b^2} J_3 \left(\frac{\id \psi }{\id \eta} \right)^2 \right] \, \id\eta  + abJ_1 \left[ \frac{k^r_{\eta=1}}{b^3} \left( \frac{\id \psi}{\id \eta} \right)^2
+		&\qquad \left. + \frac{4D_{66}}{a^2b^2} J_3 \left(\frac{\id \psi }{\id \eta} \right)^2 \right] \, \id\eta  + abJ_1 \left[ \frac{k^r_{\eta=1}}{b^3} \left( \frac{\id \psi}{\id \eta} \right)^2
 		+ \frac{k^v_{\eta=1}}{b}  \left(\psi\right)^2 \right]_{\eta=1} \\
-		&\quad + abJ_1 \left[ \frac{k^r_{\eta=-1}}{b^3} \left( \frac{\id \psi}{\id \eta} \right)^2
+		&\qquad + abJ_1 \left[ \frac{k^r_{\eta=-1}}{b^3} \left( \frac{\id \psi}{\id \eta} \right)^2
 		+ \frac{k^v_{\eta=-1}}{b} \left(\psi\right)^2 \right]_{\eta=-1},
@@
 %
-The coefficient \( T_0 \) of the kinetic energy from \Cref{eq:kine_energy_mag} for the plate can be expressed as:
+The coefficient $T_0$ of the kinetic energy from \Cref{eq:kine_energy_mag} for the plate can be expressed as:
 %
@@
 %
-By substituting \Cref{eq:poten_energy_toly2,eq:kine_energyy} into \Cref{eq:Rayleighy}, and relieving \( \delta \psi \) and \( \delta\frac{\id \psi}{\id \eta} \) in \Cref{eq:Rayleighy} by variation calculus, yields:
+By substituting \Cref{eq:poten_energy_toly2,eq:kine_energyy} into \Cref{eq:Rayleighy}, and relieving $ \delta \psi $ and $\delta\frac{\id \psi}{\id \eta}$ in \Cref{eq:Rayleighy} by variation calculus, yields:
 %
@@
 		+ \left( \frac{2D_{12}}{a^2b^2} J_2 - \frac{4D_{66}}{a^2b^2} J_3 \right) \frac{\id^2 \psi}{\id \eta^2} \right. \\
-		&\quad \left. + \left( \frac{D_{11}}{a^4} J_4 - \omega_y^2 \rho h J_1 \right) \psi \right] \delta \psi \, \id\eta \\
-		&\quad + \frac{2k^v_{\eta=-1}}{b} J_1 (\psi \delta \psi)_{\eta=-1} 
+		&\qquad \left. + \left( \frac{D_{11}}{a^4} J_4 - \omega_y^2 \rho h J_1 \right) \psi \right] \delta \psi \, \id\eta \\
+		&\qquad + \frac{2k^v_{\eta=-1}}{b} J_1 (\psi \delta \psi)_{\eta=-1} 
 		+ \frac{2k^v_{\eta=1}}{b} J_1 (\psi \delta \psi)_{\eta=1} \\
-		&\quad + \left[ \left( \frac{4D_{66}}{a^2b^2} J_3 - \frac{D_{12}}{a^2b^2} J_2 \right) \frac{\id \psi}{\id \eta} 
+		&\qquad + \left[ \left( \frac{4D_{66}}{a^2b^2} J_3 - \frac{D_{12}}{a^2b^2} J_2 \right) \frac{\id \psi}{\id \eta} 
 		- \frac{D_{22}}{b^4} J_1 \frac{\id^3 \psi}{\id \eta^3} \right] \delta \psi \Big|^{\eta=1}_{\eta=-1} \\
-		&\quad + \left( \frac{D_{12}}{a^2b^2} J_2 \psi + \frac{D_{22}}{b^4} J_1 \frac{\id^2 \psi}{\id \eta^2} \right) 
+		&\qquad + \left( \frac{D_{12}}{a^2b^2} J_2 \psi + \frac{D_{22}}{b^4} J_1 \frac{\id^2 \psi}{\id \eta^2} \right) 
 		\delta\frac{\id  \psi}{\id \eta} \Big|^{\eta=1}_{\eta=-1} \\
-		&\quad + \frac{2k^r_{\eta=-1}}{b^3} J_1 \left( \frac{\id \psi}{\id \eta} \delta\frac{\id \psi}{\id \eta} \right)_{\eta=-1} 
+		&\qquad + \frac{2k^r_{\eta=-1}}{b^3} J_1 \left( \frac{\id \psi}{\id \eta} \delta\frac{\id \psi}{\id \eta} \right)_{\eta=-1} 
 		+ \frac{2k^r_{\eta=1}}{b^3} J_1 \left( \frac{\id \psi}{\id \eta} \delta\frac{\id \psi}{\id \eta} \right)_{\eta=1}.
@@
 %
-Thus, the governing differential equation in the \( y \)-direction can be obtained from the integration part in \Cref{eq:Rayleighy2}:
+Thus, the governing differential equation in the $y$-direction can be obtained from the integration part in \Cref{eq:Rayleighy2}:
 %
@@
 %
-where \( \Omega_y = \sqrt[4]{{\omega_y^2 \rho h}/D_{11}} \).
-By substituting \( \psi(\eta) = B e^{\lambda \eta} \) into \Cref{eq:ODEy}, yields:
+where $\Omega_y = \sqrt[4]{{\omega_y^2 \rho h}/D_{11}}$.
+By substituting $\psi(\eta) = B e^{\lambda \eta}$ into \Cref{eq:ODEy}, yields:
 %
@@
 %
-The solution for \( \lambda \) can be expressed as:
+The solution for $\lambda$ can be expressed as:
 %
@@
 %
-The boundary conditions along the edges in the \( y \)-direction can be obtained from the remaining \( \delta \psi \) and \( \delta \frac{\id \psi}{\id \eta} \) parts in \Cref{eq:Rayleighy2}. 
-The shear force equilibrium can be obtained from the \( \delta \psi \) part:
+The boundary conditions along the edges in the $y$-direction can be obtained from the remaining $\delta \psi$ and $\delta \frac{\id \psi}{\id \eta}$ parts in \Cref{eq:Rayleighy2}. 
+The shear force equilibrium can be obtained from the $\delta \psi$ part:
 %
@@
 		- \frac{D_{22}}{b^4} J_1 \frac{\id^3 \psi}{\id \eta^3} \right] \Big|^{\eta=1}_{\eta=-1} \\
-		&\quad + \frac{2k^v_{\eta=-1}}{b} J_1 (\psi )_{\eta=-1} + \frac{2k^v_{\eta=1}}{b} J_1 (\psi )_{\eta=1} = 0,
-	\end{split}
-\end{equation}
-%
-and from the \( \delta \frac{\id \psi}{\id \eta} \) part, the bending moment equilibrium:
+		&\qquad + \frac{2k^v_{\eta=-1}}{b} J_1 (\psi )_{\eta=-1} + \frac{2k^v_{\eta=1}}{b} J_1 (\psi )_{\eta=1} = 0,
+	\end{split}
+\end{equation}
+%
+and from the $\delta \frac{\id \psi}{\id \eta}$ part, the bending moment equilibrium:
 %
@@
  	&+ \frac{2k^r_{\eta=-1}}{b^3} J_1 \left( \frac{\id \psi}{\id \eta} \right)_{\eta=-1} \\
- 	&+ \frac{2k^r_{\eta=1}}{b^3} J_1 \left( \frac{\id \psi}{\id \eta} \right)_{\eta=1}=0.
- \end{split}
-\end{equation}
-%
-Thus, we can obtain the shear force and bending moment equilibrium along the edges \( \eta = -1 \) and \( \eta = 1 \) from \Cref{eq:inertial_forcey,eq:inertial_forcey2}, respectively, as:
+ 	&\qquad+ \frac{2k^r_{\eta=1}}{b^3} J_1 \left( \frac{\id \psi}{\id \eta} \right)_{\eta=1}=0.
+ \end{split}
+\end{equation}
+%
+Thus, we can obtain the shear force and bending moment equilibrium along the edges $\eta = -1$ and $\eta = 1$ from \Cref{eq:inertial_forcey,eq:inertial_forcey2}, respectively, as:
 %
@@
 Substituting \Cref{eq:phi_solution2} into \Cref{eq:boundaryy} and denoting
-\( k^{v*}_{\eta} = \frac{2b^3 k^v_{\eta}}{D_{22}} \), 
-\( k^{r*}_{\eta} = \frac{2b k^r_{\eta}}{D_{22}} \), 
-\( S_{\alpha_2}=\sin\alpha_2  \), 
-\( C_{\alpha_2}=\cos\alpha_2  \), 
-\( Sh_{\alpha_2}=\sinh\alpha_2  \), 
-\( Ch_{\alpha_2}=\cosh\alpha_2 \), 
-\( S_{\beta_2}=\sin\beta_2  \), 
-\( C_{\beta_2}=\cos\beta_2  \), 
-\( Sh_{\beta_2}=\sinh\beta_2 \), and 
-\(Ch_{\beta_2}= \cosh\beta_2 \), 
+$k^{v*}_{\eta} = \frac{2b^3 k^v_{\eta}}{D_{22}} $, 
+$ k^{r*}_{\eta} = \frac{2b k^r_{\eta}}{D_{22}} $, 
+$S_{\alpha_2}=\sin\alpha_2  $, 
+$ C_{\alpha_2}=\cos\alpha_2  $, 
+$ Sh_{\alpha_2}=\sinh\alpha_2  $, 
+$ Ch_{\alpha_2}=\cosh\alpha_2 $, 
+$ S_{\beta_2}=\sin\beta_2 $, 
+$ C_{\beta_2}=\cos\beta_2 $, 
+$ Sh_{\beta_2}=\sinh\beta_2$, and 
+$Ch_{\beta_2}= \cosh\beta_2$, 
 We obtain:
@@
 %
-Note that the eigenvector \(\mathbf{B}\) can be expressed by multiplying the inverse matrix \(\mathbf{Q}_y^{-1}\) on the left-hand side of \Cref{eq:UBy1}, and then substituting \(\mathbf{B}\) into \Cref{eq:ABy1}, we obtain:
+Note that the eigenvector $\mathbf{B}$ can be expressed by multiplying the inverse matrix $\mathbf{Q}_y^{-1}$ on the left-hand side of \Cref{eq:UBy1}, and then substituting $\mathbf{B}$ into \Cref{eq:ABy1}, we obtain:
 %
@@
 %
-where the dynamic stiffness matrix, denoted as \(\mathbf{K}_y = \mathbf{R}_y \mathbf{Q}_y^{-1}\), can be obtained from \Cref{eq:DSM_eqy}.
+where the dynamic stiffness matrix, denoted as $\mathbf{K}_y = \mathbf{R}_y \mathbf{Q}_y^{-1}$, can be obtained from \Cref{eq:DSM_eqy}.
 
@@
 The Wittrick–Williams (W-W) algorithm \cite{wittrick1971general} is an effective method for determining the natural frequencies from the dynamic stiffness matrix with high reliability. 
-Instead of directly solving the equations, the algorithm computes the total number \(J\) of natural frequencies below a given frequency \(\omega^*\), which is represented as:
+Instead of directly solving the equations, the algorithm computes the total number $J$ of natural frequencies below a given frequency $\omega^*$, which is represented as:
 \begin{equation}\label{eq:WWalgorithm}
@@
 \end{equation}
-where \(J_0\) represents the number of natural frequencies for the system with both ends fully clamped, \(\mathbf{K}^{\Delta}\) is the upper triangular matrix obtained from the dynamic stiffness matrix \(\mathbf{K}\) after applying Gaussian elimination, and \(J_k(\omega^*)\) denotes the number of negative elements in the leading diagonal of \(\mathbf{K}^{\Delta}\).
-
-It should be noted that the \( J_0 \) count is a crucial aspect when applying the W-W algorithm.
+where $J_0$ represents the number of natural frequencies of the structure with all ends fully clamped, $\mathbf{K}^{\Delta}$ is the upper triangular matrix obtained from the dynamic stiffness matrix $\mathbf{K}$ after applying Gaussian elimination, and $J_k(\omega^*)$ denotes the number of negative elements in the leading diagonal of $\mathbf{K}^{\Delta}$.
+
+It should be noted that the $J_0$ count is a crucial aspect when applying the W-W algorithm.
 Many previous studies use a sufficiently fine mesh or enough terms in series expansions to capture all fully clamped natural frequencies, ensuring computational accuracy \cite{banerjee2015dynamic}.
 However, this approach can make the application process cumbersome.
-To address this issue, the fully clamped problem can be replaced with a simply supported problem, where the Navier solution for the simply supported plate is used to count \( J_0 \) \citep{liu2015exact}.
+To address this issue, the fully clamped problem can be replaced with a simply supported problem, where the Navier solution for the simply supported plate is used to count $J_0$ \citep{liu2015exact}. 
 Nevertheless, since analytical solutions in DSM methods involve an infinite series of Fourier terms, a sufficient number of truncation terms is required to ensure accuracy and convergence.
 
-However, the idea of solving the simply supported problem proposes an effective and systematic approach to indirectly determine the \( J_0 \) count for a fully clamped structure, where the boundary conditions are modeled as pinned supports rather than clamped ones \cite{han2018improved}:
+In fact, $ J_0 $ can be indirectly determined by evaluating the number of natural frequencies $ J $ of the structure under specific boundary conditions, which are generally different from the original boundary conditions \cite{han2018improved}:
 %
@@
 %
-where \( p_1 \) and \( \bar{p}_1 \) represent clamped and pinned supports, respectively.
+where $ p_1 $ denotes the fully clamped supports, and $ \bar{p}_1 $ denotes specific supports, which are typically simply supported, guided, or a combination of the two.
+For these specific boundary conditions, the eigenvalue equations of SOV type solution take the form of a single harmonic function.
 By substituting \Cref{eq:J_o_pin} into \Cref{eq:WWalgorithm} we get the algorithm as:  
@@
 %
-where \( p \) represents the original boundary conditions of the structure.
-Therefore, the challenge of determining \( J_0(p_1, \omega^*) \) can be transformed into the problem of solving \( J(\bar{p}_1, \omega^*) \) instead.
-The eigenvalue equation corresponding to the natural frequency parameter \( \Omega_x \) can be obtained from the determinant of the coefficient matrix \( \mathbf{R}_x \) in \Cref{eq:ABx}, which is given by \citep{xing2020extended}:
+where $p$ represents the original boundary conditions of the structure.
+Therefore, the challenge of determining $J_0(p_1, \omega^*)$ can be transformed into the problem of solving $ J(\bar{p}_1, \omega^*)$ instead. 
+By considering fully simply supported boundary conditions, the eigenvalue equation corresponding to the natural frequency parameter $ \Omega_x $ can be obtained from the determinant of the coefficient matrix $ \mathbf{R}_x $ in \Cref{eq:ABx}, as given by:
 %
@@
 %
-With the help of \Cref{eq:alphax1,eq:SSx}, the closed-form solution of the \(n_x\)th simply supported frequency \(\Omega_{x,n_x}\) for the given \(n_y\)-order \(\psi_{n_y}(\eta)\) can be expressed as:
+With the help of \Cref{eq:alphax1,eq:SSx}, the closed-form solution of the $n_x$-th simply supported frequency $\Omega_{x,n_x}$ for the given $n_y$-order $\psi_{n_y}(\eta)$ can be expressed as:
 %
@@
 %
-For \(\Omega_{x,n_x} \leq \Omega_x^* < \Omega_{x,n_{x+1}}\), \(J(\bar{p}_1, \Omega_x^*) = n_x\).
-Similarly, the closed-form solution of the \(n_y\)-th simply supported frequency \(\Omega_{y,n_y}\) for the given \(n_x\)-order \(\phi_{n_x}(\xi)\) can be expressed as:
+For $\Omega_{x,n_x} \leq \Omega_x^* < \Omega_{x,n_{x+1}}$, $J(\bar{p}_1, \Omega_x^*) = n_x$.
+Similarly, the closed-form solution of the $n_y$-th simply supported frequency $\Omega_{y,n_y}$ for the given $n_x$-order $\phi_{n_x}(\xi)$ can be expressed as:
 %
@@
 %
-For \(\Omega_{y,n_y} \leq \Omega_y^* < \Omega_{y,n_{y+1}}\), \(J(\bar{p}_1, \Omega_y^*) = n_y\).
+For $\Omega_{y,n_y} \leq \Omega_y^* < \Omega_{y,n_{y+1}}$, $J(\bar{p}_1, \Omega_y^*) = n_y$.
 According to the relationships 
 $\Omega_x = \sqrt[4]{{\omega_x^2 \rho h}/{D_{11}}}$ and\ $\Omega_y = \sqrt[4]{{\omega_y^2 \rho h}/{D_{11}}}$, 
-the values of \(J(\bar{p}_1, \omega_x^*)\) and \(J(\bar{p}_1, \omega_y^*)\) can be derived from \(J(\bar{p}_1, \Omega_x^*)\) and \(J(\bar{p}_1, \Omega_y^*)\), respectively.
-Therefore, this refined W-W algorithm can be applied to estimate the lower and upper bounds of the frequency range, denoted as \(\omega_l\) and \(\omega_u\), yielding an approximation for the frequency \(\omega_a \in (\omega_l, \omega_u)\).
+the values of $J(\bar{p}_1, \omega_x^*)$ and $J(\bar{p}_1, \omega_y^*)$ can be derived from $J(\bar{p}_1, \Omega_x^*)$ and $J(\bar{p}_1, \Omega_y^*)$, respectively.
+Therefore, this refined W-W algorithm can be applied to estimate the lower and upper bounds of the frequency range, denoted as $\omega_l$ and $\omega_u$, yielding an approximation for the frequency $\omega_a \in (\omega_l, \omega_u)$.
 \subsection{Mode shape computation}
-The mode shape coefficients \( A_1 \) to \( A_4 \) and \( B_1 \) to \( B_4 \) in the eigenvectors \( \mathbf{A} \) and \( \mathbf{B} \) for all classic boundary conditions are provided in \cite{xing2020extended}.
+The mode shape coefficients $ A_1 $ to $ A_4 $ and $ B_1 $ to $ B_4$ in the eigenvectors $\mathbf{A}$ and $\mathbf{B}$ for all classic boundary conditions are provided in \cite{xing2020extended}. 
 Alternatively, these coefficients can also be obtained through a simple numerical method, which this work presents as an approach.
-Here, we illustrate solving the eigenvector \( \mathbf{A} \) as an example.
-By assuming the exact natural frequency as \( \omega_k \), we can expand the coefficient matrix \( \mathbf{R}_{x} \) in \Cref{eq:ABx} using a first-order Taylor series about \( \omega_a \):
+Here, we illustrate solving the eigenvector $\mathbf{A}$ as an example.
+By assuming the exact natural frequency as $\omega_k$, we can expand the coefficient matrix $ \mathbf{R}_{x} $ in \Cref{eq:ABx} using a first-order Taylor series about $\omega_a$:
 %
@@
 %
-where the initial guess for \( \mathbf{A}^{(0)} \) is a column vector consisting of four randomly generated elements, each of which falls within the range (0,1).
+where the initial guess for $\mathbf{A}^{(0)}$ is a column vector consisting of four randomly generated elements, each of which falls within the range (0,1).
 The updated eigenvalue for the next step can be obtained as:
@@
 %
-Note that the mode shape coefficients \( A_1 \) to \( A_4 \) obtained from \(\mathbf{A}^{(i+1)}\) are applied for the elastically restrained boundary conditions.
+Note that the mode shape coefficients $A_1$ to $A_4$ obtained from $\mathbf{A}^{(i+1)}$ are applied for the elastically restrained boundary conditions.
 
@@
 \begin{itemize}[]
-	\item \textbf{Step 1} Assume initial integral parameters \(I^{(0)}_1, I^{(0)}_2, I^{(0)}_3\), and \(I^{(0)}_4\) in the \(y\)-direction.
-Using the given boundary conditions at \(\xi = -1\) and \(\xi = 1\), determine \(\mathbf{K}^{(0)}_x\) from \Cref{eq:DSM_eqx}.
-	Then, apply the computational algorithms in \Cref{sec:WWA2} to compute the lower and upper bounds of the \(n_x\)-th non-dimensional frequency parameter, \(2a\Omega^{(0)}_{l,x,n_x}\) and \(2a\Omega^{(0)}_{u,x,n_x}\), and take the average \(2a\Omega^{(0)}_{x,n_x} = (2a\Omega^{(0)}_{l,x,n_x} + 2a\Omega^{(0)}_{u,x,n_x})/2\) along with its corresponding mode shape \(\phi^{(0)}_{n_x}\), where \(n_x = 1, 2, 3, \ldots\).
-
-	\item \textbf{Step 2} Use \(\phi^{(0)}_{n_x}\) as the prescribed mode to determine \(\mathbf{K}^{(1)}_y\) in \Cref{eq:DSM_eqy}, considering the boundary conditions at \(\eta = -1\) and \(\eta = 1\). 
-	Apply the computational algorithms to obtain the \(n_y\)-th frequency parameter \(2a\Omega^{(1)}_{y,n_y}\) and its corresponding mode shape \(\psi^{(1)}_{n_y}\), where \(n_y = 1, 2, 3, \ldots\).
+	\item \textbf{Step 1} Assume initial integral parameters $I^{(0)}_1, I^{(0)}_2, I^{(0)}_3$, and $I^{(0)}_4$ in the $y$-direction.
+Using the given boundary conditions at $\xi = -1$ and $\xi = 1$, determine $\mathbf{K}^{(0)}_x$ from \Cref{eq:DSM_eqx}.
+	Then, apply the computational algorithms in \Cref{sec:WWA2} to compute the lower and upper bounds of the $n_x$-th non-dimensional frequency parameter, $2a\Omega^{(0)}_{l,x,n_x}$ and $2a\Omega^{(0)}_{u,x,n_x}$, and take the average $2a\Omega^{(0)}_{x,n_x} = (2a\Omega^{(0)}_{l,x,n_x} + 2a\Omega^{(0)}_{u,x,n_x})/2$ along with its corresponding mode shape $\phi^{(0)}_{n_x}$, where $n_x = 1, 2, 3, \ldots$.
+
+	\item \textbf{Step 2} Use $\phi^{(0)}_{n_x}$ as the prescribed mode to determine $\mathbf{K}^{(1)}_y$ in \Cref{eq:DSM_eqy}, considering the boundary conditions at $\eta = -1$ and $\eta = 1$. 
+	Apply the computational algorithms to obtain the $n_y$-th frequency parameter $2a\Omega^{(1)}_{y,n_y}$ and its corresponding mode shape $\psi^{(1)}_{n_y}$, where $n_y = 1, 2, 3, \ldots$.
 This completes the first iteration cycle.
 
-	\item \textbf{Step 3} Use \(\psi^{(1)}_{n_y}\) as the prescribed \(n_y\)-th mode shape in the \(y\)-direction to compute \(\mathbf{K}^{(1)}_x\) from \Cref{eq:DSM_eqx}, then determine the \(n_x\)-th frequency parameter \(2a\Omega^{(1)}_{x,n_x}\) and its corresponding mode shape \(\phi^{(1)}_{n_x}\).
-
-	\item \textbf{Step 4} Use \(\phi^{(1)}_{n_x}\) as the prescribed mode in the \(x\)-direction to compute the \(n_y\)-th frequency parameter \(2a\Omega^{(2)}_{y,n_y}\) and its corresponding mode shape \(\psi^{(2)}_{n_y}\), completing the second iteration cycle.
-
-	\item \textbf{Step 5} Stop the iteration if \(\lvert 2a\Omega^{(i)}_{x,n_x} - 2a\Omega^{(i+1)}_{x,n_x} \rvert \leq \Delta 2a\Omega\) or \(\lvert 2a\Omega^{(i)}_{y,n_y} - 2a\Omega^{(i+1)}_{y,n_y} \rvert \leq \Delta 2a\Omega\), where \(\Delta 2a\Omega = 2a\Omega_u - 2a\Omega_l\).
-Here, \(2a\Omega_l\) and \(2a\Omega_u\) are the lower and upper bounds of the frequency parameter range, within which the actual frequency parameter \(2a\Omega\) lies, i.e., \(2a\Omega \in (2a\Omega_l, 2a\Omega_u)\).
-The quantity \(\Delta 2a\Omega\) represents the frequency parameter interval used in the W-W algorithm.
-
-	\item \textbf{Step 6} Finally, construct the \((n_x, n_y)\)-th mode shape as \(w(\xi, \eta) = \phi_{n_x}(\xi) \psi_{n_y}(\eta)\) using \Cref{eq:displace_func}.  
+	\item \textbf{Step 3} Use $\psi^{(1)}_{n_y}$ as the prescribed $n_y$-th mode shape in the $y$-direction to compute $\mathbf{K}^{(1)}_x$ from \Cref{eq:DSM_eqx}, then determine the $n_x$-th frequency parameter $2a\Omega^{(1)}_{x,n_x}$ and its corresponding mode shape $\phi^{(1)}_{n_x}$.
+
+	\item \textbf{Step 4} Use $\phi^{(1)}_{n_x}$ as the prescribed mode in the $x$-direction to compute the $n_y$-th frequency parameter $2a\Omega^{(2)}_{y,n_y}$ and its corresponding mode shape $\psi^{(2)}_{n_y}$, completing the second iteration cycle.
+
+	\item \textbf{Step 5} Stop the iteration if $\lvert 2a\Omega^{(i)}_{x,n_x} - 2a\Omega^{(i+1)}_{x,n_x} \rvert \leq \Delta 2a\Omega$ or $\lvert 2a\Omega^{(i)}_{y,n_y} - 2a\Omega^{(i+1)}_{y,n_y} \rvert \leq \Delta 2a\Omega$, where $\Delta 2a\Omega = 2a\Omega_u - 2a\Omega_l$.
+Here, $2a\Omega_l$ and $2a\Omega_u$ are the lower and upper bounds of the frequency parameter range, within which the actual frequency parameter $2a\Omega$ lies, i.e., $2a\Omega \in (2a\Omega_l, 2a\Omega_u)$.
+The quantity $\Delta 2a\Omega$ represents the frequency parameter interval used in the W-W algorithm.
+
+	\item \textbf{Step 6} Finally, construct the $(n_x, n_y)$-th mode shape as $w(\xi, \eta) = \phi_{n_x}(\xi) \psi_{n_y}(\eta)$ using \Cref{eq:displace_func}.  
 \end{itemize}
@@
 This section presents the numerical validation of the proposed method for classic boundary conditions and rotationally restrained boundary conditions.  
-For all numerical calculations, the initial integral parameters are assumed as \(I^{(0)}_1=1\), \(I^{(0)}_2=1\), \(I^{(0)}_3=1\), and \(I^{(0)}_4=10\) in the \(y\)-direction, serving as the starting point of \textbf{Step 1} for any mode in all boundary conditions.
-In this section, the interval between the upper and lower bounds of the non-dimensional frequency parameter, \(2a\Delta\Omega\), is set to 0.005, limiting the error range.  
-According to our numerical calculations, two iteration cycles are generally sufficient to meet the convergence requirement (i.e., \(\lvert 2a\Omega^{(i)}_{x} - 2a\Omega^{(i+1)}_{x} \rvert \leq \Delta 2a\Omega\) or \(\lvert 2a\Omega^{(i)}_{y} - 2a\Omega^{(i+1)}_{y} \rvert \leq \Delta 2a\Omega\)) for most cases, with at most three cycles required when applying the iterative procedure in \Cref{sec:Application procedure}.
+For all numerical calculations, the initial integral parameters are assumed as $I^{(0)}_1=1$, $I^{(0)}_2=1$, $I^{(0)}_3=1$, and $I^{(0)}_4=10$ in the $y$-direction, serving as the starting point of \textbf{Step 1} for any mode in all boundary conditions.
+In this section, the interval between the upper and lower bounds of the non-dimensional frequency parameter, $2a\Delta\Omega$, is set to 0.005, limiting the error range.  
+According to our numerical calculations, two iteration cycles are generally sufficient to meet the convergence requirement (i.e., $\lvert 2a\Omega^{(i)}_{x} - 2a\Omega^{(i+1)}_{x} \rvert \leq \Delta 2a\Omega$ or $\lvert 2a\Omega^{(i)}_{y} - 2a\Omega^{(i+1)}_{y} \rvert \leq \Delta 2a\Omega$) for most cases, with at most three cycles required when applying the iterative procedure in \Cref{sec:Application procedure}.
 
@@
 The properties of the orthotropic plate, consistent with those in \cite{xing2020extended}, are as follows:  
-\(E_1 = 185 \nugpa\), \(E_2 = 10.5 \nugpa\), \(G_{12} = 7.3 \nugpa\), \(\rho = 1600 \urho\), and \(\nu_{12} = 0.28\).
-
-The translational springs (\(k^v_\xi\)) and rotational springs (\(k^r_\xi\)) along all edges can be set to zero or infinity (represented as \(1 \times 10^{15} \ustif\) in the numerical calculations of this study) to obtain different classic boundary conditions.
+$E_1 = 185 \nugpa$, $E_2 = 10.5 \nugpa$, $G_{12} = 7.3 \nugpa$, $\rho = 1600 \urho$, and $\nu_{12} = 0.28$.
+
+The translational springs ($k^v_\xi$) and rotational springs ($k^r_\xi$) along all edges can be set to zero or infinity (represented as $1 \times 10^{15} \ustif$ in the numerical calculations of this study) to obtain different classic boundary conditions.
 
@@
 These results demonstrate high accuracy compared to the extended SOV method, with difference remaining smaller than the frequency parameter interval $2a\Delta\Omega=0.005$. 
-The frequency parameters in both directions are equal (\(2a\Omega_x - 2a\Omega_y = 0\)) in almost all cases, with a few exceptions where \(2a\Omega_x - 2a\Omega_y = 0.005\). 
-In fact, higher accuracy compared to the extended SOV method can be achieved if the frequency parameter interval \(2a\Delta\Omega\) is set smaller than 0.005.
-It should be noted that the accuracy improves only by reducing \(2a\Delta\Omega\), and no additional iterations are required according to our calculations.
+The frequency parameters in both directions are equal ($2a\Omega_x - 2a\Omega_y = 0$) in almost all cases, with a few exceptions where $2a\Omega_x - 2a\Omega_y = 0.005$. 
+In fact, higher accuracy compared to the extended SOV method can be achieved if the frequency parameter interval $2a\Delta\Omega$ is set smaller than 0.005.
+It should be noted that the accuracy improves only by reducing $2a\Delta\Omega$, and no additional iterations are required according to our calculations.
 \Cref{fig:FFFF} shows the first six nonzero mode shapes of a square orthotropic plate with FFFF boundary conditions, where the mode shape coefficients are calculated using the numerical method developed in this study.
@@
 \subsection{Rotationally restrained boundary conditions}
-In this subsection, rectangular orthotropic plates with rotationally restrained edges (\(k^v_\xi = k^v_\eta = \infty\)) are validated.  
+In this subsection, rectangular orthotropic plates with rotationally restrained edges ($k^v_\xi = k^v_\eta = \infty$) are validated.  
 The rotational stiffness coefficients are defined as: 
@@
 The first example considers a square isotropic plate with all four edges rotationally restrained.
-The vertical translational springs along the four edges are numerically set as \( k^v_{\xi=-1} = k^v_{\xi=1} = k^v_{\eta=-1} = k^v_{\eta=1} = 1 \times 10^{12} \ustif \).
-The material properties are given as \( D_{11} = D_{22} = D_3 \) and \( v_{12} = v_{21} = 0.3 \).
-
-\Cref{tab:rot1} presents the frequency parameter \( 2a\Omega \) for different rotational stiffness coefficients \( r_{\xi} = r_{\eta} \) with values \( 0.1, 1, 10, 100, \) and \( 1000 \).  
-Notably, when \( r_{\xi} = r_{\eta} = 0 \) and \( r_{\xi} = r_{\eta} = \infty \), the boundary conditions correspond to SSSS and CCCC, respectively.
-
-Interestingly, the results indicate that the frequencies \(\Omega_x\) and \(\Omega_y\) are not strictly equal for some mode shapes under rotationally restrained boundary conditions.  
-The actual frequency \(\Omega\) lies between \(\Omega_x\) and \(\Omega_y\), which may be attributed to the fact that \(\Omega_x\) and \(\Omega_y\) satisfy Rayleigh’s principle in \Cref{eq:Rayleigh}, representing the weak-form governing equations, but do not necessarily satisfy the strong-form governing equations in \Cref{eq:governing_EOM}.
+The vertical translational springs along the four edges are numerically set as $ k^v_{\xi=-1} = k^v_{\xi=1} = k^v_{\eta=-1} = k^v_{\eta=1} = 1 \times 10^{12} \ustif $.
+The material properties are given as $ D_{11} = D_{22} = D_3 $ and $ v_{12} = v_{21} = 0.3 $.
+
+\Cref{tab:rot1} presents the frequency parameter $2a\Omega $ for different rotational stiffness coefficients  $ r_{\xi} = r_{\eta} $ with values $ 0.1, 1, 10, 100, $ and $ 1000$.  
+Notably, when $ r_{\xi} = r_{\eta} = 0 $ and $r_{\xi} = r_{\eta} = \infty$, the boundary conditions correspond to SSSS and CCCC, respectively.
+
+Interestingly, the results indicate that the frequencies $\Omega_x$ and $\Omega_y$ are not strictly equal for some mode shapes under rotationally restrained boundary conditions.  
+The actual frequency $\Omega$ lies between $\Omega_x$ and $\Omega_y$, which may be attributed to the fact that $\Omega_x$ and $\Omega_y$ satisfy Rayleigh’s principle in \Cref{eq:Rayleigh}, representing the weak-form governing equations, but do not necessarily satisfy the strong-form governing equations in \Cref{eq:governing_EOM}.
 For a physical problem with exact solutions, both \Cref{eq:Rayleigh,eq:governing_EOM} must be satisfied.  
 If this condition is not met, applying \Cref{eq:Rayleigh} still provides a viable approach for approximating the exact solution of the plate.  
-Thus, the exact frequency can be estimated as \(\Omega = (\Omega_x + \Omega_y)/2\).  
-As shown in \Cref{tab:rot1}, the maximum difference between \(\Omega\) and the solutions reported in \Citealp{zhang2019new} is less than \(1.3\%\).
-\Cref{fig:iso} illustrates the variation in mode shapes corresponding to the fundamental natural frequency as the rotational stiffness \(r_{\xi} = r_{\eta}\) increases from zero to \(\infty\), transitioning the boundary conditions from SSSS to CCCC.
+Thus, the exact frequency can be estimated as $\Omega = (\Omega_x + \Omega_y)/2$.  
+As shown in \Cref{tab:rot1}, the maximum difference between \(\Omega\) and the solutions reported in \Citealp{zhang2019new} is less than $1.3\%$.
+\Cref{fig:iso} illustrates the variation in mode shapes corresponding to the fundamental natural frequency as the rotational stiffness $r_{\xi} = r_{\eta}$ increases from zero to $\infty$, transitioning the boundary conditions from SSSS to CCCC.
 
@@
 	\caption[]  
-	{\small The first mode shape of a square isotropic plate with all four edges rotationally restrained: (a) \(r_{\xi} = r_{\eta} = 0\); (b) \(r_{\xi} = r_{\eta} = 1\); (c) \(r_{\xi} = r_{\eta} = 10\); (d) \(r_{\xi} = r_{\eta} = 20\); (e) \(r_{\xi} = r_{\eta} = 100\); (f) \(r_{\xi} = r_{\eta} = \infty\).}
+	{\small The first mode shape of a square isotropic plate with all four edges rotationally restrained: (a) $r_{\xi} = r_{\eta} = 0$; (b) $r_{\xi} = r_{\eta} = 1$; (c) $r_{\xi} = r_{\eta} = 10$; (d) $r_{\xi} = r_{\eta} = 20$; (e) $r_{\xi} = r_{\eta} = 100$; (f) $r_{\xi} = r_{\eta} = \infty$.}
 	\label{fig:iso} 
@@
 	\centering
-	\caption{The first six frequency parameters, \(2a\Omega = 2a\sqrt[4]{\rho h \omega^2/D_{11}}\), of a square isotropic plate with all four edges rotationally restrained, where \(k^r_{\xi=-1} = k^r_{\xi=1} = k^r_{\eta=-1} = k^r_{\eta=1}\).}
+	\caption{The first six frequency parameters, $2a\Omega = 2a\sqrt[4]{\rho h \omega^2/D_{11}}$, of a square isotropic plate with all four edges rotationally restrained, where $k^r_{\xi=-1} = k^r_{\xi=1} = k^r_{\eta=-1} = k^r_{\eta=1}$.}
 	\begin{tabular}{c l c c c c c c}
@@
 
-The next example considers a rectangular orthotropic plate with three simply supported edges (\(k^r_{\xi=-1} = k^r_{\xi=1} = k^r_{\eta=1} = 0\)), while the edge at \(\eta = -1\) is rotationally restrained.
-The material properties are consistent with those in \citealp{zhang2019new}, where \(2D_{11} = 2D_{22} = D_3\) and \(\nu_{12} = \nu_{21} = 0.3\).  
-\Cref{tab:oth2} shows the fundamental frequency results for different length ratios (\(b/a\)), comparing them with those reported in \citealp{zhang2019new}. 
-The maximum observed difference is $0.8\%$ when \(r_{\eta=-1} = 10\).
+The next example considers a rectangular orthotropic plate with three simply supported edges ($k^r_{\xi=-1} = k^r_{\xi=1} = k^r_{\eta=1} = 0$), while the edge at $\eta = -1$ is rotationally restrained.
+The material properties are consistent with those in \citealp{zhang2019new}, where $2D_{11} = 2D_{22} = D_3$ and $\nu_{12} = \nu_{21} = 0.3$.  
+\Cref{tab:oth2} shows the fundamental frequency results for different length ratios ($b/a$), comparing them with those reported in \citealp{zhang2019new}. 
+The maximum observed difference is $0.8\%$ when $r_{\eta=-1} = 10$.
 
@@
 	\centering
-	\caption{Fundamental frequency parameter \(2a\Omega = 2a\sqrt[4]{\rho h \omega^2/D_{11}}\) of rectangular orthotropic plates with three edges simply supported (\(k^r_{\xi=-1} = k^r_{\xi=1} = k^r_{\eta=1} = 0\)) and the edge at \(\eta = -1\) rotationally restrained.}
+	\caption{Fundamental frequency parameter $2a\Omega = 2a\sqrt[4]{\rho h \omega^2/D_{11}}$ of rectangular orthotropic plates with three edges simply supported ($k^r_{\xi=-1} = k^r_{\xi=1} = k^r_{\eta=1} = 0$) and the edge at $\eta = -1$ rotationally restrained.}
 	\begin{tabular}{c c c c c c c }
@@
 Several novel techniques have proposed to solve the eigenvalue problem and mode shape computation.
-The challenge of determining the fully clamped frequencies using the Wittrick-Williams (W-W) algorithm is resolved by finding the simply supported frequencies, whose closed-form expression can be easily derived based on the SOV method.
-
-Classical boundary conditions, such as guided, simply supported, clamped, and free edges, can be realized by setting the translational springs (\(k^v_\xi\)) and rotational springs (\(k^r_\xi\)) along the plate edges to either zero or infinity.
+The challenge of determining the fully clamped frequencies using the Wittrick-Williams (W-W) algorithm is resolved by computing the frequencies under specific boundary conditions, whose closed-form expression can be easily derived using the SOV method.
+
+Classical boundary conditions, such as guided, simply supported, clamped, and free edges, can be realized by setting the translational springs ($k^v_\xi$) and rotational springs ($k^r_\xi$) along the plate edges to either zero or infinity.
 Numerical experiments have validated accuracy of this approach for these boundary conditions.  
@@
 
-Since the SOV type solution \(\phi(\xi) \psi(\eta)\) consists of only a single term for each mode order, unlike the infinite series expansions used in the traditional DSM, each eigenvalue solution can be explicitly expressed.
+Since the SOV type solution $\phi(\xi) \psi(\eta)$ consists of only a single term for each mode order, unlike the infinite series expansions used in the traditional DSM, each eigenvalue solution can be explicitly expressed.
 This suggests the potential for obtaining more concise solutions for assembled plate structures compared to traditional DSM methods.
@@
 \section{Integral parameters}\label{appendA}
-The integral parameters \( I_1, I_2, I_3, \) and \( I_4 \) are defined as follows:
+The integral parameters $ I_1$, $I_2$, $I_3$, and $ I_4$ are defined as follows:
 %
@@
 %
-The integral parameters \( J_1 \), \( J_2 \), \( J_3 \), and \( J_4 \) can be obtained by replacing \( B_1 \) to \( B_4 \) by \( A_1 \) to \( A_4 \), respectively, and \( \alpha_2 \) and \( \beta_2 \) by \( \alpha_1 \) and \( \beta_1 \), respectively.
+The integral parameters $J_1$, $J_2$, $J_3$, and $J_4$ can be obtained by replacing $B_1$ to $B_4$ by $ A_1 $ to $A_4$, respectively, and $\alpha_2$ and $\beta_2$ by $\alpha_1$ and $\beta_1$, respectively.
 

### 2025-06-30 Paper7.tex
Proof read at last - comments in latex; make sure tables fit.

@@
 \newcommand{\ii}{\mathrm{i}\mkern1mu}
-\newcommand{\nukg}{\unit{\kilogram}\xspace}
-\newcommand{\nustif}{\unit{\newton\per\metre}\xspace}
-\newcommand{\nudamp}{\unit{\newton\second\per\metre}\xspace}
-\newcommand{\nugpa}{\si{\giga\pascal}\xspace}
+\newcommand{\nukg}{~\unit{\kilogram}\xspace}
+\newcommand{\nustif}{~\unit{\newton\per\metre}\xspace}
+\newcommand{\nudamp}{~\unit{\newton\second\per\metre}\xspace}
+\newcommand{\nugpa}{~\si{\giga\pascal}\xspace}
 \begin{document}
@@
 \begin{frontmatter}
-\title{The dynamic stiffness matrix based on the extended separation-of-variables type solution for the free vibration of orthotropic rectangular thin plates}
+\title{Dynamic stiffness matrix based on the extended separation-of-variables solution for the free vibration of orthotropic rectangular thin plates}
 \author[1]{Shiyi Mei}\ead{shiyi.mei1@monash.edu}
@@
 The method combines the advantages of the DSM method and the SOV method.
-The SOV type solution satisfies the governing differential equation derived from Rayleigh’s principle and is used to formulate the dynamic stiffness matrices.
+The SOV type solution satisfies the governing differential equation derived from Rayleigh’s principle and is used to formulate dynamic stiffness matrices.
 Owing to the characteristics of the SOV type solution, the fully clamped boundary condition problem associated with the Wittrick–Williams algorithm is resolved. 
@@
 
-Besides the approximation methods, several analytical methods have been developed over the past decades, including the Kantorovich-Krylov method \cite{kantorovich1958approximate,kerr1968extension}, the symplectic eigenfunction expansion method \cite{zhong1995new,xing2009new2}, the separation-of-variable (SOV) method \cite{xing2009new}, the dynamic stiffness matrix (DSM) method \cite{banerjee1997dynamic}, and series expansion-based methods \cite{xing2022review}.
+Besides the approximation methods, several analytical methods have been developed over past decades, including the Kantorovich-Krylov method \cite{kantorovich1958approximate,kerr1968extension}, the symplectic eigenfunction expansion method \cite{zhong1995new,xing2009new2}, the separation-of-variable (SOV) method \cite{xing2009new}, the dynamic stiffness matrix (DSM) method \cite{banerjee1997dynamic}, and series expansion-based methods \cite{xing2022review}.
 The series expansion-based methods include the superposition method \cite{timoshenko1940theory,gorman2005free}, Fourier series method \cite{khov2009accurate,li2009exact}, the finite integral transform method \cite{li2009finite,zhong2013free}, and other series methods.
@@
 To avoid solving the cumbersome transcendental frequency equation directly, the Wittrick-Williams (W-W) algorithm \cite{wittrick1971general} is applied to the eigenvalue problem.
-The W-W algorithm determines the lower and upper bounds of natural frequencies rather than solving the frequency equation directly. 
+The W-W algorithm determines the lower and upper bounds of natural frequencies to arbitrary precision rather than solving the frequency equation directly. 
 Thus, the DSM has the potential to be effectively and systematically solved using the W-W algorithm.
-However, a critical part in applying the W-W algorithm is to priorly determine all natural frequencies of the fully clamped structure within the interested frequency range.
+However, a critical part in applying the W-W algorithm is to determine all natural frequencies of the fully clamped structure within the interested frequency range, \textit{a priori}.
 Strategies such as using a sufficiently fine mesh or including a sufficient number of terms in series expansions \cite{banerjee2015dynamic} can ensure that all fully clamped frequencies are accounted for, thereby maintaining the accuracy of the algorithm.
@@
 
-In this study, the SOV method is extended to analyze the vibrations of plates with elastically restrained edges.
-The extended SOV type solution is then employed to construct the dynamic stiffness matrices, which accommodate all general homogeneous boundary conditions.
+In this study, the SOV method is further extended to analyze the vibrations of plates with elastically restrained edges.
+This extended SOV solution is then employed to construct the dynamic stiffness matrices, which accommodate all general homogeneous boundary conditions.
 By taking advantage of both the SOV and DSM methods, an enhanced W-W algorithm is developed to solve the eigenvalue problem without directly solving the eigenvalue equations.
 This enhanced approach resolves the challenge of determining fully clamped frequencies, a well-known limitation in the application of the  W-W algorithm.
-In addition, a novel numerical technique has been proposed to compute the mode shape coefficients.
+In addition, a novel numerical technique is proposed to compute the mode shape coefficients.
 
@@
 %
-where $ \alpha = a / b $ is the aspect ratio; $ \xi = x / a $ and $ \eta = y / b $ are the normalized coordinates,
-and the bending stiffness parameters are defined as:
+where $ \alpha = a / b $ is the aspect ratio; $ \xi = x / a $ and $ \eta = y / b $ are the normalized coordinates, and the bending stiffness parameters are defined as:
 %
@@
 %
+% It doesn't make sense to have 'mag' as a subscript - P.E. is just U, and it's already a scalar.
+% And it also doesn't make sense to have '0' as the subscript for maginitude for K.E., which is just K.
+% I guess you have some reason? But 'magnitude' of a scalar isn't really a thing worth highlighting.
+%
 where $\delta$ denotes variation, $U_{mag}$ is the magnitude of the potential energy of the plate, and $\omega^2 T_0$ represents the magnitude of the kinetic energy of the plate.
@@
 %
+% What is superscript 'I' below? Why doesn't 'T' have one?
+% I know you're trying to separate the two ways of calculating the same thing, but it should be consistent.
+%
 \begin{equation}\label{eq:poten_energy}
 	\begin{split}
-		U^{I} &= \frac{1}{2}\iint \Big[D_{11}\left(\frac{\partial^2 W}{\partial x^2}\right)^2 + 2D_{12}\frac{\partial^2 W}{\partial x^2}\frac{\partial^2 W}{\partial y^2} + D_{22}\left(\frac{\partial^2 W}{\partial y^2}\right)^2 \\
-		&\qquad + 4D_{66}\left(\frac{\partial^2 W}{\partial x \partial y}\right)^2\Big] \, \mathrm{d}x \, \mathrm{d}y.
+		U^{I} &= \frac{1}{2}\iint \Bigg[D_{11}\left(\frac{\partial^2 W}{\partial x^2}\right)^2 + 2D_{12}\frac{\partial^2 W}{\partial x^2}\frac{\partial^2 W}{\partial y^2} + D_{22}\left(\frac{\partial^2 W}{\partial y^2}\right)^2 \\
+		&\qquad + 4D_{66}\left(\frac{\partial^2 W}{\partial x \partial y}\right)^2\Bigg] \, \mathrm{d}x \, \mathrm{d}y.
 	\end{split}
@@
 %
+% U sub/superscript notation hell?!
+%
 \begin{equation}\label{eq:poten_energy_mag}
@@
 and
+%
+% Shouldn't this be U on the LHS? How can T = omega**2 T (whether T_0 or not)?
 %
@@
 Based on \Cref{eq:Rayleigh}, the frequencies $\omega_x$ and $\omega_y$, corresponding to the mode shapes $\phi(\xi)$ and $\psi(\eta)$, respectively, are assumed to be independent of each other.
+% worth a comment here on:
+% - is this a common assumption?
+% - Do you later validate or check this assumption?
+% - What happens if this assumption is not met?
 
@@
 Supposing the edges of the plate in both the $x$- and $y$-directions are elastically restrained by homogeneous vertical translational and rotational springs.
-The vertical translational and rotational springs at the $\xi = -1$ end are defined as $k^v_{\xi = -1}$ and $k^r_{\xi = -1}$, respectively, and at the $\xi = 1$ end as $k^v_{\xi = 1}$ and $k^r_{\xi = 1}$, respectively.
+The vertical translational and rotational springs at the $\xi = -1$ end are denoted as $k^v_{\xi = -1}$ and $k^r_{\xi = -1}$, respectively, and at the $\xi = 1$ end as $k^v_{\xi = 1}$ and $k^r_{\xi = 1}$, respectively.
 Thus, the potential energy along the supported edge in the $x$-direction can be expressed by:
@@
 %
+% What is superscript II supposed to mean?
+% Why not just use U subscript x for this contribution of these supports?
 From \Cref{eq:poten_energy_edgex}, the magnitude of total potential energy along the edges in the $x$-direction is obtained as:
@@
 %
+% Isn't this just change of variables? dimensional to non-dimensional space? Maybe say this.
+% Not sure why this now deserves a 'mag' subscript.
 The magnitude of potential energy of the plate in the $x$-direction can be obtained from \Cref{eq:poten_energy_mag,eq:poten_energy_edgex2} as:
@@
 \\
-		&\qquad \left.
-+ \frac{4 D_{66}}{a^2 b^2} \left( \frac{\partial^2 w}{\partial \xi \partial \eta} \right)^2 \right] \, \id\xi \, \id\eta + ab \int \left[\frac{k^r_{\xi=1}}{a^3} \left( \frac{\partial w}{\partial \xi} \right)^2 + \frac{k^v_{\xi=1}}{a} \left( w \right)^2 \right]_{\xi=1} \, \id \eta \\
+		&\qquad \left.  + \frac{4 D_{66}}{a^2 b^2} \left( \frac{\partial^2 w}{\partial \xi \partial \eta} \right)^2 \right] \, \id\xi \, \id\eta \\
+		&\qquad + ab \int \left[\frac{k^r_{\xi=1}}{a^3} \left( \frac{\partial w}{\partial \xi} \right)^2 + \frac{k^v_{\xi=1}}{a} \left( w \right)^2 \right]_{\xi=1} \, \id \eta \\
 		&\qquad + ab \int \left[\frac{k^r_{\xi=-1}}{a^3} \left( \frac{\partial w}{\partial \xi} \right)^2 + \frac{k^v_{\xi=-1}}{a} \left( w \right)^2 \right]_{\xi=-1} \, \id \eta
@@
 	\begin{split}
-		U_{mag}&=U^{I}_{mag}+U^{II}_{mag}\\
-		&=\frac{ab}{2} \int_{-1}^{1} \left[ \frac{D_{11}}{a^4}I_1 \left( \frac{\id^2\phi }{\id \xi^2} \right)^2 + \frac{2 D_{12}}{a^2 b^2}I_2 \frac{\id^2\phi }{\id \xi^2}\phi  + \frac{D_{22}}{b^4}I_4  \phi^2 \right.
-\\
-		&\qquad \left.
-+ \frac{4 D_{66}}{a^2 b^2}I_3 \left( \frac{\id \phi }{\id \xi}\right)^2 \right] \, \id\xi +abI_1 \left[\frac{k^r_{\xi=-1}}{a^3} \left( \frac{\id \phi}{\id \xi} \right)^2+ \frac{k^v_{\xi=-1}}{a} \left( \phi \right)^2\right]_{\xi=-1}\\
-		&\qquad+abI_1 \left[\frac{k^r_{\xi=1}}{a^3} \left( \frac{\id \phi}{\id \xi} \right)^2+ \frac{k^v_{\xi=1}}{a} \left( \phi \right)^2\right]_{\xi=1},
+		U_{mag}&=\frac{ab}{2} \int_{-1}^{1} \left[ \frac{D_{11}}{a^4}I_1 \left( \frac{\id^2\phi }{\id \xi^2} \right)^2 + \frac{2 D_{12}}{a^2 b^2}I_2 \frac{\id^2\phi }{\id \xi^2}\phi  + \frac{D_{22}}{b^4}I_4  \phi^2 \right.
+\\
+		&\qquad \left. + \frac{4 D_{66}}{a^2 b^2}I_3 \left( \frac{\id \phi }{\id \xi}\right)^2 \right] \, \id\xi \\
+		&\qquad + abI_1 \left[\frac{k^r_{\xi=-1}}{a^3} \left( \frac{\id \phi}{\id \xi} \right)^2+ \frac{k^v_{\xi=-1}}{a} \left( \phi \right)^2\right]_{\xi=-1}\\
+		&\qquad + abI_1 \left[\frac{k^r_{\xi=1}}{a^3} \left( \frac{\id \phi}{\id \xi} \right)^2+ \frac{k^v_{\xi=1}}{a} \left( \phi \right)^2\right]_{\xi=1},
 	\end{split}
@@
 %
+% The notation needs to be cleaned up a bit, or more clearly defined.
 \begin{equation}\label{eq:kine_energyx}
@@
 \end{equation}
-%
-Take the Rayleigh principle in the form:
+
+Taking the Rayleigh principle in the form:
 %
@@
 	\begin{split}
-		\delta U_{mag} &= \omega_x^2 \, \delta T_0.
-	\end{split}
-\end{equation}
-%
-By substituting \Cref{eq:poten_energy_tolx2,eq:kine_energyx} into \Cref{eq:Rayleighx}, and relieving $\delta \phi$ and $\delta\frac{\id  \phi}{\id \xi}$ in \Cref{eq:Rayleighx} by variation calculus, yields:
+		\delta U_{mag} &= \omega_x^2 \, \delta T_0,
+	\end{split}
+\end{equation}
+%
+and by substituting \Cref{eq:poten_energy_tolx2,eq:kine_energyx} into \Cref{eq:Rayleighx}, and relieving $\delta \phi$ and $\delta\frac{\id  \phi}{\id \xi}$ in \Cref{eq:Rayleighx} by calculus of variations, yields:
 %
@@
 %
+% Very nice!
+%
 \begin{equation}\label{eq:ODEx}
@@
 where $\Omega_x = \sqrt[4]{\omega_x^2 \rho h / D_{11}}$.
-By substituting $\phi(\xi) = A e^{\mu \xi}$ into \Cref{eq:ODEx}, yields:
+By substituting $\phi(\xi) = A e^{\mu \xi}$ into \Cref{eq:ODEx}, we obtain:
 %
@@
 %
-The solution for $\mu$ can be expressed as:
+And so the solution for $\mu$ can be expressed as:
 %
@@
 		- \frac{D_{11}}{a^4} I_1 \frac{\id^3 \phi}{\id \xi^3} \right] \Big|^{\xi=1}_{\xi=-1}\\
-		&\qquad+ \frac{2k^v_{\xi=-1}}{a} I_1 \left(\phi\right)_{\xi=-1}
+		&\quad\qquad+ \frac{2k^v_{\xi=-1}}{a} I_1 \left(\phi\right)_{\xi=-1}
 		 + \frac{2k^v_{\xi=1}}{a} I_1 \left(\phi\right)_{\xi=1} = 0,
@@
 	\begin{split}	
-		\left( \frac{D_{12}}{a^2b^2} I_2 \phi + \frac{D_{11}}{a^4} I_1 \frac{\partial^2 \phi}{\partial \xi^2} \right) 
-		\Big|^{\xi=1}_{\xi=-1} 
-		&+ \frac{2k^r_{\xi=-1}}{a^3} I_1 \left(\frac{\partial \phi}{\partial \xi}\right)_{\xi=-1} \\
-		& \qquad\frac{2k^r_{\xi=1}}{a^3} I_1 \left(\frac{\partial \phi}{\partial \xi}\right)_{\xi=1} = 0.
+		&\left( \frac{D_{12}}{a^2b^2} I_2 \phi + \frac{D_{11}}{a^4} I_1 \frac{\partial^2 \phi}{\partial \xi^2} \right) 
+		\Big|^{\xi=1}_{\xi=-1} \\
+		&\qquad + \frac{2k^r_{\xi=-1}}{a^3} I_1 \left(\frac{\partial \phi}{\partial \xi}\right)_{\xi=-1}
+		+ \frac{2k^r_{\xi=1}}{a^3} I_1 \left(\frac{\partial \phi}{\partial \xi}\right)_{\xi=1} = 0.
 	\end{split}
@@
 %
-Substituting \Cref{eq:phi_solution1} into \Cref{eq:boundaryx}, and denoting $ k^{v*}_{\xi} = \frac{2a^3 k^v_{\xi}}{D_{11}} $, $ k^{r*}_{\xi} = \frac{2a k^r_{\xi}}{D_{11}} $, $ S_{\alpha_1}=\sin\alpha_1 $, $ C_{\alpha_1}=\cos\alpha_1 $, $ Sh_{\alpha_1}=\sinh\alpha_1 $, $ Ch_{\alpha_1}=\cosh\alpha_1 $, $S_{\beta_1}= \sin\beta_1 $, $C_{\beta_1}=\cos\beta_1$, $Sh_{\beta_1}=\sinh\beta_1 $, and $  Ch_{\beta_1}=\cosh\beta_1 $, we have:
+Substituting \Cref{eq:phi_solution1} into \Cref{eq:boundaryx}, and denoting $ k^{u*}_{\xi} \equiv \frac{2a^3 k^u_{\xi}}{D_{11}} $ for $u \in \{r,v\}$, $ S_u \equiv \sin u $, $ C_u \equiv \cos u $, $ Sh_u \equiv \sinh u$, and $ Ch_u \equiv \cosh u $, we have:
 %
@@
 For non-trivial solutions, the characteristic equation or eigenvalue equation is obtained from the determinant of the matrix $\mathbf{R}_x$ in \Cref{eq:ABx1}, which must be zero.
-However, solving these transcendental equations are cunmbersome and tedious, thus the DSM is introducted to avoid the ineffective computation.
-
-To develop its dynamic stiffness matrix, with the help of \Cref{eq:phi_solution1}, the vertical displacement and rotation corresponding to the mode shape $\phi(\xi)$ along the $x$-direction at edges $\xi = -1$ and $\xi = 1$ can be expressed as:
-%
+However, solving these transcendental equations is cumbersome and so the DSM is introduced to avoid such a computation.
+
+To develop the plate's dynamic stiffness matrix, with the help of \Cref{eq:phi_solution1}, the vertical displacement and rotation corresponding to the mode shape $\phi(\xi)$ along the $x$-direction at edges $\xi = -1$ and $\xi = 1$ can be expressed as:
+%
+% In below - isn't alpha_1/a just b?
 \begin{equation}\label{eq:UBx}
@@
 %
-Note that the eigenvector $\mathbf{A}$ can be expressed by multiplying the inverse matrix $\mathbf{Q}_x^{-1}$ on the left side of \Cref{eq:UBx1}, and then substituting $\mathbf{A}$ into \Cref{eq:ABx1}, we obtain:
+Solving for the eigenvector $\mathbf{A}$, and then substituting into \Cref{eq:ABx1}, we obtain:
 %
@@
 \subsection{Dynamic stiffness matrix corresponding to $\omega_y$}\label{sec:DSMy}
+%
+% This section follows the previous section exactly. I'm wondering the value of giving all the same details
+% again? It canbe shortened to only provide what is different, e.g. J, alpha_2, beta_2 etc? 
+% It could start off with something like "Following the same steps as for the x-direction, we have..."
+% All my changes above apply to this section.
+% it's far too much copy & paste right now, even down to the unnecessary definitions of C and S etc
+%
 In this section, the mode shape $\phi(\xi)$ derived in $\Cref{sec:DSMx}$ is utilized to obtain the dynamic stiffness matrix in the $y$-direction.  
@@
 \begin{equation}\label{eq:J_simpx}
-	\Omega_{x,n_x} =
-	\frac{1}{b} \sqrt[4]{%
+	b \Omega^4_{x,n_x} =
 		%\large % slightly smaller than \Large
 		\begin{aligned}
-			&\left[\left(\frac{n_x\pi}{2\alpha}\right)^2 - \frac{D_{12}S_2}{D_{11}S_1} + 2 \frac{D_{66}S_3}{D_{11}S_1}\right]^2 - \left(\frac{D_{12}S_2}{D_{11}S_1} - 2 \frac{D_{66}S_3}{D_{11}S_1}\right)^2 \\
-			&+ \frac{D_{22}S_4}{D_{11}S_1}.
+			&\left[\left(\frac{n_x\pi}{2\alpha}\right)^2 - \frac{D_{12}S_2}{D_{11}S_1} + 2 \frac{D_{66}S_3}{D_{11}S_1}\right]^2 \\
+			&\qquad- \left(\frac{D_{12}S_2}{D_{11}S_1} - 2 \frac{D_{66}S_3}{D_{11}S_1}\right)^2
+			+ \frac{D_{22}S_4}{D_{11}S_1}.
 		\end{aligned}
-	}
 \end{equation}
@@
 \begin{equation}\label{eq:J_simpy}
-	\Omega_{y,n_y}= 
-	\frac{1}{a} \sqrt[4]{%
+	a\Omega^4_{y,n_y}= 
 		\begin{aligned}
-			&\frac{D_{22}}{D_{11}}\left\{\left[\left(\frac{n_y\pi\alpha}{2}\right)^2 - \frac{D_{12}T_2}{D_{22}T_1} + 2 \frac{D_{66}T_3}{D_{22}T_1}\right]^2 - \left(\frac{D_{12}T_2}{D_{22}T_1} - 2 \frac{D_{66}T_3}{D_{22}T_1}\right)^2\right.
-\\
-			&\left.  + \frac{D_{11}T_4}{D_{22}T_1}\right\}.
+			&\frac{D_{22}}{D_{11}}\Biggl\{\left[\left(\frac{n_y\pi\alpha}{2}\right)^2 - \frac{D_{12}T_2}{D_{22}T_1} + 2 \frac{D_{66}T_3}{D_{22}T_1}\right]^2 \\ 
+			&\qquad - \left(\frac{D_{12}T_2}{D_{22}T_1} - 2 \frac{D_{66}T_3}{D_{22}T_1}\right)^2
+			+ \frac{D_{11}T_4}{D_{22}T_1}\Biggr\}.
 		\end{aligned}
-	}
 \end{equation}
@@
 According to the relationships 
-$\Omega_x = \sqrt[4]{{\omega_x^2 \rho h}/{D_{11}}}$ and\ $\Omega_y = \sqrt[4]{{\omega_y^2 \rho h}/{D_{11}}}$, 
+$\Omega^4_x = {{\omega_x^2 \rho h}/{D_{11}}}$ and\ $\Omega^4_y = {{\omega_y^2 \rho h}/{D_{11}}}$, 
 the values of $J(\bar{p}_1, \omega_x^*)$ and $J(\bar{p}_1, \omega_y^*)$ can be derived from $J(\bar{p}_1, \Omega_x^*)$ and $J(\bar{p}_1, \Omega_y^*)$, respectively.
-Therefore, this refined W-W algorithm can be applied to estimate the lower and upper bounds of the frequency range, denoted as $\omega_l$ and $\omega_u$, yielding an approximation for the frequency $\omega_a \in (\omega_l, \omega_u)$.
+Therefore, this refined W-W algorithm can be applied to estimate the lower and upper bounds of the frequency range, denoted as $\omega_l$ and $\omega_u$, yielding an approximation for the frequency $\omega_a \in (\omega_l, \omega_u)$ to arbitrary precision.
 \subsection{Mode shape computation}
@@
 For all numerical calculations, the initial integral parameters are assumed as $I^{(0)}_1=1$, $I^{(0)}_2=1$, $I^{(0)}_3=1$, and $I^{(0)}_4=10$ in the $y$-direction, serving as the starting point of \textbf{Step 1} for any mode in all boundary conditions.
-In this section, the interval between the upper and lower bounds of the non-dimensional frequency parameter, $2a\Delta\Omega$, is set to 0.005, limiting the error range.  
+In this section, the interval between the upper and lower bounds of the non-dimensional frequency parameter, $2a\Delta\Omega$, is set to 0.005, although any desired level of precision can be used.
 According to our numerical calculations, two iteration cycles are generally sufficient to meet the convergence requirement (i.e., $\lvert 2a\Omega^{(i)}_{x} - 2a\Omega^{(i+1)}_{x} \rvert \leq \Delta 2a\Omega$ or $\lvert 2a\Omega^{(i)}_{y} - 2a\Omega^{(i+1)}_{y} \rvert \leq \Delta 2a\Omega$) for most cases, with at most three cycles required when applying the iterative procedure in \Cref{sec:Application procedure}.
@@
 The results for SSSS, SCSF, GCGC, CCCC, SSCC, SCCC, GGCC, CCFF, CFCF, CFFF, and FFFF boundary conditions are presented in \Cref{tab:sov1,tab:sov2,tab:sov3}.
+Note that, as is convention, S is a simple support (rotation, no translation), C is a clamped supported (no rotation or translation), G is a guided support (translation, no rotation), and F is a free edge.
 These results demonstrate high accuracy compared to the extended SOV method, with difference remaining smaller than the frequency parameter interval $2a\Delta\Omega=0.005$. 
@@
 \end{table}
-\subsection{Rotationally restrained boundary conditions}
-In this subsection, rectangular orthotropic plates with rotationally restrained edges ($k^v_\xi = k^v_\eta = \infty$) are validated.  
+\subsection{Rotational spring-supported edges}
+In this subsection, rectangular orthotropic plates with rotational spring-supported edges with no translations ($k^v_\xi = k^v_\eta = \infty$) are examined.  
 The rotational stiffness coefficients are defined as: 
@@
 
-Interestingly, the results indicate that the frequencies $\Omega_x$ and $\Omega_y$ are not strictly equal for some mode shapes under rotationally restrained boundary conditions.  
+Interestingly, the results indicate that the frequencies $\Omega_x$ and $\Omega_y$ are not strictly equal for some mode shapes under these boundary conditions.  
 The actual frequency $\Omega$ lies between $\Omega_x$ and $\Omega_y$, which may be attributed to the fact that $\Omega_x$ and $\Omega_y$ satisfy Rayleigh’s principle in \Cref{eq:Rayleigh}, representing the weak-form governing equations, but do not necessarily satisfy the strong-form governing equations in \Cref{eq:governing_EOM}.
@@
 
-In certain numerical calculations involving rotationally restrained boundary conditions, the variables $\alpha_1$ and $\alpha_2$ may take complex values rather than being purely real.  
+Interestingly, in certain numerical calculations involving rotationally restrained boundary conditions, the variables $\alpha_1$ and $\alpha_2$ may take complex values rather than being purely real.  
 Consequently, the mode shape coefficients $A_1$, $A_2$, $B_1$, and $B_2$ become complex-valued, leading to $\mathbf{R}$ and $\mathbf{Q}^{-1}$ being complex matrices.  
@@
 \section{Conclusion}
-In this study, the dynamic stiffness matrix (DSM) based on the extended separation-of-variable (SOV) type solution has been developed for the vibration analysis of an orthotropic rectangular plate with general homogeneous boundary conditions.
-
-Instead of solving highly nonlinear eigenvalue equations involved in the SOV methods, the extended SOV type solution is adopted to construct the dynamic stiffness matrices.
+In this study, the dynamic stiffness matrix (DSM) based on the extended separation-of-variable (SOV) solution has been developed for the vibration analysis of an orthotropic rectangular plate with general homogeneous boundary conditions.
+
+Instead of solving highly nonlinear eigenvalue equations involved in the SOV methods, the extended SOV solution is adopted to construct the dynamic stiffness matrices.
 Several novel techniques have proposed to solve the eigenvalue problem and mode shape computation.
@@
 
-Classical boundary conditions, such as guided, simply supported, clamped, and free edges, can be realized by setting the translational springs ($k^v_\xi$) and rotational springs ($k^r_\xi$) along the plate edges to either zero or infinity.
-Numerical experiments have validated accuracy of this approach for these boundary conditions.  
-The results shows that the SOV type solution can also be extended to handle elastically restrained boundary conditions.
-Despite certain approximations inherent in some elastically restrained cases, the maximum percentage error across all numerical experiments remains within $1.25\%$.  
-This may occur because the SOV type solution used is derived from the weak-form governing equation, which is based on Rayleigh's principle.
-
-Since the SOV type solution $\phi(\xi) \psi(\eta)$ consists of only a single term for each mode order, unlike the infinite series expansions used in the traditional DSM, each eigenvalue solution can be explicitly expressed.
+Classical boundary conditions, such as guided, simply supported, clamped, and free edges, can be realized by setting the translational springs ($k^v_\xi$) and rotational springs ($k^r_\xi$) along the plate edges to either zero or infinity, as appropriate.
+Numerical experiments validate the accuracy of this approach for these boundary conditions.  
+The results shows that the SOV solution can also be extended to handle elastically-restrained boundary conditions.
+Despite certain approximations inherent in some elastically-restrained cases, the maximum percentage error across all numerical experiments remains within $1.25\%$. 
+This may occur because the SOV solution used is derived from the weak-form governing equation, which is based on Rayleigh's principle.
+
+Since the SOV solution $\phi(\xi) \psi(\eta)$ consists of only a single term for each mode order, unlike the infinite series expansions used in the traditional DSM, each eigenvalue solution can be explicitly expressed.
+% what do you mean 'concise'?
 This suggests the potential for obtaining more concise solutions for assembled plate structures compared to traditional DSM methods.
+
+Finally, the developments reported in this paper should find good application with researchers and practitioners interested in the vibration of generally-supported rectangular orthotropic plates.
 

### 2025-07-08 Paper7.tex
update

@@
 \begin{abstract}
-The dynamic stiffness matrix (DSM) based on the extended separation-of-variables (SOV) type mode solution is developed for the free vibration analysis of an orthotropic rectangular thin plate with general homogeneous boundary conditions.
+The dynamic stiffness matrix (DSM) based on the extended separation-of-variables (SOV) solution is developed for the free vibration analysis of an orthotropic rectangular thin plate with general homogeneous boundary conditions.
 The method combines the advantages of the DSM method and the SOV method.
-The SOV type solution satisfies the governing differential equation derived from Rayleigh’s principle and is used to formulate dynamic stiffness matrices.
-Owing to the characteristics of the SOV type solution, the fully clamped boundary condition problem associated with the Wittrick–Williams algorithm is resolved. 
+The SOV solution satisfies the governing differential equation derived from Rayleigh’s principle and is used to formulate dynamic stiffness matrices.
+Owing to the characteristics of the SOV solution, the fully clamped boundary condition problem associated with the Wittrick–Williams algorithm is resolved. 
 The enhanced algorithm is further proposed to solve dynamic stiffness matrices, rather than solving eigenvalue equations.
@@
 In this study, the SOV method is further extended to analyze the vibrations of plates with elastically restrained edges.
-This extended SOV solution is then employed to construct the dynamic stiffness matrices, which accommodate all general homogeneous boundary conditions.
+This extended SOV solution is then employed to construct dynamic stiffness matrices, which accommodate all general homogeneous boundary conditions.
 By taking advantage of both the SOV and DSM methods, an enhanced W-W algorithm is developed to solve the eigenvalue problem without directly solving the eigenvalue equations.
@@
 \begin{equation}\label{eq:governing_EOM}
-	D_{11}\frac{\partial^4w}{\partial \xi^4} + 2D_3\alpha^2\frac{\partial^4w}{\partial \xi^2 \partial \eta^2} + D_{22}\alpha^4\frac{\partial^4w}{\partial \eta^4} = \rho h\alpha^4\omega^2w,
-\end{equation}
-%
-where $ \alpha = a / b $ is the aspect ratio; $ \xi = x / a $ and $ \eta = y / b $ are the normalized coordinates, and the bending stiffness parameters are defined as:
+	D_{11}\frac{\partial^4w}{\partial \xi^4} + 2D_3\chi^2\frac{\partial^4w}{\partial \xi^2 \partial \eta^2} + D_{22}\chi^4\frac{\partial^4w}{\partial \eta^4} = \rho ha^4\omega^2w,
+\end{equation}
+%
+where $ \chi = a / b $ is the aspect ratio; $ \xi = x / a $ and $ \eta = y / b $ are the normalized coordinates, and the bending stiffness parameters are defined as:
 %
@@
 	\begin{split}
-		\delta U_{mag} &= \omega^2\,\delta T_0,
+		\delta U &= \delta T,
 	\end{split}
@@
 %
-where $\delta$ denotes variation, $U_{mag}$ is the magnitude of the potential energy of the plate, and $\omega^2 T_0$ represents the magnitude of the kinetic energy of the plate.
+where $\delta$ denotes variation, $U$ is the magnitude of the potential energy of the plate, and $T$ represents the magnitude of the kinetic energy of the plate.
 The potential energy of the plate can be expressed as \cite{xing2020extended}:
@@
 	\begin{split}
-		U_{\text{mag}}^{I} &= \frac{ab}{2} \iint \left[ \frac{D_{11}}{a^4} \left( \frac{\partial^2 w}{\partial \xi^2} \right)^2 + \frac{2 D_{12}}{a^2 b^2} \frac{\partial^2 w}{\partial \xi^2} \frac{\partial^2 w}{\partial \eta^2} + \frac{D_{22}}{b^4} \left( \frac{\partial^2 w}{\partial \eta^2} \right)^2 \right.
+		U^{I} &= \frac{ab}{2} \iint \left[ \frac{D_{11}}{a^4} \left( \frac{\partial^2 w}{\partial \xi^2} \right)^2 + \frac{2 D_{12}}{a^2 b^2} \frac{\partial^2 w}{\partial \xi^2} \frac{\partial^2 w}{\partial \eta^2} + \frac{D_{22}}{b^4} \left( \frac{\partial^2 w}{\partial \eta^2} \right)^2 \right.
 \\
@@
 	\begin{split}
-		T &= \omega^2 \frac{ab}{2} \rho h \iint w^2 \, \mathrm{d} \xi \, \mathrm{d} \eta = \omega^2 T_0
+		T &= \omega^2 \frac{ab}{2} \rho h \iint w^2 \, \mathrm{d} \xi \, \mathrm{d} \eta=\omega^2T_0
 	\end{split},
@@
 %
+where, $T_0$ is defined as the coefficient of the kinetic energy.
+
 The separable form of the mode shape function $ w(\xi, \eta)$ is given by:
@@
 Based on \Cref{eq:Rayleigh}, the frequencies $\omega_x$ and $\omega_y$, corresponding to the mode shapes $\phi(\xi)$ and $\psi(\eta)$, respectively, are assumed to be independent of each other.
+This is a common and important assumption in SOV methods, and $\omega_x$ and $\omega_y$ can be different in a mathematical sense \cite{xing2020extended}.
+
 % worth a comment here on:
@@
 	\begin{split}
-		U^{II} &=  \int\left[k^r_{\xi=-1} \left( \frac{\partial W}{\partial x} \right)^2 + k^v_{\xi=-1} \left( W \right)^2\right]_{x=-a} \id y\\
+		U^{x} &=  \int\left[k^r_{\xi=-1} \left( \frac{\partial W}{\partial x} \right)^2 + k^v_{\xi=-1} \left( W \right)^2\right]_{x=-a} \id y\\
 		&\qquad +  \int\left[k^r_{\xi=1} \left( \frac{\partial W}{\partial x} \right)^2 + k^v_{\xi=1} \left( W \right)^2\right]_{x=a} \id y.
@@
 % Why not just use U subscript x for this contribution of these supports?
-From \Cref{eq:poten_energy_edgex}, the magnitude of total potential energy along the edges in the $x$-direction is obtained as:
+From \Cref{eq:poten_energy_edgex}, the magnitude of potential energy along the plate edges in the $x$-direction, expressed in dimensionless coordinates, is obtained as:
+
 %
@@
 	\begin{split}
-		U^{II}_{mag} &= ab \int\left[\frac{k^r_{\xi=-1}}{a^3} \left( \frac{\partial w}{\partial \xi} \right)^2 + \frac{k^v_{\xi=-1}}{a} \left( w \right)^2\right]_{\xi=-1} \, \id \eta \\
+		U^{x} &= ab \int\left[\frac{k^r_{\xi=-1}}{a^3} \left( \frac{\partial w}{\partial \xi} \right)^2 + \frac{k^v_{\xi=-1}}{a} \left( w \right)^2\right]_{\xi=-1} \, \id \eta \\
 		&\qquad + ab \int\left[\frac{k^r_{\xi=1}}{a^3} \left( \frac{\partial w}{\partial \xi} \right)^2 + \frac{k^v_{\xi=1}}{a} \left( w \right)^2\right]_{\xi=1} \, \id \eta.
@@
 % Not sure why this now deserves a 'mag' subscript.
-The magnitude of potential energy of the plate in the $x$-direction can be obtained from \Cref{eq:poten_energy_mag,eq:poten_energy_edgex2} as:
+The magnitude of total potential energy of the plate in the $x$-direction can be obtained from \Cref{eq:poten_energy_mag,eq:poten_energy_edgex2} as:
 %
@@
 	\begin{split}
-		U_{mag} &= U^{I}_{mag} + U^{II}_{mag} \\
+		U &= U^{I} + U^{x} \\
 		&= \frac{ab}{2} \iint \left[ \frac{D_{11}}{a^4} \left( \frac{\partial^2 w}{\partial \xi^2} \right)^2 + \frac{2 D_{12}}{a^2 b^2} \frac{\partial^2 w}{\partial \xi^2} \frac{\partial^2 w}{\partial \eta^2} + \frac{D_{22}}{b^4} \left( \frac{\partial^2 w}{\partial \eta^2} \right)^2 \right.
@@
 	\begin{split}
-		U_{mag}&=\frac{ab}{2} \int_{-1}^{1} \left[ \frac{D_{11}}{a^4}I_1 \left( \frac{\id^2\phi }{\id \xi^2} \right)^2 + \frac{2 D_{12}}{a^2 b^2}I_2 \frac{\id^2\phi }{\id \xi^2}\phi  + \frac{D_{22}}{b^4}I_4  \phi^2 \right.
+		U&=\frac{ab}{2} \int_{-1}^{1} \left[ \frac{D_{11}}{a^4}I_1 \left( \frac{\id^2\phi }{\id \xi^2} \right)^2 + \frac{2 D_{12}}{a^2 b^2}I_2 \frac{\id^2\phi }{\id \xi^2}\phi  + \frac{D_{22}}{b^4}I_4  \phi^2 \right.
 \\
@@
 %
-where the integral parameters are defined as:
-%
-\begin{equation}\label{eq:inte_phi_text}  
-	\begin{split}  
-		&I_1 = \int_{-1}^{1} \psi^2 \, \id\eta, \\  
-		&I_2 = \int_{-1}^{1} \left( \frac{\id^2 \psi}{\id \eta^2} \psi \right) \, \id\eta, \\  
-		&I_3 = \int_{-1}^{1} \left( \frac{\id \psi}{\id \eta} \right)^2 \, \id\eta, \\  
-		&I_4 = \int_{-1}^{1} \left( \frac{\id^2 \psi}{\id \eta^2} \right)^2 \, \id\eta.  
-	\end{split}  
-\end{equation}   
-%
-By taking \Cref{eq:displace_func} into account, the coefficient $T_0$ of the kinetic energy from \Cref{eq:kine_energy_mag} for the plate can be expressed as:
+where the integral parameters $I_1$, $I_2$, $I_3$, and $ I_4$ are defined and expressed in \Cref{sec:appendA}.
+
+By taking \Cref{eq:displace_func} into account, the coefficient $T_0$ of the kinetic energy from \Cref{eq:kine_energy_mag} for the plate in the $x$-direction can be expressed as:
 %
@@
 	\begin{split}
-		\delta U_{mag} &= \omega_x^2 \, \delta T_0,
+		\delta U &= \omega_x^2 \, \delta T_0,
 	\end{split}
@@
 \begin{equation}\label{eq:ODEx}
-		\frac{\id^4 \phi}{\id \xi^4}+ 2\alpha^2\left(\frac{D_{12}I_2}{D_{11}I_1}-2\frac{D_{66}I_3}{D_{11}I_1}\right)\frac{\id^2 \phi}{\id \xi^2}+\left(\alpha^4\frac{D_{22}I_4}{D_{11}I_1}-a^4\Omega_x^4\right)\phi=0,
+		\frac{\id^4 \phi}{\id \xi^4}+ 2\chi^2\left(\frac{D_{12}I_2}{D_{11}I_1}-2\frac{D_{66}I_3}{D_{11}I_1}\right)\frac{\id^2 \phi}{\id \xi^2}+\left(\chi^4\frac{D_{22}I_4}{D_{11}I_1}-a^4\Omega_x^4\right)\phi=0,
 \end{equation}
@@
 	\begin{split}
-		\mu^4 + 2\alpha^2\left(\frac{D_{12}I_2}{D_{11}I_1}-2\frac{D_{66}I_3}{D_{11}I_1}\right)\mu^2 + \left(\alpha^4\frac{D_{22}I_4}{D_{11}I_1}-a^4\Omega_x^4\right) = 0.
+		\mu^4 + 2\chi^2\left(\frac{D_{12}I_2}{D_{11}I_1}-2\frac{D_{66}I_3}{D_{11}I_1}\right)\mu^2 + \left(\chi^4\frac{D_{22}I_4}{D_{11}I_1}-a^4\Omega_x^4\right) = 0.
 	\end{split}
@@
 	\begin{align}
-		\alpha_1 &= \alpha \sqrt{\sqrt{\left(\frac{D_{12}I_2}{D_{11}I_1}-2\frac{D_{66}I_3}{D_{11}I_1}\right)^2 - \frac{D_{22}I_4}{D_{11}I_1} + b^4\Omega_x^4} + \frac{D_{12}I_2}{D_{11}I_1} - 2\frac{D_{66}I_3}{D_{11}I_1}},\label{eq:alphax1}\\
-		\beta_1 &= \alpha \sqrt{\sqrt{\left(\frac{D_{12}I_2}{D_{11}I_1}-2\frac{D_{66}I_3}{D_{11}I_1}\right)^2 - \frac{D_{22}I_4}{D_{11}I_1} + b^4\Omega_x^4} - \frac{D_{12}I_2}{D_{11}I_1} + 2\frac{D_{66}I_3}{D_{11}I_1}}.\label{eq:alphax2}
+		\alpha_1 &= \chi \sqrt{\sqrt{\left(\frac{D_{12}I_2}{D_{11}I_1}-2\frac{D_{66}I_3}{D_{11}I_1}\right)^2 - \frac{D_{22}I_4}{D_{11}I_1} + b^4\Omega_x^4} + \frac{D_{12}I_2}{D_{11}I_1} - 2\frac{D_{66}I_3}{D_{11}I_1}},\label{eq:alphax1}\\
+		\beta_1 &= \chi \sqrt{\sqrt{\left(\frac{D_{12}I_2}{D_{11}I_1}-2\frac{D_{66}I_3}{D_{11}I_1}\right)^2 - \frac{D_{22}I_4}{D_{11}I_1} + b^4\Omega_x^4} - \frac{D_{12}I_2}{D_{11}I_1} + 2\frac{D_{66}I_3}{D_{11}I_1}}.\label{eq:alphax2}
 	\end{align}
@@
 	\begin{align}
-		&  \frac{\id^3 \phi}{\id \xi^3} - \alpha^2\left( \frac{4D_{66}I_3}{D_{11}I_1}  - \frac{D_{12}I_2}{D_{11}I_1}  \right) \frac{\id \phi}{\id \xi} 
+		&  \frac{\id^3 \phi}{\id \xi^3} - \chi^2\left( \frac{4D_{66}I_3}{D_{11}I_1}  - \frac{D_{12}I_2}{D_{11}I_1}  \right) \frac{\id \phi}{\id \xi} 
 		+\frac{2a^3k^v_{\xi=-1}}{D_{11}}\phi = 0, \quad &\xi = -1, \\
-		& \frac{\id^2 \phi}{\id \xi^2} + \frac{\alpha^2 D_{12} I_2}{D_{11} I_1} \phi - \frac{2a k^r_{\xi=-1}}{D_{11}} \frac{\id \phi}{\id \xi} = 0, \quad &\xi = -1, \\
-		& \frac{\id^3 \phi}{\id \xi^3} - \alpha^2\left( \frac{4D_{66}I_3}{D_{11}I_1}  - \frac{D_{12}I_2}{D_{11}I_1}  \right) \frac{\id \phi}{\id \xi} 
+		& \frac{\id^2 \phi}{\id \xi^2} + \frac{\chi^2 D_{12} I_2}{D_{11} I_1} \phi - \frac{2a k^r_{\xi=-1}}{D_{11}} \frac{\id \phi}{\id \xi} = 0, \quad &\xi = -1, \\
+		& \frac{\id^3 \phi}{\id \xi^3} - \chi^2\left( \frac{4D_{66}I_3}{D_{11}I_1}  - \frac{D_{12}I_2}{D_{11}I_1}  \right) \frac{\id \phi}{\id \xi} 
 		-\frac{2a^3 k^v_{\xi=1}}{D_{11}} \phi = 0, \quad &\xi = 1, \\
-		& \frac{\id^2 \phi}{\id \xi^2} + \frac{\alpha^2 D_{12} I_2}{D_{11} I_1} \phi + \frac{2a k^r_{\xi=1}}{D_{11}} \frac{\id \phi}{\id \xi} = 0, \quad &\xi = 1.
+		& \frac{\id^2 \phi}{\id \xi^2} + \frac{\chi^2 D_{12} I_2}{D_{11} I_1} \phi + \frac{2a k^r_{\xi=1}}{D_{11}} \frac{\id \phi}{\id \xi} = 0, \quad &\xi = 1.
 	\end{align}
@@
 %
-Substituting \Cref{eq:phi_solution1} into \Cref{eq:boundaryx}, and denoting $ k^{u*}_{\xi} \equiv \frac{2a^3 k^u_{\xi}}{D_{11}} $ for $u \in \{r,v\}$, $ S_u \equiv \sin u $, $ C_u \equiv \cos u $, $ Sh_u \equiv \sinh u$, and $ Ch_u \equiv \cosh u $, we have:
+Substituting \Cref{eq:phi_solution1} into \Cref{eq:boundaryx}, and denoting $k^{v*}_{\xi} = \frac{2a^3 k^v_{\xi}}{D_{11}} $, 
+$ k^{r*}_{\eta} = \frac{2a k^r_{\xi}}{D_{11}} $, $ S_{\alpha_1} = \sin \alpha_1 $, $ C_{\alpha_1} =\cos \alpha_1 $, $ Sh_{\beta_1} = \sinh \beta_1$, and $ Ch_{\beta_1} = \cosh \beta_1 $, we have:
 %
@@
 	\begin{split}
-		&\gamma_1 = -\alpha_1^3 - \alpha^2 \left( \frac{4D_{66}S_3}{D_{11}I_1} - \frac{D_{12}I_2}{D_{11}I_1} \right) \alpha_1, \\
-		&\gamma_2 = \beta_1^3 - \alpha^2 \left( \frac{4D_{66}S_3}{D_{11}I_1} - \frac{D_{12}I_2}{D_{11}I_1} \right) \beta_1, \\
-		&\gamma_3 = -\alpha_1^2 + \frac{\alpha^2 D_{12} I_2}{D_{11} I_1}, \\
-		&\gamma_4 = \beta_1^2 + \frac{\alpha^2 D_{12} I_2}{D_{11} I_1}.
+		&\gamma_1 = -\alpha_1^3 - \chi^2 \left( \frac{4D_{66}S_3}{D_{11}I_1} - \frac{D_{12}I_2}{D_{11}I_1} \right) \alpha_1, \\
+		&\gamma_2 = \beta_1^3 - \chi^2 \left( \frac{4D_{66}S_3}{D_{11}I_1} - \frac{D_{12}I_2}{D_{11}I_1} \right) \beta_1, \\
+		&\gamma_3 = -\alpha_1^2 + \frac{\chi^2 D_{12} I_2}{D_{11} I_1}, \\
+		&\gamma_4 = \beta_1^2 + \frac{\chi^2 D_{12} I_2}{D_{11} I_1}.
 	\end{split}
@@
 
-The magnitude of total potential energy along the edges in the $y$-direction is given by:  
-%
-\begin{equation}\label{eq:poten_energy_edgey2}  
-	\begin{split}  
-		U^{III}_{mag} &= ab \int \left[ \frac{k^r_{\eta=-1}}{a^3} \left( \frac{\partial w}{\partial \eta} \right)^2 + \frac{k^v_{\eta=-1}}{a} w^2 \right]_{\eta=-1} \id \xi \\  
-		&\qquad + ab \int \left[ \frac{k^r_{\eta=1}}{a^3} \left( \frac{\partial w}{\partial \eta} \right)^2 + \frac{k^v_{\eta=1}}{a} w^2 \right]_{\eta=1} \id \xi.  
-	\end{split}  
-\end{equation} 
-% 
-The magnitude of potential energy of the plate in the $y$-direction can be obtained from
-\Cref{eq:poten_energy_mag,eq:poten_energy_edgey2} as:
-%
-\begin{equation}\label{eq:poten_energy_toly}
-	\begin{split}
-		U_{mag}&=U^{I}_{mag}+U^{III}_{mag}\\
-		&=\frac{ab}{2} \iint \left[ \frac{D_{11}}{a^4} \left( \frac{\partial^2 w}{\partial \xi^2} \right)^2 + \frac{2 D_{12}}{a^2 b^2} \frac{\partial^2 w}{\partial \xi^2} \frac{\partial^2 w}{\partial \eta^2} + \frac{D_{22}}{b^4} \left( \frac{\partial^2 w}{\partial \eta^2} \right)^2 \right.
-\\
-		&\qquad \left.
-+ \frac{4 D_{66}}{a^2 b^2}\left( \frac{\partial^2 w}{\partial \xi \partial \eta} \right)^2 \right] \, \id\xi \, \id\eta+ab \int \left[ \frac{k^r_{\eta=1}}{b^3} \left( \frac{\partial w}{\partial \eta} \right)^2 + \frac{k^v_{\eta=1}}{b} \left( w \right)^2 \right]_{\eta=1} \id\xi\\
-		&\qquad+ab \int \left[ \frac{k^r_{\eta=-1}}{b^3} \left( \frac{\partial w}{\partial \eta} \right)^2 + \frac{k^v_{\eta=-1}}{b} \left( w \right)^2 \right]_{\eta=-1} \id\xi.
-	\end{split}
-\end{equation}
-%
-By substituting \Cref{eq:displace_func} into \Cref{eq:poten_energy_toly}, we obtain:  
+Following the same steps as for the x-direction, the magnitude of potential energy of the plate in the $y$-direction can be obtained as:
 %
@@
 	\begin{split}
-		U_{mag} &= U^{I}_{mag} + U^{III}_{mag} \\
+		U
 		&= \frac{ab}{2} \int_{-1}^{1} \left[ \frac{D_{11}}{a^4} J_4 \psi^2 
@@
 %
-where the integral parameters are defined as:  
-%
-\begin{equation}\label{eq:inte_psi}  
-	\begin{split}  
-		&J_1 = \int_{-1}^{1} \phi^2 \, \id\xi, \\  
-		&J_2 = \int_{-1}^{1} \left( \frac{\id^2\phi}{\id\xi^2} \phi \right) \, \id\xi, \\  
-		&J_3 = \int_{-1}^{1} \left( \frac{\id\phi}{\id\xi} \right)^2 \, \id\xi, \\  
-		&J_4 = \int_{-1}^{1} \left( \frac{\id^2\phi}{\id\xi^2} \right)^2 \, \id\xi.  
-	\end{split}  
-\end{equation}  
-%
-The coefficient $T_0$ of the kinetic energy from \Cref{eq:kine_energy_mag} for the plate can be expressed as:
+where the integral parameters $J_1$, $J_2$, $J_3$, and $J_4$ are defined and expressed in \Cref{sec:appendA}.
+
+The coefficient $T_0$ of the kinetic energy from \Cref{eq:kine_energy_mag} for the plate in the $y$-direction can be expressed as:
 %
@@
 	\begin{split}
-		\delta U_{mag} &= \omega_y^2 \, \delta T_0.
-	\end{split}
-\end{equation}
-%
-By substituting \Cref{eq:poten_energy_toly2,eq:kine_energyy} into \Cref{eq:Rayleighy}, and relieving $ \delta \psi $ and $\delta\frac{\id \psi}{\id \eta}$ in \Cref{eq:Rayleighy} by variation calculus, yields:
+		\delta U &= \omega_y^2 \, \delta T_0.
+	\end{split}
+\end{equation}
+%
+By substituting \Cref{eq:poten_energy_toly2,eq:kine_energyy} into \Cref{eq:Rayleighy}, and relieving $ \delta \psi $ and $\delta\frac{\id \psi}{\id \eta}$ in \Cref{eq:Rayleighy} by calculus of variation, yields:
 %
@@
 \begin{equation}\label{eq:ODEy}
-		\frac{\id^4 \psi}{\id \eta^4} + \frac{2}{\alpha^2}\left(\frac{D_{12}J_2}{D_{22}J_1} - 2\frac{D_{66}J_3}{D_{22}J_1}\right)\frac{\id^2 \psi}{\id \eta^2} + \left( \frac{D_{11}J_4}{\alpha^4D_{22}J_1} - \frac{b^4D_{11}}{D_{22}} \Omega_y^4 \right) \psi = 0,
+		\frac{\id^4 \psi}{\id \eta^4} + \frac{2}{\chi^2}\left(\frac{D_{12}J_2}{D_{22}J_1} - 2\frac{D_{66}J_3}{D_{22}J_1}\right)\frac{\id^2 \psi}{\id \eta^2} + \left( \frac{D_{11}J_4}{\chi^4D_{22}J_1} - \frac{b^4D_{11}}{D_{22}} \Omega_y^4 \right) \psi = 0,
 \end{equation}
@@
 	\begin{split}
-		\lambda^4 + \frac{2}{\alpha^2} \left( \frac{D_{12}J_2}{D_{22}J_1} - 2\frac{D_{66}J_3}{D_{22}J_1} \right) \lambda^2 + \left( \frac{D_{11}J_4}{\alpha^4D_{22}J_1} - \frac{b^4D_{11}}{D_{22}} \Omega_y^4 \right) = 0.
+		\lambda^4 + \frac{2}{\chi^2} \left( \frac{D_{12}J_2}{D_{22}J_1} - 2\frac{D_{66}J_3}{D_{22}J_1} \right) \lambda^2 + \left( \frac{D_{11}J_4}{\chi^4D_{22}J_1} - \frac{b^4D_{11}}{D_{22}} \Omega_y^4 \right) = 0.
 	\end{split}
@@
 	\begin{align}
-		\alpha_2 &= \frac{1}{\alpha} \sqrt{ \sqrt{ \left( \frac{D_{12}J_2}{D_{22}J_1} - 2\frac{D_{66}J_3}{D_{22}J_1} \right)^2 - \frac{D_{11}J_4}{D_{22}J_1} + \frac{a^4 D_{11}}{D_{22}} \Omega_y^4 } + \frac{D_{12}J_2}{D_{22}J_1} - 2 \frac{D_{66}J_3}{D_{22}J_1}}, \\
-		\beta_2 &= \frac{1}{\alpha} \sqrt{ \sqrt{ \left( \frac{D_{12}J_2}{D_{22}J_1} - 2 \frac{D_{66}J_3}{D_{22}J_1} \right)^2 - \frac{D_{11}J_4}{D_{22}J_1} + \frac{a^4 D_{11}}{D_{22}} \Omega_y^4 } - \frac{D_{12}J_2}{D_{22}J_1} + 2 \frac{D_{66}J_3}{D_{22}J_1}}.
+		\alpha_2 &= \frac{1}{\chi} \sqrt{ \sqrt{ \left( \frac{D_{12}J_2}{D_{22}J_1} - 2\frac{D_{66}J_3}{D_{22}J_1} \right)^2 - \frac{D_{11}J_4}{D_{22}J_1} + \frac{a^4 D_{11}}{D_{22}} \Omega_y^4 } + \frac{D_{12}J_2}{D_{22}J_1} - 2 \frac{D_{66}J_3}{D_{22}J_1}}, \\
+		\beta_2 &= \frac{1}{\chi} \sqrt{ \sqrt{ \left( \frac{D_{12}J_2}{D_{22}J_1} - 2 \frac{D_{66}J_3}{D_{22}J_1} \right)^2 - \frac{D_{11}J_4}{D_{22}J_1} + \frac{a^4 D_{11}}{D_{22}} \Omega_y^4 } - \frac{D_{12}J_2}{D_{22}J_1} + 2 \frac{D_{66}J_3}{D_{22}J_1}}.
 	\end{align}
@@
 %
-Thus, we can obtain the shear force and bending moment equilibrium along the edges $\eta = -1$ and $\eta = 1$ from \Cref{eq:inertial_forcey,eq:inertial_forcey2}, respectively, as:
-%
-\begin{subequations}\label{eq:boundaryy}
-	\begin{align}
-		&  \frac{\id^3 \psi}{\id \eta^3}-\left( \frac{4D_{66}J_3}{\alpha^2D_{22}J_1}  - \frac{D_{12}J_2}{\alpha^2D_{22}J_1}  \right) \frac{\id \psi}{\id \eta} 
-		+\frac{2b^3k^v_{\eta=-1}}{D_{22}}\psi=0,\quad &\eta=-1,\\
-		& \frac{\id^2 \psi}{\id \eta^2}+\frac{D_{12}J_2}{\alpha^2D_{22}J_1} \psi -\frac{2bk^r_{\eta=-1}}{D_{22}}\frac{\id\psi }{\id \eta}=0,\quad &\eta=-1,\\
-		&  \frac{\id^3 \psi}{\id \eta^3}-\left( \frac{4D_{66}J_3}{\alpha^2D_{22}J_1}  - \frac{D_{12}J_2}{\alpha^2D_{22}J_1}  \right) \frac{\id \psi}{\id \eta} 
-		-\frac{2b^3k^v_{\eta=1}}{D_{22}}\psi=0,\quad &\eta=1,\\
-		&\frac{\id^2 \psi}{\id \eta^2}+\frac{D_{12}J_2}{\alpha^2D_{22}J_1} \psi +\frac{2bk^r_{\eta=1}}{D_{22}}\frac{\id\psi }{\id \eta}=0,\quad &\eta=1.
-	\end{align}
-\end{subequations}
-%
-Substituting \Cref{eq:phi_solution2} into \Cref{eq:boundaryy} and denoting
+Similarly, from the shear force and bending moment equilibrium, and by denoting 
 $k^{v*}_{\eta} = \frac{2b^3 k^v_{\eta}}{D_{22}} $, 
@@
 $ C_{\alpha_2}=\cos\alpha_2  $, 
-$ Sh_{\alpha_2}=\sinh\alpha_2  $, 
-$ Ch_{\alpha_2}=\cosh\alpha_2 $, 
-$ S_{\beta_2}=\sin\beta_2 $, 
-$ C_{\beta_2}=\cos\beta_2 $, 
 $ Sh_{\beta_2}=\sinh\beta_2$, and 
 $Ch_{\beta_2}= \cosh\beta_2$, 
-We obtain:
+We can obtain:
 %
@@
 	\begin{split}
-		&\zeta_1=-\alpha_2^3-\left( \frac{4D_{66}J_3}{\alpha^2D_{22}J_1}  - \frac{D_{12}J_2}{\alpha^2D_{22}J_1}  \right)\alpha_2,\\
-		&\zeta_2=\beta_2^3-\left( \frac{4D_{66}T_3}{\alpha^2D_{22}J_1}  - \frac{D_{12}J_2}{\alpha^2D_{22}J_1}  \right)\beta_2,\\
-		&\zeta_3=-\alpha_2^2+\frac{D_{12}J_2}{\alpha^2D_{22}J_1},\\
-		&\zeta_4=\beta_2^2+\frac{D_{12}J_2}{\alpha^2D_{22}J_1}.
+		&\zeta_1=-\alpha_2^3-\left( \frac{4D_{66}J_3}{\chi^2D_{22}J_1}  - \frac{D_{12}J_2}{\chi^2D_{22}J_1}  \right)\alpha_2,\\
+		&\zeta_2=\beta_2^3-\left( \frac{4D_{66}T_3}{\chi^2D_{22}J_1}  - \frac{D_{12}J_2}{\chi^2D_{22}J_1}  \right)\beta_2,\\
+		&\zeta_3=-\alpha_2^2+\frac{D_{12}J_2}{\chi^2D_{22}J_1},\\
+		&\zeta_4=\beta_2^2+\frac{D_{12}J_2}{\chi^2D_{22}J_1}.
 	\end{split}
@@
 			-S_{\alpha_2} & C_{\alpha_2} & -Sh_{\beta_2} & Ch_{\beta_2} \\
-			\frac{\alpha_2 C_{\alpha_2}}{b} & \frac{\alpha_2 S_{\alpha_2}}{b} & \frac{\beta_2 Ch_{\beta_2}}{b} & -\frac{\beta_2 Sh_{\beta_2}}{b} \\
+			\alpha_2 C_{\alpha_2}/b & \alpha_2 S_{\alpha_2}/b & \beta_2 Ch_{\beta_2}/b & -\beta_2 Sh_{\beta_2}/b \\
 			S_{\alpha_2} & C_{\alpha_2} & Sh_{\beta_2} & Ch_{\beta_2} \\
-			\frac{\alpha_2 C_{\alpha_2}}{b} & -\frac{\alpha_2 S_{\alpha_2}}{b} & \frac{\beta_2 Ch_{\beta_2}}{b} & \frac{\beta_2 Sh_{\beta_2}}{b}
+			\alpha_2 C_{\alpha_2}/b & -\frac{\alpha_2 S_{\alpha_2}}{b} & \beta_2 Ch_{\beta_2}/b & \beta_2 Sh_{\beta_2}/b
 		\end{bmatrix}
@@
 %
-Note that the eigenvector $\mathbf{B}$ can be expressed by multiplying the inverse matrix $\mathbf{Q}_y^{-1}$ on the left-hand side of \Cref{eq:UBy1}, and then substituting $\mathbf{B}$ into \Cref{eq:ABy1}, we obtain:
+Solving for the eigenvector $\mathbf{B}$, and then substituting into \Cref{eq:ABy1}, we obtain:
 %
@@
 Therefore, the challenge of determining $J_0(p_1, \omega^*)$ can be transformed into the problem of solving $ J(\bar{p}_1, \omega^*)$ instead.
-By considering fully simply supported boundary conditions, the eigenvalue equation corresponding to the natural frequency parameter $ \Omega_x $ can be obtained from the determinant of the coefficient matrix $ \mathbf{R}_x $ in \Cref{eq:ABx}, as given by:
+
+By taking fully simply supported boundary conditions as the example, the eigenvalue equation corresponding to the natural frequency parameter $ \Omega_x $ can be obtained from the determinant of the coefficient matrix $ \mathbf{R}_x $ in \Cref{eq:ABx}, as given by:
 %
@@
 		\begin{aligned}
-			&\left[\left(\frac{n_x\pi}{2\alpha}\right)^2 - \frac{D_{12}S_2}{D_{11}S_1} + 2 \frac{D_{66}S_3}{D_{11}S_1}\right]^2 \\
+			&\left[\left(\frac{n_x\pi}{2\chi}\right)^2 - \frac{D_{12}S_2}{D_{11}S_1} + 2 \frac{D_{66}S_3}{D_{11}S_1}\right]^2 \\
 			&\qquad- \left(\frac{D_{12}S_2}{D_{11}S_1} - 2 \frac{D_{66}S_3}{D_{11}S_1}\right)^2
@@
 		\begin{aligned}
-			&\frac{D_{22}}{D_{11}}\Biggl\{\left[\left(\frac{n_y\pi\alpha}{2}\right)^2 - \frac{D_{12}T_2}{D_{22}T_1} + 2 \frac{D_{66}T_3}{D_{22}T_1}\right]^2 \\ 
+			&\frac{D_{22}}{D_{11}}\Biggl\{\left[\left(\frac{n_y\pi\chi}{2}\right)^2 - \frac{D_{12}T_2}{D_{22}T_1} + 2 \frac{D_{66}T_3}{D_{22}T_1}\right]^2 \\ 
 			&\qquad - \left(\frac{D_{12}T_2}{D_{22}T_1} - 2 \frac{D_{66}T_3}{D_{22}T_1}\right)^2
@@
 
-The translational springs ($k^v_\xi$) and rotational springs ($k^r_\xi$) along all edges can be set to zero or infinity (represented as $1 \times 10^{15} \ustif$ in the numerical calculations of this study) to obtain different classic boundary conditions.
+The translational springs ($k^v$) and rotational springs ($k^r$) along all edges can be set to zero or infinity (represented as $1 \times 10^{15} \ustif$ in the numerical calculations of this study) to obtain different classic boundary conditions.
 
@@
 		\cmidrule(lr){4-10}
-		BCs & $\alpha$ & Mode & 1 & 2 & 3 & 4 & 5 & 6 & 7 \\
+		BCs & $\chi$ & Mode & 1 & 2 & 3 & 4 & 5 & 6 & 7 \\
 		\midrule
@@
 Several novel techniques have proposed to solve the eigenvalue problem and mode shape computation.
-The challenge of determining the fully clamped frequencies using the Wittrick-Williams (W-W) algorithm is resolved by computing the frequencies under specific boundary conditions, whose closed-form expression can be easily derived using the SOV method.
-
-Classical boundary conditions, such as guided, simply supported, clamped, and free edges, can be realized by setting the translational springs ($k^v_\xi$) and rotational springs ($k^r_\xi$) along the plate edges to either zero or infinity, as appropriate.
+The challenge of determining the fully clamped frequencies using the Wittrick–Williams (W–W) algorithm is resolved by computing the frequencies under specific boundary conditions, such as simply supported, guided, or a combination of the two, whose closed-form expression can be easily derived using the SOV method.
+
+Classical boundary conditions, such as guided, simply supported, clamped, and free edges, can be realized by setting the translational springs ($k^v$) and rotational springs ($k^r$) along the plate edges to either zero or infinity, as appropriate.
 Numerical experiments validate the accuracy of this approach for these boundary conditions.  
@@
 
-Since the SOV solution $\phi(\xi) \psi(\eta)$ consists of only a single term for each mode order, unlike the infinite series expansions used in the traditional DSM, each eigenvalue solution can be explicitly expressed.
-% what do you mean 'concise'?
-This suggests the potential for obtaining more concise solutions for assembled plate structures compared to traditional DSM methods.
+The SOV solution $\phi(\xi) \psi(\eta)$ consists of only one single term for each mode order, unlike the sufficiently truncated Fourier series used in the DSM for each mode, each eigenvalue solution can be explicitly expressed.
+Therefore, dynamic stiffness matrices based on the SOV solution have the minimum matrix dimension compared to existing DSM methods. 
+This suggests the potential for constructing lower-dimensional dynamic stiffness matrices for assembled plate structures than those produced by existing DSM approaches.
 
@@
 \renewcommand{\theequation}{\thesection.\arabic{equation}}
-\section{Integral parameters}\label{appendA}
+\section{Integral parameters}\label{sec:appendA}
 The integral parameters $ I_1$, $I_2$, $I_3$, and $ I_4$ are defined as follows:

### 2025-07-10 Paper7.tex
minor tweaks

@@
 \usepackage{lineno}
-\usetikzlibrary{arrows.meta} % Load the arrows.meta library
+\usetikzlibrary{arrows.meta}
 \usetikzlibrary{shapes,positioning}
@@
 \AtBeginEnvironment{appendices}{\crefalias{section}{appendix}}
-
-% Derivatives should be upright d (JSV requires it)
-% I don't have the docs for the derivate package with me, so I'll just do this bad hack for now.
-% Could update all the ODEs to use the derivative package
-% Update: hack didn't work due to \d already defined somewhere - leaving this for now
-%\DeclareMathOperator{\d}{\textnormal{d}}
 
@@
 \newcommand{\DAF}{\textnormal{DAF}}
-% Hacky - is there a better upright i?
 %\newcommand{\ii}{\textnormal{i}}
@@
 
-% I made some comments about x/L being xi - it's not used much so you can ignore these.
-% There are some cases where I added text in [square brackets] and not necessarily in a latex comment
-% Check the bib file - two references had no journal - I added these as XXXX
-% Section 4 does too much - could you consider splitting this section up a bit? 
-% I did add some more subsubsections to try structure section 4 a bit better, but I'm not sure it's optimal yet.
 \begin{frontmatter}
@@
 %
-% It doesn't make sense to have 'mag' as a subscript - P.E. is just U, and it's already a scalar.
-% And it also doesn't make sense to have '0' as the subscript for maginitude for K.E., which is just K.
-% I guess you have some reason? But 'magnitude' of a scalar isn't really a thing worth highlighting.
-%
 where $\delta$ denotes variation, $U$ is the magnitude of the potential energy of the plate, and $T$ represents the magnitude of the kinetic energy of the plate.
 The potential energy of the plate can be expressed as \cite{xing2020extended}:
-%
-% What is superscript 'I' below? Why doesn't 'T' have one?
-% I know you're trying to separate the two ways of calculating the same thing, but it should be consistent.
 %
@@
 %
-% U sub/superscript notation hell?!
-%
 \begin{equation}\label{eq:poten_energy_mag}
@@
 and
-%
-% Shouldn't this be U on the LHS? How can T = omega**2 T (whether T_0 or not)?
 %
@@
 
-% worth a comment here on:
-% - is this a common assumption?
-% - Do you later validate or check this assumption?
-% - What happens if this assumption is not met?
-
 \subsection{Dynamic stiffness matrix corresponding to $\omega_x$}\label{sec:DSMx}
@@
 %
-% What is superscript II supposed to mean?
-% Why not just use U subscript x for this contribution of these supports?
 From \Cref{eq:poten_energy_edgex}, the magnitude of potential energy along the plate edges in the $x$-direction, expressed in dimensionless coordinates, is obtained as:
@@
 %
-% Isn't this just change of variables? dimensional to non-dimensional space? Maybe say this.
-% Not sure why this now deserves a 'mag' subscript.
 The magnitude of total potential energy of the plate in the $x$-direction can be obtained from \Cref{eq:poten_energy_mag,eq:poten_energy_edgex2} as:
@@
 %
-% The notation needs to be cleaned up a bit, or more clearly defined.
 \begin{equation}\label{eq:kine_energyx}
@@
 		&\qquad + \bigg( \frac{D_{22}}{b^4} I_4 - \omega_x^2 \rho h I_1 \bigg) \phi \bigg] \delta \phi \, \id \xi \\
-		&\qquad + \frac{2k^v_{\xi=-1}}{a} I_1 \big(\phi \delta \phi\big)_{\xi=-1} 
-		+ \frac{2k^v_{\xi=1}}{a} I_1 \big(\phi \delta \phi\big)_{\xi=1} \\
+		&\qquad + \frac{2k^v_{\xi=-1}}{a} I_1 \big(\phi\, \delta \phi\big)_{\xi=-1} 
+		+ \frac{2k^v_{\xi=1}}{a} I_1 \big(\phi\, \delta \phi\big)_{\xi=1} \\
 		&\qquad + \bigg[ \bigg( \frac{4D_{66}}{a^2b^2} I_3 - \frac{D_{12}}{a^2b^2} I_2 \bigg) \frac{\id \phi}{\id \xi} 
@@
 Thus, the governing differential equation in the $ x $-direction can be obtained from the integration part in \Cref{eq:Rayleighx2}:
-%
-% Very nice!
 %
@@
 %
-Substituting \Cref{eq:phi_solution1} into \Cref{eq:boundaryx}, and denoting $k^{v*}_{\xi} = \frac{2a^3 k^v_{\xi}}{D_{11}} $, 
-$ k^{r*}_{\eta} = \frac{2a k^r_{\xi}}{D_{11}} $, $ S_{\alpha_1} = \sin \alpha_1 $, $ C_{\alpha_1} =\cos \alpha_1 $, $ Sh_{\beta_1} = \sinh \beta_1$, and $ Ch_{\beta_1} = \cosh \beta_1 $, we have:
+Substituting \Cref{eq:phi_solution1} into \Cref{eq:boundaryx}, and denoting 
+$k^{v*}_{\xi} \equiv \frac{2a^3 k^v_{\xi}}{D_{11}} $, 
+$ k^{r*}_{\eta} \equiv \frac{2a k^r_{\xi}}{D_{11}} $, 
+$ S_{\alpha_1} \equiv \sin \alpha_1 $, 
+$ C_{\alpha_1} \equiv \cos \alpha_1 $, 
+$ Sh_{\beta_1} \equiv \sinh \beta_1$, 
+and $ Ch_{\beta_1} \equiv \cosh \beta_1 $, we have:
 %
@@
 %
-% In below - isn't alpha_1/a just b?
 \begin{equation}\label{eq:UBx}
@@
 \subsection{Dynamic stiffness matrix corresponding to $\omega_y$}\label{sec:DSMy}
-%
-% This section follows the previous section exactly. I'm wondering the value of giving all the same details
-% again? It canbe shortened to only provide what is different, e.g. J, alpha_2, beta_2 etc? 
-% It could start off with something like "Following the same steps as for the x-direction, we have..."
-% All my changes above apply to this section.
-% it's far too much copy & paste right now, even down to the unnecessary definitions of C and S etc
-% 
 In this section, the mode shape $\phi(\xi)$ derived in $\Cref{sec:DSMx}$ is utilized to obtain the dynamic stiffness matrix in the $y$-direction.  
@@
 Similarly, from the shear force and bending moment equilibrium, and by denoting 
-$k^{v*}_{\eta} = \frac{2b^3 k^v_{\eta}}{D_{22}} $, 
-$ k^{r*}_{\eta} = \frac{2b k^r_{\eta}}{D_{22}} $, 
-$S_{\alpha_2}=\sin\alpha_2  $, 
-$ C_{\alpha_2}=\cos\alpha_2  $, 
-$ Sh_{\beta_2}=\sinh\beta_2$, and 
-$Ch_{\beta_2}= \cosh\beta_2$, 
-We can obtain:
+$k^{v*}_{\eta} \equiv \frac{2b^3 k^v_{\eta}}{D_{22}} $, 
+$ k^{r*}_{\eta} \equiv \frac{2b k^r_{\eta}}{D_{22}} $, 
+$S_{\alpha_2}\equiv\sin\alpha_2  $, 
+$ C_{\alpha_2}\equiv\cos\alpha_2  $, 
+$ Sh_{\beta_2}\equiv\sinh\beta_2$, and 
+$Ch_{\beta_2}\equiv \cosh\beta_2$, 
+we obtain:
 %
@@
 	b \Omega^4_{x,n_x} =
-		%\large % slightly smaller than \Large
 		\begin{aligned}

### 2025-07-25 Paper7.tex
Editor

@@
-\documentclass[preprint,12pt]{elsarticle}
+\documentclass[preprint,12pt,number]{elsarticle}
+\usepackage[percent]{overpic} % in your preamble
+\usepackage{enumitem}
+\usepackage{setspace} % for line spacing
+\biboptions{numbers,sort&compress}
 \usepackage{amsmath}
@@
 \begin{document}
-
+\onehalfspacing  % enable 1.5× spacing
 \begin{frontmatter}
-\title{Dynamic stiffness matrix based on the extended separation-of-variables solution for the free vibration of orthotropic rectangular thin plates}
+\title{A separation-of-variable dynamic stiffness matrix method for the free vibration of orthotropic rectangular thin plates}
 \author[1]{Shiyi Mei}\ead{shiyi.mei1@monash.edu}
@@
 \begin{abstract}
-The dynamic stiffness matrix (DSM) based on the extended separation-of-variables (SOV) solution is developed for the free vibration analysis of an orthotropic rectangular thin plate with general homogeneous boundary conditions.
-The method combines the advantages of the DSM method and the SOV method.
-The SOV solution satisfies the governing differential equation derived from Rayleigh’s principle and is used to formulate dynamic stiffness matrices.
-Owing to the characteristics of the SOV solution, the fully clamped boundary condition problem associated with the Wittrick–Williams algorithm is resolved. 
-The enhanced algorithm is further proposed to solve dynamic stiffness matrices, rather than solving eigenvalue equations.
-A numerical technique for mode shape computation is also introduced.
-The accuracy of the proposed method is validated through numerical experiments.
-
+	A separation-of-variable dynamic stiffness matrix (SOV-DSM) method is proposed for the free vibration analysis of an orthotropic rectangular thin plate with general homogeneous boundary conditions.  
+	Firstly, the exact SOV solution satisfying Rayleigh’s principle is extended to handle arbitrary boundary conditions and then applied to develop closed-form dynamic stiffness formulations.
+	Then, an enhanced Wittrick–Williams (W-W) algorithm is used to solve the eigenvalue problem rather than solving the highly nonlinear eigenvalue equations.
+	The $J_0$ count problem involved in applying the W-W algorithm is addressed by providing an explicit and closed-form expression for the $J_0$ term based on the characteristics of the SOV solution.
+	Furthermore, a numerical technique is provided to calculate the mode shape of the plate with any arbitrary boundary conditions.
+	The accuracy of the proposed method is validated through numerical experiments by comparison with other analytical solutions.
 \end{abstract}
@@
 The earliest exact solutions for this problem are the Navier \citep{navier1823extrait} and Levy \citep{levy1899equilibre} solutions, which require at least one pair of opposite edges to be simply supported or guided.
-To solve problems with other boundary conditions, approximate solutions such as the Rayleigh–Ritz method \cite{leissa1973free} and the Galerkin method \cite{laura1967study} have been widely applied. 
-For these approximation methods, beam functions, polynomials, trigonometric functions, and their combinations \cite{li2004vibration} are commonly used as the assumed approximate functions.
+To solve problems with other boundary conditions, approximate solutions such as the Rayleigh–Ritz method \cite{leissa1973free,lam1989vibration,zhao2025free,jain2024bending,bagheri2024analysis}, the Galerkin method \cite{laura1967study,krysl1995analysis,ma2024analysis,ma2024error,pereira2025modified} and finite element method (FEM) \cite{zhao2024fast,yang2022analysis,paccola2016continuous,carrera2024finite,yang2025semi} have been widely applied.
+For most approximation methods, beam functions \cite{ding1996natural,cheung1999free,cheung1999free2,zhou2002vibrations}, polynomials \cite{bhat1985natural,xie2025efficient,celep2025elastic,madinier2025spatial,sun2023spectral}, trigonometric functions \cite{filipich2000arbitrary,kumar2004buckling,yessenbayeva2019calculation,he2021study,su2022vibration}, and their combinations \cite{li2004vibration,cheung2000vibrations,zhou2001vibrations,monterrubio2015proof,onyeka2022application} are commonly used as the assumed approximate functions.
 The accuracy of these solutions depends on how well the assumed approximate functions represent the displacement of the plate.
 
-Besides the approximation methods, several analytical methods have been developed over past decades, including the Kantorovich-Krylov method \cite{kantorovich1958approximate,kerr1968extension}, the symplectic eigenfunction expansion method \cite{zhong1995new,xing2009new2}, the separation-of-variable (SOV) method \cite{xing2009new}, the dynamic stiffness matrix (DSM) method \cite{banerjee1997dynamic}, and series expansion-based methods \cite{xing2022review}.
-The series expansion-based methods include the superposition method \cite{timoshenko1940theory,gorman2005free}, Fourier series method \cite{khov2009accurate,li2009exact}, the finite integral transform method \cite{li2009finite,zhong2013free}, and other series methods.
+Besides the approximation methods, several analytical methods have been developed over past decades, including the Kantorovich-Krylov method \cite{kantorovich1958approximate,kerr1968extension,kerr1968application,rostami2016free,huang2015interlaminar,shufrin2016semi,singh2020three}, the symplectic method \cite{zhong1995new,xing2009new2,lim2009new,shi2024symplectic,xu2024hamiltonian,shi2025free}, the separation-of-variable (SOV) method \cite{xing2009new,xing2009new2,xing2018overall,xing2020extended,xing2020improved,xing2022review,wang2021closed,wang2021extended,wang2019highly,wang2020highly}, the dynamic stiffness matrix (DSM) method \cite{banerjee1997dynamic,papkov2019dynamic,liu2024dynamic,boscolo2011dynamic,fazzolari2013exact,ghorbel2015dynamic,williams1995wave,banerjee2015dynamic,liu2016free,liu2024wavenumber,zhou2024wavenumber,liu2015exact}, and series expansion-based methods \cite{timoshenko1940theory,gorman2005free,mochida2010transient,wang2016symplectic,hu2021new,wang2025new,khov2009accurate,li2009exact,grigorenko2003discrete,wang2016improved,leng2022new,li2009finite,zhong2013free,tian2015integral,zhang2017bending,chen2023analytical,li2024novel,zhu2024sound,shao2025analytic}.
+The series expansion-based methods include the superposition method \cite{timoshenko1940theory,gorman2005free,mochida2010transient,wang2016symplectic,hu2021new,wang2025new}, Fourier series method \cite{khov2009accurate,li2009exact,grigorenko2003discrete,wang2016improved,leng2022new}, the finite integral transform method \cite{li2009finite,zhong2013free,tian2015integral,zhang2017bending,chen2023analytical}, and other series methods \cite{li2024novel,zhu2024sound,shao2025analytic}.
 These methods represent the plate displacement in terms of an infinite series and mostly are capable of handling any general boundary conditions. 
@@
 
-Despite being a powerful method for the dynamic analysis of plate assemblies, the finite element method (FEM) requires a sufficient number of elements and is computationally expensive to accurately capture higher-order modes.
+Despite being a powerful method for the dynamic analysis of plate assemblies, the FEM requires a sufficient number of elements and is computationally expensive to accurately capture higher-order modes.
 Thus, the DSM method was developed as an accurate and efficient analytical approach to alternatively solve complex plate structures \cite{boscolo2011dynamic,fazzolari2013exact}. 
-The DSM can be considered as an analytical FEM since the mode functions of the plate are expressed by analytical solutions, where Levy-type solution \cite{ghorbel2015dynamic} or components of infinite Fourier series \cite{banerjee2015dynamic,liu2016free} are applied.
+The DSM can be considered as an analytical FEM since the mode functions of the plate are expressed by analytical solutions, where Levy-type solution \cite{ghorbel2015dynamic} or components of Fourier series \cite{williams1995wave,banerjee2015dynamic,liu2016free,liu2024wavenumber,zhou2024wavenumber} are applied.
 To avoid solving the cumbersome transcendental frequency equation directly, the Wittrick-Williams (W-W) algorithm \cite{wittrick1971general} is applied to the eigenvalue problem.
@@
 Strategies such as using a sufficiently fine mesh or including a sufficient number of terms in series expansions \cite{banerjee2015dynamic} can ensure that all fully clamped frequencies are accounted for, thereby maintaining the accuracy of the algorithm.
-However, these approaches are computationally expensive and complex, posing a significant obstacle to the wider adoption and application of the DSM method based on the W-W algorithm \cite{han2018improved}.
-To resolve the fully clamped plate problem, \citet{liu2015exact} suggested that the frequencies can be indirectly obtained from the simply supported plate problem, where the Navier solution serves as the analytical solution.
-This provides a significant enhancement to the W-W algorithm, increasing the efficiency of applying DSM methods. 
-However, the solutions are not explicit and closed-form, but are expressed in an infinite series form, where a sufficient number of truncation terms is required to ensure accuracy.
-
-Inspired by the Navier and Levy solutions, \citet{xing2009new} proposed the SOV method, which provides concise and explicit eigensolutions.
+However, these approaches are computationally expensive and complex, posing a significant obstacle to the wider adoption and application of the DSM method based on the W-W algorithm \cite{han2018improved,liu2022closed}.
+To resolve the fully clamped plate problem, Liu and Banerjee \cite{liu2015exact} suggested that the frequencies can be indirectly obtained from the simply supported plate problem, where the Navier solution serves as the analytical solution.
+This idea provides a significant enhancement to the W-W algorithm, increasing the efficiency of applying DSM methods \cite{liu2024wavenumber,zhou2024wavenumber}. 
+However, most solutions applied in these DSM methods are not explicit and closed-form, but are expressed in an infinite series form, where a sufficient number of truncation terms might be required to ensure accuracy.
+
+Inspired by the Navier and Levy solutions, Xing and Liu \cite{xing2009new} proposed the SOV method, which provides concise and explicit eigensolutions.
 The mode shape function has a separable form, $\phi(x) \psi(y)$, requiring only one $\phi(x)$ and one $\psi(y)$ for each mode order, allowing each eigenvalue equation to be explicitly expressed.
@@
 
-In this study, the SOV method is further extended to analyze the vibrations of plates with elastically restrained edges.
-This extended SOV solution is then employed to construct dynamic stiffness matrices, which accommodate all general homogeneous boundary conditions.
-By taking advantage of both the SOV and DSM methods, an enhanced W-W algorithm is developed to solve the eigenvalue problem without directly solving the eigenvalue equations.
-This enhanced approach resolves the challenge of determining fully clamped frequencies, a well-known limitation in the application of the  W-W algorithm.
+In this study, a separation-of-variable dynamic stiffness matrix (SOV-DSM) method is proposed to avoid solving transcendental eigenvalue equations in SOV methods.
+It also fills the gap caused by the limitation of closed-form dynamic stiffness formulations available for existing plate structures.
+Firstly, the SOV method is further extended to analyze the vibrations of plates with elastically restrained edges based on Rayleigh’s principle. 
+This extended SOV solution is then employed to construct dynamic stiffness matrices that accommodate general homogeneous boundary conditions.
+By taking advantage of both the SOV and DSM methods, an enhanced W–W algorithm is developed to solve the eigenvalue problem without directly solving the eigenvalue equations.
+This enhanced approach resolves the challenge of determining fully clamped frequencies, also called the $J_0$ count problem, a well-known limitation in the application of the W-W algorithm. 
+Two types of explicit and closed-form expressions for the $J_0$ term, based on specific supports such as simply supported, guided, or their combinations, are provided to improve the computational efficiency of the eigenvalue problem.
 In addition, a novel numerical technique is proposed to compute the mode shape coefficients.
 
+The paper is structured as follows: \Cref{sec:SOV-DSM} presents the SOV-DSM formulations derived from the extended SOV method, which accommodates elastically restrained boundary conditions.
+In \Cref{sec:WWA}, an enhanced W-W algorithm that resolves the $J_0$ count problem is provided to solve the dynamic stiffness matrices. 
+The explicit and closed-form expression for the $J_0$ term is provided. 
+In addition, a novel numerical technique is proposed to compute the mode shape of the plate with arbitrary boundary conditions.
+\Cref{sec:NR} validates the proposed method through numerical experiments by comparison under several boundary conditions.
+Finally, the conclusions of this paper are presented in \Cref{sec:coclusion}.
+
 \FloatBarrier
-\section{Mathematical model}\label{sec:Mathematical model}
+\section{Separation-of-variable dynamic stiffness matrix formulation}\label{sec:SOV-DSM}
+In this section, the SOV-DSM formulations for the free vibration analysis of orthotropic rectangular thin plates are developed.  
+\Cref{sec:Mathematical model} presents the mathematical model of the extended separation-of-variable method.  
+Then, the SOV-DSM formulations in the $x$- and $y$-directions will be proposed separately in \Cref{sec:DSMx} and \Cref{sec:DSMy}, according to the boundary conditions of the plate.
+
+\subsection{Mathematical model for separation-of-variable method}\label{sec:Mathematical model}
 \begin{figure}[!htbp]
@@
 
-Following the same steps as for the x-direction, the magnitude of potential energy of the plate in the $y$-direction can be obtained as:
-%
-\begin{equation}\label{eq:poten_energy_toly2}
-	\begin{split}
-		U
-		&= \frac{ab}{2} \int_{-1}^{1} \left[ \frac{D_{11}}{a^4} J_4 \psi^2 
-		+ \frac{2D_{12}}{a^2b^2} J_2 \frac{\id^2\psi }{\id \eta^2} \psi 
-		+ \frac{D_{22}}{b^4} J_1 \left(\frac{\id^2\psi }{\id \eta^2} \right)^2 \right. \\
-		&\qquad \left. + \frac{4D_{66}}{a^2b^2} J_3 \left(\frac{\id \psi }{\id \eta} \right)^2 \right] \, \id\eta  + abJ_1 \left[ \frac{k^r_{\eta=1}}{b^3} \left( \frac{\id \psi}{\id \eta} \right)^2
-		+ \frac{k^v_{\eta=1}}{b}  \left(\psi\right)^2 \right]_{\eta=1} \\
-		&\qquad + abJ_1 \left[ \frac{k^r_{\eta=-1}}{b^3} \left( \frac{\id \psi}{\id \eta} \right)^2
-		+ \frac{k^v_{\eta=-1}}{b} \left(\psi\right)^2 \right]_{\eta=-1},
-	\end{split}
-\end{equation}
-%
-where the integral parameters $J_1$, $J_2$, $J_3$, and $J_4$ are defined and expressed in \Cref{sec:appendA}.
-
-The coefficient $T_0$ of the kinetic energy from \Cref{eq:kine_energy_mag} for the plate in the $y$-direction can be expressed as:
-%
-\begin{equation}\label{eq:kine_energyy}
-	\begin{split}
-		T_0 &= \frac{ab}{2} \rho h J_1 \int_{-1}^{1} \psi^2 \, \id\eta.
-	\end{split}
-\end{equation}
-%
-Take the Rayleigh principle in the form:
+Following the same steps as for the \(x\)-direction, the Rayleigh principle is expressed in the form:  
 %
@@
 	\begin{split}
-		\delta U &= \omega_y^2 \, \delta T_0.
-	\end{split}
-\end{equation}
-%
-By substituting \Cref{eq:poten_energy_toly2,eq:kine_energyy} into \Cref{eq:Rayleighy}, and relieving $ \delta \psi $ and $\delta\frac{\id \psi}{\id \eta}$ in \Cref{eq:Rayleighy} by calculus of variation, yields:
-%
-\begin{equation}\label{eq:Rayleighy2}
-	\begin{split}
-		0 &= \int_{-1}^{1} \left[ \frac{D_{22}}{b^4} J_1 \frac{d^4 \psi}{\id \eta^4} 
-		+ \left( \frac{2D_{12}}{a^2b^2} J_2 - \frac{4D_{66}}{a^2b^2} J_3 \right) \frac{\id^2 \psi}{\id \eta^2} \right. \\
-		&\qquad \left. + \left( \frac{D_{11}}{a^4} J_4 - \omega_y^2 \rho h J_1 \right) \psi \right] \delta \psi \, \id\eta \\
-		&\qquad + \frac{2k^v_{\eta=-1}}{b} J_1 (\psi \delta \psi)_{\eta=-1} 
-		+ \frac{2k^v_{\eta=1}}{b} J_1 (\psi \delta \psi)_{\eta=1} \\
-		&\qquad + \left[ \left( \frac{4D_{66}}{a^2b^2} J_3 - \frac{D_{12}}{a^2b^2} J_2 \right) \frac{\id \psi}{\id \eta} 
-		- \frac{D_{22}}{b^4} J_1 \frac{\id^3 \psi}{\id \eta^3} \right] \delta \psi \Big|^{\eta=1}_{\eta=-1} \\
-		&\qquad + \left( \frac{D_{12}}{a^2b^2} J_2 \psi + \frac{D_{22}}{b^4} J_1 \frac{\id^2 \psi}{\id \eta^2} \right) 
-		\delta\frac{\id  \psi}{\id \eta} \Big|^{\eta=1}_{\eta=-1} \\
-		&\qquad + \frac{2k^r_{\eta=-1}}{b^3} J_1 \left( \frac{\id \psi}{\id \eta} \delta\frac{\id \psi}{\id \eta} \right)_{\eta=-1} 
-		+ \frac{2k^r_{\eta=1}}{b^3} J_1 \left( \frac{\id \psi}{\id \eta} \delta\frac{\id \psi}{\id \eta} \right)_{\eta=1}.
-	\end{split}
-\end{equation}
-%
-Thus, the governing differential equation in the $y$-direction can be obtained from the integration part in \Cref{eq:Rayleighy2}:
+		\delta U &= \omega_y^2 \, \delta T_0,
+	\end{split}
+\end{equation}
+%
+from which the governing differntial equation in the $y$-direction for $\psi$ is obatained as:
 %
@@
 \begin{align}
-		\alpha_2 &= \frac{1}{\chi} \sqrt{ \sqrt{ \left( \frac{D_{12}J_2}{D_{22}J_1} - 2\frac{D_{66}J_3}{D_{22}J_1} \right)^2 - \frac{D_{11}J_4}{D_{22}J_1} + \frac{a^4 D_{11}}{D_{22}} \Omega_y^4 } + \frac{D_{12}J_2}{D_{22}J_1} - 2 \frac{D_{66}J_3}{D_{22}J_1}}, \\
-		\beta_2 &= \frac{1}{\chi} \sqrt{ \sqrt{ \left( \frac{D_{12}J_2}{D_{22}J_1} - 2 \frac{D_{66}J_3}{D_{22}J_1} \right)^2 - \frac{D_{11}J_4}{D_{22}J_1} + \frac{a^4 D_{11}}{D_{22}} \Omega_y^4 } - \frac{D_{12}J_2}{D_{22}J_1} + 2 \frac{D_{66}J_3}{D_{22}J_1}}.
+	\alpha_2 &= \frac{1}{\chi} \sqrt{ \sqrt{ \left( \frac{D_{12}J_2}{D_{22}J_1} - 2\frac{D_{66}J_3}{D_{22}J_1} \right)^2 - \frac{D_{11}J_4}{D_{22}J_1} + \frac{a^4 D_{11}}{D_{22}} \Omega_y^4 } + \frac{D_{12}J_2}{D_{22}J_1} - 2 \frac{D_{66}J_3}{D_{22}J_1}}, \label{eq:betay1}\\
+	\beta_2 &= \frac{1}{\chi} \sqrt{ \sqrt{ \left( \frac{D_{12}J_2}{D_{22}J_1} - 2 \frac{D_{66}J_3}{D_{22}J_1} \right)^2 - \frac{D_{11}J_4}{D_{22}J_1} + \frac{a^4 D_{11}}{D_{22}} \Omega_y^4 } - \frac{D_{12}J_2}{D_{22}J_1} + 2 \frac{D_{66}J_3}{D_{22}J_1}}.\label{eq:betay2}
 \end{align}
 \end{subequations}
-%
-The boundary conditions along the edges in the $y$-direction can be obtained from the remaining $\delta \psi$ and $\delta \frac{\id \psi}{\id \eta}$ parts in \Cref{eq:Rayleighy2}. 
-The shear force equilibrium can be obtained from the $\delta \psi$ part:
-%
-\begin{equation}\label{eq:inertial_forcey}
-	\begin{split}
-		& \left[ \left( \frac{4D_{66}}{a^2b^2} J_3 - \frac{D_{12}}{a^2b^2} J_2 \right) \frac{\id \psi}{\id \eta} 
-		- \frac{D_{22}}{b^4} J_1 \frac{\id^3 \psi}{\id \eta^3} \right] \Big|^{\eta=1}_{\eta=-1} \\
-		&\qquad + \frac{2k^v_{\eta=-1}}{b} J_1 (\psi )_{\eta=-1} + \frac{2k^v_{\eta=1}}{b} J_1 (\psi )_{\eta=1} = 0,
-	\end{split}
-\end{equation}
-%
-and from the $\delta \frac{\id \psi}{\id \eta}$ part, the bending moment equilibrium:
-%
-\begin{equation}\label{eq:inertial_forcey2}	
- \begin{split}
- 	\left( \frac{D_{12}}{a^2b^2} J_2 \psi + \frac{D_{22}}{b^4} J_1 \frac{\id^2 \psi}{\id \eta^2} \right) 
- 	\Big|^{\eta=1}_{\eta=-1} 
- 	&+ \frac{2k^r_{\eta=-1}}{b^3} J_1 \left( \frac{\id \psi}{\id \eta} \right)_{\eta=-1} \\
- 	&\qquad+ \frac{2k^r_{\eta=1}}{b^3} J_1 \left( \frac{\id \psi}{\id \eta} \right)_{\eta=1}=0.
- \end{split}
-\end{equation}
 %
@@
 where the dynamic stiffness matrix, denoted as $\mathbf{K}_y = \mathbf{R}_y \mathbf{Q}_y^{-1}$, can be obtained from \Cref{eq:DSM_eqy}.
+\section*{Remarks}
+\addcontentsline{toc}{subsection}{Remarks}
+\begin{enumerate}[label=(\roman*)]
+	\item For the SOV methods, six independent unknown eigenvalues ($\alpha_1$, $\beta_1$, $\Omega_x$, $\alpha_2$, $\beta_2$, $\Omega_y$) need to be determined for each mode shape $\phi(\xi)\psi(\eta)$.
+	To solve these six variables, four eigenvalue equations are provided in \Cref{eq:alphax1,eq:alphax2,eq:betay1,eq:betay2}, while the remaining two transcendental eigenvalue equations are obtained from the determinants of $\mathbf{R}_x$ in \Cref{eq:ABx1} for the $x$-direction and $\mathbf{R}_y$ in \Cref{eq:ABy1} for the $y$-direction, respectively.
+	For classical boundary conditions such as simply supported (S), clamped (C), guided (G), and free (F) edges, these two transcendental equations have been simplified and summarized in previous works \citep{xing2020extended,xing2020improved,xing2022review}.
+	However, the process of selecting appropriate transcendental equations for the existing 55 different boundary-condition combinations remains tedious, and further simplification becomes challenging when non-classical boundary conditions are applied.
+	By simply setting the translational springs ($k^v$) and rotational springs ($k^r$) along the $x$- or $y$-direction edges to either zero or infinity, the classical boundary conditions can be recovered.
+	In this case, the transcendental equations obtained from the determinants of $\mathbf{R}_x$ and $\mathbf{R}_y$ are identical to those summarized in the existing SOV methods.
+
+	\item In the existing SOV methods, numerical techniques such as the Newton–Raphson
+	method, homotopy method and optimization methods method have been applied to solve these six unknown variables.  
+	Although all six eigenvalue equations can be solved simultaneously, the computation is very expensive and convergence issues may arise \citep{wang2021extended,wang2021closed}.  
+	Therefore, an iterative procedure \cite{xing2018overall,wang2021extended,wang2021closed,wang2019highly,wang2020highly} is preferred, in which three eigenvalue equations corresponding to ($\alpha_1$, $\beta_1$, $\Omega_x$) and the remaining three corresponding to ($\alpha_2$, $\beta_2$, $\Omega_y$) are solved separately.
+	In fact, by substituting \Cref{eq:alphax1,eq:alphax2} into the eigenvalue equation corresponding to $\mathbf{R}_x$ and \Cref{eq:betay1,eq:betay2} into the eigenvalue equation corresponding to $\mathbf{R}_y$, two highly nonlinear eigenvalue equations, involving only one variable $\Omega_x$ and $\Omega_y$, respectively, can be obtained.
+	However, these equations are difficult to solve using conventional numerical methods.
+	To address this issue, the dynamic stiffness matrices $\mathbf{K}_x(\Omega_x)$ and $\mathbf{K}_y(\Omega_y)$ are developed, whose determinants are identical to the eigenvalue equations corresponding to $\mathbf{R}_x(\Omega_x)$ and $\mathbf{R}_y(\Omega_y)$, respectively.
+	In this case, the dynamic stiffness matrices $\mathbf{K}_x(\Omega_x)$ and $\mathbf{K}_y(\Omega_y)$ can be solved efficiently using the W–W algorithm, which enhances computational robustness and ensures that no frequencies are missed.
+\end{enumerate}
 
 \section{Frequency and mode shape computation}\label{sec:WWA}
+The dynamic stiffness matrices $\mathbf{K}_x(\Omega_x)$ and $\mathbf{K}_y(\Omega_y)$ serve as the eigenvalue equations for $\Omega_x$ and $\Omega_y$, respectively, and a powerful W–W algorithm based on the SOV-DSM method is introduced in \Cref{sec:WWA2} to compute these eigenvalues.
+\Cref{sec:Mode shape} proposes a novel technique to calculate the mode shapes.  
+Finally, the iterative procedure for applying the proposed method is presented in \Cref{sec:Application procedure}.
+
 \subsection{Wittrick–Williams algorithm and enhancement}\label{sec:WWA2}
@@
 
-By taking fully simply supported boundary conditions as the example, the eigenvalue equation corresponding to the natural frequency parameter $ \Omega_x $ can be obtained from the determinant of the coefficient matrix $ \mathbf{R}_x $ in \Cref{eq:ABx}, as given by:
+By taking fully S-S boundary conditions as the basis, the eigenvalue equation corresponding to the natural frequency parameter $ \Omega_x $ can be obtained from the determinant of the coefficient matrix $ \mathbf{R}_x $ in \Cref{eq:ABx}, as given by:
 %
@@
 %
-With the help of \Cref{eq:alphax1,eq:SSx}, the closed-form solution of the $n_x$-th simply supported frequency $\Omega_{x,n_x}$ for the given $n_y$-order $\psi_{n_y}(\eta)$ can be expressed as:
+With the help of \Cref{eq:alphax1,eq:SSx}, the closed-form solution of the $n_x$-th S-S boundary conditions frequency $\Omega_{x,n_x}$ for the given $n_y$-order $\psi_{n_y}(\eta)$ can be expressed as:
 %
@@
 For $\Omega_{x,n_x} \leq \Omega_x^* < \Omega_{x,n_{x+1}}$, $J(\bar{p}_1, \Omega_x^*) = n_x$.
-Similarly, the closed-form solution of the $n_y$-th simply supported frequency $\Omega_{y,n_y}$ for the given $n_x$-order $\phi_{n_x}(\xi)$ can be expressed as:
+
+Similarly, the closed-form solution of the $n_y$-th S-S boundary conditions frequency $\Omega_{y,n_y}$ for the given $n_x$-order $\phi_{n_x}(\xi)$ can be expressed as:
 %
@@
 For $\Omega_{y,n_y} \leq \Omega_y^* < \Omega_{y,n_{y+1}}$, $J(\bar{p}_1, \Omega_y^*) = n_y$.
+
+It should be noted that the G-G boundary conditions have the same eigenvalue equations with the S-S boundary conditions, thus the G-G boundary conditions frequencies can also be directly obtained from \Cref{eq:J_simpx,eq:J_simpy}.
+The closed-form expression for the S-G boundary conditions can be found in \Cref{sec:appendB}.
+
 According to the relationships 
@@
 the values of $J(\bar{p}_1, \omega_x^*)$ and $J(\bar{p}_1, \omega_y^*)$ can be derived from $J(\bar{p}_1, \Omega_x^*)$ and $J(\bar{p}_1, \Omega_y^*)$, respectively. 
-Therefore, this refined W-W algorithm can be applied to estimate the lower and upper bounds of the frequency range, denoted as $\omega_l$ and $\omega_u$, yielding an approximation for the frequency $\omega_a \in (\omega_l, \omega_u)$ to arbitrary precision.
-\subsection{Mode shape computation}
-The mode shape coefficients $ A_1 $ to $ A_4 $ and $ B_1 $ to $ B_4$ in the eigenvectors $\mathbf{A}$ and $\mathbf{B}$ for all classic boundary conditions are provided in \cite{xing2020extended}. 
+Therefore, this enhanced W-W algorithm can be applied to estimate the lower and upper bounds of the frequency range, denoted as $\omega_l$ and $\omega_u$, yielding an approximation for the frequency $\omega_a \in (\omega_l, \omega_u)$ to arbitrary precision.
+\subsection{Mode shape computation}\label{sec:Mode shape}
+The mode shape coefficients $ A_1 $ to $ A_4 $ and $ B_1 $ to $ B_4$ in the eigenvectors $\mathbf{A}$ and $\mathbf{B}$ for all classic boundary conditions are provided in \cite{xing2020extended,xing2020improved}.
 Alternatively, these coefficients can also be obtained through a simple numerical method, which this work presents as an approach.
@@
 
+\section*{Remarks}
+\addcontentsline{toc}{subsection}{Remarks}
+\begin{enumerate}[label=(\roman*)]
+	\item The traditional W–W algorithm requires a prior expression of $J_0(p_1)$ under the C–C boundary conditions ($p_1$).  
+	However, the transcendental eigenvalue equation for C–C boundaries is complex, making it difficult to obtain a closed-form solution for the $J_0(p_1)$ term.  
+	To overcome this difficulty, $J_0(p_1)$ can be indirectly determined if the $J(\bar{p}_1)$ term is known,  
+	where the reference boundary condition $\bar{p}_1$ may correspond to any other, more tractable boundary condition.  
+	Consequently, to apply the W–W algorithm, at least one prior solution for a specific boundary condition is required.  	
+	Thanks to the SOV solution, the S–S, G–G, and S–G boundary conditions yield the simplest eigenvalue equations, involving only a single sine or cosine function.  
+	Therefore, an explicit closed-form expression of $J(\bar{p}_1)$ can be readily obtained when $\bar{p}_1$ corresponds to one of these boundary conditions.  	
+	In numerical calculations, to approximate infinite stiffness, the translational springs ($k^v$) and rotational springs ($k^r$) are assigned sufficiently large values.
+
+	\item In the existing SOV methods, the mode shape coefficients $A_1$ to $A_4$ and $B_1$ to $B_4$ are obtained from different types of transcendental eigenvalue equations for each boundary condition, resulting in distinct expressions for different boundary conditions.
+	However, the dynamic stiffness matrix $\mathbf{K}$ is applicable to all boundary conditions.  
+	Therefore, a general approach is developed to compute the mode shape coefficients for arbitrary boundary conditions,  
+	and a novel yet simple numerical technique has been introduced to implement this procedure efficiently.
+
+\end{enumerate}
+
 \FloatBarrier
-\section{Numerical Results}  
-This section presents the numerical validation of the proposed method for classic boundary conditions and rotationally restrained boundary conditions.  
+\section{Numerical Results}\label{sec:NR}  
+This section aims to validate the SOV-DSM method by comparing its results with some existing methods.  
+In \Cref{sec:Classical boundary conditions}, the results are compared with those obtained from the extended SOV method under classical boundary conditions.  
+In \Cref{sec:Rotational spring-supported}, the results are further compared with the finite integral transform method and numerical methods for rotationally restrained boundary conditions.
+
 For all numerical calculations, the initial integral parameters are assumed as $I^{(0)}_1=1$, $I^{(0)}_2=1$, $I^{(0)}_3=1$, and $I^{(0)}_4=10$ in the $y$-direction, serving as the starting point of \textbf{Step 1} for any mode in all boundary conditions.
+$\bar{p}_1$ is selected as the S–S boundary condition.
 In this section, the interval between the upper and lower bounds of the non-dimensional frequency parameter, $2a\Delta\Omega$, is set to 0.005, although any desired level of precision can be used.
@@
 
-\subsection{Classical boundary conditions}
+\subsection{Classical boundary conditions}\label{sec:Classical boundary conditions}
 In this subsection, the proposed method is validated by comparison with the extended SOV method \cite{xing2020extended}.  
@@
 The results for SSSS, SCSF, GCGC, CCCC, SSCC, SCCC, GGCC, CCFF, CFCF, CFFF, and FFFF boundary conditions are presented in \Cref{tab:sov1,tab:sov2,tab:sov3}. 
-Note that, as is convention, S is a simple support (rotation, no translation), C is a clamped supported (no rotation or translation), G is a guided support (translation, no rotation), and F is a free edge.
 These results demonstrate high accuracy compared to the extended SOV method, with difference remaining smaller than the frequency parameter interval $2a\Delta\Omega=0.005$. 
@@
 
-\begin{figure}
+\begin{figure}[p] % or [H]
 	\centering
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{figs/FFFF1.png}
-		\caption[]%
-		{{\small }}    
-		\label{fig:FFF1}
+	\resizebox{0.85\textwidth}{!}{%
+		\begin{minipage}{\textwidth}
+		\begin{subfigure}[t]{0.48\textwidth}
+			\begin{overpic}[width=\textwidth]{figs/FFFF1.png}
+				\put(-5,103){\normalsize (a)}
+			\end{overpic}
+			\label{fig:FFFF1}
+		\end{subfigure}\hfill
+		\begin{subfigure}[t]{0.48\textwidth}
+			\begin{overpic}[width=\textwidth]{figs/FFFF2.png}
+				\put(-5,103){\normalsize (b)}
+			\end{overpic}
+			\label{fig:FFFF2}
 		\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.49\textwidth}  
-		\centering 
-		\includegraphics[width=\textwidth]{figs/FFFF2.png}
-		\caption[]%
-		{{\small }}    
-		\label{fig:FFF2}
+
+		\vspace{0.4em}
+
+		% Row 2
+		\begin{subfigure}[t]{0.48\textwidth}
+			\begin{overpic}[width=\textwidth]{figs/FFFF3.png}
+				\put(-5,103){\normalsize (c)}
+			\end{overpic}
+			\label{fig:FFFF3}
+		\end{subfigure}\hfill
+		\begin{subfigure}[t]{0.48\textwidth}
+			\begin{overpic}[width=\textwidth]{figs/FFFF4.png}
+				\put(-5,103){\normalsize (d)}
+			\end{overpic}
+			\label{fig:FFFF4}
 		\end{subfigure}
-	\vfill
-	\begin{subfigure}[b]{0.49\textwidth}   
-		\centering 
-		\includegraphics[width=\textwidth]{figs/FFFF3.png}
-		\caption[]%
-		{{\small }}    
-		\label{fig:FFF3}
+
+		\vspace{0.4em}
+
+		% Row 3
+		\begin{subfigure}[t]{0.48\textwidth}
+			\begin{overpic}[width=\textwidth]{figs/FFFF5.png}
+				\put(-5,103){\normalsize (e)}
+			\end{overpic}
+			\label{fig:FFFF5}
+		\end{subfigure}\hfill
+		\begin{subfigure}[t]{0.48\textwidth}
+			\begin{overpic}[width=\textwidth]{figs/FFFF6.png}
+				\put(-5,103){\normalsize (f)}
+			\end{overpic}
+			\label{fig:FFFF6}
 		\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.49\textwidth}   
-		\centering 
-		\includegraphics[width=\textwidth]{figs/FFFF4.png}
-		\caption[]%
-		{{\small }}    
-		\label{fig:FFF4}
-	\end{subfigure}
-	\vskip\baselineskip
-	\begin{subfigure}[b]{0.49\textwidth}   
-		\centering 
-		\includegraphics[width=\textwidth]{figs/FFFF5.png}
-		\caption[]%
-		{{\small}}    
-		\label{fig:FFF5}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.49\textwidth}   
-		\centering 
-		\includegraphics[width=\textwidth]{figs/FFFF6.png}
-		\caption[]%
-		{{\small }}    
-		\label{fig:FFF6}
-	\end{subfigure}
-	\caption[]  
-	{\small The first six nonzero mode shapes of a square orthotropic plate with FFFF boundary conditions: (a) the first mode; (b) the second mode; (c) the third mode; (d) the fourth mode; (e) the fifth mode; (f) the sixth mode.}
+
+		\caption{\small%
+			The first six nonzero mode shapes of a square orthotropic plate with FFFF boundary conditions: 
+			(a) the first mode; (b) the second mode; (c) the third mode; 
+			(d) the fourth mode; (e) the fifth mode; (f) the sixth mode.}	
+		\end{minipage}
+	}
 	\label{fig:FFFF}
@@
 \end{table}
-\subsection{Rotational spring-supported edges}
+\subsection{Rotational spring-supported edges}\label{sec:Rotational spring-supported}
 In this subsection, rectangular orthotropic plates with rotational spring-supported edges with no translations ($k^v_\xi = k^v_\eta = \infty$) are examined.  
-The rotational stiffness coefficients are defined as: 
+The dimensionless rotational stiffness coefficients are defined as: 
 % 
@@
 Thus, the exact frequency can be estimated as $\Omega = (\Omega_x + \Omega_y)/2$.  
-As shown in \Cref{tab:rot1}, the maximum difference between \(\Omega\) and the solutions reported in \Citealp{zhang2019new} is less than $1.3\%$.
+As shown in \Cref{tab:rot1}, the maximum difference between \(\Omega\) and the analytical solutions of the finite integral transform method reported in \Citealp{zhang2019new} is less than $1.3\%$.
 \Cref{fig:iso} illustrates the variation in mode shapes corresponding to the fundamental natural frequency as the rotational stiffness $r_{\xi} = r_{\eta}$ increases from zero to $\infty$, transitioning the boundary conditions from SSSS to CCCC.
 
-\begin{figure}
+\begin{figure}[p] % or [H]
 	\centering
-	\begin{subfigure}[b]{0.49\textwidth}
+	\resizebox{0.85\textwidth}{!}{%
+		\begin{minipage}{\textwidth}
 		\centering
-		\includegraphics[width=\textwidth]{figs/iso0.png}
-		\caption[]%
-		{{\small }}    
+
+		% Row 1
+		\begin{subfigure}[t]{0.48\textwidth}
+			\begin{overpic}[width=\textwidth]{figs/iso0.png}
+				\put(-5,103){\normalsize (a)}
+			\end{overpic}
 			\label{fig:iso0}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.49\textwidth}  
-		\centering 
-		\includegraphics[width=\textwidth]{figs/iso1.png}
-		\caption[]%
-		{{\small }}    
+		\end{subfigure}\hfill
+		\begin{subfigure}[t]{0.48\textwidth}
+			\begin{overpic}[width=\textwidth]{figs/iso1.png}
+				\put(-5,103){\normalsize (b)}
+			\end{overpic}
 			\label{fig:iso1}
 		\end{subfigure}
-	\vfill
-	\begin{subfigure}[b]{0.49\textwidth}   
-		\centering 
-		\includegraphics[width=\textwidth]{figs/iso10.png}
-		\caption[]%
-		{{\small }}    
+
+		\vspace{0.4em}
+
+		% Row 2
+		\begin{subfigure}[t]{0.48\textwidth}
+			\begin{overpic}[width=\textwidth]{figs/iso10.png}
+				\put(-5,103){\normalsize (c)}
+			\end{overpic}
 			\label{fig:iso10}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.49\textwidth}   
-		\centering 
-		\includegraphics[width=\textwidth]{figs/iso20.png}
-		\caption[]%
-		{{\small }}    
+		\end{subfigure}\hfill
+		\begin{subfigure}[t]{0.48\textwidth}
+			\begin{overpic}[width=\textwidth]{figs/iso20.png}
+				\put(-5,103){\normalsize (d)}
+			\end{overpic}
 			\label{fig:iso20}
 		\end{subfigure}
-	\vskip\baselineskip
-	\begin{subfigure}[b]{0.49\textwidth}   
-		\centering 
-		\includegraphics[width=\textwidth]{figs/iso100.png}
-		\caption[]%
-		{{\small}}    
+
+		\vspace{0.4em}
+
+		% Row 3
+		\begin{subfigure}[t]{0.48\textwidth}
+			\begin{overpic}[width=\textwidth]{figs/iso100.png}
+				\put(-5,103){\normalsize (e)}
+			\end{overpic}
 			\label{fig:iso100}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.49\textwidth}   
-		\centering 
-		\includegraphics[width=\textwidth]{figs/isoinf.png}
-		\caption[]%
-		{{\small }}    
+		\end{subfigure}\hfill
+		\begin{subfigure}[t]{0.48\textwidth}
+			\begin{overpic}[width=\textwidth]{figs/isoinf.png}
+				\put(-5,103){\normalsize (f)}
+			\end{overpic}
 			\label{fig:isoinf}
 		\end{subfigure}
-	\caption[]  
-	{\small The first mode shape of a square isotropic plate with all four edges rotationally restrained: (a) $r_{\xi} = r_{\eta} = 0$; (b) $r_{\xi} = r_{\eta} = 1$; (c) $r_{\xi} = r_{\eta} = 10$; (d) $r_{\xi} = r_{\eta} = 20$; (e) $r_{\xi} = r_{\eta} = 100$; (f) $r_{\xi} = r_{\eta} = \infty$.}
+
+		\caption{\normalsize
+			The first vibration mode shapes of a square isotropic plate with all four edges rotationally restrained, 
+			shown for different dimensionless rotational stiffness values \(r_{\xi} = r_{\eta}\). 
+			(a) \(r_{\xi} = r_{\eta} = 0\) (simply supported);  
+			(b) \(r_{\xi} = r_{\eta} = 1\) (light rotational restraint);  
+			(c) \(r_{\xi} = r_{\eta} = 10\) (moderate restraint);  
+			(d) \(r_{\xi} = r_{\eta} = 20\);  
+			(e) \(r_{\xi} = r_{\eta} = 100\) (nearly clamped);  
+			(f) \(r_{\xi} = r_{\eta} = \infty\) (perfectly clamped edges).
+		}
 		\label{fig:iso}
+		\end{minipage}
+	}
 \end{figure}
@@
 \begin{table}[!htbp]
-	\centering
-	\caption{The first six frequency parameters, $2a\Omega = 2a\sqrt[4]{\rho h \omega^2/D_{11}}$, of a square isotropic plate with all four edges rotationally restrained, where $k^r_{\xi=-1} = k^r_{\xi=1} = k^r_{\eta=-1} = k^r_{\eta=1}$.}
+
 \begin{tabular}{c l c c c c c c}
@@
 However, the mode shapes $\phi(\xi)$ and $\psi(\eta)$ remain real-valued, and the dynamic stiffness matrix $\mathbf{K} = \mathbf{R}\mathbf{Q}^{-1}$ is a real symmetric matrix.
-Thus, the frequency $\Omega$ can be obtained by solving $\mathbf{K}$ using the refined W-W algorithm provided in this study, which avoids solving the eigenvalue equations in both the real and complex domains.
+Thus, the frequency $\Omega$ can be obtained by solving $\mathbf{K}$ using this enhanced W-W algorithm provided in this study, which avoids solving the eigenvalue equations in both the real and complex domains.
 
@@
 \FloatBarrier
-\section{Conclusion}
-In this study, the dynamic stiffness matrix (DSM) based on the extended separation-of-variable (SOV) solution has been developed for the vibration analysis of an orthotropic rectangular plate with general homogeneous boundary conditions.
-
-Instead of solving highly nonlinear eigenvalue equations involved in the SOV methods, the extended SOV solution is adopted to construct the dynamic stiffness matrices.
-Several novel techniques have proposed to solve the eigenvalue problem and mode shape computation.
-The challenge of determining the fully clamped frequencies using the Wittrick–Williams (W–W) algorithm is resolved by computing the frequencies under specific boundary conditions, such as simply supported, guided, or a combination of the two, whose closed-form expression can be easily derived using the SOV method.
+\section{Conclusion}\label{sec:coclusion}
+In this study, a separation-of-variables dynamic stiffness matrix (SOV-DSM) method has been developed for the vibration analysis of orthotropic rectangular plates with general homogeneous boundary conditions.
+The boundary conditions of the SOV-type plate are extended to homogeneous elastically restrained boundaries beyond the classical cases, resulting in two more complex eigenvalue equations. 
+Existing SOV methods face the challenge of solving six unknown variables ($\alpha_1$, $\beta_1$, $\Omega_x$, $\alpha_2$, $\beta_2$, $\Omega_y$) through six eigenvalue equations, which leads to high computational cost and convergence difficulties.
+To address this, dynamic stiffness matrices are formulated based on the SOV-type plate, and an enhanced Wittrick–Williams (W–W) algorithm is introduced to solve these matrices regardless of the complexity of the highly nonlinear eigenvalue equations derived from them.
+This enhanced W–W algorithm resolves the well-known $J_0$ problem by providing an explicit closed-form expression for the $J_0$ term, derived from the characteristics of SOV-type plates. 
+Furthermore, a novel yet simple numerical technique is proposed for mode shape calculation, making it applicable to all boundary conditions.
 
 Classical boundary conditions, such as guided, simply supported, clamped, and free edges, can be realized by setting the translational springs ($k^v$) and rotational springs ($k^r$) along the plate edges to either zero or infinity, as appropriate.
-Numerical experiments validate the accuracy of this approach for these boundary conditions.  
-The results shows that the SOV solution can also be extended to handle elastically-restrained boundary conditions.
-Despite certain approximations inherent in some elastically-restrained cases, the maximum percentage error across all numerical experiments remains within $1.25\%$. 
+Numerical experiments validate the high accuracy of this approach for these boundary conditions.  
+The results shows that the SOV solution can also be extended to handle elastically restrained boundary conditions.
+Despite certain approximations inherent in few elastically restrained cases, the maximum percentage error across all numerical experiments remains within $1.25\%$. 
 This may occur because the SOV solution used is derived from the weak-form governing equation, which is based on Rayleigh's principle.
 
-The SOV solution $\phi(\xi) \psi(\eta)$ consists of only one single term for each mode order, unlike the sufficiently truncated Fourier series used in the DSM for each mode, each eigenvalue solution can be explicitly expressed.
-Therefore, dynamic stiffness matrices based on the SOV solution have the minimum matrix dimension compared to existing DSM methods. 
-This suggests the potential for constructing lower-dimensional dynamic stiffness matrices for assembled plate structures than those produced by existing DSM approaches.
-
-Finally, the developments reported in this paper should find good application with researchers and practitioners interested in the vibration of generally-supported rectangular orthotropic plates.
+As a closed-form dynamic stiffness formulation, this approach has the potential to construct more concise and lower-dimensional dynamic stiffness matrices for orthotropic rectangular plate assemblies compared to existing DSM approaches.
 
@@
 The integral parameters $J_1$, $J_2$, $J_3$, and $J_4$ can be obtained by replacing $B_1$ to $B_4$ by $ A_1 $ to $A_4$, respectively, and $\alpha_2$ and $\beta_2$ by $\alpha_1$ and $\beta_1$, respectively.
-
+\section{$J(\bar{p}_1)$ count for S-G boundary conditions}\label{sec:appendB}
+If the S-G boundary conditions are selected as the specific boundary conditions to solve the $J(\bar{p}_1, \omega^*)$, then, from the eigenvalue equations in the $x$- and $y$-directions,
+%
+\begin{subequations}\label{eq:SGx} 
+	\begin{align}
+		&\cos 2\alpha_1 = 0,\\
+		&\cos 2\alpha_2 = 0,
+	\end{align}
+\end{subequations}
+%
+the closed-form solution of the $n_x$-th S-G boundary conditions $\Omega_{x,n_x}$ for the given $n_y$-order $\psi_{n_y}(\eta)$ , can be expressed as
+%
+\begin{equation}\label{eq:J_simpx2}
+	b \Omega^4_{x,n_x} =
+	\begin{aligned}
+		&\left[\frac{1}{\chi^2}\left(\frac{n_x\pi}{2}-\frac{\pi}{4}\right)^2 - \frac{D_{12}S_2}{D_{11}S_1} + 2 \frac{D_{66}S_3}{D_{11}S_1}\right]^2 \\
+		&\qquad- \left(\frac{D_{12}S_2}{D_{11}S_1} - 2 \frac{D_{66}S_3}{D_{11}S_1}\right)^2
+		+ \frac{D_{22}S_4}{D_{11}S_1},
+	\end{aligned}
+\end{equation}
+%
+and the closed-form solution of the $n_y$-th S-G boundary conditions frequency $\Omega_{y,n_y}$ for the given $n_x$-order $\phi_{n_x}(\xi)$ can be obtained as:
+%
+\begin{equation}\label{eq:J_simpy2}
+	a\Omega^4_{y,n_y}= 
+	\begin{aligned}
+		&\frac{D_{22}}{D_{11}}\Biggl\{\left[\chi^2\left(\frac{n_y\pi}{2}-\frac{\pi}{4}\right)^2 - \frac{D_{12}T_2}{D_{22}T_1} + 2 \frac{D_{66}T_3}{D_{22}T_1}\right]^2 \\ 
+		&\qquad - \left(\frac{D_{12}T_2}{D_{22}T_1} - 2 \frac{D_{66}T_3}{D_{22}T_1}\right)^2
+		+ \frac{D_{11}T_4}{D_{22}T_1}\Biggr\}.
+	\end{aligned}
+\end{equation}
 \end{appendices}
 \FloatBarrier
-\bibliographystyle{elsarticle-harv}
+%\bibliographystyle{elsarticle-harv}
+\bibliographystyle{elsarticle-num}
 \bibliography{bibliography}

### 2025-07-25 Paper7.tex
Proof-read before resub

@@
 \begin{abstract}
-	A separation-of-variable dynamic stiffness matrix (SOV-DSM) method is proposed for the free vibration analysis of an orthotropic rectangular thin plate with general homogeneous boundary conditions.  
+	A separation-of-variable dynamic stiffness matrix method (SOV-DSM) is proposed for the free vibration analysis of an orthotropic rectangular thin plate with general homogeneous boundary conditions.  
 	Firstly, the exact SOV solution satisfying Rayleigh’s principle is extended to handle arbitrary boundary conditions and then applied to develop closed-form dynamic stiffness formulations.
@@
 \section{Introduction}
-Rectangular plates play an important role in various engineering fields, including civil, mechanical, and aerospace engineering \citep{biancolini2005approximate}. 
+Rectangular plates play an important role in many engineering fields, including civil, mechanical, and aerospace engineering \citep{biancolini2005approximate}. 
 The free vibration of plates has been a fundamental research problem for over two centuries. 
@@
 The DSM can be considered as an analytical FEM since the mode functions of the plate are expressed by analytical solutions, where Levy-type solution \cite{ghorbel2015dynamic} or components of Fourier series \cite{williams1995wave,banerjee2015dynamic,liu2016free,liu2024wavenumber,zhou2024wavenumber} are applied.
-To avoid solving the cumbersome transcendental frequency equation directly, the Wittrick-Williams (W-W) algorithm \cite{wittrick1971general} is applied to the eigenvalue problem.
+To avoid solving the cumbersome transcendental frequency equation directly, the Wittrick-Williams (W-W) algorithm \cite{wittrick1971general} can be applied to the eigenvalue problem.
 The W-W algorithm determines the lower and upper bounds of natural frequencies to arbitrary precision rather than solving the frequency equation directly. 
@@
 This enhanced approach resolves the challenge of determining fully clamped frequencies, also called the $J_0$ count problem, a well-known limitation in the application of the W-W algorithm. 
-Two types of explicit and closed-form expressions for the $J_0$ term, based on specific supports such as simply supported, guided, or their combinations, are provided to improve the computational efficiency of the eigenvalue problem.
+Two types of explicit and closed-form expressions for the $J_0$ term, based on specific support types such as simply supported, guided, or their combinations, are provided to improve the computational efficiency of the eigenvalue problem.
 In addition, a novel numerical technique is proposed to compute the mode shape coefficients.
@@
 \Cref{sec:Mathematical model} presents the mathematical model of the extended separation-of-variable method.  
-Then, the SOV-DSM formulations in the $x$- and $y$-directions will be proposed separately in \Cref{sec:DSMx} and \Cref{sec:DSMy}, according to the boundary conditions of the plate.
+Then, the SOV-DSM formulations in the $x$- and $y$-directions are developed separately in \Cref{sec:DSMx} and \Cref{sec:DSMy}, according to the boundary conditions of the plate.
 
@@
 %
-Thus, the governing differential equation in the $ x $-direction can be obtained from the integration part in \Cref{eq:Rayleighx2}:
+Thus, the governing differential equation in the $ x $-direction can be obtained from the integration part of \Cref{eq:Rayleighx2} as:
 %
@@
 %
-and from the $\delta \frac{\id \phi}{\id \xi}$ part, the bending moment equilibrium:
+and from the $\delta \frac{\id \phi}{\id \xi}$ part, the bending moment equilibrium is:
 %
@@
 \end{subequations}
-%
+
 Substituting \Cref{eq:phi_solution1} into \Cref{eq:boundaryx}, and denoting 
@@
 \end{equation}
-%
+
 Note that the classic boundary conditions can be obtained by selecting extremely large or small spring stiffness constants.
@@
 where $\Omega_y = \sqrt[4]{{\omega_y^2 \rho h}/D_{11}}$.
-By substituting $\psi(\eta) = B e^{\lambda \eta}$ into \Cref{eq:ODEy}, yields:
+By substituting $\psi(\eta) = B e^{\lambda \eta}$ into \Cref{eq:ODEy}, we get:
 %
@@
 \end{subequations}
-%
-Similarly, from the shear force and bending moment equilibrium, and by denoting 
+
+Similarly to the $x$-direction, from the shear force and bending moment equilibrium, and by denoting 
 $k^{v*}_{\eta} \equiv \frac{2b^3 k^v_{\eta}}{D_{22}} $, 
@@
 \end{equation}
-%
-With the help of \Cref{eq:phi_solution2}, the vertical displacement and rotation corresponding to the mode shape $\psi$ along the $y$-direction at the edges $\eta = -1$ and $\eta = 1$ can be expressed as:
+
+With the help of \Cref{eq:phi_solution2}, the vertical displacement and rotation corresponding to the mode shape $\psi$ along the $y$-direction at the edges $\eta = -1$ and $\eta = 1$ can then be expressed as:
 %
@@
 where the dynamic stiffness matrix, denoted as $\mathbf{K}_y = \mathbf{R}_y \mathbf{Q}_y^{-1}$, can be obtained from \Cref{eq:DSM_eqy}.
-\section*{Remarks}
-\addcontentsline{toc}{subsection}{Remarks}
+
+\subsection{Remarks}
+% \addcontentsline{toc}{subsection}{Remarks}
 \begin{enumerate}[label=(\roman*)]
@@
 
-\subsection{Application procedure}\label{sec:Application procedure}
+\subsection{Numerical procedure}\label{sec:Application procedure}
 The procedure of the proposed method is as follows:   
@@
 
-\section*{Remarks}
-\addcontentsline{toc}{subsection}{Remarks}
+\subsection{Remarks}
+% \addcontentsline{toc}{subsection}{Remarks}
 \begin{enumerate}[label=(\roman*)]
@@
 \section{Conclusion}\label{sec:coclusion}
-In this study, a separation-of-variables dynamic stiffness matrix (SOV-DSM) method has been developed for the vibration analysis of orthotropic rectangular plates with general homogeneous boundary conditions.
+In this study, a separation-of-variables dynamic stiffness matrix method (SOV-DSM) has been developed for the vibration analysis of orthotropic rectangular plates with general homogeneous boundary conditions.
 The boundary conditions of the SOV-type plate are extended to homogeneous elastically restrained boundaries beyond the classical cases, resulting in two more complex eigenvalue equations. 
